### 2016-09-21 HRI/Parts/Antecedents.tex
Base articles, they should be modify before any submission

An experiment was designed to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness, which correspond to four basic emotions suggested by Ekman~\cite{Ekman2001}. These features were selected after the study on emotion projection in robotics, humans and previous case studies. The robotic platform used in the experiment is holonomic, which are characterized by the possibility to move in any direction without the necessity to have a specific orientation, i.e., they are free to move taking any desired orientation. The experiment was performed at Politecnico di Milano, campus Leonardo during the months of June and July of 2015.  A total of 49 volunteers were involved: 12 female and 37 male. The average age of the participants was 25.28 with standard deviation of 2.8, with a minimum age of 20 and maximum of 32.

For each table were calculated the mean, standard deviation, and median. It was not possible to use  ANOVA test over the data because the assumption of normality is not achieved in the collected data. This was check using the Shapiro-Wilk Test.
Additionally, a contingency table for each emotion was generated in each treatment as it is depicted in  Table~\ref{table:table_contingency},  where the intensity for the other emotions is calculated as the mean of them, including the option of ''other''. For all tables, including the contingency, were calculated the Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$), which is a reliability coefficient to measure the agreement among different participants. Unlike other coefficients (Kappa), $\alpha$ is a generalization of several known reliability indices, and it applies to:

\begin{table}
\caption{Contingency table formula used for each emotion and treatment. Where $k$ is the kth treatment, $j$ is jth emotion for the kth treatment, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
\label{table:table_contingency}
\small
\begin{tabular}{|l|l|l|}
\hline
Participant & Desire Emotion & Other Emotions \\
\hline
$1$ & $Value_{k,j}^{1}$  & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{1})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
$2$ & $Value_{k,j}^{2}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
... & ... & ...\\
\hline
$n$ & $Value_{k,j}^{n}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
\multicolumn{3}{c}{}
\end{tabular}
\end{table}

\begin{itemize}

	\item Any number of observers.

	\item Any number of categories.

	\item Any type of data.

	\item Incomplete or missing data.

	\item Large and small sample sizes.
\end{itemize}

This calculation was done using the R package \textit{irr}. To improve the table interpretation, it was decided to just record the emotions' alpha values that had a mean greater than zero. Therefore, tables with a top ten ranking have been set up. The raking considered: (i) the mean of the respective emotions, (ii) the alpha agreement for the respective emotion, and (iii) the alpha agreement for the treatment. The decision to give more importance to emotion's alpha rather than intensity average was taken basing on the consideration that most participants agreed on their observation. From the results was possible to notice:

\begin{itemize}

	\item Fear was the only emotion that had six over ten movements obtaining both general and specific alpha agreement over 0.41, which is the lower bound for moderate agreement~\cite{Viera2005}. It seems that people perceive as fear when the robot is looking at them and moving far from them fast.

	\item It seems that people attribute sadness to slow velocities with slow angular velocity and small oscillation angle. Regarding the other two features, there is not a concrete pattern that could lead to make a generalization.

	\item Happiness is attributed to different values of the independent variables. It seems that happiness is mainly attributed to fast angular velocities and big oscillations angles. However specific agreement among the other features is not present.

	\item Anger seems to be attribute to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them.

\end{itemize}

### 2016-09-21 HRI/Parts/CaseStudy.tex
Base articles, they should be modify before any submission

The case study was done at Researcher's Night 2014 with two main objectives (i) cross-validate the findings obtained from the experiment, and (ii) use the Emotional Enrichment System to verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.

\subsection{Design and Setup}

This case study uses the results obtained in the experiment and was designed to have two parts (i) emotion expression through changes in linear velocity, angular velocity, oscillation angle, orientation and direction. 
%Figure~\ref{fig:example_movements} presents an example of these variables. 
(ii) Presentation of a small scene to verify whether the participants would prefer scenes when the robot shows emotions or not. the Emotional Enrichment System was used in both cases (with and without emotions). Two web-cams and eight Alvar tags were added to use Kalman filter to improve robots localization in the stage. The detection of the AR tags is done through the use of the ROS package ar\_track\_alvar~\cite{artag2015}. The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/FourthCase.png} 
	\caption{Environment setup for the case study.}
	\label{fig:setup_fourth}
\end{figure}

\subsubsection{Emotion Description}

The parameters selected for each of the four emotions (\textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) are shown in Table~\ref{table:selected_fourth}. The main considerations to select the two implementations for each emotion were: (i) the linear velocity should be greater than $0$. In other words the robot should show some linear displacement. And (ii) it should be in the top 10 list of the emotion obtained in the experiment.

\begin{table}
\centering
\small
\caption{Parameters' values selected from the experiment.}
		\label{table:selected_fourth}
		\begin{tabular}{|c|c|c|c|c|c|c|}
			\hline
\rotatebox{90}{\textbf{Emotion } }&
\rotatebox{90}{\textbf{Direction  ($rad$)}}&
\rotatebox{90}{\textbf{Orientation ($rad$)} }&
\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
\rotatebox{90}{\textbf{Angular Velocity ($rad/s$) }}&
\rotatebox{90}{\textbf{Angle ($rad$)}}&
\rotatebox{90}{\textbf{Treatment ID}}\\	
			\hline
			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&29\\
			\cline{2-7}
			&$0$&$0$&$900$&$3$&$0.174$&38\\
			\hline
			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&144\\
			\cline{2-7}
			&$0$&$0$&$900$&$1$&$0.087$&31\\
			\hline
			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&113\\
			\cline{2-7}
			&$\pi$&$\pi$&$500$&$2$&$0.087$&102\\
			\hline
			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&130\\
			\cline{2-7}
			&$0$&$\pi$&$200$&$1$&$0.349$&52\\
			\hline
			\end{tabular}
\end{table}

\subsubsection{Scene}
%TODO change this part of the text and give some information about this, and  motivate its use, which bassically is to verify the emotional enrichment system
As it was already mentioned, actors should adapt to different circumstances during the performance. Following this approach, the stage was discretized in 9x9 matrix as is shown in Figure~\ref{fig:stage_division}. Thus, the movements of the robot are given in terms of the matrix positions. This allows the adaptation to different stage dimensions because the robot's final position is calculated by the Emotional Enrichment System during execution taken under consideration the stage dimensions. For instance, during the scene's preparation in the laboratory the stage was 3 meters per 3 meters, but in the final presentation the stage was 2.5 meters per 2.5 meters.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseScene.png} 
	\caption{Stage discretization  used for the small scene. The blue squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
	\label{fig:stage_division}
\end{figure} 
%TODO Change this paragraph and motivate the reason this is important and instead of puting the figures, write the references to those figures
The scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (Figure~\ref{fig:StageDirections}), close to the right wing. Then, the robot moves to upstage right center and rotates by $\pi/2$ left (Figure~\ref{fig:BodyPosition}). Next the robot moves to the right center to then go to the center. When it arrives there, it turns full back and move backwards to downstage center with a full front orientation. There, it turns full back to move to center. Finally the robot turns to profile right and it does a step back; then it goes to the upstage center and then upstage right. The sequence of movements programmed to the robot are depicted in Figure~\ref{fig:movement}.
\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{./Images/fourthCaseSceneD.png} 
	\caption{Sequence of movements done by the robot. The red arrows show the trajectory done by the robot, while the numbers show the order among the movements. a) The first ten movements b) The last five movements }
	\label{fig:movement}
\end{figure*}

The relation between emotion and movement is as follow: movements one, two, three, four and five are expressed without any emotion. Movements six, seven, eight, nine and ten show fear. Movement eleven depicts happiness, and the remaining movements depict sadness. The two scenes are executed by the Emotional Enrichment System using the same ''script'' and the emotion selection is done manually via graphical interface (Figure~\ref{fig:graphical_interface}).The ''script'' were written in JSON using the language described in the Section~\ref{}.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/InterfaceExperiment.png} 
	\caption{Graphical interface used to communicate with the Emotional Enrichment System. a) It is the interface used to send the actions sequence. b) It is the interface used to send a emotion and its intensity.}
	\label{fig:graphical_interface}
\end{figure}

\subsection{Study}

This case study was done during Researchers' Night, 2015. During a period of two days, people were asked to participate to this study. Each subject was exposed to two rounds, in each one the robot was performing a different emotion. And  they were also exposed twice to a small scene, one with emotion and other without emotions. The emotions showed in each trial and the order of the scenes (with or without emotion) were generated randomly beforehand. The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender. The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76.

### 2016-09-21 HRI/Parts/Conclusions.tex
Base articles, they should be modify before any submission

The case study presented in this chapter was done to cross validate the findings in the experiment. For each one of the four emotions studied in the experiment were selected two set of parameters. The results show that both implementations of happiness were confused with anger and excitement, while one implementation of anger was just confused with excitement. Both implementations of sadness were confused with tenderness and fear. Both implementations of fear had a recognition rate over 50\%. Additionally to the cross validation, it was done a small scene to check if people have preference to scenes where emotional movements are presented or not. The results show that people prefer scenes with emotional movements.

### 2016-09-21 HRI/Parts/Results.tex
Base articles, they should be modify before any submission

Table~\ref{table:result_fourth} summarizes the results obtained during the case study. 
\begin{table*}
\centering
\small
\caption{Summary of the answers obtained in the case study.}
		\label{table:result_fourth}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline	
			&\multicolumn{5}{|c|}{\textbf{Features}}&\multicolumn{7}{c|}{\textbf{Emotions}}&\\
			\cline{2-13}
\rotatebox{90}{\textbf{Presented/Reported } }&
\rotatebox{90}{\textbf{Direction  ($rad$)}}&
\rotatebox{90}{\textbf{Orientation ($rad$)} }&
\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
\rotatebox{90}{\textbf{Angular Velocity ($rad/s$) }}&
\rotatebox{90}{\textbf{Angle ($rad$)}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{ \textbf{Anger}} &
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Excitement}}&
\rotatebox{90}{\textbf{Tenderness}}&
\rotatebox{90}{\textbf{Other}}&
\rotatebox{90}{\textbf{Total}}\\	
			\hline
			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&8&16&7&4&16&4&7&62\\
			\cline{2-14}
			&$0$&$0$&$900$&$3$&$0.174$&11&11&6&2&19&3&1&53\\
			\hline
			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&7&5&6&2&21&7&1&49\\
			\cline{2-14}
			&$0$&$0$&$900$&$1$&$0.087$&14&29&13&2&13&3&2&76\\
			\hline
			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&6&2&28&1&9&6&0&52\\
			\cline{2-14}
			&$\pi$&$\pi$&$500$&$2$&$0.087$&7&3&37&2&20&4&1&74\\
			\hline
			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&3&5&17&14&5&16&5&65\\
			\cline{2-14}
			&$0$&$\pi$&$200$&$1$&$0.349$&5&5&15&28&6&15&7&81\\
			\hline
			\end{tabular}
\end{table*}

It could be observed that the two implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}. In a similar way, the first implementation of \textit{Anger} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects that were exposed to the first implementation of \textit{Anger}.
The second implementation of \textit{Anger} showed an improvement of perception from 10\% to 38\%. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
Both implementations of \textit{Fear} had a high level of recognition 54 \% and 50 \% and mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation. Finally, the two implementation of \textit{Sadness} was confused with \textit{Fear} and \textit{Tenderness}.

To verify these misinterpretations among the implemented emotions, a Fisher's exact test was applied for ten different combinations. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation. The results are shown in Table~\ref{table:result_compare_fourth}. As this analysis suggest, the two implementation of \textit{Anger} were perceived as two different emotions. Also shows that the two implementation of Happiness were perceived to be similar to the second implementation of Anger.

\begin{table}
\centering
\small
\caption{Pair comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
		\label{table:result_compare_fourth}
		\begin{tabular}{|c|c|c|}
			\hline	
\textbf{Pair Compared} & \textbf{p-value} & \textbf{p-value*}\\	
			\hline
			Happiness 1 vs Happiness 2 &0.38&1.0\\
			\hline
			Anger 1 vs Anger 2 & 7.3e-4&4.4e-3\\
			\hline
			Anger 2 vs Happiness 1 & 0.137&0.69\\
			\hline
			Anger 2 vs Happiness 2 & 0.157&0.69\\
			\hline
			Fear 1 vs Fear 2 & 0.74&1.0\\
			\hline
			Sadness 1 vs Sadness 2 & 0.665&1.0\\
			\hline
			Fear 1 vs Sadness 1& 8.35e-5&5.8e-4\\
			\hline
			Fear 1 vs Sadness 2 & 5e-7&4e-6\\
			\hline
			Fear 2 vs Sadness 1 & 2e-7&1.8e-6\\
			\hline
			Fear 2 vs Sadness 2 & 1e-7&1e-6\\
			\hline
			\end{tabular}
\end{table}

An analysis was done for each emotion, therefore it was created a contingency matrix such as was done in the previous studies. For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed. The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that second implementation of \textit{Anger}, both of \textit{Fear} and \textit{Sadness} have an impact in the perception of the emotion and they are considered as different implementation respect the rest of implementations. While both implementation of \textit{Happiness} and first of \textit{Anger} are considered as similar to the other implementation.

\clearpage
\begin{table*}
\centering
\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the case study.} 
\label{table:Precision2}
		\begin{tabular}{|p{3 cm}|p{2 cm}|c|c|c|}
		\hline
		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
		\hline
		Happiness 1 & 0.13 & 0.79 & 0.11 & 0.74\\
		\hline
		Happiness 2 & 0.21 & 0.81& 3.7 &0.054\\
		\hline
		Anger 1 & 0.1 & 0.8 & 3.8e-29 & 1\\
		\hline
		Anger 2 & 0.38 & 0.81 & 34.4 & 4.47e-9\\
		\hline
		Fear 1 & 0.54 & 0.8 & 36.2 & 1.8-e9\\
		\hline 
		Fear 2 & 0.5 & 0.78 & 35.8 & 5.3e-10\\
		\hline
		Sadness 1 & 0.22 & 0.85 & 27.4 & 1.63e-7\\
		\hline
		Sadness 2 & 0.35 & 0.85 & 72.9 & 2.2e-16\\		 
		\hline
			\end{tabular}
\end{table*}

 For each of the contingency tables the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, are reported in table~\ref{table:nir}. The results reveal that the only implementation with enough statistical evidence is the second implementation of \textit{Sadness}. 
Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape. Another important factor to highlight is the impact words enlisted in the questionnaire have on the perception rate. As it was expected in the experiment, \textit{Excitement} and \textit{Tenderness} were confused with other emotions with similar arousal level. In this precise case the emotions Anger and Happiness were confused with Excitement, and Sadness and Fear emotions were confused with Tenderness. Despite the bias generated by the two mental states enlisted in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

\begin{table*}
\centering
		\caption{Classification accuracy of the presented emotions by the single panels, computed as mentioned in the text, with corresponding 95\% confidence interval, no-information rate, and p-value that accuracy is greater than the NIR.}		
		\label{table:nir_fourth}
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
	& \multicolumn{5}{|c|}{\textbf{Features}} & & & &\\
\cline{2-6}				
\rotatebox{90}{\textbf{Presented Emotion}}&
\rotatebox{90}{\textbf{Direction  ($rad$)}}&
\rotatebox{90}{\textbf{Orientation ($rad$) }}&
\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
\rotatebox{90}{\textbf{Angular Velocity ($rad/s$)} }&
\rotatebox{90}{\textbf{Angle ($rad$)}}&
\rotatebox{90}{\textbf{Classification Accuracy}}&
\rotatebox{90}{\textbf{95\% CI}}&
\rotatebox{90}{\textbf{No-Information Rate}}&
\rotatebox{90}{\textbf{P-Value [Acc $>$ NIR]}}\\
				\hline
			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&0.79&(0.75,0.82)&0.89&1.0\\
			\cline{2-10}
			&$0$&$0$&$900$&$3$&$0.174$&0.81&(0.77,0.84)&0.88&1.0\\
			\hline
			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&0.8&(0.76,0.83)&0.88&1.0\\
			\cline{2-10}
			&$0$&$0$&$900$&$1$&$0.087$&0.89&(0.76,0.84)&0.83&0.95\\
			\hline
			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&0.79&(0.75,0.83)&0.88&1\\
			\cline{2-10}
			&$\pi$&$\pi$&$500$&$2$&$0.087$&0.78&(0.73,0.81)&0.83&0.99\\
			\hline
			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&0.85&(0.81,0.88)&0.84&0.47\\
			\cline{2-10}
			&$0$&$\pi$&$200$&$1$&$0.349$&0.85&(0.81,0.88)&0.81&0.035\\
			\hline
			\end{tabular}
\end{table*}

The results obtained form the small scene are presented in Table~\ref{table:preference_selection}. A chi-squared test with one degree of freedom with an alpha of $0.5$ was done to verify if there was enough statistical evidence to accept our hypotheses: (i) people prefer scenes with emotions and (ii) gender has no impact on the preference. The results of the tests show that there is enough statistical evidence to accept our first hypothesis and reject the second one, with p-values of $1.42E-6$ and $0.85$, respectively.

Additionally, the Emotional Enrichment System was used in the two parts of the case used. Although, there was not done any measure of any variable of the system, two things could be said about the system. First it enables the possibility to adapt same script to different stage measures with any impact in the script.  Second, that it does not block the execution of an action when an emotion is changed.
\begin{table}
\centering
		\caption{Answers obtained for the small scene.}		
		\label{table:preference_selection}
			\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Gender}&\textbf{With Emotion}&\textbf{Without Emotion}&\textbf{Total}\\
			\hline
			Male & 84 & 43 & 127\\
			\hline
			Female & 81 & 45 & 126\\
			\hline
			\end{tabular}
\end{table}

### 2016-09-21 HRI/Parts/System.tex
Base articles, they should be modify before any submission

\subsection{Robotic Platform}
\subsection{Emotion Enrichment System}

### 2016-09-21 JournalIJSR/IJSR.tex
Base articles, they should be modify before any submission

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%%!PS-Adobe-3.0 EPSF-3.0
%%%BoundingBox: 19 19 221 221
%%%CreationDate: Mon Sep 29 1997
%%%Creator: programmed by hand (JK)
%%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{slashbox}     
\usepackage{subfigure}
\usepackage{breakcites}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Identifying Values to Express Emotions with a Non-Anthropomorphic Platform%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Julian M. Angel-Fernandez         \and
        Andrea Bonarini %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Julian M. Angel-Fernandez \at
              Automation and Control Institute, Vienna University of Technology,\\ Vienna, Austria \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{jangelfe@tuwien.ac.at}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Andrea Bonarini \at
              Andrea Bonarini, Dipartimento di Elettronica, Informazione e Bioingegneria,Politecnico di Milano,\\
               Milan, Italy \\
              \email{andrea.bonarini@polimi.it}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that cannot have a humanoid shape, and still have to be accepted by humans. As a consequence other characteristics should be exploited to support robot acceptance. This paper presents an experiment made to understand the contribution of angular and linear velocity of a non-anthropomorphic robot, its body orientation, and movement direction on humans' perception of emotion. A top 10 table was created for each enlisted emotion using alpha agreement for the whole treatment and for the desired emotion. These results suggest values that could guide implementation of the studied emotions in this experiment in other social robots.
\keywords{Robot-Human Interaction \and Emotion Projection}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Related Work}
\input{./Parts/Emotion_Projection}
\section{The System}
\label{sec:system}
\input{./Parts/Platform}
\section{Experiment's Design}
\label{sec:experiment}
\input{./Parts/ExperimentDesign}
\section{Study}
\label{sec:study}
\input{./Parts/Study}
\section{Results}
\label{sec:result}
\input{./Parts/Results}
\section{Conclusions and Further Work}
\input{./Parts/Conclusion}
\bibliographystyle{spmpsci}
\bibliography{Bibliography,BibloNew,Biblography}

\end{document}
% end of file template.tex

### 2016-09-21 JournalIJSR/Parts/Conclusion.tex
Base articles, they should be modify before any submission

This paper presented an experiment made to understand the contribution of angular and linear velocity, body's orientation, and movement direction on humans' perception of emotion expression by a non-anthropomorphic platform. The emotions covered in this experiment correspond to four of those enlisted by Ekman~\cite{Ekman2001} as basic emotions: anger, happiness, fear and sadness. To study the contribution of the desired features, a non-anthropomorphic, holonomic platform was used. The experiment was conducted at Politecnico di Milano, and involved 49 participants, each exposed to 20 over 195 movements, selected randomly for each participant. The Krippendorff's alpha agreement~\cite{Krippendorff2007} was used to calculate the consensus about the interpretation of each treatment. Using  alpha and the average emotion intensity attributed to each movement a top 10 movement table for each of the emotions was created.

The values obtained in this experiment could be used to express emotions in non-anthropomorphic platforms. It is still needed to cross validate the values and to determine what values from the top ten could be used more "accurately" to express the desired emotion. It is important to mention that is not expected to have a 100\% of correct emotion recognition by the participants. As it has been observed in previous work in humans and robots, it is not possible to get a 100\% of correct recognition. This cross validation would help to reduce the number of feature combinations to the ones with higher possibility of identification. Moreover, additional experiments should be done to obtain analogous values for changes in shape and in different platform's size.

### 2016-09-21 JournalIJSR/Parts/Emotion_Projection.tex
Base articles, they should be modify before any submission

Although it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010}, human studies provide guidelines about possible features and values that could be used to generate emotional motion.

\subsection{Human Studies}

Emotion plays an important role in human-human interaction, and can be expressed through diverse channels such as body gestures and poses, body movements, face expressions. Given the complex structure of human face, where more than 43 muscles act, face configurations are considered as a primary channel to express emotion. As a consequence, many works have focused on facial expression, mainly, but not only, influenced by the work done by Ekman~\cite{Ekman2004}. Fortunately, the role that body plays in emotions projection has been recognized and has started to be studied~\cite{Gelder2008,Wallboot1998}. Nevertheless, the amount of works related to body expression of emotions is still small compared to studies on facial expression.

Analysing some of the few works that have studied human body expressiveness, it is possible to recognize two different methodologies to create the data base of movements to be assessed during the experiments. Applying a first methodology, human actors (either professionals, or amateurs) are asked to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}. Each trial is recorded and later shown to each subject, who evaluates all the sequences. The second methodology uses virtual agents~\cite{Roether2009,Venture2014} to generate the very same set up for the experiments; the agent's movements are generated from the data recorded from human actors.

The work done by Wallboot~\cite{Wallboot1998} has been used as a referenced by others.
His work addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects. His results reaffirm that movement and body postures are indicative of intensity for some emotions, while, for other emotions, these two characteristics seem to be enough to identify them.

Complementary studies using virtual agents have been performed by  Kluwer and collaborators~\cite{Kluwer2004}, who studied the contribution of postures and angle view in the interpretation of emotions. They generated 176 static positions for happiness, anger, disgust, fear, sadness and surprise. Each image was later rendered from three different angles (front, left, and above and behind left shoulder) producing a total of 528 images. All the participants were exposed to all 528 images and were asked to label the image with the emotions that best represent it. Their results show that five out of six emotions were quite weel recognized independently from the angle of view. However, disgust was in some postures confused with fear.

The main drawback of all these projects is the use of video recorded sequences, which misses the impact related to a complete physical experience.

\subsection{Robotic Studies}
%%%%%%%%%%%%%%%%%%%%%%

The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused also on faces. One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions. The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}) plus \textit{interest}. The face's physical design was done so to invite humans to treat it as if it was a social creature. The interaction studies done with this platform were conceived to consider a person as a caregiver and the robot as the receiver; it seems that the system was capable to engage people in a long term interaction. To achieve this goal, the system had six sub-systems: vision, hearing, motivational, behavioral, speaking, and emotion selection system. Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants. In this experiment, each participant was asked to look at seven videos, one for each implemented emotion. After a video was projected, each participant selected the emotion from a list containing  the seven implemented emotions, only. The results showed a percentage of recognition over 57\%.

%%%%%%%%%%%%%%%%%%%%%%%%
Saerbeck and Christoph~\cite{Saerbeck2010} analyzed the relationship between robots' motion characteristics and perceived affect. They first did a literature review to select characteristics that could be used to show affection. From their literature review, they decided to use acceleration and curvature on robot's trajectory. 
Using these two characteristics, they did an experiment with eighteen participants. For the experiment they used two different platforms (iCat and Roomba) to verify if the embodiment had any impact on affection determination. For the Roomba researchers decided to use a circular trajectory in the room. While for the iCat two objects were place in front of it. It starts in a central position to then move to the left  right and back to center. 
To reduce variables' possibilities, they picked three definite values for each variable. Each participant was exposed to both embodiments and all possible variable combinations. To assess participants' perception, they used PANAS~\cite{WatsonClarkTellegen88} and Self-Assessment Manikin (SAM)~\cite{Lang2008}. Their results show that there was no significant difference between the two embodiments used and that participants were able to assign different emotions to the movement patterns shown to them. 
More importantly, they found out that acceleration is correlated with the perceived arousal but not with valence.

%%%%%%%%%%%%%%%%
As part of their work on detecting emotions in humans, with a case of use in robot games, Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from movement. The behavior parameters were selected based on the work done by Camurri et al.~\cite{pop00002}. To focus participants' attention on movement, they used the e-puck platform~\cite{Mondada09thee-puck}. 
Their experiment is not fully described, but authors highlighted that the subjects were not given any list with possible emotions, rather they asked participants how they think that the robot was feeling. The results showed a very high recognition rate for the implementations of sadness, nervousness, and fear. The implementations for anger and happiness were confused.

%%%%%%%%%%%%%%%%
Barakova and collaborators used a closet robot~\cite{Barakova2013}, which does not show any anthropomorphic resemblance, to study new possibilities in social interaction. This closet robot can perceive human presence and react to show behaviours that could be perceived as emotions or mental states. The closet robot had several sensors to detect human state and several lights to convey its behaviours. The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love). A pilot to test the five implemented behaviours was made. The five behaviours correspond to two implementations of dominance, two of submission, and a neutral behaviour. These behaviours differ from each other in the way that the light is turned on and its intensity. From pilot's results, they selected two most convincing behaviours, one dominant and one submissive. Using these two behaviours, they did an experiment with three different scenarios, in which all the participants were exposed. To measure participants' appreciations, they used the Social Dominance Orientation (SDO)~\cite{ pratto1994social} questionnaire and SAM. Their results suggest that people prefer systems that display submissive behaviors. More importantly, their findings suggest that electronic systems can elicit a type of reactions different from the one expected on theories of interpersonal communication.

%%%%%%%%%%%%%%%%
Using a humanoid platform NAO~\cite{NAO2013}, Ca\~namero and collaborators~\cite{Canamero2010,Beck2010} studied the perception of key body poses designed to show emotions. They suggested that the techniques used to convey emotions in virtual characters could not be used in robots, due to the fact that virtual characters have no physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007, Canamero2010}. They proposed a set of poses that could be used to express emotions with NAO, paying a particular attention to the contribution of the head. They did two experiments in which they show the participants different poses and each participant had to pick one emotion from the list given to them. The list presented to the subjects included six emotions: pride, happiness, excitement, fear, sadness and anger. Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement respectively. The major finding from their experiments is that moving the head up improved the identification of pride, happiness, and excitement. While moving the head down improved the identification of anger and sadness. However, these key poses are taken statically, without any displacement of the robot in the environment.

%%%%%%%%%%%%%%%%%%%%%%
Li and Chignell~\cite{Li2011} used a teddy bear robot capable to move its arms and head to study their contribution on emotion projection. To achieve this, they did a total of four studies. In the first one, four participants were asked to create a gesture that the robot would do in one of the twelve scenarios presented to them. These gestures were recorded and used in the second study. The experiment consisted of two parts: one just showing the gestures, and the second one describing a scenario were the gestures were generated. The participants had to select from a list the emotion that they thought the robot was conveying. The list included basic emotions and mental states, which were selected from the comments obtained during the first study. The results showed that giving a context increased the recognition rate. In the third experiment, they asked five novices and five puppeteers to create gestures for each of the six Ekman's basic emotions. The gestures generated were recorded and used as input in their last test, where the subjects had to select an emotion from a list including the names of the six basic Ekman's emotions. Their results showed that it is possible to convey emotions just using movements in the head and arms. Also they found out that the gestures made by the puppeteers had a better recognition for disgust and fear. Although they presented numerical information about their findings, this information is shown in a way that is not possible to discern the recognition rate of each emotion for each experiment.

%%%%%%%%%%%%%%%%%%%%%%
Daryl~\cite{Arras2012} is an anthropomorphic robot, without facial expression, nor limbs, but with mobility capabilities. This platform was used to test whether it is possible to project emotions without using cues used in a human-like platform (e.g., tail, ears and head). This robot has head, ears, ability to generate colors in a RGB-LED set positioned in its chest, and a speaker system. The head had no capabilities to show facial expressions, but its movements and robot translations were used to show emotions. The emotions implemented were: happiness, sadness, fear, curiosity, disappointment, and embarrassment. During the experiments done by the researchers, special attention was put to the final distance between the robot and the subject, but the approaching velocity and the followed trajectory were not taken into consideration. The subjects were exposed to a sequence of movements. For each sequence the subject was asked to rate the intensity of each emotion enlisted in a five-point Likert scale questionnaire. The enlisted emotions were the six implemented plus anger, disgust and surprise. Their results showed that participants gave a higher intensity to the desired emotion, also similar ones, such as sadness and disappointment.

%%%%%%%%%%%%%%%%%%%%%%%
Using the platform WABIAN-2R, Destephe and collaborators~\cite{Destephe2013b} studied the attribution of emotion to a robot's gait. To obtain the robot's movements, the researchers asked two professional actors to walk in a room conveying anger, happiness, sadness, and fear with different intensities (low, regular, normal, high, and exaggerated). All the actors' walking were recorded using a Cortex motion capture system. These data were later reported to robot's embodiment. To verify their data, the researchers first did a pilot study with just two emotions (happiness and sadness) and thirteen subjects~\cite{Destephe2013}. Each subject was exposed to a series of videos. After each video, the subject was asked to select one emotion from a list (happiness, neutral, or sadness) and to state the intensity of the selected emotion. The videos showed were not made with the real robot, but with a virtual model of the robot. From the results obtained, they decided not to use the low intensity because it had a very low recognition rate. During the experiment they adopted the same procedure, emotion and its intensity, but this time showing all the emotions and intensities, excluding low, to the participants. Their results showed that sadness was recognized 73.81\% (average) of the times with an intensity of 21.43\%, happiness was recognized 66.67\% (average) of the times with an intensity of 30.95\%, anger was recognized 61.9\% of the times with an intensity of 26.19\%, and fear was recognized 83.33\% (average) of the times with an intensity of 28.58\%. These results show that people could reasonably well recognize emotions from the robot's gait.

%%%%%%%%%%%%%%%%%%%%%%%
Lakatos and Collaborators~\cite{Lakatos2014} take inspiration from human-animal interaction
to create behaviours that could enrich human-robot interaction. They conducted an experiment to analyse the recognition rate of emotion expression, using as inspiration the movements done by dogs to convey emotions. The experiment was done using a Wizard-of-Oz scene and its goal was to determine if people could distinguish two emotions (happiness and fear). They use a game approach to determine participant's appraisal of the robot emotion. This was done in order to avoid asking the participants the emotion they believe the robot is eliciting. Therefore, in the experiment, each participant had two balls (yellow and black) and they could play with the robot using one of this balls at a time. However, one of the balls triggers robot's happiness and the other fear. The dog's favourite ball was changed from participant to participant to avoid any bias for the balls' color. The results of this experiment showed that the participants decided to use more dog's favourite ball to play with the dog, which is consistent with the idea that the participants could discern which ball produced ''happiness'' in the robot.

%%%%%%%%%%%%%%%%% %
Brown and Howard focused their interest on head and arm movements using the DARwIn-OP platform~\cite{Brown2014}. Their hypothesis was that using some principles, that they evaluated as important, it is possible to express happiness and sadness in a way that people could recognize. These principles establish that to show happiness is necessary to quiclkly move robot's head up and arms up. While to express sadness the head goes down, arms down, both slowly. To test their hypothesis they conducted an experiment with thirteen participants. Each participant was exposed to fifteen sequences of poses and he/she had to answer for each sequence a five-point Likert scale (very-sad to very happy, with neutral in the middle). They obtained a 95\%, 59\%, and 94\% of accuracy for happiness, neutral and sadness respectively. Although their results show that their key features are determinant to convey happiness and sadness.

%%%%%%%%%%%%%%%%%%%
Sharma and collaborators~\cite{Sharma2013} used a quadrotor to study how different Laban's effort~\cite{Laban1968} parameters could impact on the perception of affection. A professional Laban certified actor was asked to generate 16 different paths, for each one changing one of the four Laban's parameters (space, weight, time, and flow). Each generated path was recorded using the Vicon motion-tracking system. Then, they did an experiment were people were asked to assess each path using the Self-assessment Manikin (SAM)~\cite{Lang2008}. In order to analyse the results, they mapped them on the circumplex model of emotion, and evaluated the contribution of each Laban's parameter in the 2-D circumplex model (arousal and valence). The results show that it is possible to increase both valence and arousal by using a more indirect space, or by performing the motion more quickly, and to decrease valence or arousal by a more direct use of space, or a more sustained motion. 
Although they suggest the use of Laban's model as a tool to specify affection movements in Human-Robot Interaction, how to use these parameters in the actual implementation remains an open question, since Laban defined them qualitatively, with reference to human people, and they leave very open questions about the most appropriate numerical values to be used with robots.

%%%%%%%%%%%%%%%%%%%
Suk and collaborators studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-human or animal like object~\cite{NAM2014}. Two experiments were designed to determine the relationship among these features and the emotional interpretation. To assess participants' emotional response they used SAM. The first experiment was focused on speed and smoothness movement features, selecting five different values for each one of these two features. Each participant was exposed to twenty five movements. After a participant observed a movement, the participant marked the two SAM graphic figures (pleasure and arousal).
The results from this first experiment show that the arousal increases as speed increases, but that there is not any clear tendency for smoothness. In the second experiment they evaluated the other two features (granularity and volume) using the same procedure followed in the first experiment. Their results show that granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal. As overall result, they found a major contribution of speed on arousal and minor contribution of granularity and volume.

%%%%%%%%%%%%%%%%%%%
To improve the coordination between humans and robots Novikova and Watss~\cite{Novika2015} proposed the use of emotion. They did studies using a own built platform called E4 to verify whether people could detect emotions from a non-human like platform. The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design. In all their experiments they used six emotional expressions (scared, surprised, excited, angry, happy, sad) and neutral. The emotion list used in their experiments was balanced using the 2-D circumplex model (arousal and valence), selecting three from each quadrant for a total of twelve emotions, plus the options of ``other'' and ``don't know''. They obtained a recognition rate of 52\%, 42\%, 41\%, 36\% and 15\% for surprise, fear, sadness, happiness, and anger respectively.

These works presented in this section provide guidance about features that could be exploited to project certain emotions. However, range of values to convey specific emotions will guide other researchers in what values could be used to convey their desire emotion or what values not to use because they could be misinterpreted as negative emotions.

%TODO Maybe the table could summarize what presented. It would also be nice if you could say some words either at the end of each presentation or at the begining, so to justify why you have selected them and not others, and what they bring as important for your work.

%%%%%%%%%%%%%%%%%%
%Table~\ref{table:comparison_work_emotion_projection} summarizes all the robotics studies to convey emotion that we considered, highlighting the following characteristics:
%\begin{itemize}
%	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
%	\item \textit{Platform used} gives the name of the platform used in the study;
%	\item The\textit{Locomotion} criterion was added to put in evidence whether the platform uses displacement movement to express emotion;
%	\item \textit{Emotion Evaluation Method} refers to the methodology used to collect the data in the studies.
%	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
%	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
%	\item \textit{Type of test} tells if it was done an experiment or a case study.
%	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The media considered were: movement, body posture and face poses.
%\end{itemize}
%\begin{table}[h]
%\caption{Comparison among works on emotion projection in robotics. NA = Not Available}
%\label{table:comparison_work_emotion_projection}
%\begin{center}
%\tiny %\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\begin{tabular}{|p{1.0 cm}|p{0.5 cm}|p{0.9 cm}|p{0.8 cm}|p{0.8 cm}|p{1.1 cm}|p{0.9 cm}|p{1.1 cm}|p{0.8 cm}|p{0.8 cm}|}
%%\begin{tabular}{|p{1.5 cm}|p{1.0 cm}|p{1.5 cm}|p{1.5 cm}|p{1.5 cm}|p{2.0 cm}|p{1.5}|p{2.0 cm}|p{1.0 cm}|p{1.5 cm}|}
%\hline 
%\textbf{Work} & \textbf{Year} & \textbf{Embodiment} & \textbf{Platform Used} & \textbf{Locomotion} & \textbf{Emotion Evaluation Method} & \textbf{Emotion Presentation} & \textbf{Emotions Implemented} &  \textbf{Type of test} & \textbf{How is the emotion conveyed?}\\ 
%\hline 
%Breazeal~\cite{Breazeal2002} & 2002 & Face & Kismet & NA & Questionnaire & Video & Happiness, surprise, anger, disgust, fear, sadness and interest & Experiment & Face poses\\ 
%\hline
%Saerbeck and Christoph~\cite{Saerbeck2010} &2010& Animal/ Non-Human like& iCat / Roomba & NA / Differential &PANAS and SAM & Real Robot & NA & Experiment & Movement\\
%\hline 
%Ca\~namero and collaborators~\cite{Canamero2010,Beck2010}& 2010 &Human-Like & NAO & Bipedal & Questionnaire & Real robot & Anger, sadness, fear, pride, happiness, and excitement & Experiment & Body poses\\
%\hline
%Li and Chignell~\cite{Li2011}&2011&Animal-Like& Teddy Bear Robot& NA & Questionnaire & Video (Real robot) & Random + Anger, disgust, fear, happiness, sadness, and surprise & Experiment & Body poses\\ 
%\hline
%Barakova and collaborators~\cite{Barakova2013} & 2013 & NA & Closet robot& NA & SDO and SAM & Real robot & NA & Experiment & Changing lights on and intensity\\ 
%\hline
%Sharma and collaborators~\cite{Sharma2013}& 2013 & Non-Human/Animal & Quadrotor & Aerial & SAM + Questionnaire + Interview &  Real Robot & Laban's poles & Experiment & Movement\\
%\hline
%Destephe and collaborators~\cite{Destephe2013b}&2013&Human-like & WABIAN-2R & Bipedal & Questionnaire & Video (Virtual Robot) & Fear, anger, happiness, and sadness & Experiment & Movement (Gait)+Body Poses\\
%\hline 
%Embgen and collaborators~\cite{Arras2012} & 2014 & Human-like & Daryl &  Differential& Questionnaire & Real Robot & Happiness, sadness, fear, curiosity, embarrassment, and disappointment & Experiment & Movement + Body poses \\ 
%\hline
%Lakatos and Collaborators~\cite{Lakatos2014}& 2014 & Animal-Like & Dog & Holonomic & Indirect (Interaction with the robot) & Real Robot & Happiness and Fear & Experiment & Move + Body poses \\
%\hline
%Brown and Howard~\cite{Brown2014} & 2014& Human-Like & DARwIn-OP & Bipedal & Questionnaire & Real Robot & Happiness and sadness & Experiment & Body poses\\
%\hline
%Suk and collaborators ~\cite{NAM2014}& 2014 &  Non-Human/Animal & Self-made & NA & SAM & Real Robot & NA & Experiment & Speed, smoothness, granularity and volume\\
%\hline
%Novikova and Watss~\cite{Novika2015}& 2015&Non-Human/Animal & Lego & Differential& Questionnaire& Real Robot & Scared, surprise, excited, angry, neutral, happiness and sadness & Experiment& Movement + Poses\\
%\hline 
%\end{tabular} 
%\end{center}
%\end{table}

### 2016-09-21 JournalIJSR/Parts/ExperimentDesign.tex
Base articles, they should be modify before any submission

The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation to express happiness, anger, sadness and fear, which are four out of six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

\subsection{Independent Variables}

The definitions of the selected independent variables are reported here below.

\begin{itemize}
	\item \textbf{Angular velocity} is the rotational speed  ($\omega$) of the robot with respect to its center.

	\item \textbf{Oscillation angle} is the maximum extension in which the robot will rotate around its center in the oscillating movement ($\theta$).

	\item \textbf{Linear velocity} is the rate of change of the position of the robot ($V$).

	\item \textbf{Direction with respect to participant's perspective} is the angle generated from the participant's point of view with respect to the robots trajectory ($D$).

	\item \textbf{Orientation of the body with respect to participant's perspective} is the robot's body orientation with respect to the robot's trajectory ($\phi$).

\end{itemize}

The three first variables are shown in Figure~\ref{fig:angular_movement}. As it could be observed, robot's frame of reference is draw to show that it could move straight while is rotating.

\begin{figure}
	\centering
	\includegraphics[width=0.80\textwidth]{./Images/ExampleMovement.png} 
	\caption{Example of the features used in the experiment. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement. The two black arrows in the robot's middle depict robot's frame of reference.}
	\label{fig:angular_movement}

\end{figure}

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Dependent Variables}

\begin{itemize}
	\item \textbf{Emotion:} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed,  two mental states that could be misinterpreted from these emotions, and the option of ``other'', where participants could write their own interpretation. 
	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.

	\item \textbf{Emotion's intensity:} indicate the emotion intensity as perceived by the subject. This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.

\end{itemize}
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Independents' Variables Values}

It was decided to select specific for all independents variables, discrete values to make the experiment feasible. First, a simple test to evaluate when significant changes could be perceived was performed on a small sample of independent subjects. Base on this test specific values for oscillation angle, and angular and linear velocities were selected. For the remaining two variables were selected the cases that could be beneficial for the experiment. 
The chosen values are shown in Table~\ref{table:variables_values}.

\begin{table}[htb]
\caption{Possible values for each of the independent variables.}
\begin{tabular}{|c|c|c|c|c|}
\hline
\backslashbox{Variable}{Possibilities} & First & Second & Third & Fourth\\
\hline   
Angular Velocity ($rad/sec$)& $0$ & $1$ & $2$ & $3$\\
\hline
Oscillation Angle ($rad$)& $0$ & $0.087$ & $0.175$ & $0.349$\\
\hline
Linear Velocity ($mm/sec$) & $0$ & $200$ & $500$ & $900$\\
\hline
Direction ($rad$)&$0$&$\pi$&$\frac{-\pi}{2}$& \\
\hline
Orientation ($rad$) & $0$ & $\pi$ & & \\
\hline 
\multicolumn{5}{c}{}
\end{tabular} 
\label{table:variables_values}
\end{table}

To get a better idea about the Direction and Orientation values, in Figure~\ref{fig:possibilities_orientation_direction} are reported all the possibilities for these two variables.

\begin{figure}
	\centering
	\includegraphics[width=1.0\textwidth]{./Images/possibilities_case.png} 
	\caption{Combination of direction and orientation. The crosses symbolize the final position. The robot represents the initial position with its orientation, which is represented through the robot's frame of reference. The dash big square represents robot's movement zone, while the small represents participant's zone. a) Direction = $0$ and Orientation = $0$. b) Direction = $0$ and Orientation = $\pi$. c) Direction = $\pi$ and Orientation = $\pi$. d) Direction = $\pi$ and Orientation = $0$. e) Direction = $\frac{-\pi}{2}$ and Orientation = $0$. f) Direction = $\frac{-\pi}{2}$ and Orientation = $\pi$}
	\label{fig:possibilities_orientation_direction}
\end{figure}

The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, were generated from the combination of independent variables' values for a total of 384 combinations. All the experiences that would not add any significant information to the experiment were deleted, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of treatments to 195.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Participants' Sequence}

It was decided that each subject will be just exposed to twenty over one hundred and ninety five possible experiences, which lasted  from 10 to 15 minutes. This was decided because each subject was a volunteer and would not perceive any monetary remuneration, so the time dedicated to the experiment had to be kept limited. The twenty treatments were selected picking a number without replacement from 1 to 195.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

\subsection{Setup}

The experiment's setup and dimensions are shown in the Figure~\ref{fig:setup}. The crosses symbolize possible starting points, which were selected depending on the direction's value, as it is showed in Figure~\ref{fig:possibilities_orientation_direction}.

\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{./Images/ExperimentGeneral.png} 
	\caption{Setup for the experiment. The crosses symbolize the possible starting points.}
	\label{fig:setup}
\end{figure}

### 2016-09-21 JournalIJSR/Parts/Introduction.tex
Base articles, they should be modify before any submission

Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}. However  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states. This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been used to convey emotions.
Nevertheless in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011} , in some cases like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

The amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those that exploit anthropomorphic features. Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented by them. For example Suk and collaborators~\cite{NAM2014} in their study gives specific values for acceleration, curvature, and but their connection to specific emotions is not given. Rather, they gave a relationship between their features and values in terms of pleasure/arousal dimensions. This could lead to select features to convey certain emotions but it would be even better to know specific range of values for those features to convey certain emotions or to know the values that could be misinterpreted with negative emotions.

In order to get a better understanding of other features and values that could be used to convey specific emotions, this paper presents an experiment that was designed to identify specific values for some movement features that could be used to express the following emotions, selected among the ones suggested by Ekman as basic~\cite{Ekman2004}: happiness, anger, fear and sadness. The considered features are oscillation angle, linear and angular velocity, direction and orientation, identified as independent variables. The perceived emotions and their intensities were considered as dependent variables. It is to be observed that it was given the possibility to the subjects to provide their evaluation of emotional intensity for more than one emotion for each experience. The experiment took place in Politecnico di Milano during June and July of 2015, where students from diverse departments were asked to participate without any economical retribution. Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was used to evaluate the agreement among the participants for each treatment. For each of the four emotions was generated a top 10 list based on alpha agreement and perceived intensity. The results suggest that fear is perceived when the robot is looking at them and moving far from them fast. Sadness is attributed to slow velocities with slow angular velocity and small oscillation angle. Anger is attributed to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them.

This paper is organized as follows. The next section introduces previous studies done in human emotion and robot emotions projection. Section~\ref{sec:system} introduces the robotic platform and the software used in the experiment. The experiment's design is explained in section~\ref{sec:experiment}. Finally sections~\ref{sec:study} and~\ref{sec:result} presents the study done and the obtained results.

### 2016-09-21 JournalIJSR/Parts/Platform.tex
Base articles, they should be modify before any submission

The system used in the experiment is composed by a non-anthropomorphic platform and software architecture that enrich robot's movements with emotion. The robotic platform was envisioned to be as simpler as possible to let the study of the desired characteristics.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware and Mechanical}

A holonomic platform was built to be used in the experiment. This type of platforms are characterized by the possibility to move in any direction without the necessity to have a specific orientation, i.e., they are free to move taking any desired orientation. Therefore, it was possible to imitate movements that are done by humans. For example, people move straight even if they turn their whole body a bit. The platform has a diameter of 25 cm and height of 25 cm. Figure~\ref{fig:ThirdDesign} shows the platform's blue prints and the real platform. Robot's frame of reference, in which all the velocities are going to be calculated, are depicted by the two black arrows. So, as it could be observed, to make the robot move forward it must be send a velocity in $y$ axis.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Images/DesignThird.png} 
	\caption{Design of the platform. a) Base platform, this layer is used to carry the batteries. The two black arrows represent robot's frame of reference. b) First layer, which includes the Arduino and the H-Bridges to control the motors. c) Second layer with the Odroid-U3 and the mechanical structure to support the upper part. d) Lateral view of the version.}
	\label{fig:ThirdDesign}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%platform_base
\subsection{Software}
To ensure robot's velocity it was implemented a PID controller for each motor. PID's set point is established by a controller that could receive two different types of commands. The first commands is robot's velocities ($<V_x,V_y,\omega>$), which are given in robot's frame of reference. The second command is a point ($<x, Y, \theta>$), which is given in the general frame of reference. This frame of reference is set every time the system is reset or boot. For example, if the robot finishes a trajectory and then it is reset, the new frame is going to be in the robot's current position.

Additional to this low level control, it was created a graphical interface~\ref{fig:experimental_interface} to reduce the possibility on introducing wrong values for a desired sequence. This interface loads the sequences from a .txt file and displays sequences' numbers on it. Every time that a new sequence should be presented to a participant, the sequence's number is selected in the interface, which will display sequence's values. Once the robot has been positioned to the correct position, the execution could be started by clicking on send button. Here two commands are send, one resetting the controller and the second the desire position. In case that the sequence's execution should be aborted, it should be clicked the button stop.

\begin{figure}
	\centering
	\includegraphics[width=0.60\textwidth]{./Images/ExperimentInterface.png} 
	\caption{Interface used in the experiment. Once a sequence is selected, the interface shows sequence's values. Also, the interface give information about the current position of the robot and its velocity.}
	\label{fig:experimental_interface}
\end{figure}

### 2016-09-21 JournalIJSR/Parts/Results.tex
Base articles, they should be modify before any submission

A total of 980 answers were collected, and a minimum of 5 trials for each motion type. A table with participants' answers was generated for each treatment. Table~\ref{table:example_table} is an example of the generated tables.

\begin{table}
\caption{Example of the table generated for each movement. This table corresponds to the treatment with $ID=1$.}
\label{table:example_table}
\begin{tabular}{ | l | p{1.3 cm} | l | p{1.3 cm} | l | l | l | l | l | l | l | l |  }
\hline
	\rotatebox{90}{ \textbf{Sex}} & 
	\rotatebox{90}{ \textbf{Background}} & 
	\rotatebox{90}{ \textbf{Age}} & 
	\rotatebox{90}{ \textbf{Country of Origin}} & 
	\rotatebox{90}{ \textbf{Happy}} &
	\rotatebox{90}{ \textbf{Excited}} & 
	\rotatebox{90}{ \textbf{Tender}} & 
	\rotatebox{90}{ \textbf{Scared}} & 
	\rotatebox{90}{ \textbf{Angry}} & 
	\rotatebox{90}{ \textbf{Sad}} & 
	\rotatebox{90}{ \textbf{Other}} & 
	\rotatebox{90}{ \textbf{Explain}} \\ \hline
	Masculine & electronic engineering & 29 & Iran &  0 & 2 & 8 & 0 & 0 & 0 & 0 & \  \\ \hline
	Feminine & Computer science & 25 & Italy &  0 & 0 & 6 & 0 & 0 & 8 & 0 & \  \\ \hline
	Masculine & Computer science & 24 & Italy &  0 & 0 & 0 & 8 & 0 & 7 & 0 & \  \\ \hline
	Feminine & Science pedagogiche & 26 & Italy &  0 & 0 & 0 & 0 & 0 & 0 & 7 & Dubbioso \\ \hline
	Masculine & Computer science & 24 & Italy &  4 & 8 & 0 & 0 & 0 & 0 & 0 & \  \\ \hline
\multicolumn{12}{c}{}
\end{tabular}
\end{table}

For each table, mean, standard deviation, and median were calculated. It was not possible to use ANOVA test over the data because the assumption of normality is not achieved in the collected data. This was checked using the Shapiro-Wilk Test.
Additionally, a contingency table for each emotion was generated in each treatment as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean, including the option of other. For all tables, including the contingency,  the Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated: it is a reliability coefficient to measure the agreement among different participants. Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to: any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.

This calculation was done using the R's package \textit{irr}. To improve the table interpretation, it was decided to just register the emotions' alpha values that had a mean greater than zero. The $\alpha$ for each treatment is shown in Figure~\ref{fig:alpha_treatment}. Additionally, for each emotion was generated a table with a top ten ranking treatments that considers the following items:(i) the mean intensity of the respective emotions, (ii) the alpha agreement for the respective emotion, and (iii) the alpha agreement for the specific treatment. To generate these tables, were first organized by the mean, then by the emotion's agreement and finally by the general agreement.
The decision to give more importance to emotion's alpha was taken based on the situation that the participants could be agreed about the precise emotion but not for the rest of the words enlisted. 
From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:

\begin{itemize}

	\item Fear was the only emotion that had six over ten movements obtaining both general and specific alpha agreement over 0.41, which is the lower bound for moderate agreement~\cite{Viera2005}. Also, it was mostly selected (eight over ten) when $direction = \pi$ and $orientation = \pi$. The angle and the angular velocity attributed six over ten times were $0.087$ and $2$, respectively. So it seems that people perceive as fear when the robot is looking at them and moving far from them fast.

	\item Sadness was mostly attributed to linear velocities of $0 mm/s$ (two over ten) and $200 mm/s$ (eight over ten), and angular velocities of $0 rad/s$ and $1 rad/s$, with higher predilection of the second (eight over ten). It seems that people attribute sadness to slow velocities with slow angular velocity and small oscillation angle. Regarding the other two features, there is not a concrete pattern that could lead to make a generalization.

	\item Happiness is attributed to different values of the independent variables. But it is the only emotion that is highly perceived when the linear velocity is $0$ with four over ten. However the oscillation angle for these four cases is equally divided between the values $0.174$ and $3.49$. So it seems that happiness is mainly attributed to fast angular velocities and big oscillations angles. However specific agreement among the other features is not present.

	\item Anger is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$. It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them. 
\end{itemize} 
%alpha general

\begin{figure}
	\centering
	\includegraphics[width=1.0\textwidth]{./Images/Alpha.png} 
	\caption{Alpha values for each movement.}
	\label{fig:alpha_treatment}
\end{figure}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Happiness.  This tops table was generated by ordering the results from highest to lowest first by Happy mean, then by Happy alpha, and finally by Movement alpha.}
\label{table:happy_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &   
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	0 & 0 & 500 & 3 & 0.349 &  0.38 & 0.71 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 6.8 & 3 & 2.6 & 0 & 1.4 & 0 & 1.4 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.174 &  0.53 & 0.71 & 0 & 0 & 0 & 0 & 0 & 0 & 6.8 & 3.8 & 2 & 0 & 0 & 0 & 0 \\ \hline
	0 & 0 & 900 & 3 & 0.174 &  0.33 & 0.22 & 0 & 0.13 & 0 & 0 & 0 & 0 & 6.6 & 2.6 & 0.6 & 0 & 1.6 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 0 & 3 & 0.349 &   0.21 & 0.21 & 0 & 0.13 & 0 & 0.23 & 0.34 & 0 & 6.6 & 3.6 & 1.4 & 2 & 0.8 & 0.4 & 0 \\ \hline
	$\pi$ & 0 & 900 & 3 & 0.349 &   0.48 & 0.11 & 0.72 & 0.12 & 0 & 0.76 & 0 & 0 & 6.4 & 6.8 & 1.2 & 4 & 0.2 & 0 & 0 \\ \hline
	0 & $\pi$ & 0 & 2 & 0.349 &  0.34 & 0.71 & 0 & 0 & 0.13 & 0.47 & 0.23 & 0 & 6 & 1.4 & 3.2 & 1.6 & 0.4 & 0.6 & 0 \\ \hline
	$\pi$ & $\pi$ & 0 & 2 & 0.174 &   0.31 & 0.12 & 0 & 0 & 0.61 & 0 & 0 & 0.13 & 6 & 4.8 & 4.8 & 0.4 & 0 & 0 & 2 \\ \hline
	$\pi$ & 0 & 500 & 2 & 0.349 &  0.43 & 0.11 & 0 & 0 & 0 & 0.13 & 0 & 0 & 6 & 0 & 3.4 & 0 & 0.6 & 0 & 2 \\ \hline
	0 & 0 & 500 & 1 & 0.174 &  0.24 & 0.11 & 0 & 0 & 0 & 0 & 0 & 0.13 & 6 & 4 & 4.2 & 0 & 2.2 & 0 & 1.2 \\ \hline
	$\pi$ & 0 & 200 & 3 & 0.349 &  0.28 & 0.22 & 0 & 0 & 0 & 0 & 0 & 0 & 5.8 & 0.8 & 3 & 0 & 0 & 0 & 1.4 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Anger.  This tops table was generated by ordering from highest to lowest first by Angry mean, then by Angry alpha, and finally by Movement alpha.}
\label{table:Angry_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &  
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	0 & 0 & 0 & 2 & 0.087 & 0.19 & 0 & 0.13 & 0.13 & 0.13 & 0.22 & 0 & 0 & 3.2 & 1.4 & 1.2 & 1.8 & 6.4 & 0 & 0 \\ \hline
	0 & 0 & 900 & 2 & 0.087 & 0.29 & 0.13 & 0 & 0.76 & 0.13 & 0.21 & 0 & 0 & 1.6 & 3.8 & 0.2 & 1 & 6.4 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 900 & 0 & 0 & 0.60 & 0 & 0 & 0 & 0.13 & 0.73 & 0 & 0 & 0 & 1.6 & 0 & 1.4 & 6.2 & 0 & 0 \\ \hline
	0 & 0 & 900 & 3 & 0.349 & 0.44 & 0 & 0 & 0 & 0 & 0.12 & 0 & 0 & 3 & 5 & 0 & 2.8 & 6.2 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 200 & 3 & 0.087 & 0.41 & 0 & 0 & 0 & 0 & 0.11 & 0.47 & 0 & 0 & 4.8 & 2.6 & 0 & 5.8 & 0.4 & 0 \\ \hline
	$\pi$ & 0 & 500 & 3 & 0.087 & 0.44 & 0.13 & 0 & 0 & 0 & 0.43 & 0 & 0 & 0.8 & 2.6 & 0 & 1.4 & 5.2 & 0 & 0 \\ \hline
	0 & 0 & 200 & 3 & 0.087 & 0.13 & 0.13 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 2.4 & 5.2 & 0 & 1.8 \\ \hline
	0 & 0 & 900 & 1 & 0.087 & 0.54 & 0 & 0.16 & 0 & 0 & 0.16 & 0 & 0 & 2.4 & 6.4 & 0 & 0 & 5 & 0 & 0 \\ \hline
	0 & 0 & 900 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 0.13 & 0 & 0 & 0.13 & 1.6 & 3 & 1 & 1.6 & 5 & 0 & 1.8 \\ \hline
	$\pi$ & 0 & 500 & 2 & 0.087 & 0.30 & 0.13 & 0 & 0 & 0 & 0.21 & 0 & 0 & 1 & 1.8 & 0 & 3.4 & 4.8 & 0 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Fear.  This tops table was generated by ordering from highest to lowest first by Fear mean, then by Fear alpha, and finally by Movement alpha.}
\label{table:Scared_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	$\pi$ & $\pi$ & 900 & 2 & 0.174 & 0.85 & 0 & 0 & 0.15 & 0.83 & 0 & 0 & 0 & 0 & 0 & 1.2 & 9.6 & 0 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 900 & 1 & 0.087  & 0.73 & 0 & 0 & 0.15 & 0.79 & 0 & 0.79 & 0 & 0 & 0 & 0.6 & 9.6 & 0 & 0.2 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 3 & 0.087 & 0.41 & 0.13 & 0 & 0 & 0.75 & 0 & 0 & 0 & 2 & 3.4 & 0 & 9 & 3.6 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 2 & 0.174 & 0.33 & 0.24 & 0.24 & 0 & 0.34 & 0.24 & 0 & 0.25 & 1.33 & 1.5 & 0 & 7.83 & 0.66 & 0 & 1.66 \\ \hline
	$\pi$ & $\pi$ & 500 & 2 & 0.087 & 0.68 & 0 & 0 & 0 & 0.72 & 0.13 & 0 & 0 & 0 & 0 & 0 & 7.8 & 0.6 & 2.20 & 0 \\ \hline
	$\pi$ & $\pi$ & 200 & 2 & 0.087 & 0.44 & 0.13 & 0.13 & 0 & 0.66 & 0 & 0 & 0 & 1 & 1 & 1.2 & 7.6 & 1.6 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.087 & 0.35 & 0.35 & 0.13 & 0 & 0.22 & 0 & 0 & 0 & 0.4 & 1.2 & 0 & 7.4 & 3 & 0 & 0 \\ \hline
	0 & $\pi$ & 900 & 3 & 0.087 & 0.53 & 0 & 0 & 0 & 0.30 & 0 & 0 & 0 & 0 & 0 & 0 & 7 & 2.20 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 3 & 0.349 & 0.20 & 0.13 & 0.13 & 0 & 0.16 & 0.34 & 0 & 0 & 1.8 & 1.6 & 0 & 6.8 & 0.4 & 2.4 & 0 \\ \hline
	$\pi$ & $\pi$ & 200 & 2 & 0.174 & 0.53 & 0 & 0 & 0.13 & 0.71 & 0.13 & 0.13 & 0 & 0 & 0 & 1 & 6.6 & 0.8 & 1.2 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Sadness.  This tops table was generated by ordering from highest to lowest first by Sadness mean, then by Sadness alpha, and finally by Movement alpha.}
\label{table:Sad_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	$\pi$ & 0 & 200 & 1 & 0.349 & 0.64 & 0 & 0 & 0 & 0 & 0.13 & 0.73 & 0.13 & 0 & 0 & 0 & 0 & 1.2 & 7.4 & 1.6 \\ \hline
	0 & $\pi$ & 0 & 1 & 0.349 & 0.39 & 0 & 0 & 0.13 & 0 & 0 & 0.22 & 0 & 0 & 0 & 1.8 & 0 & 0 & 7.2 & 3.2 \\ \hline
	0 & 0 & 200 & 1 & 0.349 & 0.18 & 0.13 & 0 & 0 & 0 & 0.13 & 0.11 & 0 & 1.6 & 2 & 5.4 & 2.6 & 1.6 & 6 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 200 & 0 & 0 & 0.10 & 0.13 & 0.29 & 0 & 0 & 0 & 0 & 0 & 0.8 & 0.4 & 1.8 & 0 & 0 & 6 & 3.2 \\ \hline
	$\pi$ & $\pi$ & 200 & 1 & 0.349 & 0 & 0 & 0 & 0.13 & 0.13 & 0.14 & 0 & 0 & 0 & 0 & 0.6 & 1.4 & 1.2 & 6 & 2.4 \\ \hline
	0 & $\pi$ & 200 & 0 & 0 & 0.27 & 0.13 & 0 & 0 & 0 & 0 & 0.21 & 0 & 1.2 & 0 & 3.4 & 1.8 & 0 & 5.8 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 1 & 0.087 & 0.14 & 0 & 0.13 & 0.13 & 0.13 & 0 & 0.21 & 0.13 & 0 & 2 & 2 & 1.2 & 0 & 5.8 & 1.6 \\ \hline
	0 & $\pi$ & 200 & 1 & 0.349 & 0.40 & 0 & 0.13 & 0 & 0 & 0 & 0.57 & 0.13 & 0 & 0.8 & 3 & 3 & 0 & 5.6 & 0.6 \\ \hline
	$\pi$ & $\pi$ & 200 & 0 & 0 & 0.32 & 0.69 & 0.69 & 0 & 0 & 0 & 0.16 & 0 & 0.2 & 0.2 & 1.2 & 3.2 & 0 & 5.4 & 0 \\ \hline
	0 & $\pi$ & 200 & 1 & 0.087 & 0.36 & 0 & 0 & 0 & 0 & 0 & 0.16 & 0 & 0 & 0 & 3.6 & 3.6 & 0 & 5.4 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\caption{Contingency table formula used for each emotion and treatment. Where $k$ is the kth treatment, $j$ is jth emotion for the kth treatment, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
\label{table:table_contingency}
\small
\begin{tabular}{|l|l|l|}
\hline
Participant & Desire Emotion & Other Emotions \\
\hline
$1$ & $Value_{k,j}^{1}$  & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{1})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
$2$ & $Value_{k,j}^{2}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
... & ... & ...\\
\hline
$n$ & $Value_{k,j}^{n}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
\multicolumn{3}{c}{}
\end{tabular}
\end{table}

### 2016-09-21 JournalIJSR/Parts/Study.tex
Base articles, they should be modify before any submission

The information about all the subjects was collected using a Google form. To maintain participants anonymity, not personal information that could be used to trace them back was collected. The procedure used with each subject is described here below.

\begin{enumerate}

	\item The subject was asked to fill out the following information:

	\begin{itemize}
		\item Sex
		\item Career
		\item Age
		\item Country of origin.
	\end{itemize}

	\item The robot was shown to the participant and the experiment procedure is explained.

	\item An example of the questionnaire was presented and a sample movement of the robot shown.

	\item The subject is exposed to a specific movement sequence according to the following steps:

	\begin{enumerate}

		\item The subject is exposed to the movement generated by a configuration of values.

		\item The subject could use as much time as needed to select values for intensity of the different terms in the questionnaire.

		\item After the subject had completed his/her selection about the current movement, the sequence is repeated for the rest of movements.

	\end{enumerate}
\end{enumerate}

The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used. The experiment was performed at Politecnico di Milano, involving subjects with different backgrounds. %campus Leonardo during the months of June and July of 2015.  
A total of 49 volunteers were involved: 12 females and 37 males. The average age of the subjects was 25.28, with standard deviation of 2.8, with a minimum age of 20 and maximum of 32. The subjects' country of origin and their backgrounds are shown in the Table~\ref{table:country} and Table~\ref{table:career}, respectively.

\begin{figure}
	\centering
	\includegraphics[width=0.90\textwidth]{./Images/example_survey.png} 
	\caption{Example of the questionnaire used in the experiment.}
	\label{fig:questionnaire_example}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% 
\begin{table}[h]
\caption{Subjects' Country of origin.}
\label{table:country}
\begin{tabular}{|c|c|}
\hline
\textbf{Country} & \textbf{Counting} \\
\hline
Albania & 1 \\
\hline
Bosnia & 1 \\
\hline
Brazil & 2 \\
\hline
Colombia & 4 \\
\hline
Germany & 1 \\
\hline
Greece & 1 \\
\hline
Iran & 5 \\
\hline
Italy & 33 \\
\hline
Moldova & 1 \\
\hline 
\multicolumn{2}{c}{}
\end{tabular} 
\end{table}
%%%%%%%%%%%%%%%%

\begin{table}[h]
\caption{Subjects' Background.}
\label{table:career}
\begin{tabular}{|c|c|}
\hline
\textbf{Career} & \textbf{Counting}\\
\hline
Aeronautical Engineering & 1 \\
\hline
Architecture & 1 \\
\hline
Social assistance & 1 \\
\hline
Automation & 1 \\
\hline
Bio-medical Engineering & 5 \\
\hline
Computer Science & 33 \\
\hline
Electronic Engineering & 2 \\
\hline
Mechanical Engineering & 2 \\
\hline
Nursery & 1 \\
\hline
Pedagogical Science & 1 \\
\hline
Tourism & 1 \\
\hline
\multicolumn{2}{c}{}
\end{tabular} 
\end{table}

### 2016-09-25 HRI/Parts/RelatedWork.tex
Changes in both articles.

--- 2016-09-21 JournalIJSR/Parts/Emotion_Projection.tex
@@
-Although it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010}, human studies provide guidelines about possible features and values that could be used to generate emotional motion.
-
-\subsection{Human Studies}
-
-Emotion plays an important role in human-human interaction, and can be expressed through diverse channels such as body gestures and poses, body movements, face expressions.
-Given the complex structure of human face, where more than 43 muscles act, face configurations are considered as a primary channel to express emotion.
-As a consequence, many works have focused on facial expression, mainly, but not only, influenced by the work done by Ekman~\cite{Ekman2004}.
-Fortunately, the role that body plays in emotions projection has been recognized and has started to be studied~\cite{Gelder2008,Wallboot1998}.
-Nevertheless, the amount of works related to body expression of emotions is still small compared to studies on facial expression.
-
-Analysing some of the few works that have studied human body expressiveness, it is possible to recognize two different methodologies to create the data base of movements to be assessed during the experiments.
-Applying a first methodology, human actors (either professionals, or amateurs) are asked to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}.
-Each trial is recorded and later shown to each subject, who evaluates all the sequences.
-The second methodology uses virtual agents~\cite{Roether2009,Venture2014} to generate the very same set up for the experiments; the agent's movements are generated from the data recorded from human actors.
-
-The work done by Wallboot~\cite{Wallboot1998} has been used as a referenced by others.
-His work addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
-His results reaffirm that movement and body postures are indicative of intensity for some emotions, while, for other emotions, these two characteristics seem to be enough to identify them.
-
-Complementary studies using virtual agents have been performed by  Kluwer and collaborators~\cite{Kluwer2004}, who studied the contribution of postures and angle view in the interpretation of emotions.
-They generated 176 static positions for happiness, anger, disgust, fear, sadness and surprise.
-Each image was later rendered from three different angles (front, left, and above and behind left shoulder) producing a total of 528 images.
-All the participants were exposed to all 528 images and were asked to label the image with the emotions that best represent it.
-Their results show that five out of six emotions were quite weel recognized independently from the angle of view.
-However, disgust was in some postures confused with fear.
-
-The main drawback of all these projects is the use of video recorded sequences, which misses the impact related to a complete physical experience.
-
-\subsection{Robotic Studies}
-%%%%%%%%%%%%%%%%%%%%%%
-
 The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused also on faces.
@@
 The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}) plus \textit{interest}.
-The face's physical design was done so to invite humans to treat it as if it was a social creature.
-The interaction studies done with this platform were conceived to consider a person as a caregiver and the robot as the receiver; it seems that the system was capable to engage people in a long term interaction.
-To achieve this goal, the system had six sub-systems: vision, hearing, motivational, behavioral, speaking, and emotion selection system.
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
@@
 After a video was projected, each participant selected the emotion from a list containing  the seven implemented emotions, only.
-The results showed a percentage of recognition over 57\%.
+The results showed high percentage of recognition (over 57\%).
 
@@
 Using these two characteristics, they did an experiment with eighteen participants.
-For the experiment they used two different platforms (iCat and Roomba) to verify if the embodiment had any impact on affection determination.
-For the Roomba researchers decided to use a circular trajectory in the room.
-While for the iCat two objects were place in front of it.
-It starts in a central position to then move to the left  right and back to center.
-To reduce variables' possibilities, they picked three definite values for each variable.
+They used two different platforms (iCat and Roomba) to verify if the embodiment had any impact on affection determination.
 Each participant was exposed to both embodiments and all possible variable combinations.
@@
 %%%%%%%%%%%%%%%%
-As part of their work on detecting emotions in humans, with a case of use in robot games, Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from movement.
-The behavior parameters were selected based on the work done by Camurri et al.~\cite{pop00002}.
-To focus participants' attention on movement, they used the e-puck platform~\cite{Mondada09thee-puck}.
-Their experiment is not fully described, but authors highlighted that the subjects were not given any list with possible emotions, rather they asked participants how they think that the robot was feeling.
-The results showed a very high recognition rate for the implementations of sadness, nervousness, and fear.
-The implementations for anger and happiness were confused.
-
-%%%%%%%%%%%%%%%%
-Barakova and collaborators used a closet robot~\cite{Barakova2013}, which does not show any anthropomorphic resemblance, to study new possibilities in social interaction.
-This closet robot can perceive human presence and react to show behaviours that could be perceived as emotions or mental states.
-The closet robot had several sensors to detect human state and several lights to convey its behaviours.
-The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love).
-A pilot to test the five implemented behaviours was made.
-The five behaviours correspond to two implementations of dominance, two of submission, and a neutral behaviour.
-These behaviours differ from each other in the way that the light is turned on and its intensity.
-From pilot's results, they selected two most convincing behaviours, one dominant and one submissive.
-Using these two behaviours, they did an experiment with three different scenarios, in which all the participants were exposed.
-To measure participants' appreciations, they used the Social Dominance Orientation (SDO)~\cite{ pratto1994social} questionnaire and SAM.
-Their results suggest that people prefer systems that display submissive behaviors.
-More importantly, their findings suggest that electronic systems can elicit a type of reactions different from the one expected on theories of interpersonal communication.
-
-%%%%%%%%%%%%%%%%
-Using a humanoid platform NAO~\cite{NAO2013}, Ca\~namero and collaborators~\cite{Canamero2010,Beck2010} studied the perception of key body poses designed to show emotions.
+Ca\~namero and collaborators~\cite{Canamero2010,Beck2010} studied the perception of key body poses designed to show emotions using a NAO~\cite{NAO2013}.
 They suggested that the techniques used to convey emotions in virtual characters could not be used in robots, due to the fact that virtual characters have no physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007, Canamero2010}.
 They proposed a set of poses that could be used to express emotions with NAO, paying a particular attention to the contribution of the head.
-They did two experiments in which they show the participants different poses and each participant had to pick one emotion from the list given to them.
-The list presented to the subjects included six emotions: pride, happiness, excitement, fear, sadness and anger.
 Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement respectively.
@@
 While moving the head down improved the identification of anger and sadness.
-However, these key poses are taken statically, without any displacement of the robot in the environment.
-
-%%%%%%%%%%%%%%%%%%%%%%
-Li and Chignell~\cite{Li2011} used a teddy bear robot capable to move its arms and head to study their contribution on emotion projection.
-To achieve this, they did a total of four studies.
-In the first one, four participants were asked to create a gesture that the robot would do in one of the twelve scenarios presented to them.
-These gestures were recorded and used in the second study.
-The experiment consisted of two parts: one just showing the gestures, and the second one describing a scenario were the gestures were generated.
-The participants had to select from a list the emotion that they thought the robot was conveying.
-The list included basic emotions and mental states, which were selected from the comments obtained during the first study.
-The results showed that giving a context increased the recognition rate.
-In the third experiment, they asked five novices and five puppeteers to create gestures for each of the six Ekman's basic emotions.
-The gestures generated were recorded and used as input in their last test, where the subjects had to select an emotion from a list including the names of the six basic Ekman's emotions.
-Their results showed that it is possible to convey emotions just using movements in the head and arms.
-Also they found out that the gestures made by the puppeteers had a better recognition for disgust and fear.
-Although they presented numerical information about their findings, this information is shown in a way that is not possible to discern the recognition rate of each emotion for each experiment.
 
@@
 This robot has head, ears, ability to generate colors in a RGB-LED set positioned in its chest, and a speaker system.
-The head had no capabilities to show facial expressions, but its movements and robot translations were used to show emotions.
 The emotions implemented were: happiness, sadness, fear, curiosity, disappointment, and embarrassment.
-During the experiments done by the researchers, special attention was put to the final distance between the robot and the subject, but the approaching velocity and the followed trajectory were not taken into consideration.
+During the experiments done by the researchers, special attention was put to the final distance between the robot and the subject.
 The subjects were exposed to a sequence of movements.
@@
 The enlisted emotions were the six implemented plus anger, disgust and surprise.
-Their results showed that participants gave a higher intensity to the desired emotion, also similar ones, such as sadness and disappointment.
+Their results showed that participants gave a higher intensity to the desired emotion, also when similar ones emotions were presented, such as sadness and disappointment.
 
@@
 These data were later reported to robot's embodiment.
-To verify their data, the researchers first did a pilot study with just two emotions (happiness and sadness) and thirteen subjects~\cite{Destephe2013}.
 Each subject was exposed to a series of videos.
-After each video, the subject was asked to select one emotion from a list (happiness, neutral, or sadness) and to state the intensity of the selected emotion.
+After each video, the subject was asked to select one emotion from a listand to state the intensity of the selected emotion.
 The videos showed were not made with the real robot, but with a virtual model of the robot.
-From the results obtained, they decided not to use the low intensity because it had a very low recognition rate.
-During the experiment they adopted the same procedure, emotion and its intensity, but this time showing all the emotions and intensities, excluding low, to the participants.
 Their results showed that sadness was recognized 73.81\% (average) of the times with an intensity of 21.43\%, happiness was recognized 66.67\% (average) of the times with an intensity of 30.95\%, anger was recognized 61.9\% of the times with an intensity of 26.19\%, and fear was recognized 83.33\% (average) of the times with an intensity of 28.58\%.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-Lakatos and Collaborators~\cite{Lakatos2014} take inspiration from human-animal interaction
-to create behaviours that could enrich human-robot interaction.
-They conducted an experiment to analyse the recognition rate of emotion expression, using as inspiration the movements done by dogs to convey emotions.
-The experiment was done using a Wizard-of-Oz scene and its goal was to determine if people could distinguish two emotions (happiness and fear).
-They use a game approach to determine participant's appraisal of the robot emotion.
-This was done in order to avoid asking the participants the emotion they believe the robot is eliciting.
-Therefore, in the experiment, each participant had two balls (yellow and black) and they could play with the robot using one of this balls at a time.
-However, one of the balls triggers robot's happiness and the other fear.
-The dog's favourite ball was changed from participant to participant to avoid any bias for the balls' color.
-The results of this experiment showed that the participants decided to use more dog's favourite ball to play with the dog, which is consistent with the idea that the participants could discern which ball produced ''happiness'' in the robot.
-
 %%%%%%%%%%%%%%%%% %
 Brown and Howard focused their interest on head and arm movements using the DARwIn-OP platform~\cite{Brown2014}.
-Their hypothesis was that using some principles, that they evaluated as important, it is possible to express happiness and sadness in a way that people could recognize.
-These principles establish that to show happiness is necessary to quiclkly move robot's head up and arms up.
-While to express sadness the head goes down, arms down, both slowly.
+Their hypothesis was that using some principles, that they determined as important, it is possible to express happiness and sadness in a way that people could recognize.
+These principles establish that to show happiness is necessary to move robot's head up, arms up, and it should be done fast.
+While to express sadness the head goes down, arms down, and it should be done slow.
 To test their hypothesis they conducted an experiment with thirteen participants.
@@
 They obtained a 95\%, 59\%, and 94\% of accuracy for happiness, neutral and sadness respectively.
-Although their results show that their key features are determinant to convey happiness and sadness.
 
@@
 The results show that it is possible to increase both valence and arousal by using a more indirect space, or by performing the motion more quickly, and to decrease valence or arousal by a more direct use of space, or a more sustained motion.
-Although they suggest the use of Laban's model as a tool to specify affection movements in Human-Robot Interaction, how to use these parameters in the actual implementation remains an open question, since Laban defined them qualitatively, with reference to human people, and they leave very open questions about the most appropriate numerical values to be used with robots.
+Although they suggest the use of Laban's description as a tool to specify affection movements in Human-Robot Interaction, how to use these parameters in the actual implementation remains an open question, since Laban defined them qualitatively, with reference to human people, and they leave very open questions about the most appropriate numerical values.
 
 %%%%%%%%%%%%%%%%%%%
-Suk and collaborators studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-human or animal like object~\cite{NAM2014}.
+Suk and e.t.
+studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-human or animal like object~\cite{NAM2014}.
 Two experiments were designed to determine the relationship among these features and the emotional interpretation.
@@
 In the second experiment they evaluated the other two features (granularity and volume) using the same procedure followed in the first experiment.
-Their results show that granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal.
+Their results show that granularity is positively correlated with pleasure and arousal.
+On the other volume is negatively correlated with pleasure and positively correlated with arousal.
 As overall result, they found a major contribution of speed on arousal and minor contribution of granularity and volume.
@@
 They did studies using a own built platform called E4 to verify whether people could detect emotions from a non-human like platform.
-The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design.
+The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design
+.
 In all their experiments they used six emotional expressions (scared, surprised, excited, angry, happy, sad) and neutral.
@@
 They obtained a recognition rate of 52\%, 42\%, 41\%, 36\% and 15\% for surprise, fear, sadness, happiness, and anger respectively.
-
-These works presented in this section provide guidance about features that could be exploited to project certain emotions.
-However, range of values to convey specific emotions will guide other researchers in what values could be used to convey their desire emotion or what values not to use because they could be misinterpreted as negative emotions.
-
-%TODO Maybe the table could summarize what presented.
-It would also be nice if you could say some words either at the end of each presentation or at the begining, so to justify why you have selected them and not others, and what they bring as important for your work.
-
-%%%%%%%%%%%%%%%%%%
-%Table~\ref{table:comparison_work_emotion_projection} summarizes all the robotics studies to convey emotion that we considered, highlighting the following characteristics:
-%\begin{itemize}
-%	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
-%	\item \textit{Platform used} gives the name of the platform used in the study;
-%	\item The\textit{Locomotion} criterion was added to put in evidence whether the platform uses displacement movement to express emotion;
-%	\item \textit{Emotion Evaluation Method} refers to the methodology used to collect the data in the studies.
-%	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
-%	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
-%	\item \textit{Type of test} tells if it was done an experiment or a case study.
-%	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The media considered were: movement, body posture and face poses.
-%\end{itemize}
-%\begin{table}[h]
-%\caption{Comparison among works on emotion projection in robotics. NA = Not Available}
-%\label{table:comparison_work_emotion_projection}
-%\begin{center}
-%\tiny %\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-%\begin{tabular}{|p{1.0 cm}|p{0.5 cm}|p{0.9 cm}|p{0.8 cm}|p{0.8 cm}|p{1.1 cm}|p{0.9 cm}|p{1.1 cm}|p{0.8 cm}|p{0.8 cm}|}
-%%\begin{tabular}{|p{1.5 cm}|p{1.0 cm}|p{1.5 cm}|p{1.5 cm}|p{1.5 cm}|p{2.0 cm}|p{1.5}|p{2.0 cm}|p{1.0 cm}|p{1.5 cm}|}
-%\hline 
-%\textbf{Work} & \textbf{Year} & \textbf{Embodiment} & \textbf{Platform Used} & \textbf{Locomotion} & \textbf{Emotion Evaluation Method} & \textbf{Emotion Presentation} & \textbf{Emotions Implemented} &  \textbf{Type of test} & \textbf{How is the emotion conveyed?}\\
-%\hline 
-%Breazeal~\cite{Breazeal2002} & 2002 & Face & Kismet & NA & Questionnaire & Video & Happiness, surprise, anger, disgust, fear, sadness and interest & Experiment & Face poses\\ 
-%\hline
-%Saerbeck and Christoph~\cite{Saerbeck2010} &2010& Animal/ Non-Human like& iCat / Roomba & NA / Differential &PANAS and SAM & Real Robot & NA & Experiment & Movement\\
-%\hline 
-%Ca\~namero and collaborators~\cite{Canamero2010,Beck2010}& 2010 &Human-Like & NAO & Bipedal & Questionnaire & Real robot & Anger, sadness, fear, pride, happiness, and excitement & Experiment & Body poses\\
-%\hline
-%Li and Chignell~\cite{Li2011}&2011&Animal-Like& Teddy Bear Robot& NA & Questionnaire & Video (Real robot) & Random + Anger, disgust, fear, happiness, sadness, and surprise & Experiment & Body poses\\
-%\hline
-%Barakova and collaborators~\cite{Barakova2013} & 2013 & NA & Closet robot& NA & SDO and SAM & Real robot & NA & Experiment & Changing lights on and intensity\\ 
-%\hline
-%Sharma and collaborators~\cite{Sharma2013}& 2013 & Non-Human/Animal & Quadrotor & Aerial & SAM + Questionnaire + Interview &  Real Robot & Laban's poles & Experiment & Movement\\
-%\hline
-%Destephe and collaborators~\cite{Destephe2013b}&2013&Human-like & WABIAN-2R & Bipedal & Questionnaire & Video (Virtual Robot) & Fear, anger, happiness, and sadness & Experiment & Movement (Gait)+Body Poses\\
-%\hline 
-%Embgen and collaborators~\cite{Arras2012} & 2014 & Human-like & Daryl &  Differential& Questionnaire & Real Robot & Happiness, sadness, fear, curiosity, embarrassment, and disappointment & Experiment & Movement + Body poses \\
-%\hline
-%Lakatos and Collaborators~\cite{Lakatos2014}& 2014 & Animal-Like & Dog & Holonomic & Indirect (Interaction with the robot) & Real Robot & Happiness and Fear & Experiment & Move + Body poses \\
-%\hline
-%Brown and Howard~\cite{Brown2014} & 2014& Human-Like & DARwIn-OP & Bipedal & Questionnaire & Real Robot & Happiness and sadness & Experiment & Body poses\\
-%\hline
-%Suk and collaborators ~\cite{NAM2014}& 2014 &  Non-Human/Animal & Self-made & NA & SAM & Real Robot & NA & Experiment & Speed, smoothness, granularity and volume\\
-%\hline
-%Novikova and Watss~\cite{Novika2015}& 2015&Non-Human/Animal & Lego & Differential& Questionnaire& Real Robot & Scared, surprise, excited, angry, neutral, happiness and sadness & Experiment& Movement + Poses\\
-%\hline 
-%\end{tabular} 
-%\end{center}
-%\end{table}

### 2016-09-25 HRI/Parts/System.tex
Changes in both articles.

@@
+The system used is divided in the platform and emotional enrichment system.
+
 \subsection{Robotic Platform}
+
+A non-anthropomorphic robotic platform without any bio-inspired appearance was developed and used in this case study.
+The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
+The platform could be observed in Figure~\ref{fig:Robot}
+
+\begin{figure}[t]
+\centering%
+\subfigure {\includegraphics[height=3cm]{./Images/DSC_0447.JPG}}
+\hspace{2mm}
+\subfigure{\includegraphics[height=3cm]{./Images/TriskarThird.png}}
+\caption{Platform used in the case study (left), and holonomics's blue prints (right). The arrows represent robot's frame of reference.
+\label{fig:Robot}}
+\end{figure}
+
 \subsection{Emotion Enrichment System}
+
+The main idea of Emotional Enrichment System (EES) is to blend an emotion and a action to produce an "emotional action".
+However this is not far as previous works have done so far.
+The system has been envisioned to also allow:
+
+\begin{itemize}
+	\item Interoperability among different platform.
+	\item Introduction of new parameters and emotions.
+	\item Interface with diverse action decision system.
+\end{itemize}
+
+In other words, the system could be thought as a box that receives a desire action, action's parameters and emotions to blend them together without paying particular attention who or how the decision to execute a particular action with specific parameters were made.
+This is achieved through the use of text messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.
+To change the emotion without affecting the action that is being executed, these information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity.
+
+Every time the system receives a new action, it verifies if the action exists and the parameters corresponds to the action.
+If these two conditions are met, then the system checks if the action is compound or simple.
+If it is a simple, the system proceeds to add all the required actions (emotive actions) and change their parameters to convey the desired emotion.
+On the other hand if the action is compound, the action is first decomposed in simple actions (mandatory actions).
+Each one of these actions is then process to add their emotive actions.
+However, this addition is done taking in consideration to not add any action that was previously added.
+Once all the set of simple actions and their parameters are determined, the system proceeds to verify the drivers' existence to execute these actions in the desired platform.
+If the system finds out that one or more mandatory actions could not be executed, it triggers a message to inform that the desire action could not be executed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Simple and Compound Actions}
+To achieve actions' enrichment with emotions, two different types of actions are used: simple and compound actions.
+Simple actions are actions that could be considered as ''atomic''; these actions can be enriched with emotion changing their specific parameters.
+For example, consider two simple actions: speak and move body.
+The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement.
+Therefore, for the speaking action the following parameters are expected: text, pitch and tone.
+On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints.
+Since each action is characterized by different parameters, the parameters' modifications to obtain an emotional action will be different for each of them.
+
+\subsubsection{Emotional Execution Tree}
+The \textit{Emotional Enrichment System}  is grounded on the use of \textit{Emotional Execution Tree} ($EXT$), which is a computational representation of actions desired actions that should be executed.
+$EXT$ is a connected acyclic graph with vertices and  edges.
+The root and non-leaf nodes could be \textit{parallel} or \textit{sequence} type.
+The parallel node could be one out of four different sub-types: action and emotion synchronous, action synchronous and emotion asynchronous, action asynchronous and emotion synchronous, or action and emotion asynchronous.
+Sequential nodes could just be one of two sub-types: emotion synchronous or asynchronous.
+Action synchronous means that each time that a parallel node receives a finish notification (success or failure), it will send a finish message to all the nodes that derived from it.
+On the other hand, emotion synchronous means that each time that a node (sequence or parallel) receives an emotion synchronization message, it will propagate the message to all the actions in the branches.
+This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action.
+Finally, the leaf nodes could only be simple action nodes.
+All the nodes can assume two levels: principal or secondary.
+If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary cannot propagate any message to its predecessor.
+
+\subsubsection{Implementation}
+Figure~\ref{fig:system_architecture} presents the design used to achieve the desire goals.
+As it could be observed, the system is divided in two parts.
+The first part in charge to enrich a given action with a desired emotion, and the second in charge to hide the real execution of the action.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=1.0\textwidth]{Images/SystemArchitecture.png} 	
+	\caption{General system design.
+Each simple action corresponds to one ROS node, and there is just one node for the emotion enrichment system.
+The ovals represent the ROS topic parameters, rectangles represent \textit{black boxes}, and texts outside containers represent input files that contain the system parametrization.}
+	\label{fig:system_architecture}
+\end{figure*}
+
+The process to enrich an action is threefold as follows:
+\begin{enumerate}
+
+	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received.
+The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described on the message.
+This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
+When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created.
+
+	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase.
+In this phase new $sa$ are added to the $ext$ and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
+This process is broken down in two steps.
+First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
+Second, the emotional parameters are modulated based on the emotion's intensity and character traits.
+
+	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
+The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
+In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.
+
+\end{enumerate}

### 2016-09-25 JournalIJSR/IJSR.tex
Changes in both articles.

@@
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[twocolumn]{svjour3}          % twocolumn
 %
@@
 \usepackage{breakcites}
+
 %
@@
 \institute{Julian M. Angel-Fernandez \at
-              Automation and Control Institute, Vienna University of Technology,\\ Vienna, Austria \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
+              Automation and Control Institute, Vienna University of Technology,\\ Karlsplatz 13, 1040 Vienna, Austria \\
+              Tel.: +43-158801\\
               \email{jangelfe@tuwien.ac.at}           %  \\
@@
               Andrea Bonarini, Dipartimento di Elettronica, Informazione e Bioingegneria,Politecnico di Milano,\\
-               Milan, Italy \\
+              Piazza Leonardo da Vinci 32, 20133 Milan, Italy \\
               \email{andrea.bonarini@polimi.it}

### 2016-09-26 HRI/Parts/Antecedents.tex
Small correction in the Antecedents, which is a description of the experiment, the system. There is still need work on the case study description.

@@
-An experiment was designed to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness, which correspond to four basic emotions suggested by Ekman~\cite{Ekman2001}.
-These features were selected after the study on emotion projection in robotics, humans and previous case studies.
-The robotic platform used in the experiment is holonomic, which are characterized by the possibility to move in any direction without the necessity to have a specific orientation, i.e., they are free to move taking any desired orientation.
-The experiment was performed at Politecnico di Milano, campus Leonardo during the months of June and July of 2015.
+An experiment was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness, which correspond to four basic emotions suggested by Ekman~\cite{Ekman2001}.
+These features were selected after study emotion projection in robotics, humans (i.e.
+previous work and theatre) and previous case studies.
+The robotic platform used in the experiment is holonomic, which are characterized by the possibility to move in any direction without necessity to have a specific orientation, i.e., they are free to move taking any desired orientation.
+The experiment was performed at the university campus during the months of June and July of 2015.
 A total of 49 volunteers were involved: 12 female and 37 male.
@@
 
-For each table were calculated the mean, standard deviation, and median.
-It was not possible to use  ANOVA test over the data because the assumption of normality is not achieved in the collected data.
+A Google form was used to collect participants' answers.
+The form included the four emotions plus two mental states (i.e.
+excitement and tenderness) and option ''other''.
+These mental state were added to see if people could confuse the desired emotion with them.
+Each participant was exposed to twenty over one hundred and ninety five possible treatments.
+The whole process, including a brief explanation and assessment lasted  from 10 to 15 minutes.
+This was decided because each subject was a volunteer and would not perceive any monetary remuneration, so the time dedicated to the experiment had to be kept limited.
+The twenty treatments were selected picking a number without replacement from 1 to 195.
+For each presented treatment, participants were asked to give an intensity perceived for each option in the form.
+
+After collecting all the data, it was created a table for each treatment.
+Each table contain the following information mean, standard deviation, and median.
+ANOVA test was not possible to be used over the data because the assumption of normality is not achieved in the collected data.
 This was check using the Shapiro-Wilk Test.
-Additionally, a contingency table for each emotion was generated in each treatment as it is depicted in  Table~\ref{table:table_contingency},  where the intensity for the other emotions is calculated as the mean of them, including the option of ''other''.
+Additional to these table, a contingency table for each emotion was generated in each treatment as it is depicted in  Table~\ref{table:table_contingency},  where the intensity for the other emotions is calculated as the mean of them, including the option of ''other''.
 For all tables, including the contingency, were calculated the Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$), which is a reliability coefficient to measure the agreement among different participants.

### 2016-09-26 HRI/Parts/CaseStudy.tex
Changes in both articles.
Small correction in the Antecedents, which is a description of the experiment, the system. There is still need work on the case study description.

@@
-The case study was done at Researcher's Night 2014 with two main objectives (i) cross-validate the findings obtained from the experiment, and (ii) use the Emotional Enrichment System to verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
+The case study was done at Researcher's Night 2015 with two main objectives (i) cross-validate the findings obtained from the experiment, and (ii) use the Emotional Enrichment System to verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
 
@@
 This case study uses the results obtained in the experiment and was designed to have two parts (i) emotion expression through changes in linear velocity, angular velocity, oscillation angle, orientation and direction.
-%Figure~\ref{fig:example_movements} presents an example of these variables. 
 (ii) Presentation of a small scene to verify whether the participants would prefer scenes when the robot shows emotions or not.
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 		\label{table:selected_fourth}
-		\begin{tabular}{|c|c|c|c|c|c|c|}
+		\begin{tabular}{|c|p{0.9 cm}|p{0.9 cm}|p{0.9 cm}|p{1.05 cm}|p{0.9 cm}|}
 			\hline
-\rotatebox{90}{\textbf{Emotion } }&
-\rotatebox{90}{\textbf{Direction  ($rad$)}}&
-\rotatebox{90}{\textbf{Orientation ($rad$)} }&
-\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
-\rotatebox{90}{\textbf{Angular Velocity ($rad/s$) }}&
-\rotatebox{90}{\textbf{Angle ($rad$)}}&
-\rotatebox{90}{\textbf{Treatment ID}}\\	
+%\rotatebox{90}{\textbf{Emotion } }&
+%\rotatebox{90}{\textbf{Direction  ($rad$)}}&
+%\rotatebox{90}{\textbf{Orientation ($rad$)} }&
+%\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
+%\rotatebox{90}{\textbf{Angular Velocity ($rad/s$) }}&
+%\rotatebox{90}{\textbf{Angle ($rad$)}}\\	
+\textbf{Emotion}&\textbf{Direc-tion  ($rad$)} & \textbf{Orien-tation ($rad$)} & \textbf{Linear Velocity ($mm/s$) } & \textbf{Angular Velocity ($rad/s$) } & \textbf{Angle ($rad$)} \\
 			\hline
-			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&29\\
-			\cline{2-7}
-			&$0$&$0$&$900$&$3$&$0.174$&38\\
+			Happiness 1&$0$&$0$&$500$&$3$&$0.349$\\
 			\hline
-			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&144\\
-			\cline{2-7}
-			&$0$&$0$&$900$&$1$&$0.087$&31\\
+			Happiness 2&$0$&$0$&$900$&$3$&$0.174$\\
 			\hline
-			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&113\\
-			\cline{2-7}
-			&$\pi$&$\pi$&$500$&$2$&$0.087$&102\\
+			Anger 1&$\pi$&$0$&$500$&$3$&$0.087$\\
 			\hline
-			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&130\\
-			\cline{2-7}
-			&$0$&$\pi$&$200$&$1$&$0.349$&52\\
+			Anger 2&$0$&$0$&$900$&$1$&$0.087$\\
+			\hline
+			Fear 1&$\pi$&$\pi$&$900$&$2$&$0.174$\\
+			\hline
+			Fear 2&$\pi$&$\pi$&$500$&$2$&$0.087$\\
+			\hline
+			Sadness 1&$\pi$&$0$&$200$&$1$&$0.349$\\
+			\hline
+			Sadness 1&$0$&$\pi$&$200$&$1$&$0.349$\\
 			\hline
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{./Images/fourthCaseSceneD.png} 
+	\includegraphics[width=0.85\textwidth]{./Images/fourthCaseSceneD.png} 
 	\caption{Sequence of movements done by the robot.

### 2016-09-26 HRI/Parts/System.tex
Small correction in the Antecedents, which is a description of the experiment, the system. There is still need work on the case study description.

@@
-The system used is divided in the platform and emotional enrichment system.
+The same system used in the experiment was used in the case study presented in this paper and they are explained in the following subsection.
 
@@
 
-A non-anthropomorphic robotic platform without any bio-inspired appearance was developed and used in this case study.
+The non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance.
 The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
-The platform could be observed in Figure~\ref{fig:Robot}
+The platform could be observed in Figure~\ref{fig:Robot}.
+The Arduino Due is in charge to be the interface between the hardware (e.g.
+motors) and Odroid, which host all the emotion enrichment system.
 
@@
 However this is not far as previous works have done so far.
-The system has been envisioned to also allow:
+Therefore, the system has been envisioned to also allow:
 
@@
 
-In other words, the system could be thought as a box that receives a desire action, action's parameters and emotions to blend them together without paying particular attention who or how the decision to execute a particular action with specific parameters were made.
-This is achieved through the use of text messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.
-To change the emotion without affecting the action that is being executed, these information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity.
+In other words, the system could be thought as a box that receives a desire action, action's parameters and emotion to blend them together without paying particular attention on who or how the decision to execute a the particular action was made.
+This is achieved through the use of messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.
+These information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity.
+This is done to do not affect the action's execution.
 
@@
 \subsubsection{Simple and Compound Actions}
+
 To achieve actions' enrichment with emotions, two different types of actions are used: simple and compound actions.
@@
 Since each action is characterized by different parameters, the parameters' modifications to obtain an emotional action will be different for each of them.
+On the other hand, compound action is an action created from other compound or simple actions.
+For example, suppose that it is required that the robot has to \textit{recite} some dialogue and \textit{walk} to a different position, as doing a trajectory.
+A possible implementation could consist on speak simple action in parallel to two consecutive action walk, which is also a compound action that is composed by three parallel actions: balance left arm, balance right arm, and move body.
+
+Although compound actions could be used to generate diversity of actions from simple actions, the main drawback of this approach is that all possible combination of actions should code in the system to be used.
+Using the example previously described, if it is decided to have three positions instead of two, then it would mean that a new compound action should be implemented to have an action in which could be specified three positions.
+To overcome this limitation, it was created a language to specify actions that are not implemented in the system.
+A computational representation of these language is used to execute the actions described in this language.
 
 \subsubsection{Emotional Execution Tree}
-The \textit{Emotional Enrichment System}  is grounded on the use of \textit{Emotional Execution Tree} ($EXT$), which is a computational representation of actions desired actions that should be executed.
+The \textit{Emotional Enrichment System}  is grounded on the use of \textit{Emotional Execution Tree} ($EXT$), which is a computational representation of desired actions that must be executed. 
 $EXT$ is a connected acyclic graph with vertices and  edges.
@@
 
-The process to enrich an action is threefold as follows:
+The action enrichment is achieved through the following phases:
 \begin{enumerate}
@@
 	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received.
-The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described on the message.
-This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
+The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described in the message.
+This parameters' verification is done on the implemented description for each simple action, which describes the parameters that are mandatory and those that are optional.
 When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created.
@@
 	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase.
-In this phase new $sa$ are added to the $ext$ and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
+In this phase new simple actions are added to the $ext$ and the simple action's parameters are modified following the emotion description, which is loaded from files.
 This process is broken down in two steps.
-First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
+First, all actions that are required to convey the desired emotion, and that are not yet present in the branch are added.
 Second, the emotional parameters are modulated based on the emotion's intensity and character traits.

### 2016-10-04 HRI/Parts/CaseStudy.tex
Changes in the HRI article

@@
 The case study was done at Researcher's Night 2015 with two main objectives (i) cross-validate the findings obtained from the experiment, and (ii) use the Emotional Enrichment System to verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
-
-\subsection{Design and Setup}
-
-This case study uses the results obtained in the experiment and was designed to have two parts (i) emotion expression through changes in linear velocity, angular velocity, oscillation angle, orientation and direction.
-(ii) Presentation of a small scene to verify whether the participants would prefer scenes when the robot shows emotions or not.
-the Emotional Enrichment System was used in both cases (with and without emotions).
-Two web-cams and eight Alvar tags were added to use Kalman filter to improve robots localization in the stage.
-The detection of the AR tags is done through the use of the ROS package ar\_track\_alvar~\cite{artag2015}.
+The Emotional Enrichment System was used in both cases.
+To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage.
+The detection of the AR tags was done through the use of the ROS package ar\_track\_alvar~\cite{artag2015}.
 The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.
@@
 
-\subsubsection{Emotion Description}
+\subsection{Emotion Description}
 
-The parameters selected for each of the four emotions (\textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) are shown in Table~\ref{table:selected_fourth}.
+The parameters selected for each of four emotions (\textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) are shown in Table~\ref{table:selected_fourth}.
 The main considerations to select the two implementations for each emotion were: (i) the linear velocity should be greater than $0$.
@@
 
-\subsubsection{Scene}
-%TODO change this part of the text and give some information about this, and  motivate its use, which bassically is to verify the emotional enrichment system
-As it was already mentioned, actors should adapt to different circumstances during the performance.
-Following this approach, the stage was discretized in 9x9 matrix as is shown in Figure~\ref{fig:stage_division}.
-Thus, the movements of the robot are given in terms of the matrix positions.
-This allows the adaptation to different stage dimensions because the robot's final position is calculated by the Emotional Enrichment System during execution taken under consideration the stage dimensions.
+\subsection{Scene}
+
+Stage discretization was used to give zones of movements instead of absolute positions.
+This idea was brought from human theatrical actors, who prepared their movements based on zones on the stage~\cite{wilson2009theatre}.
+This allows them to adapt their position based on other actors.
+Therefore, the stage was discretized in 9x9 matrix as is shown in Figure~\ref{fig:stage_division}.
+Robot's movements are given in terms of the matrix positions to the Emotional Enrichment System.
+This allows the adaptation to different stage dimensions because robot's final position is calculated by the Emotional Enrichment System during execution, which takes under consideration the stage dimensions given.
 For instance, during the scene's preparation in the laboratory the stage was 3 meters per 3 meters, but in the final presentation the stage was 2.5 meters per 2.5 meters.
@@
 \end{figure}
-%TODO Change this paragraph and motivate the reason this is important and instead of puting the figures, write the references to those figures
-The scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (Figure~\ref{fig:StageDirections}), close to the right wing.
-Then, the robot moves to upstage right center and rotates by $\pi/2$ left (Figure~\ref{fig:BodyPosition}).
+
+The scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
+Then, the robot moves to upstage right center and rotates by $\pi/2$ left (See~\cite{Artopia}).
 Next the robot moves to the right center to then go to the center.
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{./Images/fourthCaseSceneD.png} 
+	\includegraphics[width=0.95\textwidth]{./Images/fourthCaseSceneD.png} 
 	\caption{Sequence of movements done by the robot.
@@
 Movement eleven depicts happiness, and the remaining movements depict sadness.
-The two scenes are executed by the Emotional Enrichment System using the same ''script'' and the emotion selection is done manually via graphical interface (Figure~\ref{fig:graphical_interface}).The ''script'' were written in JSON using the language described in the Section~\ref{}.
+The two scenes are executed by the Emotional Enrichment System using the same ''script'' and the emotion selection is done manually via graphical interface (Figure~\ref{fig:graphical_interface}).
 
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{./Images/InterfaceExperiment.png} 
+	\includegraphics[width=0.48\textwidth]{./Images/InterfaceExperiment.png} 
 	\caption{Graphical interface used to communicate with the Emotional Enrichment System.

### 2016-10-04 HRI/Parts/Conclusions.tex
Changes in the HRI article

@@
-The case study presented in this chapter was done to cross validate the findings in the experiment.
-For each one of the four emotions studied in the experiment were selected two set of parameters.
+The case study presented in this paper was done to cross validate the findings in the experiment and verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
+For each one of four emotions (i.e.
+Anger, Happiness, Sadness and Fear) studied in the experiment were selected a two set of parameters.
+These parameters were described in files and used as input to the Enrichment Emotional System, which was in charge to combine actions with emotions.
 The results show that both implementations of happiness were confused with anger and excitement, while one implementation of anger was just confused with excitement.
@@
 Both implementations of fear had a recognition rate over 50\%.
-Additionally to the cross validation, it was done a small scene to check if people have preference to scenes where emotional movements are presented or not.
-The results show that people prefer scenes with emotional movements.
+Scene's results show that people prefer scenes with emotional movements and there is not any difference in gender.
+
+Additionally to the results already mentioned, there are words that could bias participants' perception.
+For instance happiness and anger were considered as excitement.
+This misinterpretation should not be a surprise given the fact that there is not a unique definition of emotion~\cite{Plutchik2001,cacioppo2000handbook}, and each person would interpret a situation differently, so they will give a different label to the presented movement.
+Moreover a misinterpretation of Happiness and Anger could suggest that additional features (e.g.
+trajectory or shape) should be added to increase differentiation between these two emotions.
+For example, Venture and collaborators~\cite{Venture2014} had found out that in human bodies the recognition rate of anger and fear are increased when torso and head are downwards.
+On the other hand, they found that happiness perception is increased when the torso and head are move upwards.
+This example could bring some insight to possible body changes that could occur in non-human like bodies, but it should tested in this kind of platforms to confirm if the same impact is reached.

### 2016-10-04 HRI/Parts/Introduction.tex
Changes in the HRI article

Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}. Many psychological studies have been focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states. This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been used to convey emotions.
However in many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}, for instance in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

It has been noticed that the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those exploiting anthropomorphic features. Moreover, these works do not give specific range of values for the characteristics used to expressed  emotions implemented. For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature,  but their connection to specific emotions is not explicited. Rather, they establish a relationship between their values and pleasure/arousal dimensions. This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristics to avoid  misinterpretation with wrong emotions. These values could be used in social robotics to show emotions and as consequence increase their acceptance.

This paper is organized as follows. Section~\ref{sec:related_work} introduce some previous works done in conveying emotion. Then the experiment is briefly described in section~\ref{sec:experiment}. Section~\ref{sec:system} presents the platform used in the case study and the Emotional Enrichment System. Finally, sections~\ref{sec:case} and~\ref{sec:results} presented case study's design and results.

### 2016-10-04 HRI/Parts/RelatedWork.tex
Changes in the HRI article

@@
-The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused also on faces.
+A direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused also on faces.
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
@@
 In this experiment, each participant was asked to look at seven videos, one for each implemented emotion.
-After a video was projected, each participant selected the emotion from a list containing  the seven implemented emotions, only.
+After a video was projected, each participant selected a emotion from a list, which contained seven implemented emotions.
 The results showed high percentage of recognition (over 57\%).
@@
 They first did a literature review to select characteristics that could be used to show affection.
-From their literature review, they decided to use acceleration and curvature on robot's trajectory.
+From their review, they decided to use acceleration and curvature on robot's trajectory.
 Using these two characteristics, they did an experiment with eighteen participants.
@@
 Ca\~namero and collaborators~\cite{Canamero2010,Beck2010} studied the perception of key body poses designed to show emotions using a NAO~\cite{NAO2013}.
-They suggested that the techniques used to convey emotions in virtual characters could not be used in robots, due to the fact that virtual characters have no physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007, Canamero2010}.
-They proposed a set of poses that could be used to express emotions with NAO, paying a particular attention to the contribution of the head.
+They suggested that techniques used to convey emotions in virtual characters could not be used in robots, due to the fact that virtual characters have no physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007, Canamero2010}.
+They proposed a set of poses that could be used to express emotions with a NAO, paying a particular attention to head's contribution.
 Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement respectively.
@@
 Using the platform WABIAN-2R, Destephe and collaborators~\cite{Destephe2013b} studied the attribution of emotion to a robot's gait.
-To obtain the robot's movements, the researchers asked two professional actors to walk in a room conveying anger, happiness, sadness, and fear with different intensities (low, regular, normal, high, and exaggerated).
+To obtain  robot's movements, the researchers asked two professional actors to walk in a room conveying anger, happiness, sadness, and fear with different intensities (low, regular, normal, high, and exaggerated).
 All the actors' walking were recorded using a Cortex motion capture system.
@@
 Each subject was exposed to a series of videos.
-After each video, the subject was asked to select one emotion from a listand to state the intensity of the selected emotion.
+After each video, the subject was asked to select one emotion from a list and state the intensity of the selected emotion.
 The videos showed were not made with the real robot, but with a virtual model of the robot.
@@
 %%%%%%%%%%%%%%%%% %
-Brown and Howard focused their interest on head and arm movements using the DARwIn-OP platform~\cite{Brown2014}.
+Brown and Howard focused their interest on head and arm movements using a DARwIn-OP platform~\cite{Brown2014}.
 Their hypothesis was that using some principles, that they determined as important, it is possible to express happiness and sadness in a way that people could recognize.
@@
 They did studies using a own built platform called E4 to verify whether people could detect emotions from a non-human like platform.
-The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design
-.
+The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design.
 In all their experiments they used six emotional expressions (scared, surprised, excited, angry, happy, sad) and neutral.

### 2016-10-04 HRI/Parts/Results.tex
Changes in both articles.
Changes in the HRI article

@@
-Table~\ref{table:result_fourth} summarizes the results obtained during the case study. 
-\begin{table*}
+Table~\ref{table:result_fourth} summarizes results obtained during the case study. 
+\begin{table}[h]
 \centering
@@
 		\label{table:result_fourth}
-		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+		\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 			\hline
-			&\multicolumn{5}{|c|}{\textbf{Features}}&\multicolumn{7}{c|}{\textbf{Emotions}}&\\
-			\cline{2-13}
 \rotatebox{90}{\textbf{Presented/Reported } }&
-\rotatebox{90}{\textbf{Direction  ($rad$)}}&
-\rotatebox{90}{\textbf{Orientation ($rad$)} }&
-\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
-\rotatebox{90}{\textbf{Angular Velocity ($rad/s$) }}&
-\rotatebox{90}{\textbf{Angle ($rad$)}}&
 \rotatebox{90}{\textbf{Happiness}}&
@@
 			\hline
-			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&8&16&7&4&16&4&7&62\\
-			\cline{2-14}
-			&$0$&$0$&$900$&$3$&$0.174$&11&11&6&2&19&3&1&53\\
+			Happiness 1&8&16&7&4&16&4&7&62\\
 			\hline
-			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&7&5&6&2&21&7&1&49\\
-			\cline{2-14}
-			&$0$&$0$&$900$&$1$&$0.087$&14&29&13&2&13&3&2&76\\
+			Happiness 2&11&11&6&2&19&3&1&53\\
 			\hline
-			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&6&2&28&1&9&6&0&52\\
-			\cline{2-14}
-			&$\pi$&$\pi$&$500$&$2$&$0.087$&7&3&37&2&20&4&1&74\\
+			Anger 1&7&5&6&2&21&7&1&49\\
 			\hline
-			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&3&5&17&14&5&16&5&65\\
-			\cline{2-14}
-			&$0$&$\pi$&$200$&$1$&$0.349$&5&5&15&28&6&15&7&81\\
+			Anger 2&14&29&13&2&13&3&2&76\\
+			\hline
+			Fear 1&6&2&28&1&9&6&0&52\\
+			\hline
+			Fear 2&7&3&37&2&20&4&1&74\\
+			\hline
+			Sadness 1&3&5&17&14&5&16&5&65\\
+			\hline
+			Sadness 2&5&5&15&28&6&15&7&81\\
 			\hline
 			\end{tabular}
-\end{table*}
+\end{table}
 
-It could be observed that the two implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}.
-In a similar way, the first implementation of \textit{Anger} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects that were exposed to the first implementation of \textit{Anger}.
+It could be observed that two implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}.
+In a similar way, the first implementation of \textit{Anger} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
 The second implementation of \textit{Anger} showed an improvement of perception from 10\% to 38\%. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
@@
 
-To verify these misinterpretations among the implemented emotions, a Fisher's exact test was applied for ten different combinations.
+To verify these misinterpretations among implemented emotions, a Fisher's exact test was applied for ten different combinations.
 Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation.
 The results are shown in Table~\ref{table:result_compare_fourth}.
-As this analysis suggest, the two implementation of \textit{Anger} were perceived as two different emotions.
-Also shows that the two implementation of Happiness were perceived to be similar to the second implementation of Anger.
+As this analysis suggest, two implementation of \textit{Anger} were perceived as two different emotions.
+Also shows that two implementation of Happiness were perceived to be similar to the second implementation of Anger.
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 
-An analysis was done for each emotion, therefore it was created a contingency matrix such as was done in the previous studies.
-For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed.
+A contingency matrix was created for each emotion to analysi each one.
+For each table the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed.
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that second implementation of \textit{Anger}, both of \textit{Fear} and \textit{Sadness} have an impact in the perception of the emotion and they are considered as different implementation respect the rest of implementations.
+They show that there is significant evidence to conclude that second implementation of \textit{Anger}, both of \textit{Fear} and \textit{Sadness} have an impact in the perception of the emotion and they are considered as different implementation respect other implementations.
 While both implementation of \textit{Happiness} and first of \textit{Anger} are considered as similar to the other implementation.
@@
 \clearpage
-\begin{table*}
+\begin{table}[h]
 \centering
+\small
 \caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the case study.} 
 \label{table:Precision2}
-		\begin{tabular}{|p{3 cm}|p{2 cm}|c|c|c|}
+		\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|c|c|}
 		\hline
@@
 			\end{tabular}
-\end{table*}
+\end{table}
 
  For each of the contingency tables the classification accuracy and the no-information rate (NIR), i.e.
-the accuracy that had been obtained by random selection, are reported in table~\ref{table:nir}.
-The results reveal that the only implementation with enough statistical evidence is the second implementation of \textit{Sadness}.
+the accuracy that had been obtained by random selection, are reported in table~\ref{table:nir_fourth}.
+The results reveal that only implementation with enough statistical evidence is \textit{Sadness}' second implementation.
 Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape.
 Another important factor to highlight is the impact words enlisted in the questionnaire have on the perception rate.
-As it was expected in the experiment, \textit{Excitement} and \textit{Tenderness} were confused with other emotions with similar arousal level.
-In this precise case the emotions Anger and Happiness were confused with Excitement, and Sadness and Fear emotions were confused with Tenderness.
-Despite the bias generated by the two mental states enlisted in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
+As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level.
+In this precise case the emotions Anger, Happiness and Fear were confused with Excitement, and Sadness was confused with Tenderness.
+Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
 
-\begin{table*}
+\begin{table}[h]
 \centering
+\small
 		\caption{Classification accuracy of the presented emotions by the single panels, computed as mentioned in the text, with corresponding 95\% confidence interval, no-information rate, and p-value that accuracy is greater than the NIR.}
 		\label{table:nir_fourth}
-			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+			\begin{tabular}{|p{1.8 cm}|c|c|c|c|}
 				\hline		
-	& \multicolumn{5}{|c|}{\textbf{Features}} & & & &\\
-\cline{2-6}				
 \rotatebox{90}{\textbf{Presented Emotion}}&
-\rotatebox{90}{\textbf{Direction  ($rad$)}}&
-\rotatebox{90}{\textbf{Orientation ($rad$) }}&
-\rotatebox{90}{\textbf{Linear Velocity ($mm/s$) }}&
-\rotatebox{90}{\textbf{Angular Velocity ($rad/s$)} }&
-\rotatebox{90}{\textbf{Angle ($rad$)}}&
 \rotatebox{90}{\textbf{Classification Accuracy}}&
@@
 				\hline
-			\multirow{2}{*}{Happiness}&$0$&$0$&$500$&$3$&$0.349$&0.79&(0.75,0.82)&0.89&1.0\\
-			\cline{2-10}
-			&$0$&$0$&$900$&$3$&$0.174$&0.81&(0.77,0.84)&0.88&1.0\\
+			Happiness 1&0.79&(0.75,0.82)&0.89&1.0\\
 			\hline
-			\multirow{2}{*}{Anger}&$\pi$&$0$&$500$&$3$&$0.087$&0.8&(0.76,0.83)&0.88&1.0\\
-			\cline{2-10}
-			&$0$&$0$&$900$&$1$&$0.087$&0.89&(0.76,0.84)&0.83&0.95\\
+			Happiness 2&0.81&(0.77,0.84)&0.88&1.0\\
 			\hline
-			\multirow{2}{*}{Fear}&$\pi$&$\pi$&$900$&$2$&$0.174$&0.79&(0.75,0.83)&0.88&1\\
-			\cline{2-10}
-			&$\pi$&$\pi$&$500$&$2$&$0.087$&0.78&(0.73,0.81)&0.83&0.99\\
+			Anger 1&0.8&(0.76,0.83)&0.88&1.0\\
 			\hline
-			\multirow{2}{*}{Sadness}&$\pi$&$0$&$200$&$1$&$0.349$&0.85&(0.81,0.88)&0.84&0.47\\
-			\cline{2-10}
-			&$0$&$\pi$&$200$&$1$&$0.349$&0.85&(0.81,0.88)&0.81&0.035\\
+			Anger 2&0.89&(0.76,0.84)&0.83&0.95\\
+			\hline
+			Fear 1&0.79&(0.75,0.83)&0.88&1\\
+			\hline
+			Fear 2&0.78&(0.73,0.81)&0.83&0.99\\
+			\hline
+			Sadness 1&0.85&(0.81,0.88)&0.84&0.47\\
+			\hline
+			Sadness 2&0.85&(0.81,0.88)&0.81&0.035\\
 			\hline
 			\end{tabular}
-\end{table*}
+\end{table}
 
@@
 Second, that it does not block the execution of an action when an emotion is changed.
-\begin{table}
+\begin{table}[h]
 \centering

### 2016-10-08 JournalIJSR/IJSR.tex
Add files via upload

@@
 \begin{abstract}
-Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that cannot have a humanoid shape, and still have to be accepted by humans.
-As a consequence other characteristics should be exploited to support robot acceptance.
-This paper presents an experiment made to understand the contribution of angular and linear velocity of a non-anthropomorphic robot, its body orientation, and movement direction on humans' perception of emotion.
-A top 10 table was created for each enlisted emotion using alpha agreement for the whole treatment and for the desired emotion.
-These results suggest values that could guide implementation of the studied emotions in this experiment in other social robots.
+Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that cannot have a humanoid shape, and still have to interact with humans.
+As a consequence,  features not related with shape should be exploited to support robot acceptance.
+This paper presents an experiment made to understand the contribution to humans' perception of emotion of angular and linear velocity, body orientation, and movement direction of a non-anthropomorphic robot.
+A top 10 table of feature values combination was created for each enlisted emotion using alpha agreement for the whole treatment and for the desired emotion.
+The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
 \keywords{Robot-Human Interaction \and Emotion Projection}
@@
 \input{./Parts/Platform}
-\section{Experiment's Design}
+\section{Experimental Design}
 \label{sec:experiment}
 \input{./Parts/ExperimentDesign}
-\section{Study}
-\label{sec:study}
-\input{./Parts/Study}
 \section{Results}

### 2016-10-08 JournalIJSR/Parts/Conclusion.tex
Add files via upload

@@
 This paper presented an experiment made to understand the contribution of angular and linear velocity, body's orientation, and movement direction on humans' perception of emotion expression by a non-anthropomorphic platform.
-The emotions covered in this experiment correspond to four of those enlisted by Ekman~\cite{Ekman2001} as basic emotions: anger, happiness, fear and sadness.
+The emotions covered in this experiment correspond to four of the ones enlisted by Ekman~\cite{Ekman2001} as basic emotions: anger, happiness, fear and sadness.
 To study the contribution of the desired features, a non-anthropomorphic, holonomic platform was used.
@@
 The values obtained in this experiment could be used to express emotions in non-anthropomorphic platforms.
-It is still needed to cross validate the values and to determine what values from the top ten could be used more "accurately" to express the desired emotion.
+It is still needed to cross validate the values and to determine what values from the top ten could more accurately express the desired emotion.
 It is important to mention that is not expected to have a 100\% of correct emotion recognition by the participants.

### 2016-10-08 JournalIJSR/Parts/Emotion_Projection.tex
Add files via upload

@@
 As a consequence, many works have focused on facial expression, mainly, but not only, influenced by the work done by Ekman~\cite{Ekman2004}.
-Fortunately, the role that body plays in emotions projection has been recognized and has started to be studied~\cite{Gelder2008,Wallboot1998}.
-Nevertheless, the amount of works related to body expression of emotions is still small compared to studies on facial expression.
+However, the role that body plays in emotion projection was recognized, too, and started to be studied~\cite{Gelder2008,Wallboot1998}.
+Nevertheless, the amount of works related to body expression of emotions is still small compared to studies about facial expression.
 
@@
 Applying a first methodology, human actors (either professionals, or amateurs) are asked to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}.
-Each trial is recorded and later shown to each subject, who evaluates all the sequences.
+Each trial is recorded and later shown to each subjects that have to classify all the sequences.
 The second methodology uses virtual agents~\cite{Roether2009,Venture2014} to generate the very same set up for the experiments; the agent's movements are generated from the data recorded from human actors.
 
-The work done by Wallboot~\cite{Wallboot1998} has been used as a referenced by others.
-His work addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
+The work done by Wallboot~\cite{Wallboot1998} has been used as a reference by others.
+It addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
 His results reaffirm that movement and body postures are indicative of intensity for some emotions, while, for other emotions, these two characteristics seem to be enough to identify them.
+%TODO I cannot understand: do you mean that in the later case movement and body postures could only be used for identification, but not for detecting the intensity?
+The sentence is not clear.
 
@@
 All the participants were exposed to all 528 images and were asked to label the image with the emotions that best represent it.
-Their results show that five out of six emotions were quite weel recognized independently from the angle of view.
-However, disgust was in some postures confused with fear.
+Their results show that five out of six emotions were quite well recognized independently from the angle of view., while disgust was for some postures confused with fear.
 
 The main drawback of all these projects is the use of video recorded sequences, which misses the impact related to a complete physical experience.
+For instance, it is clearly different facing an angry robot really rushing against us, or looking at a video where this happens.
 
@@
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
-The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}) plus \textit{interest}.
+The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}), plus \textit{interest}.
+%TODO Let's have a common code: if emotions are in italic, they have o be so in all the paper.
+If they are not, italic should disappear here and wherever it has been used.
 The face's physical design was done so to invite humans to treat it as if it was a social creature.
@@
 After a video was projected, each participant selected the emotion from a list containing  the seven implemented emotions, only.
-The results showed a percentage of recognition over 57\%.
+The results showed a percentage of recognition of about 57\%.
 
@@
 While for the iCat two objects were place in front of it.
-It starts in a central position to then move to the left  right and back to center.
+It starts in a central position to then move to the left, right, and back to center.
 To reduce variables' possibilities, they picked three definite values for each variable.
@@
 Their results show that there was no significant difference between the two embodiments used and that participants were able to assign different emotions to the movement patterns shown to them.
-More importantly, they found out that acceleration is correlated with the perceived arousal but not with valence.
+More importantly, they found out that acceleration was correlated with the perceived arousal, but not with valence.
 
@@
 Their results suggest that people prefer systems that display submissive behaviors.
-More importantly, their findings suggest that electronic systems can elicit a type of reactions different from the one expected on theories of interpersonal communication.
+More importantly, their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
 
@@
 The list presented to the subjects included six emotions: pride, happiness, excitement, fear, sadness and anger.
-Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement respectively.
+Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement, respectively.
 The major finding from their experiments is that moving the head up improved the identification of pride, happiness, and excitement.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Li and Chignell~\cite{Li2011} used a teddy bear robot capable to move its arms and head to study their contribution on emotion projection.
+Li and Chignell~\cite{Li2011} used a teddy bear robot capable to move its arms and head to study the contribution of these movements to emotion projection.
 To achieve this, they did a total of four studies.
@@
 In the third experiment, they asked five novices and five puppeteers to create gestures for each of the six Ekman's basic emotions.
-The gestures generated were recorded and used as input in their last test, where the subjects had to select an emotion from a list including the names of the six basic Ekman's emotions.
-Their results showed that it is possible to convey emotions just using movements in the head and arms.
+The generated gestures were recorded and used as input in their last test, where the subjects had to select an emotion from a list including the names of the six basic Ekman's emotions.
+Their results showed that it is possible to convey emotions just using movements of head and arms.
 Also they found out that the gestures made by the puppeteers had a better recognition for disgust and fear.
@@
 Daryl~\cite{Arras2012} is an anthropomorphic robot, without facial expression, nor limbs, but with mobility capabilities.
-This platform was used to test whether it is possible to project emotions without using cues used in a human-like platform (e.g., tail, ears and head).
+This platform was used to test whether it is possible to project emotions without using cues used in a human-like platform (e.g., tail, ears, and head).
 This robot has head, ears, ability to generate colors in a RGB-LED set positioned in its chest, and a speaker system.
@@
 The enlisted emotions were the six implemented plus anger, disgust and surprise.
-Their results showed that participants gave a higher intensity to the desired emotion, also similar ones, such as sadness and disappointment.
+Their results showed that participants gave a higher intensity to the desired emotion, but also to similar ones, such as in the case of sadness and disappointment.
 
@@
 All the actors' walking were recorded using a Cortex motion capture system.
-These data were later reported to robot's embodiment.
+These data were then reported to robot's embodiment.
 To verify their data, the researchers first did a pilot study with just two emotions (happiness and sadness) and thirteen subjects~\cite{Destephe2013}.
@@
 After each video, the subject was asked to select one emotion from a list (happiness, neutral, or sadness) and to state the intensity of the selected emotion.
-The videos showed were not made with the real robot, but with a virtual model of the robot.
+The showed videos were not made with the real robot, but with a virtual model of the robot.
 From the results obtained, they decided not to use the low intensity because it had a very low recognition rate.
@@
 Their results showed that sadness was recognized 73.81\% (average) of the times with an intensity of 21.43\%, happiness was recognized 66.67\% (average) of the times with an intensity of 30.95\%, anger was recognized 61.9\% of the times with an intensity of 26.19\%, and fear was recognized 83.33\% (average) of the times with an intensity of 28.58\%.
+%TODO What does it mean "with an intensity of x%?
 These results show that people could reasonably well recognize emotions from the robot's gait.
@@
 They conducted an experiment to analyse the recognition rate of emotion expression, using as inspiration the movements done by dogs to convey emotions.
-The experiment was done using a Wizard-of-Oz scene and its goal was to determine if people could distinguish two emotions (happiness and fear).
+The experiment was done using a Wizard-of-Oz setting and its goal was to determine if people could distinguish two emotions (happiness and fear).
 They use a game approach to determine participant's appraisal of the robot emotion.
@@
 Their hypothesis was that using some principles, that they evaluated as important, it is possible to express happiness and sadness in a way that people could recognize.
-These principles establish that to show happiness is necessary to quiclkly move robot's head up and arms up.
+These principles establish that to show happiness is necessary to quickly move robot's head up and arms up.
 While to express sadness the head goes down, arms down, both slowly.
@@
 They obtained a 95\%, 59\%, and 94\% of accuracy for happiness, neutral and sadness respectively.
-Although their results show that their key features are determinant to convey happiness and sadness.
+Their results show that the selected features are determinant to convey happiness and sadness.
 
@@
 Each generated path was recorded using the Vicon motion-tracking system.
-Then, they did an experiment were people were asked to assess each path using the Self-assessment Manikin (SAM)~\cite{Lang2008}.
+Then, they did an experiment were people were asked to assess each path using the Self-Assessment Manikin (SAM)~\cite{Lang2008}.
 In order to analyse the results, they mapped them on the circumplex model of emotion, and evaluated the contribution of each Laban's parameter in the 2-D circumplex model (arousal and valence).
@@
 %%%%%%%%%%%%%%%%%%%
-Suk and collaborators studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-human or animal like object~\cite{NAM2014}.
+Suk and collaborators studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-bioinspired object~\cite{NAM2014}. %TODO What is granularity for this robot?
 Two experiments were designed to determine the relationship among these features and the emotional interpretation.
@@
 
-These works presented in this section provide guidance about features that could be exploited to project certain emotions.
-However, range of values to convey specific emotions will guide other researchers in what values could be used to convey their desire emotion or what values not to use because they could be misinterpreted as negative emotions.
+The works presented in this section provide guidance about features that could be exploited to project certain emotions.
+However, range of values to convey specific emotions will guide other researchers in what values could be used to convey the desired emotion or what values not to use because they could be misinterpreted as negative emotions.
+%TODO I cannot catch the meaning of the last sentence.
+Starting with "However" raises the expectation of something negative, e.g., nobody provides values for the features that could be used.
+The sentence seems instead positive.
+So, either remove "However" or make evident what is negative in the statement.
 

### 2016-10-08 JournalIJSR/Parts/ExperimentDesign.tex
Changes in both articles.
Add files via upload

@@
-The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation to express happiness, anger, sadness and fear, which are four out of six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
+The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation can give to the expression of happiness, anger, sadness, and fear, which are four out of the six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
 %%%%%%%%%%%%%%%%%%%
@@
 \begin{itemize}
-	\item \textbf{Angular velocity} is the rotational speed  ($\omega$) of the robot with respect to its center.
+	\item \textbf{Angular velocity} is the rotational velocity  ($\omega$) of the robot with respect to its center.
 
-	\item \textbf{Oscillation angle} is the maximum extension in which the robot will rotate around its center in the oscillating movement ($\theta$).
+	\item \textbf{Oscillation angle} is the maximum extension of the robot's rotation around its center in the oscillating movement ($\theta$).
 
@@
 
-	\item \textbf{Direction with respect to participant's perspective} is the angle generated from the participant's point of view with respect to the robots trajectory ($D$).
+	\item \textbf{Direction with respect to participant's perspective} is the angle generated from the participant's point of view with respect to the robot's trajectory ($D$).
 
@@
 
-The three first variables are shown in Figure~\ref{fig:angular_movement}. As it could be observed, robot's frame of reference is draw to show that it could move straight while is rotating.
+The three first variables are shown in Figure~\ref{fig:angular_movement}. The robot's frame of reference is drawn to show that it could move straight while it is rotating.
 
@@
 	\centering
-	\includegraphics[width=0.80\textwidth]{./Images/ExampleMovement.png} 
+	\includegraphics[width=0.48\textwidth]{./Images/ExampleMovement.png} 
 	\caption{Example of the features used in the experiment.
@@
 
-%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%
-\subsection{Dependent Variables}
+\subsubsection*{Independent Variables values}
 
-\begin{itemize}
-	\item \textbf{Emotion:} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
-	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed,  two mental states that could be misinterpreted from these emotions, and the option of ``other'', where participants could write their own interpretation.
-	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.
+Specific, discrete values were selected for all independent variables, to make the experiment feasible.
+First, a simple test to evaluate when significant changes could be perceived was performed on a small sample of independent subjects.
+Based on this test, specific values for oscillation angle, and angular and linear velocities were selected.
+The values for the remaining two variables were selected according to what was needed by the experiment.
+%TODO I've tried to make this sentence clearer, but it is still obscure.
+What does it mean?
 
-	\item \textbf{Emotion's intensity:} indicate the emotion intensity as perceived by the subject.
-This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.
-
-\end{itemize}
-%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%
-\subsection{Independents' Variables Values}
-
-It was decided to select specific for all independents variables, discrete values to make the experiment feasible.
-First, a simple test to evaluate when significant changes could be perceived was performed on a small sample of independent subjects.
-Base on this test specific values for oscillation angle, and angular and linear velocities were selected.
-For the remaining two variables were selected the cases that could be beneficial for the experiment.
 The chosen values are shown in Table~\ref{table:variables_values}.
@@
 \begin{table}[htb]
-\caption{Possible values for each of the independent variables.}
+\centering
+\caption{Values for each of the independent variables in the experiment.}
 \begin{tabular}{|c|c|c|c|c|}
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{./Images/possibilities_case.png} 
+	\includegraphics[width=0.48\textwidth]{./Images/possibilities_case.png} 
 	\caption{Combination of direction and orientation.
@@
 The robot represents the initial position with its orientation, which is represented through the robot's frame of reference.
-The dash big square represents robot's movement zone, while the small represents participant's zone.
+The dashed big square represents the robot's movement zone, while the small one on the side represents the subjects' zone.
 a) Direction = $0$ and Orientation = $0$.
@@
 
-The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, were generated from the combination of independent variables' values for a total of 384 combinations.
-All the experiences that would not add any significant information to the experiment were deleted, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of treatments to 195.
+The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, %TODO What does "desired procedures to compare" mean?
+were generated from the combination of independent variables' values for a total of 384 combinations.
+All the experiences that would not add any significant information to the experiment were removed, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of experiences to 195.
 
@@
 %%%%%%%%%%%%%%%%%%%
-\subsection{Participants' Sequence}
+%%%%%%%%%%%%%%%%%%%
+\subsection{Dependent Variables}
 
-It was decided that each subject will be just exposed to twenty over one hundred and ninety five possible experiences, which lasted  from 10 to 15 minutes.
-This was decided because each subject was a volunteer and would not perceive any monetary remuneration, so the time dedicated to the experiment had to be kept limited.
-The twenty treatments were selected picking a number without replacement from 1 to 195.
+\begin{itemize}
+	\item \textbf{Emotion} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
+	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed, two mental states that could be misinterpreted from these emotions, and the option of ``other''.
+	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.
+
+	\item \textbf{Emotion's intensity} indicates the emotion intensity as perceived by the subject.
+This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.
+
+\end{itemize}
 %%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%
+\subsection{Participants}
+
+It was decided that each subject had to be exposed to twenty over one hundred and ninety five possible experiences, trial that lasted  from 10 to 15 minutes.
+This was decided because each subject was a volunteer, so the time dedicated to the experiment had to be kept limited.
+The twenty treatments were selected picking a number without replacement from 1 to 195.
+A total of 980 answers were collected, guaranteeing a minimum of 5 trials for each motion type.
+
+The experiment was performed at Politecnico di Milano, involving subjects with different backgrounds.
+A total of 49 volunteers were involved: 12 females and 37 males.
+The average age of the subjects was 25.28, with standard deviation of 2.8, with a minimum age of 20 and maximum of 32.
+The subjects' country of origin and their backgrounds are shown in the Table~\ref{table:country} and Table~\ref{table:career}, respectively.
+
+%%%%%%%%%%%%%%%%%%%%% 
+\begin{table}[h]
+\centering
+\caption{Subjects' Country of origin.}
+\label{table:country}
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Country} & \textbf{Counting} \\
+\hline
+Albania & 1 \\
+\hline
+Bosnia & 1 \\
+\hline
+Brazil & 2 \\
+\hline
+Colombia & 4 \\
+\hline
+Germany & 1 \\
+\hline
+Greece & 1 \\
+\hline
+Iran & 5 \\
+\hline
+Italy & 33 \\
+\hline
+Moldova & 1 \\
+\hline 
+\multicolumn{2}{c}{}
+\end{tabular} 
+\end{table}
+%%%%%%%%%%%%%%%%
+
+\begin{table}[h]
+\centering
+\caption{Subjects' Background.}
+\label{table:career}
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Career} & \textbf{Counting}\\
+\hline
+Aeronautical Engineering & 1 \\
+\hline
+Architecture & 1 \\
+\hline
+Social assistance & 1 \\
+\hline
+Automation & 1 \\
+\hline
+Bio-medical Engineering & 5 \\
+\hline
+Computer Science & 33 \\
+\hline
+Electronic Engineering & 2 \\
+\hline
+Mechanical Engineering & 2 \\
+\hline
+Nursery & 1 \\
+\hline
+Pedagogical Science & 1 \\
+\hline
+Tourism & 1 \\
+\hline
+\multicolumn{2}{c}{}
+\end{tabular} 
+\end{table}
+ %TODO I would say how many times each experience was tested. This is a needed parameter for this experimental setup.
+%%%%%%%%%%%%%%%%%%%
+
+The information from each subject was collected using a web-based form.
+To maintain anonymity, no personal information that could be used to trace the subject back was collected.
+The procedure used with each subject is described here below.
+
+\begin{enumerate}
+
+	\item The subject was asked to fill out the following information:
+
+	\begin{itemize}
+		\item Sex
+		\item Background
+		\item Age
+		\item Country of origin
+	\end{itemize}
+
+	\item The robot was shown to the participant and the experiment procedure explained.
+
+	\item An example of the questionnaire was presented and a sample movement of the robot shown.
+
+	\item The subject was exposed to a specific movement sequence according to the following steps:
+
+	\begin{enumerate}
+
+		\item The subject is exposed to the movement generated by a configuration of values.
+
+		\item The subject could use as much time as needed to select values for intensity of the different terms in the questionnaire.
+
+		\item After the subject had completed his/her selection about the current movement, the robot is positioned to the new starting point, and the sequence is repeated from step 1.(a) for the rest of movements.
+
+	\end{enumerate}
+\end{enumerate}
+
+The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{./Images/example_survey.png} 
+	\caption{Example of the questionnaire used in the experiment.}
+	\label{fig:questionnaire_example}
+\end{figure}
+
 \subsection{Setup}
 
-The experiment's setup and dimensions are shown in the Figure~\ref{fig:setup}.
+The experimental setup and dimensions are shown in the Figure~\ref{fig:setup}.
 The crosses symbolize possible starting points, which were selected depending on the direction's value, as it is showed in Figure~\ref{fig:possibilities_orientation_direction}.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{./Images/ExperimentGeneral.png} 
+	\includegraphics[width=0.45\textwidth]{./Images/ExperimentGeneral.png} 
 	\caption{Setup for the experiment. The crosses symbolize the possible starting points.}

### 2016-10-08 JournalIJSR/Parts/Introduction.tex
Add files via upload

@@
-Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}.
-However  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
-This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been used to convey emotions.
-Nevertheless in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
-Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011} , in some cases like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
+%TODO Here, even before what follows, the need for emotion expression should be justified, ad possibily supported by literature
+
+Emotions and mental states are not just presented through facial expression, but also by body postures and other features~\cite{Gelder2008}.
+However,  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
+This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been widely used to convey emotions.
+Nevertheless, in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
+Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
+In some cases, like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
 This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.
@@
 The amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those that exploit anthropomorphic features.
-Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented by them.
-For example Suk and collaborators~\cite{NAM2014} in their study gives specific values for acceleration, curvature, and but their connection to specific emotions is not given.
-Rather, they gave a relationship between their features and values in terms of pleasure/arousal dimensions.
-This could lead to select features to convey certain emotions but it would be even better to know specific range of values for those features to convey certain emotions or to know the values that could be misinterpreted with negative emotions.
+Moreover, these works do not prescribe any specific range of values for the characteristics to be used to express the  implemented emotionsb.
+For example, Suk and collaborators~\cite{NAM2014}, in their study, give specific values for acceleration, curvature, but their connection to specific emotions is not given.
+Rather, they give a relationship between their features and values in terms of valence and arousal.
+This could lead to select features to convey certain emotions, but it would be better to know the specific range of values for those features to convey the single emotions, or to know the values that could lead to misinterpret the emotional expression.
 
-In order to get a better understanding of other features and values that could be used to convey specific emotions, this paper presents an experiment that was designed to identify specific values for some movement features that could be used to express the following emotions, selected among the ones suggested by Ekman as basic~\cite{Ekman2004}: happiness, anger, fear and sadness.
-The considered features are oscillation angle, linear and angular velocity, direction and orientation, identified as independent variables.
+In order to get a better understanding of other features and values that could be used to convey specific emotions, this paper presents an experiment that was designed to identify specific values for some movement features that could be used to express the following emotions, selected among the ones suggested by Ekman as basic~\cite{Ekman2004}: happiness, anger, fear, and sadness.
+The considered features are: oscillation angle, linear and angular velocity, direction and orientation, identified as independent variables.
 The perceived emotions and their intensities were considered as dependent variables.
@@
 For each of the four emotions was generated a top 10 list based on alpha agreement and perceived intensity.
-The results suggest that fear is perceived when the robot is looking at them and moving far from them fast.
-Sadness is attributed to slow velocities with slow angular velocity and small oscillation angle.
-Anger is attributed to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them.
+The results suggest that fear is perceived when the robot is looking at the subjects while moving far from them fast.
+Sadness is associated to slow velocities with slow angular velocity and small oscillation angle.
+Anger is attributed to fast velocities, both angular and linear, small angle of oscillation and the robot facing the subjects while approaching them.
 
@@
 The experiment's design is explained in section~\ref{sec:experiment}.
-Finally sections~\ref{sec:study} and~\ref{sec:result} presents the study done and the obtained results.
+Finally sections~\ref{sec:study} and~\ref{sec:result} present the study done and the obtained results.

### 2016-10-08 JournalIJSR/Parts/Platform.tex
Changes in both articles.
Add files via upload

@@
 The system used in the experiment is composed by a non-anthropomorphic platform and software architecture that enrich robot's movements with emotion.
-The robotic platform was envisioned to be as simpler as possible to let the study of the desired characteristics.
+The robotic platform was envisioned to be as simple as possible to limit the influence of shape on the study of the desired characteristics.
 
@@
 Therefore, it was possible to imitate movements that are done by humans.
-For example, people move straight even if they turn their whole body a bit.
+For example, people do not have constaraints in movement, and can take any direction in any moment.
 The platform has a diameter of 25 cm and height of 25 cm.
 Figure~\ref{fig:ThirdDesign} shows the platform's blue prints and the real platform.
-Robot's frame of reference, in which all the velocities are going to be calculated, are depicted by the two black arrows.
-So, as it could be observed, to make the robot move forward it must be send a velocity in $y$ axis.
+Robot's frame of reference, in which all the velocities are going to be calculated, is depicted by the two black arrows.
+So, as it could be observed, to make the robot move forward a velocity along the $y$ axis is selected by the control system.
 
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{Images/DesignThird.png} 
+	\includegraphics[width=0.48\textwidth]{Images/DesignThird.png} 
 	\caption{Design of the platform.
@@
 The two black arrows represent robot's frame of reference.
-b) First layer, which includes the Arduino and the H-Bridges to control the motors.
-c) Second layer with the Odroid-U3 and the mechanical structure to support the upper part.
-d) Lateral view of the version.}
+b) First layer, which includes Arduino and the H-Bridges to control the motors.
+c) Second layer with Odroid-U3 and the mechanical structure to support the upper part.
+d) Lateral view of the robot.}
 	\label{fig:ThirdDesign}
@@
 \subsection{Software}
-To ensure robot's velocity it was implemented a PID controller for each motor.
-PID's set point is established by a controller that could receive two different types of commands.
-The first commands is robot's velocities ($<V_x,V_y,\omega>$), which are given in robot's frame of reference.
-The second command is a point ($<x, Y, \theta>$), which is given in the general frame of reference.
+To guarantee that the correct robot's velocity for each motor could be achieved, a PID controller was implemented.
+PID's set point is established by a higher level controller that could receive two different types of commands.
+The first commands are robot's velocities ($<V_x,V_y,\omega>$), given in robot's reference frame.
+The second command is a set point ($<x, Y, \theta>$) to be reached, given in the world reference frame.
 This frame of reference is set every time the system is reset or boot.
 For example, if the robot finishes a trajectory and then it is reset, the new frame is going to be in the robot's current position.
+%TODO From this description it seems that this second reference frame is again associated to the robot, in particular that it is a reference frame that is activated when the robot starts, and does not move with the robot.
+So it is a world reference frame reset each time the robot starts a new movement.
+It should have a name, to be found.
+If it was always associated with the robot it would have been called "deictic".
 
-Additional to this low level control, it was created a graphical interface~\ref{fig:experimental_interface} to reduce the possibility on introducing wrong values for a desired sequence.
+%TODO I'm sorry, but the following is an implementation detail that does not add anything to the scientific relevance of this paper, and this is not a paper about the interface.
+%In addition to this low level control, a graphical interface, depicted in Figure~\ref{fig:experimental_interface}, was created to reduce the possibility of introducing wrong values for a desired sequence.
 This interface loads the sequences from a .txt file and displays sequences' numbers on it.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.60\textwidth]{./Images/ExperimentInterface.png} 
-	\caption{Interface used in the experiment.
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.45\textwidth]{./Images/ExperimentInterface.png} 
+%	\caption{Interface used in the experiment.
 Once a sequence is selected, the interface shows sequence's values.
 Also, the interface give information about the current position of the robot and its velocity.}
-	\label{fig:experimental_interface}
-\end{figure}
+%	\label{fig:experimental_interface}
+%\end{figure}

### 2016-10-08 JournalIJSR/Parts/Results.tex
Changes in both articles.
Add files via upload

@@
-A total of 980 answers were collected, and a minimum of 5 trials for each motion type.
-A table with participants' answers was generated for each treatment.
-Table~\ref{table:example_table} is an example of the generated tables.
+A table with subjects' answers was generated for each experience. Table~\ref{table:example_table} is an example of the generated tables.
 
-\begin{table}
-\caption{Example of the table generated for each movement. This table corresponds to the treatment with $ID=1$.}
+\begin{table*}
+\centering
+\caption{Example of the table generated for each experience. This table corresponds to the experience with $ID=1$.}
 \label{table:example_table}
-\begin{tabular}{ | l | p{1.3 cm} | l | p{1.3 cm} | l | l | l | l | l | l | l | l |  }
+\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |  }
 \hline
@@
 	Masculine & Computer science & 24 & Italy &  0 & 0 & 0 & 8 & 0 & 7 & 0 & \  \\ \hline
-	Feminine & Science pedagogiche & 26 & Italy &  0 & 0 & 0 & 0 & 0 & 0 & 7 & Dubbioso \\ \hline
+	Feminine & Pedagogical Science & 26 & Italy &  0 & 0 & 0 & 0 & 0 & 0 & 7 & Dubbioso \\ \hline
 	Masculine & Computer science & 24 & Italy &  4 & 8 & 0 & 0 & 0 & 0 & 0 & \  \\ \hline
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
 For each table, mean, standard deviation, and median were calculated.
-It was not possible to use ANOVA test over the data because the assumption of normality is not achieved in the collected data.
+It was not possible to use ANOVA test over the data because the assumption of normality is not satisfied in the collected data.
 This was checked using the Shapiro-Wilk Test.
-Additionally, a contingency table for each emotion was generated in each treatment as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean, including the option of other.
+Additionally, a contingency table for each emotion was generated in each experience as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean, including the option ``other''.
 For all tables, including the contingency,  the Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated: it is a reliability coefficient to measure the agreement among different participants.
-Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to: any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.
+Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.
 
@@
 To improve the table interpretation, it was decided to just register the emotions' alpha values that had a mean greater than zero.
-The $\alpha$ for each treatment is shown in Figure~\ref{fig:alpha_treatment}.
-Additionally, for each emotion was generated a table with a top ten ranking treatments that considers the following items:(i) the mean intensity of the respective emotions, (ii) the alpha agreement for the respective emotion, and (iii) the alpha agreement for the specific treatment.
-To generate these tables, were first organized by the mean, then by the emotion's agreement and finally by the general agreement.
+The $\alpha$ for each experience is shown in Figure~\ref{fig:alpha_experience}.
+Additionally, for each emotion was generated a table with a top ten ranking experiences that considers the following items:(i) the mean intensity of the respective emotions, (ii) the alpha agreement for the respective emotion, and (iii) the alpha agreement for the specific experience.
+Experiences in these tables were first organized by mean, then by the emotion's agreement and finally by general agreement.
+%TODO This is critical, it is not clear (make an example) and should be fully justified, since on this is based all the reasoning about results
+
 The decision to give more importance to emotion's alpha was taken based on the situation that the participants could be agreed about the precise emotion but not for the rest of the words enlisted.
+%TODO You just said that the first is the mean, not alpha...
+This sentence is not clear, anyway
 From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:
@@
 The angle and the angular velocity attributed six over ten times were $0.087$ and $2$, respectively.
-So it seems that people perceive as fear when the robot is looking at them and moving far from them fast.
+So it seems that people perceive the movement as a fear expression when the robot is looking at them and moving far from them fast.
 
@@
 It seems that people attribute sadness to slow velocities with slow angular velocity and small oscillation angle.
-Regarding the other two features, there is not a concrete pattern that could lead to make a generalization.
+Regarding the other two features, there is not any defined pattern that could lead to make a generalization.
 
@@
 However the oscillation angle for these four cases is equally divided between the values $0.174$ and $3.49$.
-So it seems that happiness is mainly attributed to fast angular velocities and big oscillations angles.
-However specific agreement among the other features is not present.
+%TODO BTW, is this angle in radians?
+It is a quite big difference...
+So it seems that happiness is mainly attributed to fast angular velocities and big oscillations angles. Specific agreement among the other features is not present.
 
 	\item Anger is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$.
-It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them.
+It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the persons while approaching them.
 \end{itemize} 
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\caption{Alpha values for each movement.}
-	\label{fig:alpha_treatment}
-\end{figure}
+	\label{fig:alpha_experience}
+\end{figure*}
 
@@
 \begin{table}
-\caption{Contingency table formula used for each emotion and treatment.
-Where $k$ is the kth treatment, $j$ is jth emotion for the kth treatment, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
+\caption{Contingency table formula used for each emotion and experience.
+Where $k$ is the kth experience, $j$ is jth emotion for the kth experience, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
 \label{table:table_contingency}

### 2016-10-08 JournalIJSR/Parts/Study.tex
Changes in both articles.
Add files via upload

@@
-The information about all the subjects was collected using a Google form.
-To maintain participants anonymity, not personal information that could be used to trace them back was collected.
+The information from each subject was collected using a web-based form.
+To maintain anonymity, no personal information that could be used to trace the subject back was collected.
 The procedure used with each subject is described here below.
@@
 		\item Sex
-		\item Career
+		\item Job
 		\item Age
@@
 
-	\item The robot was shown to the participant and the experiment procedure is explained.
+	\item The robot was shown to the participant and the experiment procedure explained.
 
@@
 
-	\item The subject is exposed to a specific movement sequence according to the following steps:
+	\item The subject was exposed to a specific movement sequence according to the following steps:
 
@@
 
-		\item After the subject had completed his/her selection about the current movement, the sequence is repeated for the rest of movements.
+		\item After the subject had completed his/her selection about the current movement, the robot is positioned to the new starting point, and the sequence is repeated from step 1.(a) for the rest of movements.
 
@@
 
-The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias.
-Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
-The experiment was performed at Politecnico di Milano, involving subjects with different backgrounds.
-%campus Leonardo during the months of June and July of 2015.
-A total of 49 volunteers were involved: 12 females and 37 males.
-The average age of the subjects was 25.28, with standard deviation of 2.8, with a minimum age of 20 and maximum of 32.
-The subjects' country of origin and their backgrounds are shown in the Table~\ref{table:country} and Table~\ref{table:career}, respectively.
+The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
 
@@
 	\centering
-	\includegraphics[width=0.90\textwidth]{./Images/example_survey.png} 
+	\includegraphics[width=0.48\textwidth]{./Images/example_survey.png} 
 	\caption{Example of the questionnaire used in the experiment.}
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%% 
-\begin{table}[h]
-\caption{Subjects' Country of origin.}
-\label{table:country}
-\begin{tabular}{|c|c|}
-\hline
-\textbf{Country} & \textbf{Counting} \\
-\hline
-Albania & 1 \\
-\hline
-Bosnia & 1 \\
-\hline
-Brazil & 2 \\
-\hline
-Colombia & 4 \\
-\hline
-Germany & 1 \\
-\hline
-Greece & 1 \\
-\hline
-Iran & 5 \\
-\hline
-Italy & 33 \\
-\hline
-Moldova & 1 \\
-\hline 
-\multicolumn{2}{c}{}
-\end{tabular} 
-\end{table}
-%%%%%%%%%%%%%%%%
-
-\begin{table}[h]
-\caption{Subjects' Background.}
-\label{table:career}
-\begin{tabular}{|c|c|}
-\hline
-\textbf{Career} & \textbf{Counting}\\
-\hline
-Aeronautical Engineering & 1 \\
-\hline
-Architecture & 1 \\
-\hline
-Social assistance & 1 \\
-\hline
-Automation & 1 \\
-\hline
-Bio-medical Engineering & 5 \\
-\hline
-Computer Science & 33 \\
-\hline
-Electronic Engineering & 2 \\
-\hline
-Mechanical Engineering & 2 \\
-\hline
-Nursery & 1 \\
-\hline
-Pedagogical Science & 1 \\
-\hline
-Tourism & 1 \\
-\hline
-\multicolumn{2}{c}{}
-\end{tabular} 
-\end{table}

### 2016-10-18 JournalInteractionStudies/Journal-AISB.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

\documentclass[man,floatsintext]{apa6}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{apacite}
\usepackage{rotating}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{slashbox}
\newcommand{\co}{\cellcolor{gray!40}}

\title{Robots Showing Emotions: Emotion Representation with no bio-inspired Body}
\author{Julian M. Angel-Fernandez and Andrea Bonarini}
\affiliation{Department of Electronics, Information, and Bioengineering\\ Politecnico di Milano\\ Milan, Italy\\
email: \{julianmauricio.angel,andrea.bonarini\}@polimi.it}

\abstract{Robots should be able to represent emotional states to interact with people as social agents. There are cases where robots cannot have bio-inspired bodies, for instance because the task to be performed requires a special shape, as in the case of home cleaners, package carriers, and many others. In these cases, emotional states have to be represented by exploiting movements of the body. In this paper, we present a set of case studies aimed to identify specific values to convey emotion though changes in linear and angular velocities, which might be applied on different non-bio-inspired bodies. The work originates from some of the most considered emotion expression theories and from emotion coding for people. We show that people can recognize some emotional expressions better than others, and we propose some directions to express emotions exploiting only bio-neutral movement.
}

\shorttitle{Robots Showing Emotions}

\begin{document}
\maketitle
\section{Introduction}
\input{./Parts/introduction}
\section{Related Work}
\label{sec:related_work}
\input{./Parts/Emotion_Projection}
\section{System}
\label{sec:robotic_platform}
\input{./Parts/system}
\section{Case Studies}
\label{sec:cases}
\input{./Parts/case_studies}
\section{Conclusions and Further Work}
\input{./Parts/conclusions}
\bibliographystyle{apacite}
\bibliography{Bibliography,Biblography,BibloNew}
\end{document}

### 2016-10-18 JournalInteractionStudies/Parts/Emotion_Projection.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused on faces. One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions. The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}), plus \textit{interest}.

Studies focused on robotics bodies can be partitioned in two groups: platforms that resemble humans or animals, and those that don't. Moreover, the implemented emotions vary among works, with a special tendency to include happiness. Questionnaires to assess people's perception are often adopted in works that use human or animal like platforms~\cite{Canamero2010,Beck2010,Li2011,Destephe2013b,Arras2012,Brown2014}. A relevant exception is the work done by Lakatos and collaborators~\cite{Lakatos2014} who assessed the participant's perception based on interaction through a play. In the experiment, each participant had two balls (yellow and black) and he could play with the robot using one of this balls. However, one of the balls would trigger robot's happiness and the other sadness.

Regarding the movement or poses design, three major approaches could be found. In the first approach, actors are asked to perform different walks conveying emotions~\cite{Destephe2013b}. These movements are later reproduced with the robot, as closely as possible. A second approach is to ask some subjects to design the movements~\cite{Li2011}. The last approach is the empirical approach, where researches come with poses and movements based on their own experience~\cite{Canamero2010,Beck2010,Arras2012,Brown2014}. One major finding from diverse works~\cite{Canamero2010,Beck2010,Brown2014} is that moving the head up improved the identification of pride, happiness, and excitement. While moving the head down improved the identification of anger and sadness.

On the other hand, the works that use platforms with no resemblance to persons or animals could be sub-divided in three groups. A first group study the possibility to convey emotions with their platforms~\cite{Arras2012, Novika2015, BarakovaL10}. The second group focus on determining the contribution of different features in the perception of emotions~\cite{Saerbeck2010,Barakova2013, Sharma2013, NAM2014}.
The second group use pre-defined procedures to assess the participants' perception, such as Self-Assessment Manikin (SAM)~\cite{Lang2008}, possibly combined  with other procedures such as Social Dominance Orientation (SDO)~\cite{pratto1994social} and PANAS~\cite{WatsonClarkTellegen88}.

It is important to mention the use of Laban’s Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}. Besides the fact that these works found that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the correlation between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.

Table~\ref{table:comparison_work_emotion_projection} summarizes all the robotics studies already mentioned, highlighting the following characteristics:
\begin{itemize}
	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
	\item \textit{Platform used} gives the name of the platform used on the study;
	\item The\textit{Locomotion} gives information about the capabilities of the platform., because, even having a human-like embodiment, it does not mean that the platform can move;
	\item \textit{Emotion Evaluation Method} refers to the methodology used to collect the data in the studies.
	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The mediums considered were: movement, body posture and face poses.
\end{itemize}
\clearpage
\begin{table}[h]
\caption{Comparison among works on emotion projection in robotics. NA = Not Available}
\label{table:comparison_work_emotion_projection}
\begin{center}
\tiny %\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\begin{tabular}{|p{2.3 cm}|p{1.5 cm}|p{1.3 cm}|p{1.4 cm}|p{1.4 cm}|p{1.0 cm}|p{2.2 cm}|p{1.4 cm}|}
%\begin{tabular}{|p{1.5 cm}|p{1.0 cm}|p{1.5 cm}|p{1.5 cm}|p{1.5 cm}|p{2.0 cm}|p{1.5}|p{2.0 cm}|p{1.0 cm}|p{1.5 cm}|}
\hline 
\textbf{Work}  & \textbf{Embodiment} & \textbf{Platform Used} & \textbf{Locomotion} & \textbf{Emotion Evaluation Method} & \textbf{Emotion Presentation} & \textbf{Emotions Implemented}  & \textbf{How is the emotion conveyed?}\\ 
\hline 
Breazeal~\cite{Breazeal2002}  & Face & Kismet & NA & Questionnaire & Video & Happiness, surprise, anger, disgust, fear, sadness and interest &  Face poses\\ 
\hline
Saerbeck and Christoph~\cite{Saerbeck2010} & Animal / Non-Human like& iCat / Roomba & NA / Differential &PANAS and SAM & Real Robot & NA &  Movement\\
\hline 
Ca\~namero and collaborators~\cite{Canamero2010,Beck2010}&Human-Like & NAO & Bipedal & Questionnaire & Real robot & Anger, sadness, fear, pride, happiness, and excitement &  Body poses\\
\hline
Li and Chignell~\cite{Li2011}& Animal-Like& Teddy Bear Robot& NA & Questionnaire & Video (Real robot) & Random + Anger, disgust, fear, happiness, sadness, and surprise  & Body poses\\ 
\hline
Barakova and collaborators~\cite{Barakova2013} & NA & Closet robot& NA & SDO and SAM & Real robot & NA*  & Changing lights on and intensity\\ 
\hline
Sharma and collaborators~\cite{Sharma2013} & Non-Human / Animal & Quadrotor & Aerial & SAM + Questionnaire + Interview &  Real Robot & Laban's poles & Movement\\
\hline
Destephe and collaborators~\cite{Destephe2013b}&Human-like & WABIAN-2R & Bipedal & Questionnaire & Video (Virtual Robot) & Fear, anger, happiness, and sadness & Movement (Gait)+Body Poses\\
\hline 
Embgen and collaborators~\cite{Arras2012} & Human-like & Daryl &  Differential& Questionnaire & Real Robot & Happiness, sadness, fear, curiosity, embarrassment, and disappointment & Movement + Body poses \\ 
\hline
Lakatos and Collaborators~\cite{Lakatos2014}& Animal-Like & Dog & Holonomic & Indirect (Interaction with the robot) & Real Robot & Happiness and Fear &  Move + Body poses \\
\hline
Brown and Howard~\cite{Brown2014}& Human-Like & DARwIn-OP & Bipedal & Questionnaire & Real Robot & Happiness and sadness & Body poses\\
\hline
Novikova and Watss~\cite{Novika2015}&Non-Human/ Animal & Undetermine & Differential& Questionnaire& Real Robot & Scared, surprise, excited, angry, neutral, happiness and sadness &  Movement + Poses\\
\hline 
\end{tabular} 
\end{center}
\end{table}

### 2016-10-18 JournalInteractionStudies/Parts/case_studies.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

In total, we did one pilot and four case studies using changes in linear and angular velocity, and oscillation angle to convey emotion. These features are depicted in Figure~\ref{fig:features}. The pilot was used to test the prototype and identify possible improvements. The values for the first two case studies were selected empirically, while for the third the Laban's description of emotion expression was followed. The final case study used values identified through the previous trials. 
%TODO add some information about the relationship among all the case studies
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{./Images/ExampleMovement.png}
	\caption{Example of the features used in all case studies. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement.}
	\label{fig:features}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%
\section{First Case Study}
With our first version of the platform (Figure~\ref{fig:triskar-first-design}), we decided to do our first case study at the Museum of Science and Technology in Milan, where high school students and families were coming for an event that lasted 4 days. 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design}
Each group of participants was exposed to three rounds, in each of which the robot was performing a different emotion expression. The sequence of rounds was generated randomly without repeating any emotion in the same sequence. The subjects were asked to mark which emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride. It was also added the option to answer: ''Unknown''. Although these ten options were enlisted, just the first eight emotions were implemented. To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.\\
Additionally, it was decided to locate the robot $1.5 mts$ away from the participants and with its front facing them every time that a new emotion was showed, as shown in  Figure~\ref{fig:setup}. 
\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{./Images/FirstCase.png} 
	\caption{First case study setup.}
	\label{fig:setup}
\end{figure}  
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Description}
It was decided to follow an empirical design for this case study, consisting in taking into account the features that could be changed in the robot base and in composing them to express some basic emotions. The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.\\
The features that could easily be perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:
\begin{itemize}
	\item \textit{Speed} is the target speed for the robot during the movement. It could take one out of five values: very slow (100 mm/s), slow (200 $mm/s$), normal slow (300 $mm/s$), normal (400 $mm/s$), and fast (800 $mm/s$).
	\item \textit{Front/Back} represents the fact that the robot moves backwards at some point in its movement, before going forward again; the possible values are: ''yes1``, which means that the robot goes back only once, ''yes2`` when the robot goes back twice, and ''no`` if the robot goes only forward.
	\item \textit{Shoulder} considers the movement of the upper part: ''asymmetric`` when the two beams move asymmetrically, alternatively, one forward, and the other backward, ''close``, when the upper parts get close to each other, a combination of the two (''close-2``), and ''none``. 
	\item \textit{Shoulder Amplitude} is the maximum angle that the two beams have to rotate. There are five possibilities: ''none`` ($0^\circ$), ''small`` ($10^\circ$), ''medium`` ($30^\circ$), ''large`` ($50^\circ$), and ''huge`` ($70^\circ$).
	\item \textit{Angular Velocity} $\omega$ is classified as: ''none`` (0 $mm/s$), ''slow`` (300 $mm/s$), ''medium`` (500 $mm/s$), and ''fast`` (800 $mm/s$).
	\item \textit{Body Rotation Amplitude} is the maximum  rotation angle around its center that the robot base can reach during the linear movement (it is a holonomic base); it could be: ''none`` ($0$) rad, ''small`` ($0.1$) rad, ''medium`` ($0.3$) rad, ''large`` ($0.5$) rad, and ''huge`` ($0.7$) rad.
\end{itemize}
\begin{table}[tbh]
\begin{center}
\small
\caption{Features that were presented to the audience, and their values. Embarr. is Embarrassment and Asy. is Asymmetric.}
\label{table:features}
\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|p{1.5 cm}|p{1.6 cm}|p{1.6 cm}|m{1.5 cm}|}
\hline 
\textbf{Emotion} & \textbf{Speed} & \textbf{Front/Back} & \textbf{Shoulder} & \textbf{Shoulder Amplitude} & \textbf{Angular Velocity} & \textbf{Body Rotation Amplitude} \\ 
\hline
Anger & Fast & No & Asy. & Medium & None & Very Small \\
\hline
Sadness & Very Slow & Yes-1 & Close-2 & None & Slow & Small \\
\hline
Fear & Normal Slow & Yes-2 & Close-2 + Asy. & Small & None & None \\ 
\hline
%Fear 2 & Slow & Yes-2 & Close-2 + Asymmetric & Small & None & Small \\
%\hline
Embarr. & Slow & No & Asy. & Large & Slow & Small \\
\hline
Happiness & Fast & No & Asy. & Medium & Fast & Small \\
\hline
Disgust & Slow & No & Few Asy. & Small & None & Very Small \\
\hline
Curiosity & Normal & No & Asy. & Medium & Slow & Large \\
\hline
Neutral & Normal & No & Asy. & Medium & None & None \\
\hline
\end{tabular}
\end{center}
\vspace{-0.5cm}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Setup}
There was no specific group size, since this was determined by the amount of people that got close to the booth at a given moment. Therefore, there were groups with just one person and others with 24 persons. The total amount of volunteers was 154: 55 males, 26 females, and 73 that did not specify their gender. The average age was 21.95 with a standard deviation of 12.26, minimum age was 5, maximum 62.
\subsection{Results}
Table~\ref{table:results_1} shows the results obtained in the first case study. 
\begin{table}[tbh]
\caption{Answers obtained the first case study. On each row is the emotion that was intended to express, and on the columns the reported emotions.
.}
\small
\label{table:results_1}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &23 &11 &3 &4 &7 &6 &1 &0 &0 &4 &59&38.98\%\\
\hline
Curiosity &2 &9 &3 &9 &2 &3 &2 &8 &3 &0 &41&21.95\%\\
\hline
Disgust& 1 & 11& 1& 3& 7& 3& 6& 8& 5& 1& 46&2.17\%\\
\hline
Embarr. & 3& 11& 0& 8& 9& 3& 0& 4& 2& 1& 41&19.51\%\\
\hline
Fear & 3& 29& 5& 25& 22& 2& 2& 0& 2& 2& 92&22.82\%\\
\hline
Happiness & 15& 4& 0& 2& 3& 28& 4& 4& 2& 1& 63&44.44\%\\
\hline
Neutral & 5& 0& 1& 1& 0& 1& 0& 3& 2& 0& 13&0\%\\
\hline
Sadness & 4& 5& 1& 11& 13& 0& 2& 3& 7& 0& 46&23.81\%\\
\hline
\end{tabular}
\end{table}
Table~\ref{table:results_1} shows that the best emotion perceived was Happiness and the worst one Disgust, with 44\% and 2\% respectively of accuracy. Moreover, some movements were designed to convey a specific emotion, but a different emotion was perceived. For example the intended Sadness was identified by 14\% of subjects exposed to it, while 25.5\% perceived it as Fear. The neutral behaviour was not much considered, possibly because people, in this setting, expected to see something specific, not a neutral movement. To analyse whether each emotional expression was misinterpreted with others a Fisher's exact test was applied for each possible combination of emotions implemented. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get better p-value estimation. 
The results showed that people perceived the following implementations as similar, having a $p-value>0.05$: curiosity-disgust, curiosity-embarrassment, curiosity-sadness, disgust-embarrassment, disgust-sadness, embarrassment-fear, embarrassment-sadness, and fear-sadness.

Moreover, an analysis was done per groups, for each presented emotion. Excluding unknown and uncertain answers, we have considered the answers of each subject that was presented an emotion produced by the robot. For each emotion we considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one (in any of the other two experiences each did), and how many recognized an emotion different from the considered one when presented a different emotion. This lead for each presented emotion to a table like the one reported in Table~\ref{table:singleEmotion} for Happiness. 
\begin{table}
\begin{center}
\small
\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
\backslashbox{Presented}{Reported}&Happiness&Other\\
\hline 
Happiness&28&4\\
\hline 
Other&30&96\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}
For each of these tables the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, have been computed with the R package CARET~\cite{caret}.
The results show that some implementations of emotion expression (i.e., Anger ($p-value=1e-3$) and Happiness ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.
%%%%%%%%%%%%%%%%%%%%%
\section{Second Case Study}
Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotions, but this time a context to the emotional state of the robot was provided by playing a little scene. This is motivated by the fact that that emotions are triggered by stimuli~\cite{Plutchik2001,cacioppo2000handbook}.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design}
A little scene was created for each emotion to give a context to the participants. The procedure and questionnaire were the same as the one adopted for the first case. However, it was added a variant of the Fear emotion (Fear2), in which the robot finishes its trajectory far from the person. As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups. The sequences were generated randomly and without repeating an emotion in a sequence.\\
As in the first case study, the total distance covered by the robot was $1.5 mts$, but this time the robot was facing the actor. The distance from the participants to the robot and actor was $1.5 mts$, as shown in Figure~\ref{fig:setup2}. 
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/SecondCase.png} 
	\caption{Setup of the second case study.}
	\label{fig:setup2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}
The laboratory open day of 2013 was used to perform the scenes and actions and to collect data. Eight groups participated, each one with approximately 20 volunteers for a total of 156: 51 males, 17 females, and 88 that did not provide their gender. The average age was 26.34 with a standard deviation of 12.44, and with a minimum age of 11 and maximum of 65.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}
Table~\ref{table:results_2} shows the results obtained in the second case study.
\begin{table}[tbh]
\caption{Answers obtained in the second case studies. On each row is the emotion that was intended to express, and on the columns the reported emotions.}
\small
\label{table:results_2}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &41 &1 &2 &0 &6 &9 &0 &2 &0 &1 &62&66.13\%\\
\hline
Curiosity &8 &38 &0 &3 &0 &4 &1 &1 &1 &4 &60&63.33\%\\
\hline
Disgust& 6& 2& 5& 4& 3& 0& 4& 7& 4& 3& 38&13.16\%\\
\hline
Embarr. & 7& 2& 1& 4& 12& 0& 0& 1& 10& 0& 37&10.81\%\\
\hline
Fear & 0& 13& 0& 17& 10& 6& 0& 0& 0& 0& 46&21.74\%\\
\hline
Fear2 & 3& 0& 5& 5& 35& 0& 1& 0& 2& 0& 51&68.63\%\\
\hline
Happiness & 0& 1& 0& 0& 5& 55& 1& 0& 0& 1& 63&87.30\%\\
\hline
Neutral & 1& 3& 2& 5& 7& 9& 5& 5& 1& 1& 39&12.82\%\\
\hline
Sadness & 0& 4& 2& 22& 14& 0& 2& 3& 15& 1& 63&23.81\%\\
\hline
\end{tabular}
\end{table}
In the second case study, the results were considerably better, where four out of the nine showed emotions had a percentage of recognition higher than 60\% (Anger, Happiness, Curiosity and Fear2). Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions. As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions. The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<\alpha$.  Comparing the percentage from both cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves its recognition. However, if the conveyed emotion does not match the scene, the audience does not recognize it. This shows that even giving information about the situation, and using a human actor to provide the context, people could not recognize the emotion if the correct features are not exploited. To verify this, it was done a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test. The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases. This would suggest that the combination of stimuli (scene + actor) and correct robot's movements are necessary to the correct emotional interpretation. However with the adopted setup, it was impossible to determine which factor had more relevance.
%%%%%%%%%%%%%%%%%%%%%
\section{Third Case Study}
The third case study was designed to explore the possibility to adopt for robot's movements the emotional movement descriptions reported in human body studies, and followed the methodology used by Sharma and collaborators~\cite{Sharma2013} to select the emotions to be implemented and enlisted in the questionnaire. The second version of the platform was used in this case study (Figure~\ref{fig:triskar-second-design}).
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental setup}
From the previous experience it was decided to implemented just four emotions, which reduce the number of possible sequences. To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma. The emotions implemented were: \textit{Happiness} (I quadrant), \textit{Anger} (II quadrant), \textit{Sadness} (III quadrant), and \textit{Content} (IV quadrant). To reduce the probability that the correct emotion could be selected by chance four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant. These emotions were: \textit{Frustration}, \textit{Boredom}, \textit{Astonishment} and \textit{Tiredness}. The final questionnaire had nine possibilities (eight emotions and ``Unknown'').

In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion the robot has expressed?}".
The setup used in this case study is depicted in the Figure~\ref{fig:setup2}.
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/ThirdCase.png} 
	\caption{Setup of the third case study.}
	\label{fig:setup2} %TODO check whether it is the correct setup. Yes, it was two meters and with some boxes to not let the participants move over the robots path. OK, just because the number did not match (setup2 for the 3rd case study)
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions} 
Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.\\
The specific values selected for each emotion are reported as follow:
\begin{itemize}
	\item \textit{\textit{Anger}:} the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$. An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.
	\item \textit{\textit{Happiness}:} as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.
	\item \textit{Sadness:} the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$. This emotion expression did not include any angular rotation.
	\item \textit{Content:} the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest. The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
\end{itemize}
It is important to notice that these parameters do not include any changes in the upper part of the body, since the changes done in the platform significantly decreased the emotion expression of the upper part.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}
This case study was done during the Rome Maker Faire, 2014. During a period of four days, people were asked to participate to this study. Each subject was exposed to two rounds: in each one, the robot was performing a different emotion. During the first two days, the open questionnaire was used, while during the last two days the multiple option questionnaire was used. The total number of volunteers for the closed list questionnaire was 91: 52 males, 38 females, and 11 that chose not to specify their gender. The average age was 30.98 years, with standard deviation of 15.12, minimum age was 4 and maximum 71. The total amount of participants assessing the study with the open questionnaire was 84: 47 males, 36 females, and 1 that did not specify; the average age was 24 years, with standard deviation of 15.8, minimum age was 5 and maximum 59. 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}
From the open questionnaire, different terms to describe both emotions and mental states were obtained. In table~\ref{table:open_questionnaire} are reported the results. In order to reduce the quantity of words, words that have a similar meaning were grouped, for example words as \textit{Fear}, \textit{Terror}, \textit{Scared}, and \textit{Worried} were grouped under the label \textit{Fear}. Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly. \textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.\\
From these results is possible to highlight two important facts:
\begin{itemize}
	\item The language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion. 
	\item The movements that could be designed as emotional are also associated to mental states of the robots. This is evident in the words obtained from the presentation of four ''emotional'' movements, such as \textit{cold} (referring that the robot was feeling cold), \textit{tenderness}, \textit{shyness}, \textit{power}, \textit{hurry}, \textit{looking for something}, \textit{he wants something}, \textit{enthusiasm}, \textit{sympathy}, \textit{vanity}, and \textit{obedience}. 
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
		\caption{Results obtained from the open questionnaire.}
		\label{table:open_questionnaire}
		\small
			\begin{tabular}{|c|c|c|c|c|c|}
				\hline
					\backslashbox{Presented}{Reported}&\textit{Anger}&\textit{Happiness}&\textit{Sadness}&\textit{Content}&Total\\
				\hline
					\textit{Anger}& 3&6&7&5&21\\
				\hline
					\textit{Happiness}&12& 18&0&6&36\\
				\hline
					\textit{Sadness}&0&0& 8&3&11\\
				\hline
					\textit{Content}&2&0&0& 0&2\\
				\hline
					\textit{Fear}&4&5&14&13&36\\
				\hline
					\textit{Tiredness}&1&0&1&1&3\\
				\hline
					\textit{Cold}&2&0&2&1&5\\
				\hline
					\textit{Shyness}&1&0&4&4&9\\
				\hline
					\textit{Agitated}&4&1&0&0&5\\
				\hline
					\textit{Power}&4&1&0&0&5\\
				\hline
					\textit{Hurry}&0&1&0&0&1\\
				\hline
					\textit{Looking for something}&1&0&1&0&2\\
				\hline
					\textit{He wants something}&1&0&1&0&2\\
				\hline
					\textit{Tenderness}&1&0&1&2&4\\
				\hline
					\textit{Uncertainty}&1&2&0&0&3\\
				\hline
					\textit{Enthusiasm}&1&0&0&0&1\\
				\hline
					\textit{Sympathy}&1&0&2&4&7\\
				\hline
					\textit{Curiosity}&1&2&3&3&9\\
				\hline
					\textit{Shame}&0&0&0&1&1\\
				\hline
					\textit{Nothing}&1&2&1&0&4\\
				\hline
					\textit{Vanity}&1&0&0&0&1\\
				\hline
					\textit{Obedience}&0&0&0&1&1\\
				\hline
					\textit{Total}&43&38&44&46&171\\
				\hline
			\end{tabular}
\end{table}
A summary of the obtained answers is provided in Table~\ref{table:result_list_emotions}.
\begin{table}
\centering
\small
\caption{Answers obtained in the case study.}
		\label{table:result_list_emotions}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
			\hline	
\rotatebox{90}{\backslashbox{Presented}{Reported}}&
\rotatebox{90}{\textit{Anger}}&
\rotatebox{90}{ \textit{Happiness}} &
\rotatebox{90}{\textit{Sadness}}&
\rotatebox{90}{\textit{Content}}&
\rotatebox{90}{\textit{Frustration}}&
\rotatebox{90}{\textit{Boredom}}&
\rotatebox{90}{\textit{Astonishment}}&
\rotatebox{90}{\textit{Tiredness}}&
\rotatebox{90}{\textit{Unknown}}&
\rotatebox{90}{Total}\\	
			\hline
				\textit{Anger}& 19&8&1&5&7&2&5&1&0&48\\
			\hline
				\textit{Happiness}&18& 19&0&9&5&1&5&1&0&58\\
			\hline
				\textit{Sadness}&1&9& 12&2&4&5&7&6&0&46\\
			\hline
				\textit{Content}&2&8&7& 4&6&8&5&10&0&50\\	
			\hline	
			\end{tabular}
\end{table}
An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
Additional two confusion matrices were created: one merging the results from all high (\textit{Anger}, \textit{Happiness}, \textit{Frustration} and \textit{Astonishment}) and low (\textit{Sadness}, \textit{Content}, \textit{Boredom}, and \textit{Tiredness}) arousal emotions; and the other one merges the results of positive (\textit{Happiness}, \textit{Content}, \textit{Astonishment}, and \textit{Tiredness}) and negative (\textit{Anger}, \textit{Frustration}, \textit{Boredom}, and \textit{Sadness}) emotions. For each of these tables were calculated the positive predictive value, accuracy and a Pearson's $\chi^2$. The results are shown in table~\ref{table:Precision}. They show that there is significant evidence to conclude that anger, happiness, and sadness have an impact in the perception of the emotion, while the implementation of content does not have any significant impact in the emotion perception. Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence. \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
	\begin{center}
\small
		\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the third case study.} 
\label{table:Precision}
		\begin{tabular}{|p{3 cm}|p{2 cm}|c|c|c|}
		\hline
		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
		\hline		
		High/Low Arousal & 0.81 & 0.69 & 28.7 & 8.29e-8\\
		\hline
		Positive/Negative Valence & 0.56 & 0.55 & 1.9 & 0.167\\
		\hline
		\hline
		Anger & 0.4 & 0.75&13.923 & 1.9e-4\\
		\hline
		Happiness & 0.33 & 0.68&4.88&2.7e-2\\
		\hline
		Sadness & 0.26 & 0.79&15.22&9.5e-5\\
		\hline
		Content & 0.08 & 0.69&6e-2&0.8 \\		 
		\hline
		\end{tabular}
	\end{center}
\end{table}
To analyse whether each emotion expression was misinterpreted with other implementations, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of emotions implemented, which gives a total of seven combinations. %The results are shown in the the Table~\ref{table:chi}. 
The results suggest that the implementations of anger and happiness ($p-value=0.492$), and, respectively, sadness and content ($p-value=0.492$) are interpreted as similar, while the other emotion expressions are distinguished from each other.\\ %TODO The same p-value? Very strange...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}
%\small
%	\begin{center}
%		\caption{Pairwise comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the third case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.} 
%		\label{table:chi}
%		\begin{tabular}{|c|c|c|c|c|}
%		\hline
%		\multirow{2}{*}{\textbf{Pair Compared}}&\multicolumn{2}{|c|}{\textbf{List Questionnaire}}&\multicolumn{2}{|c|}{\textbf{Open Questionnaire}}\\
%		\cline{2-5}
%		& \textbf{p-value} & \textbf{p-value*}& \textbf{p-value} & \textbf{p-value*}\\
%		\hline
%		Anger vs Happiness & 0.4903&0.9&0.2879&0.492\\
%		\hline 
%		Anger vs Sadness  & 2.85e-5&1.01e-5&6.09e-7&3.05e-6\\
%		\hline
%		Anger vs Content &1.2e-4&9e-5&7.9e-3&0.0239\\
%		\hline
%		Happiness vs Sadness &7.81e-7&6e-7&1.8e-8&1.08e-7\\
%		\hline
%		Happiness vs Content &2.2e-6&6e-7&3.4e-4&1.36e-3\\
%		\hline
%		Sadness vs Content& 0.7036&0.9&0.246&0.492\\
%		\hline		
%		\end{tabular}
%	\end{center}
%\end{table}
From the results of both questionnaires, we can say that \textit{Anger} and \textit{Happiness} were confused, as well \textit{Sadness} and \textit{Content}. \textit{Fear} was written as emotion when the two emotions with low arousal (\textit{Sadness} and \textit{Content}) were shown. These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions.
%%%%%%%%%%%%%%%%%%%%%%
\section{Fourth Case Study}
After the first and third case studies, it was evident the necessity to better understand how the characteristics are related with each other and how they can be used to convey emotions. Therefore, it was decided to perform an experiment to get a better insight on the contribution of angular and linear velocity, angle of oscillation, direction and orientation. To cross-validate the data collected in this experiment, we decided to do a final case study.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental setup}
From the results obtained on our experiments, we selected two combinations (angular velocity, oscillation angle, linear velocity, orientation and direction) with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in a experiment done after third case study. As in the previous case studies, a questionnaire was used. However, this time the emotions selected were the same used during the experiment: anger, fear, sadness and happiness. Moreover, two mental states were added: excited and tender, which corresponds to high and low arousal, respectively. As it was done in the previous cases, the questionnaire included the option ''unknown''. Although the platform used was the last version (Figure~\ref{fig:triskar-third-design}), the upper part was cut off to allow comparisons with the platform used in the other experiments. The case study set up could be seen in the Figure~\ref{fig:setup_fourth}.
\begin{figure}
	\centering
	\includegraphics[width=0.60\textwidth]{./Images/FourthCase.png} 
	\caption{Environment setup for the fourth case study. The crosses symbolize the two possible starting points.}
	\label{fig:setup_fourth}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions} 
The selected emotion descriptions could be seen in Table~\ref{table:features_2}
\begin{table}[tbh]
\begin{center}
\caption{Combination of features selected for the fourth case study.}
\label{table:features_2}
\small
\begin{tabular}{|c|c|p{2.5 cm}|p{2 cm}|p{2 cm}|p{2.5cm}|}
\hline 
\textbf{Emotion} & \textbf{Direction} & \textbf{Orientation} & \textbf{Linear Velocity} $mm/sec$& \textbf{Angular Velocity} $rad/sec$& \textbf{Oscillation Angle} $rad$\\
\hline
Happiness 1 & Getting close & Looking at the person & $500$  & $3$ & $0.349$ \\
\hline
Happiness 2 & Getting close & Looking at the person & $900$ & $3$ & $0.174$ \\
\hline
Fear 1 & Getting far & Looking at the person & $900$ & $2$ & $0.174$ \\
\hline
Fear 2 & Getting far & Looking at the person & $500$ & $2$ & $0.087$ \\
\hline
Angry 1 & Getting far & Giving the back & $500$ & $3$ & $0.087$ \\
\hline
Angry 2 & Getting close & Looking at the person & $900$ & $1$ & $0.087$ \\
\hline
Sadness 1 & Getting far & Giving the back & $200$ & $1$ & $0.349$ \\
\hline
Sadness 2 & Getting close & Giving the back & $200$ & $1$  & $0.349$ \\
\hline
\end{tabular}
\end{center}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}
This case study was done during the 2015 Researchers' Night. During a period of two days, people were asked to participate to this study. As in the third case study, each participant was exposed to only two emotions. The emotion sequences presented to the participants were established before hand, and randomized. The total number of participants was 256: 128 males, 126 females, and 2 unknown. The average age was 27.29 years, with standard deviation of 16.5, minimum age was 4 and maximum 76. 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}
Table~\ref{table:result_fourth} summarizes the results obtained during the case study.
\begin{table}
\centering
\small
\caption{Summary of the answers obtained in the fourth case study.}
		\label{table:result_fourth}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
			\hline	
\rotatebox{90}{\textbf{Presented/Reported } }&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{ \textbf{Anger}} &
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Excitement}}&
\rotatebox{90}{\textbf{Tenderness}}&
\rotatebox{90}{\textbf{Other}}&
\rotatebox{90}{\textbf{Total}}&
\rotatebox{90}{\textbf{Percentage}}\\	
			\hline
			Happiness 1&8&16&7&4&16&4&7&62&13\%\\
			\hline
			Happiness 2&11&11&6&2&19&3&1&53&21\%\\
			\hline
			Anger 1&7&5&6&2&21&7&1&49&10\%\\
			\hline
			Anger 2&14&29&13&2&13&3&2&76&38\%\\
			\hline
			Fear 1&6&2&28&1&9&6&0&52&54\%\\
			\hline
			Fear 2&7&3&37&2&20&4&1&74&50\%\\
			\hline
			Sadness 1&3&5&17&14&5&16&5&65&22\%\\
			\hline
			Sadness 2&5&5&15&28&6&15&7&81&35\%\\
			\hline
			\end{tabular}
\end{table} 
It could be observed that both implementations of Happiness are confused with Anger and Excitement, as it could have been expected. The first implementation of Anger was mostly confused with Excitement, which was perceived by twenty one over forty nine participants, while the second implementation showed an improvement from 10\% to 38\% on recognition. This implementation was perceived also has Happiness, Fear and Excitement by fourteen, twelve, and thirteen respectively. Both implementations of Fear have a high level of recognition 54\% and 50\% and mostly confused with excitement, nine for the first implementation and twenty for the second implementation. Lastly, the first implementation of Sadness was confused with Fear and Tenderness by twelve and sixteen respectively. The second implementation was confused again with Fear and Tenderness by thirteen and twenty-eight respectively.\\
To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied for 10 different combinations. The results are shown in Table~\ref{table:result_compare_fourth}. As the results suggest, the implementation of Anger is the only one that was considered as different.\\
\begin{table}
\centering
\small
\caption{Pairwise comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the fourth case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
		\label{table:result_compare_fourth}
		\begin{tabular}{|c|c|c|}
			\hline	
\textbf{Pair Compared} & \textbf{p-value} & \textbf{p-value*}\\	
			\hline
			Happiness 1 vs Happiness 2 &0.38&1.0\\
			\hline
			Anger 1 vs Anger 2 & 7.3e-4&4.4e-3\\
			\hline
			Anger 2 vs Happiness 1 & 0.137&0.69\\
			\hline
			Anger 2 vs Happiness 2 & 0.157&0.69\\
			\hline
			Fear 1 vs Fear 2 & 0.74&1.0\\
			\hline
			Sadness 1 vs Sadness 2 & 0.665&1.0\\
			\hline
			Fear 1 vs Sadness 1& 8.35e-5&5.8e-4\\
			\hline
			Fear 1 vs Sadness 2 & 5e-7&4e-6\\
			\hline
			Fear 2 vs Sadness 1 & 2e-7&1.8e-6\\
			\hline
			Fear 2 vs Sadness 2 & 1e-7&1e-6\\
			\hline
			\end{tabular}
\end{table} 
As it was done in the previous case studies a contingency matrix was computed.
For each of these tables were calculated the positive predictive value, accuracy and a Pearson's $\chi^2$. The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and one of Anger do not have any significant impact on the emotion perception.\\
\clearpage
\begin{table}
\centering
\small
\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the fourth case study.} 
\label{table:Precision2}
		\begin{tabular}{|p{3 cm}|p{2 cm}|c|c|c|}
		\hline
		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
		\hline
		Happiness 1 & 0.13 & 0.79 & 0.11 & 0.74\\
		\hline
		Happiness 2 & 0.21 & 0.81& 3.7 &0.054\\
		\hline
		Anger 1 & 0.1 & 0.8 & 3.8e-29 & 1\\
		\hline
		Anger 2 & 0.38 & 0.81 & 34.4 & 4.47e-9\\
		\hline
		Fear 1 & 0.54 & 0.8 & 36.2 & 1.8-e9\\
		\hline 
		Fear 2 & 0.5 & 0.78 & 35.8 & 5.3e-10\\
		\hline
		Sadness 1 & 0.22 & 0.85 & 27.4 & 1.63e-7\\
		\hline
		Sadness 2 & 0.35 & 0.85 & 72.9 & 2.2e-16\\		 
		\hline
			\end{tabular}
\end{table} 
It is important to notice that the results were obtained using the lower part of the robot without any change in shape. Another factor to consider is the high impact of the words enlisted in the questionnaire had in the detection rate. These words included two mental states that could be confused with the other four emotions enlisted, as it is reflected in the results. Despite the bias generated by these two words, the recognition rates of five over eight emotion expressions were over 35\%, being the two implementations of Fear the ones with the highest recognition rate (54\% for the first and 50\% for the second).

### 2016-10-18 JournalInteractionStudies/Parts/conclusions.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

Four case studies were done to study the contribution of angular velocity, linear velocity, oscillation angle, and shape change in emotion expression from a non-bio-inspired robot. The results collected during all case studies show that a correct combination of linear and angular velocity, oscillation angle, and direction can be used to convey emotions that could be distinguished from each other. Also, they suggest that it is necessary to modify the robot's shape to increase people's emotion recognition rate. This result is congruent with the results obtained in the studies done to understand what features are more relevant when humans convey emotions~\cite{Roether2009,Venture2014}.\\
The lessons learned after these four case studies can be summarized as:
\begin{itemize}
	\item It is possible to convey emotions through changes in angular and linear velocity of a non-bio-inspired body also without changes in the body shape. This lesson opens the door to the inclusion of simple "emotion" to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.
	\item The change in the body shape increases the emotion identification rate of the observers. However, the characteristics that should be changed to increment the emotions perception are still to be investigated.
	\item Although Laban's notation is adequate to code people's movements, robots need precise values to define their actions. As a consequence, the Laban's theory needs to be instantiated to the robots' situation, to enable comparison between different works.
	\item Emotions come as a reaction to an event. Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions. For example, the action Fear was well perceived by the participants when the robot get far from them, as they were inducing it.
	\item Giving the participants the possibility to write their interpretation of the robot's movements was not going to be helpful to assess what emotion they thought the robot was conveying during case studies. Although there are plenty of procedures that have been proposed to determine the emotion that a person could be thinking at (e.g., SAM), they could just be used in a controlled environment where the experimenter could spend long periods of time with the participant. This is not the case of exhibitions where people would agree to stop just for a couple of minutes. On the other side, exhibitions make it possible to collect a large number of subjects representative of a varied population.
	\item Using a real platform to perform the case studies increases the enthusiasms of the participants and possibly their willingness to participate in the study. Although we did not evaluate directly this item during our case studies, it was observed during the set up that people were curious to see the robot moving. Also, during the pilot two kids had a different reaction when the robot was getting close to them. One of them was scared of the robot, while the other was curious about the robot.
\end{itemize}
Further work should be done to understand how the combination of changes in the body shape could contribute to the expression of emotions. It is also necessary to recreate a simple scene to give the context to the participants, but this time just using two robots. This will eliminate possible clues that could be given by the human actor.

### 2016-10-18 JournalInteractionStudies/Parts/introduction.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context. Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most of the works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs. Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others. In all these cases, emotions can be expressed with the only available body, exploiting movement features.
\\
The work presented in this paper focuses on the identification of movement features that could be considered platform independent, thus could be used to express emotions with a wide range of robots. We devised a very simple robot base, with no resemblance to humans or animals, and we proposed its movements to subjects, to identify how they could interpret the movements they could see from a robot in front of them. We performed live trials to keep into consideration factors that could influence the evaluation: the full perception of movement and noise, and the interaction with a physical robot are different if the same scene is lived in first person, or seen on a screen as a movie.
\\
The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments~\cite{Sharma2013}.
\\
Finally, we could identify a set of very basic movement features that could be used to express emotions and, most importantly, the range of values for these features that could led to successful implementations.
\\
This paper is organized as follows. The next section provides a brief overview of relevant work related to emotion expression in robots. Section system outlines the platform used in the case studies. The section case studies presents the design and results for all four case studies.

### 2016-10-18 JournalInteractionStudies/Parts/system.tex
Current version of the article. The following things should be addressed:
Dear Mr Angel Fernandez,

Thank you for resubmitting your manuscript to "Interaction Studies". In the meantime I have received a number of reviews. On this basis I suggest that minor revisions are required. The reviewers raise a number of issues that need to be addressed before the manuscript can be published. 

For your guidance, the full reviewers' comments are appended below.

To summarise, while both reviewers acknowledge improvements to the paper, there remain some issues that should be resolved. These are as follow

The system used in the case studies here reported has been developed to support the identification of features that could be used to project emotions with a non-bio-inspired platform. This system is composed of two complementary parts: robotic platform and emotional enrichment system. The platform has been envisioned to be as simple as possible without any resemblance to human-like embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions. 
\subsection{Robotic Platform}
The platform is a holonomic base, as shown in Figure~\ref{fig:holonomic-platform}. The first prototype included three metal gear motors with encoders, an Arduino Mega micro-controller, one servo motor and X-Bee system to enable the communication between Arduino and a remote computer. The mechanical design of the prototype is shown in Figure~\ref{fig:triskar-prototype}. A PID controller for each wheel was implemented and tuned to guarantee linear and angular velocity.
\\
This prototype was modified after the first experiments to improve the expressiveness of the upper part. Two additional servo motors and a mechanical structure to support all these motors were added. The two motors attached to beams could be controlled to obtain an asymmetric or opening-closing movement. 
The third motor deforms the upper part of the foam. Figure~\ref{fig:triskar-first-design} shows the placement of the motors. To hide the structure, foam and a light blue cloth covering the foam were used, as it could be seen in Figure~\ref{fig:triskar-cover}. The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Promarker}. 
\\
Although this version showed the possibility to convey emotions, still it was not autonomous enough to host the emotional enrichment system. Therefore, an Odroid-U3 microcomputer was added, communicating with Arduino Mega via ROS-Serial.
Also, it was decided to make some improvements in the upper part. Two reasons motivated this changes. First the deformation system was not changing the shape enough to be clearly perceived by subjects; second, the beams were damaging the foam. Therefore, a lever  was added to the deformation motor, and a piece of rubber was adopted to safely connect the beams with the foam. The final arrangement is shown in Figure~\ref{fig:triskar-second-design}.\\ 
The final version, with improved computational power (Arduino Due instead of Mega) is shown in Figure~\ref{fig:triskar-third-design}.
\begin{figure}
	\centering
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/TriskarThird.png}
	\caption{Holonomic Base used in all the platform's version.}
	\label{fig:holonomic-platform}
	\end{subfigure}
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/upperFirstB.png}
	\caption{Platform prototype.}
	\label{fig:triskar-prototype}
	\end{subfigure}
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/upperSecondC.png}
	\caption{First version design.}
	\label{fig:triskar-first-design}
	\end{subfigure}
	\\
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/upperThirdD.png}
	\caption{Second version design.}
	\label{fig:triskar-second-design}
	\end{subfigure}
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/upperFourthD.png}
	\caption{Third version design.}
	\label{fig:triskar-third-design}
	\end{subfigure}
	\begin{subfigure}[c]{0.3\textwidth}
	\centering
	\includegraphics[width=\textwidth]{./Images/Triskar2.jpg}
	\caption{Platform with cover.}
	\label{fig:triskar-cover}
	\end{subfigure}
	\caption{Triskarino platform.}
	\label{fig:robot}
\end{figure}

### 2016-10-18 JournalInteractionStudies/Rebuttal2.txt
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

General

Reviewer 1
*****************************************
One sentece to introduce next case study was added at the end of each case study

Reviewer 3
*****************************************
Case study titles were changed:
First Case study: Empirical Emotion Parameters
Second Case Study: Addition of Context
Third Case Study: Literature Emotional Parameters

### 2016-10-18 JournalInteractionStudies/Parts/case_studies.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

@@
 The final case study used values identified through the previous trials.
+
 %TODO add some information about the relationship among all the case studies
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 %%%%%%%%%%%%%%%%%%%%%
-\section{First Case Study}
+
+\section{First Case Study: Empirical Emotion Parameters}
+
 With our first version of the platform (Figure~\ref{fig:triskar-first-design}), we decided to do our first case study at the Museum of Science and Technology in Milan, where high school students and families were coming for an event that lasted 4 days.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Design}
+
 Each group of participants was exposed to three rounds, in each of which the robot was performing a different emotion expression.
@@
 Although these ten options were enlisted, just the first eight emotions were implemented.
-To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.\\
+To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.
+
 Additionally, it was decided to locate the robot $1.5 mts$ away from the participants and with its front facing them every time that a new emotion was showed, as shown in  Figure~\ref{fig:setup}.
-\begin{figure}
+
+\begin{figure}[h]
 	\centering
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Emotion Description}
+
 It was decided to follow an empirical design for this case study, consisting in taking into account the features that could be changed in the robot base and in composing them to express some basic emotions.
@@
 The features that could easily be perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:
+
 \begin{itemize}
+
 	\item \textit{Speed} is the target speed for the robot during the movement.
 It could take one out of five values: very slow (100 mm/s), slow (200 $mm/s$), normal slow (300 $mm/s$), normal (400 $mm/s$), and fast (800 $mm/s$).
+
 	\item \textit{Front/Back} represents the fact that the robot moves backwards at some point in its movement, before going forward again; the possible values are: ''yes1``, which means that the robot goes back only once, ''yes2`` when the robot goes back twice, and ''no`` if the robot goes only forward.
+
 	\item \textit{Shoulder} considers the movement of the upper part: ''asymmetric`` when the two beams move asymmetrically, alternatively, one forward, and the other backward, ''close``, when the upper parts get close to each other, a combination of the two (''close-2``), and ''none``.
+
 	\item \textit{Shoulder Amplitude} is the maximum angle that the two beams have to rotate.
 There are five possibilities: ''none`` ($0^\circ$), ''small`` ($10^\circ$), ''medium`` ($30^\circ$), ''large`` ($50^\circ$), and ''huge`` ($70^\circ$).
+
 	\item \textit{Angular Velocity} $\omega$ is classified as: ''none`` (0 $mm/s$), ''slow`` (300 $mm/s$), ''medium`` (500 $mm/s$), and ''fast`` (800 $mm/s$).
+
 	\item \textit{Body Rotation Amplitude} is the maximum  rotation angle around its center that the robot base can reach during the linear movement (it is a holonomic base); it could be: ''none`` ($0$) rad, ''small`` ($0.1$) rad, ''medium`` ($0.3$) rad, ''large`` ($0.5$) rad, and ''huge`` ($0.7$) rad.
 \end{itemize}
+
 \begin{table}[tbh]
@@
 \end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Experimental Setup}
+
 There was no specific group size, since this was determined by the amount of people that got close to the booth at a given moment.
@@
 The average age was 21.95 with a standard deviation of 12.26, minimum age was 5, maximum 62.
+
 \subsection{Results}
+
 Table~\ref{table:results_1} shows the results obtained in the first case study. 
@@
 \end{table}
+
 Table~\ref{table:results_1} shows that the best emotion perceived was Happiness and the worst one Disgust, with 44\% and 2\% respectively of accuracy.
@@
 This lead for each presented emotion to a table like the one reported in Table~\ref{table:singleEmotion} for Happiness.
-\begin{table}
+
+\begin{table}[h]
 \begin{center}
@@
 \end{table}
+
 For each of these tables the classification accuracy and the no-information rate (NIR), i.e.
@@
 The results show that some implementations of emotion expression (i.e., Anger ($p-value=1e-3$) and Happiness ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.
+
+The result shows that it is possible to convey some emotions using just movement and a non-bio-inspired embodiment.
+Moreover, showing emotional states in a context that puts in evidence the stimulus that produced them (as it would happen in a real application) might improve the perception of the emotions, as it is known also for human-human relationships, and this is study in the second case study.
+
 %%%%%%%%%%%%%%%%%%%%%
-\section{Second Case Study}
+\section{Second Case Study: Addition of Context}
+
 Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotions, but this time a context to the emotional state of the robot was provided by playing a little scene.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Design}
+
 A little scene was created for each emotion to give a context to the participants.
@@
 As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups.
-The sequences were generated randomly and without repeating an emotion in a sequence.\\
+The sequences were generated randomly and without repeating an emotion in a sequence.
+
 As in the first case study, the total distance covered by the robot was $1.5 mts$, but this time the robot was facing the actor.
 The distance from the participants to the robot and actor was $1.5 mts$, as shown in Figure~\ref{fig:setup2}.
-\begin{figure}
+
+\begin{figure}[h]
 	\centering
@@
 \subsection{Study}
+
 The laboratory open day of 2013 was used to perform the scenes and actions and to collect data.
@@
 The average age was 26.34 with a standard deviation of 12.44, and with a minimum age of 11 and maximum of 65.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Results}
+
 Table~\ref{table:results_2} shows the results obtained in the second case study.
+
 \begin{table}[tbh]
@@
 \end{table}
+
 In the second case study, the results were considerably better, where four out of the nine showed emotions had a percentage of recognition higher than 60\% (Anger, Happiness, Curiosity and Fear2).
@@
 This would suggest that the combination of stimuli (scene + actor) and correct robot's movements are necessary to the correct emotional interpretation.
-However with the adopted setup, it was impossible to determine which factor had more relevance.
+This opens the question about the influence that could have the human actor and the scene on the recognition rate.
+Although the study of their influence could be beneficial, it was decided to continue the studies on the values that could be used to express emotions.
+Therefore it was devise a third case study that uses values informed in the literature.
+
 %%%%%%%%%%%%%%%%%%%%%
-\section{Third Case Study}
+\section{Third Case Study: Literature Emotional Parameters}
+
 The third case study was designed to explore the possibility to adopt for robot's movements the emotional movement descriptions reported in human body studies, and followed the methodology used by Sharma and collaborators~\cite{Sharma2013} to select the emotions to be implemented and enlisted in the questionnaire.
 The second version of the platform was used in this case study (Figure~\ref{fig:triskar-second-design}).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Experimental setup}
+
 From the previous experience it was decided to implemented just four emotions, which reduce the number of possible sequences.
@@
 The setup used in this case study is depicted in the Figure~\ref{fig:setup2}.
-\begin{figure}
+
+\begin{figure}[h]
 	\centering
@@
 	\caption{Setup of the third case study.}
-	\label{fig:setup2} %TODO check whether it is the correct setup.
-Yes, it was two meters and with some boxes to not let the participants move over the robots path.
-OK, just because the number did not match (setup2 for the 3rd case study)
+	\label{fig:setup2} 
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Emotion Descriptions}
+
 Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
-Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.\\
+Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.
+
 The specific values selected for each emotion are reported as follow:
+
 \begin{itemize}
+
 	\item \textit{\textit{Anger}:} the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$.
 An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.
+
 	\item \textit{\textit{Happiness}:} as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement.
 	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.
+
 	\item \textit{Sadness:} the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$.
 This emotion expression did not include any angular rotation.
+
 	\item \textit{Content:} the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest.
@@
 \end{itemize}
+
 It is important to notice that these parameters do not include any changes in the upper part of the body, since the changes done in the platform significantly decreased the emotion expression of the upper part.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Study}
+
 This case study was done during the Rome Maker Faire, 2014.
@@
 The total amount of participants assessing the study with the open questionnaire was 84: 47 males, 36 females, and 1 that did not specify; the average age was 24 years, with standard deviation of 15.8, minimum age was 5 and maximum 59.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Results}
+
 From the open questionnaire, different terms to describe both emotions and mental states were obtained.
@@
 Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly.
-\textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.\\
+\textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.
+
 From these results is possible to highlight two important facts:
+
 \begin{itemize}
+
 	\item The language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion.
+
 	\item The movements that could be designed as emotional are also associated to mental states of the robots.
 This is evident in the words obtained from the presentation of four ''emotional'' movements, such as \textit{cold} (referring that the robot was feeling cold), \textit{tenderness}, \textit{shyness}, \textit{power}, \textit{hurry}, \textit{looking for something}, \textit{he wants something}, \textit{enthusiasm}, \textit{sympathy}, \textit{vanity}, and \textit{obedience}.
+
 \end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
+\begin{table}[h]
 \centering
@@
 \end{table}
+
 A summary of the obtained answers is provided in Table~\ref{table:result_list_emotions}.
-\begin{table}
+
+\begin{table}[h]
 \centering
@@
 \end{table}
+
 An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
@@
 Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence.
-\\
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
+\begin{table}[h]
 	\begin{center}
@@
 \end{table}
+
 To analyse whether each emotion expression was misinterpreted with other implementations, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of emotions implemented, which gives a total of seven combinations.
-%The results are shown in the the Table~\ref{table:chi}.
-The results suggest that the implementations of anger and happiness ($p-value=0.492$), and, respectively, sadness and content ($p-value=0.492$) are interpreted as similar, while the other emotion expressions are distinguished from each other.\\ %TODO The same p-value?
+The results suggest that the implementations of anger and happiness ($p-value=0.492$), and, respectively, sadness and content ($p-value=0.492$) are interpreted as similar, while the other emotion expressions are distinguished from each other.
+%TODO The same p-value?
 Very strange...
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}
-%\small
-%	\begin{center}
-%		\caption{Pairwise comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the third case study.
-The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
-%		\label{table:chi}
-%		\begin{tabular}{|c|c|c|c|c|}
-%		\hline
-%		\multirow{2}{*}{\textbf{Pair Compared}}&\multicolumn{2}{|c|}{\textbf{List Questionnaire}}&\multicolumn{2}{|c|}{\textbf{Open Questionnaire}}\\
-%		\cline{2-5}
-%		& \textbf{p-value} & \textbf{p-value*}& \textbf{p-value} & \textbf{p-value*}\\
-%		\hline
-%		Anger vs Happiness & 0.4903&0.9&0.2879&0.492\\
-%		\hline 
-%		Anger vs Sadness  & 2.85e-5&1.01e-5&6.09e-7&3.05e-6\\
-%		\hline
-%		Anger vs Content &1.2e-4&9e-5&7.9e-3&0.0239\\
-%		\hline
-%		Happiness vs Sadness &7.81e-7&6e-7&1.8e-8&1.08e-7\\
-%		\hline
-%		Happiness vs Content &2.2e-6&6e-7&3.4e-4&1.36e-3\\
-%		\hline
-%		Sadness vs Content& 0.7036&0.9&0.246&0.492\\
-%		\hline		
-%		\end{tabular}
-%	\end{center}
-%\end{table}
 From the results of both questionnaires, we can say that \textit{Anger} and \textit{Happiness} were confused, as well \textit{Sadness} and \textit{Content}.
@@
 These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions.
+
+%TODO write a sentence explaining the results and justying why the experiment and cross validation
+
 %%%%%%%%%%%%%%%%%%%%%%
-\section{Fourth Case Study}
+\section{Fourth Case Study: Experiment Cross-Validation}
+
 After the first and third case studies, it was evident the necessity to better understand how the characteristics are related with each other and how they can be used to convey emotions.
@@
 To cross-validate the data collected in this experiment, we decided to do a final case study.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Experimental setup}
+
 From the results obtained on our experiments, we selected two combinations (angular velocity, oscillation angle, linear velocity, orientation and direction) with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in a experiment done after third case study.
@@
 The case study set up could be seen in the Figure~\ref{fig:setup_fourth}.
-\begin{figure}
+
+\begin{figure}[h]
 	\centering
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Emotion Descriptions}
+
 The selected emotion descriptions could be seen in Table~\ref{table:features_2}
@@
 \subsection{Study}
+
 This case study was done during the 2015 Researchers' Night.
@@
 The average age was 27.29 years, with standard deviation of 16.5, minimum age was 4 and maximum 76.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Results}
+
 Table~\ref{table:result_fourth} summarizes the results obtained during the case study.
-\begin{table}
+
+\begin{table}[h]
 \centering
@@
 \end{table}
+
 It could be observed that both implementations of Happiness are confused with Anger and Excitement, as it could have been expected.
@@
 Lastly, the first implementation of Sadness was confused with Fear and Tenderness by twelve and sixteen respectively.
-The second implementation was confused again with Fear and Tenderness by thirteen and twenty-eight respectively.\\
+The second implementation was confused again with Fear and Tenderness by thirteen and twenty-eight respectively.
+
 To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied for 10 different combinations.
 The results are shown in Table~\ref{table:result_compare_fourth}.
-As the results suggest, the implementation of Anger is the only one that was considered as different.\\
-\begin{table}
+As the results suggest, the implementation of Anger is the only one that was considered as different.
+
+\begin{table}[h]
 \centering
@@
 \end{table}
+
 As it was done in the previous case studies a contingency matrix was computed.
@@
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and one of Anger do not have any significant impact on the emotion perception.\\
+They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and one of Anger do not have any significant impact on the emotion perception.
+
 \clearpage
-\begin{table}
+\begin{table}[h]
 \centering
@@
 \end{table}
+
 It is important to notice that the results were obtained using the lower part of the robot without any change in shape.

### 2016-10-18 JournalInteractionStudies/Parts/conclusions.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

@@
 Also, they suggest that it is necessary to modify the robot's shape to increase people's emotion recognition rate.
-This result is congruent with the results obtained in the studies done to understand what features are more relevant when humans convey emotions~\cite{Roether2009,Venture2014}.\\
+This result is congruent with the results obtained in the studies done to understand what features are more relevant when humans convey emotions~\cite{Roether2009,Venture2014}.
+
 The lessons learned after these four case studies can be summarized as:
+
 \begin{itemize}
+
 	\item It is possible to convey emotions through changes in angular and linear velocity of a non-bio-inspired body also without changes in the body shape.
 This lesson opens the door to the inclusion of simple "emotion" to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.
+
 	\item The change in the body shape increases the emotion identification rate of the observers.
 However, the characteristics that should be changed to increment the emotions perception are still to be investigated.
+
 	\item Although Laban's notation is adequate to code people's movements, robots need precise values to define their actions.
 As a consequence, the Laban's theory needs to be instantiated to the robots' situation, to enable comparison between different works.
+
 	\item Emotions come as a reaction to an event.
@@
 For example, the action Fear was well perceived by the participants when the robot get far from them, as they were inducing it.
+
 	\item Giving the participants the possibility to write their interpretation of the robot's movements was not going to be helpful to assess what emotion they thought the robot was conveying during case studies.
@@
 On the other side, exhibitions make it possible to collect a large number of subjects representative of a varied population.
+
 	\item Using a real platform to perform the case studies increases the enthusiasms of the participants and possibly their willingness to participate in the study.
@@
 One of them was scared of the robot, while the other was curious about the robot.
+
 \end{itemize}
+
 Further work should be done to understand how the combination of changes in the body shape could contribute to the expression of emotions.

### 2016-10-18 JournalInteractionStudies/Parts/introduction.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

@@
 In all these cases, emotions can be expressed with the only available body, exploiting movement features.
-\\
+
 The work presented in this paper focuses on the identification of movement features that could be considered platform independent, thus could be used to express emotions with a wide range of robots.
@@
 We performed live trials to keep into consideration factors that could influence the evaluation: the full perception of movement and noise, and the interaction with a physical robot are different if the same scene is lived in first person, or seen on a screen as a movie.
-\\
+
 The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments~\cite{Sharma2013}.
-\\
+
 Finally, we could identify a set of very basic movement features that could be used to express emotions and, most importantly, the range of values for these features that could led to successful implementations.
-\\
+
 This paper is organized as follows.

### 2016-10-18 JournalInteractionStudies/Parts/system.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

@@
 The platform has been envisioned to be as simple as possible without any resemblance to human-like embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions.
+
 \subsection{Robotic Platform}
@@
 A PID controller for each wheel was implemented and tuned to guarantee linear and angular velocity.
-\\
+
 This prototype was modified after the first experiments to improve the expressiveness of the upper part.
@@
 The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Promarker}.
-\\
+
 Although this version showed the possibility to convey emotions, still it was not autonomous enough to host the emotional enrichment system.
@@
 Therefore, a lever  was added to the deformation motor, and a piece of rubber was adopted to safely connect the beams with the foam.
-The final arrangement is shown in Figure~\ref{fig:triskar-second-design}.\\
+The final arrangement is shown in Figure~\ref{fig:triskar-second-design}.
+
 The final version, with improved computational power (Arduino Due instead of Mega) is shown in Figure~\ref{fig:triskar-third-design}.
-\begin{figure}
+\begin{figure}[h]
 	\centering

### 2016-10-30 JournalInteractionStudies/Rebuttal2.txt
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 General
+* IT was corrected Cañamero reference
+* It was added the following article as reference: Relationship between color and emotion
+* Introduction parapragh on Case study section was extended to include the conexion and create a better connection among the papers.
+
+* One sentece to introduce next case study was added at the end of each case study
 
@@
 *****************************************
-One sentece to introduce next case study was added at the end of each case study
 
+>>Q: First case study: There is no discussion of the results.
+Whilst the statistical analysis is now clearer, the authors should explain what has been learned in relation to theses results.
+Why were Happiness and Anger recognized?
+Do the authors have some hypothesis?
+Can any generalization be drawn?
+
+>>Q: Second case study: What were the scenarios?
+A: a link to a video, which shows the emotions, was added
+>>Q: "However, if the conveyed emotion does not match the scene, the audience does not recognize it.": How can the design allow for such claim?
+Is this supported by the results?
+Is it possible that only the context was recognized regardless of what the robot was doing?
+A: the sentence were changed, to "this opens the question about the influence that could have the human actor and the scene on the recognition rate"
+>>Q: Third one: Why was the questionnaire changed half way?
+It is well established that velocity is related to arousal. Why additional features are needed? The literature suggests that it is enough to discriminate between low and high velocity.
+A: The re
 Reviewer 3

### 2016-10-30 JournalInteractionStudies/Journal-AISB.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 
+%TODO (Done)change non-human like to non-antrhropomorphic
+%TODO (Done)add a paragrahp at begining of section Case studies explaining the path followed
+%TODO (Done) correct the paragraph written
+%TODO (Done) make modification to case studies subtitles to give more information
+%TODO (Done)review reference: . A. Russell and J.-A. Bachorowski et al., "Facial and vocal expressions of emotion," Annu. Rev. Psychol., vol. 54, no. 1, pp. 329-349, 2003.
+%TODO Write a paragraph with this information
+%TODO (Done)Add the relevant case study number to Table 2, 4, 6, 7, 11
+%TODO Pg. 18, line 9. Add the word "respectively" at the end, since it could also be interpreted as "low and high arousal emotions are difficult to discriminate between each other".
+%TODO (Done) correct Cañamero reference
+%TODO (Done) find a reference for color 
+%TODO (Done)make all the names for emotions expressed the same way (e.g. capital initial and italic, or only capital initial, or only italic, or nothing).
+
 \abstract{Robots should be able to represent emotional states to interact with people as social agents.
@@
 In these cases, emotional states have to be represented by exploiting movements of the body.
-In this paper, we present a set of case studies aimed to identify specific values to convey emotion though changes in linear and angular velocities, which might be applied on different non-bio-inspired bodies.
-The work originates from some of the most considered emotion expression theories and from emotion coding for people.
+In this paper, we present a set of case studies aimed at identifying specific values to convey emotion trough changes in linear and angular velocities, which might be applied on different non-anthropomorphic bodies.
+This work originates from some of the most considered emotion expression theories and from emotion coding for people.
 We show that people can recognize some emotional expressions better than others, and we propose some directions to express emotions exploiting only bio-neutral movement.

### 2016-10-30 JournalInteractionStudies/Parts/Emotion_Projection.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 Studies focused on robotics bodies can be partitioned in two groups: platforms that resemble humans or animals, and those that don't.
-Moreover, the implemented emotions vary among works, with a special tendency to include happiness.
-Questionnaires to assess people's perception are often adopted in works that use human or animal like platforms~\cite{Canamero2010,Beck2010,Li2011,Destephe2013b,Arras2012,Brown2014}.
+Moreover, the implemented emotions vary among works, with a tendency to include happiness.
+Questionnaires to assess people's perception are often adopted in works that use anthropomorphic platforms~\cite{Canamero2010,Beck2010,Li2011,Destephe2013b,Arras2012,Brown2014}.
 A relevant exception is the work done by Lakatos and collaborators~\cite{Lakatos2014} who assessed the participant's perception based on interaction through a play.
 In the experiment, each participant had two balls (yellow and black) and he could play with the robot using one of this balls.
-However, one of the balls would trigger robot's happiness and the other sadness.
+One of the balls would trigger robot's happiness and the other sadness.
 
-Regarding the movement or poses design, three major approaches could be found.
+Regarding the movement or pose design, three major approaches could be found.
 In the first approach, actors are asked to perform different walks conveying emotions~\cite{Destephe2013b}.
@@
 The second group focus on determining the contribution of different features in the perception of emotions~\cite{Saerbeck2010,Barakova2013, Sharma2013, NAM2014}.
-The second group use pre-defined procedures to assess the participants' perception, such as Self-Assessment Manikin (SAM)~\cite{Lang2008}, possibly combined  with other procedures such as Social Dominance Orientation (SDO)~\cite{pratto1994social} and PANAS~\cite{WatsonClarkTellegen88}.
+This group use pre-defined procedures to assess the participants' perception, such as Self-Assessment Manikin (SAM)~\cite{Lang2008}, possibly combined  with other procedures such as Social Dominance Orientation (SDO)~\cite{pratto1994social} and PANAS~\cite{WatsonClarkTellegen88}.
 
 It is important to mention the use of Laban’s Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}.
-Besides the fact that these works found that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the correlation between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.
+Besides the fact that these works report that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the relationship between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.
 
@@
 \begin{itemize}
+
 	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
+
 	\item \textit{Platform used} gives the name of the platform used on the study;
+
 	\item The\textit{Locomotion} gives information about the capabilities of the platform., because, even having a human-like embodiment, it does not mean that the platform can move;
+
 	\item \textit{Emotion Evaluation Method} refers to the methodology used to collect the data in the studies.
+
 	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
+
 	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
+
 	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The mediums considered were: movement, body posture and face poses.
+
 \end{itemize}
+
 \clearpage
@@
 \end{table}
+
+Despite the possibility to use human actors to determine features and values to convey emotions or the findings done in the works previously discussed, there is a need to get a better understanding on how convey emotions with non-anthropomorphic platform.
+This is due to the following reasons.
+First, it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010} due to robots' physical capabilities.
+Second, the significance of the agreement obtained from the studies that used human actors is on discussion~\cite{Russell2003}.
+Third, no all possible features present in a non-anthropomorphic platform are studied in the literature (e.g.
+angular velocity).

### 2016-10-30 JournalInteractionStudies/Parts/case_studies.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
-In total, we did one pilot and four case studies using changes in linear and angular velocity, and oscillation angle to convey emotion.
+In total, we did one pilot and four case studies using changes in linear and angular velocity, and oscillation angle to convey emotions.
 These features are depicted in Figure~\ref{fig:features}.
 The pilot was used to test the prototype and identify possible improvements.
-The values for the first two case studies were selected empirically, while for the third the Laban's description of emotion expression was followed.
-The final case study used values identified through the previous trials.
+The features' values for the first case study were selected empirically and just robots' movement was presented to participants.
+The results suggested that was possible convey some emotions, but it was decided to give a context to each emotion to verify if that could increased the recognition rate.
+Therefore, a second case study was done.
+Each emotion was presented to the participants in a small scene, which was portrayed by the robot and a non professional human actor.
+The results suggested that showing the emotion in a context improve the recognition of some emotions.
+However the study of the impact of the actor and context were out of this research.
+To compare literature on emotion projection, a third case study was done with parameters collected from diverse works, which encoded their emotions' description using Laban's.
+With similar results between first and third case study, we decided to do an experiment to determine values that better represent some emotions~\cite{Angel2017}.
+Thus a final case study was done to cross-validate experiment's findings.
 
-%TODO add some information about the relationship among all the case studies
 \begin{figure}[h]
@@
 $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$).
-The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement.}
+The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with both angular and linear movement.}
 	\label{fig:features}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Design}
 
-Each group of participants was exposed to three rounds, in each of which the robot was performing a different emotion expression.
+\subsection{Experimental Design}
+
+Each group of participants was exposed to three rounds, in each of which the robot was expressing a different emotion.
 The sequence of rounds was generated randomly without repeating any emotion in the same sequence.
-The subjects were asked to mark which emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride.
-It was also added the option to answer: ''Unknown''.
+The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride.
+The option to answer ``Unknown'' was also included.
 Although these ten options were enlisted, just the first eight emotions were implemented.
@@
 
-Additionally, it was decided to locate the robot $1.5 mts$ away from the participants and with its front facing them every time that a new emotion was showed, as shown in  Figure~\ref{fig:setup}.
+Additionally, every time that a new emotion was showed, the robot started $1.5 mts$ away from the participants, with its front facing them, as shown in  Figure~\ref{fig:setup}.
 
@@
 
-It was decided to follow an empirical design for this case study, consisting in taking into account the features that could be changed in the robot base and in composing them to express some basic emotions.
-The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.\\
-The features that could easily be perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:
+It was decided to follow an empirical design for this case study, by considering the features that could be changed in the robot base and by composing them to express some basic emotions.
+The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.
+The features that could be easily perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:
 
@@
 \small
-\caption{Features that were presented to the audience, and their values. Embarr. is Embarrassment and Asy. is Asymmetric.}
+\caption{Features that were presented in the first case study to the audience, and their respective values. Embarr. is Embarrassment and Asy. is Asymmetric.}
 \label{table:features}
@@
 \begin{table}[tbh]
-\caption{Answers obtained the first case study. On each row is the emotion that was intended to express, and on the columns the reported emotions.
-.}
+\caption{Answers obtained in the first case study. On each row is the emotion that was intended to express, and on the columns the reported emotions.}
 \small
@@
 The neutral behaviour was not much considered, possibly because people, in this setting, expected to see something specific, not a neutral movement.
-To analyse whether each emotional expression was misinterpreted with others a Fisher's exact test was applied for each possible combination of emotions implemented.
+To analyse whether each emotional expression was misinterpreted with others a Fisher's exact test was applied for each implemented combination of emotions.
 Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get better p-value estimation.
@@
 \small
-\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness).}
+\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness for the first case study).}
 \label{table:singleEmotion}
@@
 The result shows that it is possible to convey some emotions using just movement and a non-bio-inspired embodiment.
-Moreover, showing emotional states in a context that puts in evidence the stimulus that produced them (as it would happen in a real application) might improve the perception of the emotions, as it is known also for human-human relationships, and this is study in the second case study.
-
+In particular, stronger emotions have been recognized better than milder ones, and emotions typically conveyed by facial expressions (e.g., Disgust) were less recognized.
 %%%%%%%%%%%%%%%%%%%%%
@@
 
-Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotions, but this time a context to the emotional state of the robot was provided by playing a little scene.
+Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotion expressions, but this time a context to the emotional state of the robot was provided by playing a little scene.
 This is motivated by the fact that that emotions are triggered by stimuli~\cite{Plutchik2001,cacioppo2000handbook}.
@@
 
-\subsection{Design}
+\subsection{Experimental design}
 
-A little scene was created for each emotion to give a context to the participants.
-The procedure and questionnaire were the same as the one adopted for the first case.
-However, it was added a variant of the Fear emotion (Fear2), in which the robot finishes its trajectory far from the person.
+A little scene was created for each emotion were an actor played the stimulus to trigger an emotion\footnote{The scenes could be seen in the following link \url{https://www.youtube.com/watch?v=AXAglJKLwbI}}; for instance, he yelled at the robot that then showed fear.
+The procedure and questionnaire were the same as those adopted for the first case.
+However, a variant of the Fear emotion (Fear2) was added, in which the robot finishes its trajectory far from the person.
 As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups.
-The sequences were generated randomly and without repeating an emotion in a sequence.
+The sequences were generated randomly, without repeating the same emotion in a sequence.
 
-As in the first case study, the total distance covered by the robot was $1.5 mts$, but this time the robot was facing the actor.
-The distance from the participants to the robot and actor was $1.5 mts$, as shown in Figure~\ref{fig:setup2}.
+As in the first case study, the total distance covered by the robot was $1.5 m$, but this time the robot was facing the actor.
+The distance from the participants to the robot and actor was $1.5 m$, as shown in Figure~\ref{fig:setup2}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Study}
+\subsection{Experimental setup}
 
-The laboratory open day of 2013 was used to perform the scenes and actions and to collect data.
+The laboratory open day of 2013 was used to perform the scenes and to collect data.
 Eight groups participated, each one with approximately 20 volunteers for a total of 156: 51 males, 17 females, and 88 that did not provide their gender.
@@
 As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions.
-The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<\alpha$.
-Comparing the percentage from both cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves its recognition.
-However, if the conveyed emotion does not match the scene, the audience does not recognize it.
-This shows that even giving information about the situation, and using a human actor to provide the context, people could not recognize the emotion if the correct features are not exploited.
-To verify this, it was done a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test.
-The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases.
-This would suggest that the combination of stimuli (scene + actor) and correct robot's movements are necessary to the correct emotional interpretation.
+The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<(\alpha = 0.05)$.
+Comparing the percentage from both the first two cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves the recognition of some emotions, but for others remains still low.
+Our hypothesis is that there must be a match between robot's movements with the given context and actors performance to increase the recognition rate.
+If one or all do not fit participants' idea of the emotion, this one is not going to be recognized.
+To verify this, a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test was done.
+The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases, which correspond to the emotions with lower recognition rate.
 This opens the question about the influence that could have the human actor and the scene on the recognition rate.
-Although the study of their influence could be beneficial, it was decided to continue the studies on the values that could be used to express emotions.
-Therefore it was devise a third case study that uses values informed in the literature.
+Although the study of this could be beneficial, it was decided to leave this to future work.
+Instead, a third case study was devised, where values presented in the literature for emotion expression in humans were adopted in the quest for more recognizable emotion expressions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Experimental setup}
+\subsection{Experimental design}
 
-From the previous experience it was decided to implemented just four emotions, which reduce the number of possible sequences.
+In order to reduce the number of possible sequences, it was decided to implemented only four emotions.
 To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma.
-The emotions implemented were: \textit{Happiness} (I quadrant), \textit{Anger} (II quadrant), \textit{Sadness} (III quadrant), and \textit{Content} (IV quadrant).
+The emotions implemented were: Happiness (I quadrant), Anger (II quadrant), Sadness (III quadrant), and Content (IV quadrant).
 To reduce the probability that the correct emotion could be selected by chance four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant.
-These emotions were: \textit{Frustration}, \textit{Boredom}, \textit{Astonishment} and \textit{Tiredness}.
-The final questionnaire had nine possibilities (eight emotions and ``Unknown'').
+These emotions were: Frustration, Boredom, Astonishment and Tiredness.
+The final questionnaire had nine possibilities (eight emotions and ``Unknown''), and was better founded on psychological theory than the previous ones.
 
-In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion the robot has expressed?}".
-The setup used in this case study is depicted in the Figure~\ref{fig:setup2}.
+In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion has the robot expressed?}".
+The setup used in this case study is depicted in Figure~\ref{fig:setup2}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Emotion Descriptions}
+\subsection{Emotion Description}
 
 Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
-Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.
+Generally speaking, these works use the Laban's model to code their emotional expressions, which is based on linguistic terms and leaves to the designer (and the reader) their specific interpretation.
 
@@
 
-	\item \textit{\textit{Anger}:} the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$.
+	\item Anger: the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$.
 An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.
 
-	\item \textit{\textit{Happiness}:} as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement.
+	\item Happiness: as in Anger, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
 	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.
 
-	\item \textit{Sadness:} the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$.
+	\item Sadness: the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$.
 This emotion expression did not include any angular rotation.
 
-	\item \textit{Content:} the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest.
+	\item Content: the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest.
 The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Study}
+\subsection{Experimental setup}
 
@@
 During the first two days, the open questionnaire was used, while during the last two days the multiple option questionnaire was used.
-The total number of volunteers for the closed list questionnaire was 91: 52 males, 38 females, and 11 that chose not to specify their gender.
+The total number of volunteers for the closed list questionnaire was 91: 52 males, 38 females, and 11 that did not specify their gender.
 The average age was 30.98 years, with standard deviation of 15.12, minimum age was 4 and maximum 71.
@@
 In table~\ref{table:open_questionnaire} are reported the results.
-In order to reduce the quantity of words, words that have a similar meaning were grouped, for example words as \textit{Fear}, \textit{Terror}, \textit{Scared}, and \textit{Worried} were grouped under the label \textit{Fear}.
-Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly.
-\textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.
+In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label Fear.
+Also, three out of four emotions (Anger, Happiness and Sadness) were at least once listed correctly.
+Sadness and Content were mostly perceived as Fear, being reported 31\% and 28\% of the time, respectively.
 
@@
 	\item The movements that could be designed as emotional are also associated to mental states of the robots.
-This is evident in the words obtained from the presentation of four ''emotional'' movements, such as \textit{cold} (referring that the robot was feeling cold), \textit{tenderness}, \textit{shyness}, \textit{power}, \textit{hurry}, \textit{looking for something}, \textit{he wants something}, \textit{enthusiasm}, \textit{sympathy}, \textit{vanity}, and \textit{obedience}.
+This is evident in the words obtained from the presentation of four ``emotional'' movements, such as: cold (referring that the robot was feeling cold), tenderness, shyness, power, hurry, looking for something, he wants something, enthusiasm, sympathy, vanity, and obedience.
 
@@
 \centering
-		\caption{Results obtained from the open questionnaire.}
+		\caption{Results obtained from the open questionnaire in the third case study.}
 		\label{table:open_questionnaire}
@@
 				\hline
-					\backslashbox{Presented}{Reported}&\textit{Anger}&\textit{Happiness}&\textit{Sadness}&\textit{Content}&Total\\
+					\backslashbox{Presented}{Reported}&Anger&Happiness&Sadness&Content&Total\\
 				\hline
-					\textit{Anger}& 3&6&7&5&21\\
+					Anger& 3&6&7&5&21\\
 				\hline
-					\textit{Happiness}&12& 18&0&6&36\\
+					Happiness&12& 18&0&6&36\\
 				\hline
-					\textit{Sadness}&0&0& 8&3&11\\
+					Sadness&0&0& 8&3&11\\
 				\hline
-					\textit{Content}&2&0&0& 0&2\\
+					Content&2&0&0& 0&2\\
 				\hline
-					\textit{Fear}&4&5&14&13&36\\
+					Fear&4&5&14&13&36\\
 				\hline
-					\textit{Tiredness}&1&0&1&1&3\\
+					Tiredness&1&0&1&1&3\\
 				\hline
-					\textit{Cold}&2&0&2&1&5\\
+					Cold&2&0&2&1&5\\
 				\hline
-					\textit{Shyness}&1&0&4&4&9\\
+					Shyness&1&0&4&4&9\\
 				\hline
-					\textit{Agitated}&4&1&0&0&5\\
+					Agitated&4&1&0&0&5\\
 				\hline
-					\textit{Power}&4&1&0&0&5\\
+					Power&4&1&0&0&5\\
 				\hline
-					\textit{Hurry}&0&1&0&0&1\\
+					Hurry&0&1&0&0&1\\
 				\hline
-					\textit{Looking for something}&1&0&1&0&2\\
+					Looking for something&1&0&1&0&2\\
 				\hline
-					\textit{He wants something}&1&0&1&0&2\\
+					He wants something&1&0&1&0&2\\
 				\hline
-					\textit{Tenderness}&1&0&1&2&4\\
+					Tenderness&1&0&1&2&4\\
 				\hline
-					\textit{Uncertainty}&1&2&0&0&3\\
+					Uncertainty&1&2&0&0&3\\
 				\hline
-					\textit{Enthusiasm}&1&0&0&0&1\\
+					Enthusiasm&1&0&0&0&1\\
 				\hline
-					\textit{Sympathy}&1&0&2&4&7\\
+					Sympathy&1&0&2&4&7\\
 				\hline
-					\textit{Curiosity}&1&2&3&3&9\\
+					Curiosity&1&2&3&3&9\\
 				\hline
-					\textit{Shame}&0&0&0&1&1\\
+					Shame&0&0&0&1&1\\
 				\hline
-					\textit{Nothing}&1&2&1&0&4\\
+					Nothing&1&2&1&0&4\\
 				\hline
-					\textit{Vanity}&1&0&0&0&1\\
+					Vanity&1&0&0&0&1\\
 				\hline
-					\textit{Obedience}&0&0&0&1&1\\
+					Obedience&0&0&0&1&1\\
 				\hline
-					\textit{Total}&43&38&44&46&171\\
+					Total&43&38&44&46&171\\
 				\hline
@@
 \small
-\caption{Answers obtained in the case study.}
+\caption{Answers obtained from the closed list group in the third case study.}
 		\label{table:result_list_emotions}
@@
 \rotatebox{90}{\backslashbox{Presented}{Reported}}&
-\rotatebox{90}{\textit{Anger}}&
-\rotatebox{90}{ \textit{Happiness}} &
-\rotatebox{90}{\textit{Sadness}}&
-\rotatebox{90}{\textit{Content}}&
-\rotatebox{90}{\textit{Frustration}}&
-\rotatebox{90}{\textit{Boredom}}&
-\rotatebox{90}{\textit{Astonishment}}&
-\rotatebox{90}{\textit{Tiredness}}&
-\rotatebox{90}{\textit{Unknown}}&
+\rotatebox{90}{Anger}&
+\rotatebox{90}{ Happiness} &
+\rotatebox{90}{Sadness}&
+\rotatebox{90}{Content}&
+\rotatebox{90}{Frustration}&
+\rotatebox{90}{Boredom}&
+\rotatebox{90}{Astonishment}&
+\rotatebox{90}{Tiredness}&
+\rotatebox{90}{Unknown}&
 \rotatebox{90}{Total}\\	
 			\hline
-				\textit{Anger}& 19&8&1&5&7&2&5&1&0&48\\
+				Anger&19&8&1&5&7&2&5&1&0&48\\
 			\hline
-				\textit{Happiness}&18& 19&0&9&5&1&5&1&0&58\\
+				Happiness&18&19&0&9&5&1&5&1&0&58\\
 			\hline
-				\textit{Sadness}&1&9& 12&2&4&5&7&6&0&46\\
+				Sadness&1&9&12&2&4&5&7&6&0&46\\
 			\hline
-				\textit{Content}&2&8&7& 4&6&8&5&10&0&50\\	
+				Content&2&8&7&4&6&8&5&10&0&50\\	
 			\hline	
@@
 An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
-Additional two confusion matrices were created: one merging the results from all high (\textit{Anger}, \textit{Happiness}, \textit{Frustration} and \textit{Astonishment}) and low (\textit{Sadness}, \textit{Content}, \textit{Boredom}, and \textit{Tiredness}) arousal emotions; and the other one merges the results of positive (\textit{Happiness}, \textit{Content}, \textit{Astonishment}, and \textit{Tiredness}) and negative (\textit{Anger}, \textit{Frustration}, \textit{Boredom}, and \textit{Sadness}) emotions.
-For each of these tables were calculated the positive predictive value, accuracy and a Pearson's $\chi^2$.
+Additional two confusion matrices were created: one merging the results from all high (Anger, Happiness, Frustration and Astonishment) and low (Sadness, Content, Boredom, and Tiredness) arousal emotions; the other matrix merges the results of positive (Happiness, Content, Astonishment, and Tiredness) and negative (Anger, Frustration, Boredom, and Sadness) emotions.
+For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated.
 The results are shown in table~\ref{table:Precision}.
@@
 
-To analyse whether each emotion expression was misinterpreted with other implementations, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of emotions implemented, which gives a total of seven combinations.
-The results suggest that the implementations of anger and happiness ($p-value=0.492$), and, respectively, sadness and content ($p-value=0.492$) are interpreted as similar, while the other emotion expressions are distinguished from each other.
+To analyse whether each emotion expression was misinterpreted with other implementations, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.
+The results suggest that the implementations of anger and happiness ($p-value=0.9$), and, respectively, sadness and content ($p-value=0.9$) are interpreted as similar, while the other emotion expressions are distinguished from each other.
 %TODO The same p-value?
 Very strange...
+PLEASE CHECK WHY
+%TODO Julian Answered: because the holm-bonferroni correction
 
-From the results of both questionnaires, we can say that \textit{Anger} and \textit{Happiness} were confused, as well \textit{Sadness} and \textit{Content}.
-\textit{Fear} was written as emotion when the two emotions with low arousal (\textit{Sadness} and \textit{Content}) were shown.
-These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions.
-
-%TODO write a sentence explaining the results and justying why the experiment and cross validation
+From the results of both questionnaires, we can say that Anger and Happiness were confused, as well Sadness and Content.
+Fear was selected as emotion when the two emotions with low arousal (Sadness and Content) were shown.
+These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions, respectively.
+With similar results between first and third case study, we decided to do an experiment to determine values that better represent some emotions~\cite{Angel2017}.
 
@@
 After the first and third case studies, it was evident the necessity to better understand how the characteristics are related with each other and how they can be used to convey emotions.
-Therefore, it was decided to perform an experiment to get a better insight on the contribution of angular and linear velocity, angle of oscillation, direction and orientation.
+Therefore, it was decided to perform an experiment~\cite{Angel2017} to get a better insight on the contribution of angular and linear velocity, angle of oscillation, direction and orientation.
 To cross-validate the data collected in this experiment, we decided to do a final case study.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Experimental setup}
+\subsection{Experimental design}
 
-From the results obtained on our experiments, we selected two combinations (angular velocity, oscillation angle, linear velocity, orientation and direction) with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in a experiment done after third case study.
+From the results obtained on our experiments, we selected two treatments with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in a experiment done after third case study.
 As in the previous case studies, a questionnaire was used.
-However, this time the emotions selected were the same used during the experiment: anger, fear, sadness and happiness.
-Moreover, two mental states were added: excited and tender, which corresponds to high and low arousal, respectively.
+This time, the emotions listed in the questionnaire were the same used during the experiment: Anger, Fear, Sadness, and Happiness.
+Moreover, two mental states were added: Excited and Tender, which correspond to high and low arousal, respectively.
 As it was done in the previous cases, the questionnaire included the option ''unknown''.
@@
 
-Table~\ref{table:result_fourth} summarizes the results obtained during the case study.
+Table~\ref{table:result_fourth} summarizes the results obtained from this fourth case study.
 
@@
 It could be observed that both implementations of Happiness are confused with Anger and Excitement, as it could have been expected.
-The first implementation of Anger was mostly confused with Excitement, which was perceived by twenty one over forty nine participants, while the second implementation showed an improvement from 10\% to 38\% on recognition.
-This implementation was perceived also has Happiness, Fear and Excitement by fourteen, twelve, and thirteen respectively.
-Both implementations of Fear have a high level of recognition 54\% and 50\% and mostly confused with excitement, nine for the first implementation and twenty for the second implementation.
-Lastly, the first implementation of Sadness was confused with Fear and Tenderness by twelve and sixteen respectively.
-The second implementation was confused again with Fear and Tenderness by thirteen and twenty-eight respectively.
+The first implementation of Anger was recognized as Anger just 10\% of the times, but it was confused as Excitement 42\%.
+On the other hand the second implementation showed an improvement from 10\% to 38\% on recognition.
+This implementation was perceived also as Happiness, Fear and Excitement by 18\%, 17\%, and 17\%, respectively.
+Both implementations of Fear have a high level of recognition 54\% and 50\% and are mostly confused with Excitement, 17\% for the first implementation and 27\% for the second implementation.
+Lastly, the first implementation of Sadness was confused with Fear and Tenderness by 26\% and 24\%, respectively.
+The second implementation was confused again with Fear and Tenderness by 19\% and 19\%, respectively.
 
@@
 The results are shown in Table~\ref{table:result_compare_fourth}.
-As the results suggest, the implementation of Anger is the only one that was considered as different.
+As the results suggest, the two implementations of Anger are the only ones that were considered as different among all others.
 
@@
 
-As it was done in the previous case studies a contingency matrix was computed.
-For each of these tables were calculated the positive predictive value, accuracy and a Pearson's $\chi^2$.
+As it was done in the previous case studies a contingency matrix was computed for each emotion 
+For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated.
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and one of Anger do not have any significant impact on the emotion perception.
+They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and the other one of Anger do not have any significant impact on the emotion perception.
 
@@
 It is important to notice that the results were obtained using the lower part of the robot without any change in shape.
-Another factor to consider is the high impact of the words enlisted in the questionnaire had in the detection rate.
-These words included two mental states that could be confused with the other four emotions enlisted, as it is reflected in the results.
-Despite the bias generated by these two words, the recognition rates of five over eight emotion expressions were over 35\%, being the two implementations of Fear the ones with the highest recognition rate (54\% for the first and 50\% for the second).
+Another factor to consider is the high impact that the terms enlisted in the questionnaire had in the detection rate.
+These terms included two mental states that could be confused with the other four emotions enlisted, as it is reflected in the results.
+Despite the bias generated by these two terms, the recognition rates for five over eight emotion expressions were over 35\%, being the two implementations of Fear the ones with the highest recognition rate (54\% for the first and 50\% for the second).

### 2016-10-30 JournalInteractionStudies/Parts/conclusions.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 
-	\item Using a real platform to perform the case studies increases the enthusiasms of the participants and possibly their willingness to participate in the study.
+	\item Using a real platform to perform the case studies triggers the enthusiasm of participants and, possibly, their willingness to participate in the study.
 Although we did not evaluate directly this item during our case studies, it was observed during the set up that people were curious to see the robot moving.
@@
 It is also necessary to recreate a simple scene to give the context to the participants, but this time just using two robots.
-This will eliminate possible clues that could be given by the human actor.
+This could eliminate possible clues that could be given by the human actor.

### 2016-10-30 JournalInteractionStudies/Parts/introduction.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context.
-Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most of the works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs.
+Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs.
 Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
@@
 
-The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments~\cite{Sharma2013}.
+The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologist~\cite{Russell2003}.
 
@@
 The next section provides a brief overview of relevant work related to emotion expression in robots.
-Section system outlines the platform used in the case studies.
-The section case studies presents the design and results for all four case studies.
+Section~\ref{sec:robotic_platform} outlines the platform used in the case studies.
+Section~\ref{sec:cases} presents the design and results for all four case studies.

### 2016-10-30 JournalInteractionStudies/Parts/system.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

@@
 This system is composed of two complementary parts: robotic platform and emotional enrichment system.
-The platform has been envisioned to be as simple as possible without any resemblance to human-like embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions.
+The platform has been envisioned to be as simple as possible without any resemblance to anthropomorphic embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions.
 
@@
 To hide the structure, foam and a light blue cloth covering the foam were used, as it could be seen  in Figure~\ref{fig:triskar-cover}.
-The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Promarker}.
+The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Naz2012}.
 
@@
 Also, it was decided to make some improvements in the upper part.
-Two reasons motivated this changes.
+Two reasons motivated these changes.
 First the deformation system was not changing the shape enough to be clearly perceived by subjects; second, the beams were damaging the foam.

### 2016-10-31 JournalInteractionStudies/Rebuttal2.txt
Update Rebuttal2.txt
I have added something and changed something. It has to be completed.

--- 2016-10-18 JournalInteractionStudies/Rebuttal2.txt
@@
 General
+* Cañamero reference has been fixed
+* The following article was added as reference: Relationship between color and emotion
+* Introduction paragraph on Case study section was extended to include the conection and create a better connection among the case studies.
+
+* One sentece to introduce the next case study was added at the end of each case study
 
@@
 *****************************************
-One sentece to introduce next case study was added at the end of each case study
+
+>>Q: First case study: There is no discussion of the results.
+Whilst the statistical analysis is now clearer, the authors should explain what has been learned in relation to theses results.
+Why were Happiness and Anger recognized?
+Do the authors have some hypothesis?
+Can any generalization be drawn?
+A: Some comments about this have been inserted
+>>Q: Second case study: What were the scenarios?
+A: a link to a video, which shows the scenarios for each emotion was added
+>>Q: "However, if the conveyed emotion does not match the scene, the audience does not recognize it.": How can the design allow for such claim?
+Is this supported by the results?
+Is it possible that only the context was recognized regardless of what the robot was doing?
+A: the sentence were changed, to "this opens the question about the influence that could have the human actor and the scene on the recognition rate".
+Anyway the case study allowed to evaluate if the presented emotion representation was coherent with the scene, as supported by data.
+This has been written in the text.
+>>Q: Third one: Why was the questionnaire changed half way?
+A: the questionnaire was canged to focus on a smalle number of emotions, according to what is done in literature.
+>>Q: It is well established that velocity is related to arousal. Why additional features are needed? The literature suggests that it is enough to discriminate between low and high velocity.
+A: The goal was to distinguish among a set of different emotions, not only on low and high arousal. The other features enable a richer characterization of emotions, as shown by data.
 

### 2016-11-08 JournalInteractionStudies/Rebuttal2.txt
Update Rebuttal2.txt

@@
 
-* One sentece to introduce the next case study was added at the end of each case study
+* One sentence to introduce the next case study was added at the end of each case study
 
@@
 >>Q: Third one: Why was the questionnaire changed half way?
-A: the questionnaire was canged to focus on a smalle number of emotions, according to what is done in literature.
+A: the questionnaire was canged to focus on a smaller number of emotions, according to what is done in literature.
 >>Q: It is well established that velocity is related to arousal. Why additional features are needed? The literature suggests that it is enough to discriminate between low and high velocity.

### 2016-11-27 JournalInteractionStudies/Parts/Emotion_Projection.tex
Add files via upload

@@
-The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused on faces.
+The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused on face poses.
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
-The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}), plus \textit{interest}.
+The face had enough degrees of freedom to portray the basic emotions such as \textit{interest} and all those suggested by Ekman~\cite{Ekman2004}: \textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}.
 
@@
 
-	\item The\textit{Locomotion} gives information about the capabilities of the platform., because, even having a human-like embodiment, it does not mean that the platform can move;
+	\item \textit{Locomotion} gives information about the  displacement capabilities of the platform;
 
@@
 
-	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
+	\item \textit{Emotions Implemented} gives the list of emotions presented to the subjects;
 
-	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The mediums considered were: movement, body posture and face poses.
+	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The considered media were: movement, body posture, and face poses.
 
@@
 
-Despite the possibility to use human actors to determine features and values to convey emotions or the findings done in the works previously discussed, there is a need to get a better understanding on how convey emotions with non-anthropomorphic platform.
-This is due to the following reasons.
+Despite the possibility to use human actors to determine features and values to convey emotions or the findings obtained in the mentioned works, there is a need to get a better understanding about how to convey emotions with non-anthropomorphic platforms.
+This is due to three main reasons.
 First, it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010} due to robots' physical capabilities.
 Second, the significance of the agreement obtained from the studies that used human actors is on discussion~\cite{Russell2003}.
-Third, no all possible features present in a non-anthropomorphic platform are studied in the literature (e.g.
+Third, some of the possible features present in a non-anthropomorphic platform are not considered in literature (e.g.
 angular velocity).

### 2016-11-27 JournalInteractionStudies/Parts/case_studies.tex
Add files via upload

@@
 The pilot was used to test the prototype and identify possible improvements.
-The features' values for the first case study were selected empirically and just robots' movement was presented to participants.
-The results suggested that was possible convey some emotions, but it was decided to give a context to each emotion to verify if that could increased the recognition rate.
-Therefore, a second case study was done.
-Each emotion was presented to the participants in a small scene, which was portrayed by the robot and a non professional human actor.
-The results suggested that showing the emotion in a context improve the recognition of some emotions.
-However the study of the impact of the actor and context were out of this research.
-To compare literature on emotion projection, a third case study was done with parameters collected from diverse works, which encoded their emotions' description using Laban's.
-With similar results between first and third case study, we decided to do an experiment to determine values that better represent some emotions~\cite{Angel2017}.
-Thus a final case study was done to cross-validate experiment's findings.
+The feature values for the first case study were selected empirically and robot's movements were presented to participants.
+The results suggested that it was possible to convey some emotions, but it was decided to give a context to each emotion to test whether this could increase the recognition rate.
+A second case study was designed.
+Each emotion was presented to the participants in the context of a small scene, which was portrayed by the robot and a non professional human actor.
+The results suggested that showing the emotion in a context can improve the recognition of some emotions, so that the robotic emotional expression could be at least perceived as coherent with the context.
+However, the study of the impact of the actor and context were not in the aims of this research.
+To compare with literature on emotion projection, a third case study was implemented using parameters collected from diverse works, which encoded their emotion implementations using Laban's model.
+Having obtained similar results in both the first and third case studies, we decided to do an experiment to determine values that could better represent some emotions~\cite{Angel2017}.
+Thus, a final case study was done to cross-validate the so-far obtained findings.
 
@@
 	\includegraphics[width=0.75\textwidth]{./Images/ExampleMovement.png}
-	\caption{Example of the features used in all case studies.
+	\caption{Example applying the features used in all case studies.
 $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$).
@@
 The sequence of rounds was generated randomly without repeating any emotion in the same sequence.
-The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride.
+The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to express, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, pride, and neutral.
 The option to answer ``Unknown'' was also included.
@@
 
-Table~\ref{table:results_1} shows that the best emotion perceived was Happiness and the worst one Disgust, with 44\% and 2\% respectively of accuracy.
+Table~\ref{table:results_1} shows that the best emotion perceived was \textit{happiness} and the worst one \textit{disgust}, with 44\% and 2\% respectively of accuracy.
 Moreover, some movements were designed to convey a specific emotion, but a different emotion was perceived.
-For example the intended Sadness was identified by 14\% of subjects exposed to it, while 25.5\% perceived it as Fear.
+For example the intended \textit{sadness} was identified by 14\% of subjects exposed to it, while 25.5\% perceived it as \textit{fear}.
 The neutral behaviour was not much considered, possibly because people, in this setting, expected to see something specific, not a neutral movement.
@@
 Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get better p-value estimation.
-The results showed that people perceived the following implementations as similar, having a $p-value>0.05$: curiosity-disgust, curiosity-embarrassment, curiosity-sadness, disgust-embarrassment, disgust-sadness, embarrassment-fear, embarrassment-sadness, and fear-sadness.
+The results showed that people perceived the following implementations as similar, having a $p-value>0.05$: \textit{curiosity-disgust}, \textit{curiosity-embarrassment}, \textit{curiosity-sadness}, \textit{disgust-embarrassment}, \textit{disgust-sadnes}s, \textit{embarrassment-fear}, \textit{embarrassment-sadness}, and \textit{fear-sadness}.
 
 Moreover, an analysis was done per groups, for each presented emotion.
-Excluding unknown and uncertain answers, we have considered the answers of each subject that was presented an emotion produced by the robot.
+Excluding unknown and uncertain answers, we have considered the answers of each subject to whom an emotion produced by the robot was presented.
 For each emotion we considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one (in any of the other two experiences each did), and how many recognized an emotion different from the considered one when presented a different emotion.
-This lead for each presented emotion to a table like the one reported in Table~\ref{table:singleEmotion} for Happiness.
+This lead to a table for each presented emotion, like the one reported in Table~\ref{table:singleEmotion} for \textit{happiness}.
 
@@
 \small
-\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness for the first case study).}
+\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here \textit{happiness} for the first case study).}
 \label{table:singleEmotion}
@@
 
-For each of these tables the classification accuracy and the no-information rate (NIR), i.e.
-the accuracy that had been obtained by random selection, have been computed with the R package CARET~\cite{caret}.
-The results show that some implementations of emotion expression (i.e., Anger ($p-value=1e-3$) and Happiness ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.
+For each of these tables the classification accuracy and the no-information rate (NIR), i.e., the accuracy that had been obtained by random selection, have been computed with the R package CARET~\cite{caret}.
+The results show that some implementations of emotion expression (i.e., \textit{anger} ($p-value=1e-3$) and \textit{happiness} ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.
 
 The result shows that it is possible to convey some emotions using just movement and a non-bio-inspired embodiment.
-In particular, stronger emotions have been recognized better than milder ones, and emotions typically conveyed by facial expressions (e.g., Disgust) were less recognized.
+In particular, stronger emotions have been recognized better than milder ones, and emotions typically conveyed by facial expressions (e.g., \textit{disgust}) were less recognized.
 %%%%%%%%%%%%%%%%%%%%%
@@
 
-A little scene was created for each emotion were an actor played the stimulus to trigger an emotion\footnote{The scenes could be seen in the following link \url{https://www.youtube.com/watch?v=AXAglJKLwbI}}; for instance, he yelled at the robot that then showed fear.
+A little scene was created for each emotion were an actor played the stimulus to trigger an emotion\footnote{The scenes could be seen following the link \url{https://www.youtube.com/watch?v=AXAglJKLwbI}}; for instance, he yelled at the robot that then showed \textit{fear}.
 The procedure and questionnaire were the same as those adopted for the first case.
-However, a variant of the Fear emotion (Fear2) was added, in which the robot finishes its trajectory far from the person.
+However, a variant of the \textit{fear} emotion (\textit{Fear2}) was added, in which the robot finishes its trajectory far from the person.
 As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups.
@@
 
-As in the first case study, the total distance covered by the robot was $1.5 m$, but this time the robot was facing the actor.
-The distance from the participants to the robot and actor was $1.5 m$, as shown in Figure~\ref{fig:setup2}.
+As in the first case study, the total distance covered by the robot was $1.5 m$, but this time the robot was facing the actor, instead than the public.
+The distance from the participants to the scene (including robot and actor) was $1.5 m$, as shown in Figure~\ref{fig:setup2}.
 
@@
 
-The laboratory open day of 2013 was used to perform the scenes and to collect data.
+The laboratory Open Day was used to perform the scenes and to collect data.
 Eight groups participated, each one with approximately 20 volunteers for a total of 156: 51 males, 17 females, and 88 that did not provide their gender.
@@
 
-In the second case study, the results were considerably better, where four out of the nine showed emotions had a percentage of recognition higher than 60\% (Anger, Happiness, Curiosity and Fear2).
+In this second case study, the results were considerably better: four out of the nine showed emotion representations had a recognition percentage higher than 60\% (Anger, Happiness, Curiosity and Fear2).
 Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions.
@@
 Comparing the percentage from both the first two cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves the recognition of some emotions, but for others remains still low.
-Our hypothesis is that there must be a match between robot's movements with the given context and actors performance to increase the recognition rate.
-If one or all do not fit participants' idea of the emotion, this one is not going to be recognized.
+Our hypothesis is that there must be a match between robot's movements with the given context and actor's performance to increase the recognition rate.
+If one or both do not fit participants' idea of the emotion, this one is not going to be recognized.
 To verify this, a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test was done.
@@
 
-The third case study was designed to explore the possibility to adopt for robot's movements the emotional movement descriptions reported in human body studies, and followed the methodology used by Sharma and collaborators~\cite{Sharma2013} to select the emotions to be implemented and enlisted in the questionnaire.
+The third case study was designed to explore the possibility to adopt for robot's movements the emotional movement descriptions reported in human body studies.
+The methodology used by Sharma and collaborators~\cite{Sharma2013} was adopted to select the emotions to be implemented and enlisted in the questionnaire.
 The second version of the platform was used in this case study (Figure~\ref{fig:triskar-second-design}).
@@
 To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma.
-The emotions implemented were: Happiness (I quadrant), Anger (II quadrant), Sadness (III quadrant), and Content (IV quadrant).
-To reduce the probability that the correct emotion could be selected by chance four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant.
-These emotions were: Frustration, Boredom, Astonishment and Tiredness.
+The implemented emotions were: \textit{happiness} (I quadrant), \textit{anger} (II quadrant), \textit{sadness} (III quadrant), and \textit{content} (IV quadrant).
+To reduce the probability that the correct emotion could be selected by chance, four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant.
+These emotions were: \textit{frustration}, \textit{boredom}, \textit{astonishment}, and \textit{tiredness}.
 The final questionnaire had nine possibilities (eight emotions and ``Unknown''), and was better founded on psychological theory than the previous ones.
 
-In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion has the robot expressed?}".
+In order to study the influence that could be generated by the given list of emotions to the participants, it was presented, to another set of subjects, an open questionnaire that did not list any emotion, but rather had a space where they could write a term to answer the question: "\textit{What emotion has the robot expressed?}".
 The setup used in this case study is depicted in Figure~\ref{fig:setup2}.
@@
 Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
-Generally speaking, these works use the Laban's model to code their emotional expressions, which is based on linguistic terms and leaves to the designer (and the reader) their specific interpretation.
+Generally speaking, these works use the Laban's model to code their emotional expressions, which is based on linguistic terms and leaves to the designer their specific interpretation.
 
@@
 From the open questionnaire, different terms to describe both emotions and mental states were obtained.
-In table~\ref{table:open_questionnaire} are reported the results.
+The results are reported in table~\ref{table:open_questionnaire}.
 In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label Fear.
@@
 
-From these results is possible to highlight two important facts:
+From these results two important facts emerge.
 
@@
 
-	\item The movements that could be designed as emotional are also associated to mental states of the robots.
+	\item The movements that could be designed as emotional are also associated to mental states attributed to the robot.
 This is evident in the words obtained from the presentation of four ``emotional'' movements, such as: cold (referring that the robot was feeling cold), tenderness, shyness, power, hurry, looking for something, he wants something, enthusiasm, sympathy, vanity, and obedience.
@@
 An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
-Additional two confusion matrices were created: one merging the results from all high (Anger, Happiness, Frustration and Astonishment) and low (Sadness, Content, Boredom, and Tiredness) arousal emotions; the other matrix merges the results of positive (Happiness, Content, Astonishment, and Tiredness) and negative (Anger, Frustration, Boredom, and Sadness) emotions.
+Additional two confusion matrices were created: one merging the results from all high (\textit{anger}, \textit{happiness}, \textit{frustration} and \textit{astonishment}) and low (\textit{sadness}, \textit{content}, \textit{boredom}, and \textit{tiredness}) arousal emotions; the other matrix merges the results of positive (\textit{happiness}, \textit{content}, \textit{astonishment}, and \textit{tiredness}) and negative (\textit{anger}, \textit{frustration}, \textit{boredom}, and \itemsadness) emotions.
 For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated.
 The results are shown in table~\ref{table:Precision}.
-They show that there is significant evidence to conclude that anger, happiness, and sadness have an impact in the perception of the emotion, while the implementation of content does not have any significant impact in the emotion perception.
+They show that there is significant evidence to conclude that \textit{anger}, \textit{\textit{happiness}}, and \textit{sadness} could be perceived, while the implementation of \textit{content} was not significantly recognized.
 Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence.
@@
 
-To analyse whether each emotion expression was misinterpreted with other implementations, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.
-The results suggest that the implementations of anger and happiness ($p-value=0.9$), and, respectively, sadness and content ($p-value=0.9$) are interpreted as similar, while the other emotion expressions are distinguished from each other.
-%TODO The same p-value?
-Very strange...
-PLEASE CHECK WHY
-%TODO Julian Answered: because the holm-bonferroni correction
+To analyse whether any emotion expression was misinterpreted with any other, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.
+The results suggest that the implementations of \textit{anger} and \textit{happiness} ($p-value=0.9$), and, respectively, \textit{sadness} and \textit{content} ($p-value=0.9$) are interpreted as similar, while all the other emotion expressions are distinguished from each other.
 
-From the results of both questionnaires, we can say that Anger and Happiness were confused, as well Sadness and Content.
-Fear was selected as emotion when the two emotions with low arousal (Sadness and Content) were shown.
+From the results of both questionnaires, we can say that \textit{anger} and \textit{happiness} were confused, as well \textit{sadness} and \textit{content}.
+\textit{Fear} was selected when the two emotions with low arousal (\textit{sadness} and \textit{content}) were shown.
 These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions, respectively.
-With similar results between first and third case study, we decided to do an experiment to determine values that better represent some emotions~\cite{Angel2017}.
+Having obtained similar results in the first and third case studies, we decided to design an experiment to identify values that could lead to better expressions of some emotions~\cite{Angel2017}.
 
@@
 
-From the results obtained on our experiments, we selected two treatments with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in a experiment done after third case study.
+From the results obtained on our experiments, we selected two emotion implementations with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in an experiment done after the third case study.
 As in the previous case studies, a questionnaire was used.
-This time, the emotions listed in the questionnaire were the same used during the experiment: Anger, Fear, Sadness, and Happiness.
-Moreover, two mental states were added: Excited and Tender, which correspond to high and low arousal, respectively.
+This time, the emotions listed in the questionnaire were the same used during the experiment: \textit{anger}, \textit{fear}, \textit{sadness}, and \textit{happiness}.
+Moreover, two mental states were added: \textit{excited} and \textit{tender}, which correspond to high and low arousal, respectively.
 As it was done in the previous cases, the questionnaire included the option ''unknown''.
 Although the platform used was the last version (Figure~\ref{fig:triskar-third-design}), the upper part was cut off to allow comparisons with the platform used in the other experiments.
-The case study set up could be seen in the Figure~\ref{fig:setup_fourth}.
+The case study set up could be seen in Figure~\ref{fig:setup_fourth}.
 
@@
 
-The selected emotion descriptions could be seen in Table~\ref{table:features_2}
+The parameter's values for the selected emotions are presented in Table~\ref{table:features_2}.
 \begin{table}[tbh]
@@
 
-It could be observed that both implementations of Happiness are confused with Anger and Excitement, as it could have been expected.
-The first implementation of Anger was recognized as Anger just 10\% of the times, but it was confused as Excitement 42\%.
-On the other hand the second implementation showed an improvement from 10\% to 38\% on recognition.
-This implementation was perceived also as Happiness, Fear and Excitement by 18\%, 17\%, and 17\%, respectively.
-Both implementations of Fear have a high level of recognition 54\% and 50\% and are mostly confused with Excitement, 17\% for the first implementation and 27\% for the second implementation.
-Lastly, the first implementation of Sadness was confused with Fear and Tenderness by 26\% and 24\%, respectively.
-The second implementation was confused again with Fear and Tenderness by 19\% and 19\%, respectively.
+It could be observed that both implementations of \textit{happiness} are confused with \textit{anger} and \textit{excitement}, as it could have been expected.
+The first implementation of \textit{anger} was recognized as \textit{anger} just 10\% of the times, but it was confused as \textit{excitement} 42\%.
+On the other hand, the second implementation showed an improvement from 10\% to 38\% on recognition.
+This implementation was perceived also as \textit{happiness}, \textit{fear} and \textit{excitement} by 18\%, 17\%, and 17\%, respectively.
+Both implementations of \textit{fear} have a high level of recognition 54\% and 50\% and are mostly confused with \textit{excitement}, 17\% for the first implementation and 27\% for the second implementation.
+Lastly, the first implementation of \textit{sadness} was confused with \textit{fear} and \textit{tenderness} by 26\% and 24\%, respectively.
+The second implementation was confused again with \textit{fear} and \textit{tenderness} by 19\% and 19\%, respectively.
 
@@
 The results are shown in Table~\ref{table:result_compare_fourth}.
-As the results suggest, the two implementations of Anger are the only ones that were considered as different among all others.
+As the results suggest, the two implementations of \textit{anger} are the only ones that were considered as different from all others.
 
@@
 
-As it was done in the previous case studies a contingency matrix was computed for each emotion 
+As it was done in the previous case studies a contingency matrix was computed for each emotion. 
 For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated.
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that one implementation of Anger, and both those of Fear and Sadness have an impact in the perception of the emotion, while both implementations of Happiness and the other one of Anger do not have any significant impact on the emotion perception.
+They show that there is significant evidence to conclude that one implementation of \textit{anger}, and both those of \textit{fear} and \textit{sadness} could be perceived correctly, while both implementations of \textit{happiness} and the other one of \textit{anger} were not.
 

### 2016-11-27 JournalInteractionStudies/Parts/conclusions.tex
Add files via upload

@@
 	\item It is possible to convey emotions through changes in angular and linear velocity of a non-bio-inspired body also without changes in the body shape.
-This lesson opens the door to the inclusion of simple "emotion" to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.
+This lesson opens the door to the inclusion of simple emotion representation to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.
 
@@
 Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions.
-For example, the action Fear was well perceived by the participants when the robot get far from them, as they were inducing it.
+For example, the emotional expression of \textit{fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.
 
 	\item Giving the participants the possibility to write their interpretation of the robot's movements was not going to be helpful to assess what emotion they thought the robot was conveying during case studies.
-Although there are plenty of procedures that have been proposed to determine the emotion that a person could be thinking at (e.g., SAM), they could just be used in a controlled environment where the experimenter could spend long periods of time with the participant.
+Although there are plenty of procedures proposed to determine the emotion that a person could be thinking at (e.g., SAM), they could be used only in a controlled environment where the experimenter could spend long periods of time with each subject.
 This is not the case of exhibitions where people would agree to stop just for a couple of minutes.

### 2016-11-27 JournalInteractionStudies/Parts/introduction.tex
Add files via upload

@@
 Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs.
-Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
+Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting in emotion expressions that could not be broadly used in most platforms.
 There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others.
@@
 
-The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologist~\cite{Russell2003}.
+The obtained results show that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologists~\cite{Russell2003}.
 

### 2016-11-30 JournalInteractionStudies/Parts/Emotion_Projection.tex
Minor changes based on the last comments

@@
 The last approach is the empirical approach, where researches come with poses and movements based on their own experience~\cite{Canamero2010,Beck2010,Arras2012,Brown2014}.
-One major finding from diverse works~\cite{Canamero2010,Beck2010,Brown2014} is that moving the head up improved the identification of pride, happiness, and excitement.
-While moving the head down improved the identification of anger and sadness.
+One major finding from diverse works~\cite{Canamero2010,Beck2010,Brown2014} is that moving the head up improved the identification of \textit{pride}, \textit{happiness}, and \textit{excitement}.
+While moving the head down improved the identification of \textit{anger} and \textit{sadness}.
 
@@
 
-It is important to mention the use of Laban’s Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}.
+It is important to mention the use of Laban's Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}.
 Besides the fact that these works report that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the relationship between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.
@@
 
-	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
+	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two.
 
-	\item \textit{Platform used} gives the name of the platform used on the study;
+	\item \textit{Platform used} gives the name of the platform used on the study.
 
-	\item \textit{Locomotion} gives information about the  displacement capabilities of the platform;
+	\item \textit{Locomotion} gives information about the  displacement capabilities of the platform.
 
@@
 
-	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
+	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method.
 
-	\item \textit{Emotions Implemented} gives the list of emotions presented to the subjects;
+	\item \textit{Emotions Implemented} gives the list of emotions presented to the subjects.
 

### 2016-11-30 JournalInteractionStudies/Parts/case_studies.tex
Minor changes based on the last comments

@@
 A second case study was designed.
-Each emotion was presented to the participants in the context of a small scene, which was portrayed by the robot and a non professional human actor.
+Each emotion was presented to the participants in a context of a small scene, which was portrayed by the robot and a non-professional human actor.
 The results suggested that showing the emotion in a context can improve the recognition of some emotions, so that the robotic emotional expression could be at least perceived as coherent with the context.
@@
 To compare with literature on emotion projection, a third case study was implemented using parameters collected from diverse works, which encoded their emotion implementations using Laban's model.
-Having obtained similar results in both the first and third case studies, we decided to do an experiment to determine values that could better represent some emotions~\cite{Angel2017}.
+Having obtained similar results in both first and third case studies, we decided to do an experiment to determine values that could better represent some emotions~\cite{Angel2017}.
 Thus, a final case study was done to cross-validate the so-far obtained findings.
@@
 The sequence of rounds was generated randomly without repeating any emotion in the same sequence.
-The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to express, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, pride, and neutral.
+The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to express, selecting among a set of nine possible options: \textit{anger}, \textit{curiosity}, \textit{disgust}, \textit{embarrassment}, \textit{fear}, \textit{happiness}, \textit{sadness}, \textit{pride}, and \textit{neutral}.
 The option to answer ``Unknown'' was also included.
@@
 
-Additionally, every time that a new emotion was showed, the robot started $1.5 mts$ away from the participants, with its front facing them, as shown in  Figure~\ref{fig:setup}.
+Additionally, every time that a new emotion was showed, the robot started $1.5 m$ away from the participants, with its front facing them, as shown in  Figure~\ref{fig:setup}.
 
@@
 
-It was decided to follow an empirical design for this case study, by considering the features that could be changed in the robot base and by composing them to express some basic emotions.
-The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.
-The features that could be easily perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:
+It was decided to follow an empirical design for this case study, by considering features that could be changed in the robot base and by composing them to express some basic emotions.
+The first implementations were tested and tuned basing on the emotions perceived by us from the robot's movement.
+The features that could be easily perceived are summarized in table~\ref{table:features}, and each selected feature is described here below:
 
@@
 \hline
-%Fear 2 & Slow & Yes-2 & Close-2 + Asymmetric & Small & None & Small \\
-%\hline
 Embarr. & Slow & No & Asy. & Large & Slow & Small \\
@@
 
-There was no specific group size, since this was determined by the amount of people that got close to the booth at a given moment.
+There was no specific group size, since this was determined by the amount of people that got close to the both at a given moment.
 Therefore, there were groups with just one person and others with 24 persons.
@@
 
-In this second case study, the results were considerably better: four out of the nine showed emotion representations had a recognition percentage higher than 60\% (Anger, Happiness, Curiosity and Fear2).
-Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions.
+In this second case study, the results were considerably better: four out of the nine showed emotion representations had a recognition percentage higher than 60\% (\textit{Anger}, \textit{Happiness}, \textit{Curiosity} and \textit{Fear2}).
+Another important point to highlight is that \textit{Sadness}, \textit{Fear} and \textit{Embarrassment} were still perceived as different emotions.
 As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions.
-The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<(\alpha = 0.05)$.
+The results suggest that no implementation was considered as similar by the participants, since for all we have $p-value<(\alpha = 0.05)$.
 Comparing the percentage from both the first two cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves the recognition of some emotions, but for others remains still low.
@@
 To verify this, a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test was done.
-The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases, which correspond to the emotions with lower recognition rate.
+The results suggest that implementations of \textit{Disgust} ($p=0.088$), \textit{Fear} ($p=0.206$) and \textit{Sadness} ($p=0.269$) are perceived as the same in both cases, which correspond to the emotions with lower recognition rate.
 This opens the question about the influence that could have the human actor and the scene on the recognition rate.
@@
 To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma.
-The implemented emotions were: \textit{happiness} (I quadrant), \textit{anger} (II quadrant), \textit{sadness} (III quadrant), and \textit{content} (IV quadrant).
+The implemented emotions were: \textit{Happiness} (I quadrant), \textit{Anger} (II quadrant), \textit{Sadness} (III quadrant), and \textit{Content} (IV quadrant).
 To reduce the probability that the correct emotion could be selected by chance, four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant.
-These emotions were: \textit{frustration}, \textit{boredom}, \textit{astonishment}, and \textit{tiredness}.
+These emotions were: \textit{Frustration}, \textit{Boredom}, \textit{Astonishment}, and \textit{Tiredness}.
 The final questionnaire had nine possibilities (eight emotions and ``Unknown''), and was better founded on psychological theory than the previous ones.
@@
 
-	\item Anger: the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$.
+	\item \textit{Anger}: the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$.
 An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.
 
-	\item Happiness: as in Anger, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
+	\item \textit{Happiness}: as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement.
 	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.
 
-	\item Sadness: the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$.
+	\item \textit{Sadness}: the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$.
 This emotion expression did not include any angular rotation.
 
-	\item Content: the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest.
+	\item \textit{Content}: the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest.
 The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
@@
 The results are reported in table~\ref{table:open_questionnaire}.
-In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label Fear.
-Also, three out of four emotions (Anger, Happiness and Sadness) were at least once listed correctly.
-Sadness and Content were mostly perceived as Fear, being reported 31\% and 28\% of the time, respectively.
+In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label \textit{Fear}.
+Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly.
+\textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being reported 31\% and 28\% of the time, respectively.
 
@@
 
-	\item The language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion.
+	\item Language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion.
 
-	\item The movements that could be designed as emotional are also associated to mental states attributed to the robot.
+	\item Movements that could be designed as emotional are also associated to mental states attributed to the robot.
 This is evident in the words obtained from the presentation of four ``emotional'' movements, such as: cold (referring that the robot was feeling cold), tenderness, shyness, power, hurry, looking for something, he wants something, enthusiasm, sympathy, vanity, and obedience.
@@
 			\hline	
-\rotatebox{90}{\backslashbox{Presented}{Reported}}&
+\backslashbox{Presented}{Reported}&
 \rotatebox{90}{Anger}&
@@
 An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
-Additional two confusion matrices were created: one merging the results from all high (\textit{anger}, \textit{happiness}, \textit{frustration} and \textit{astonishment}) and low (\textit{sadness}, \textit{content}, \textit{boredom}, and \textit{tiredness}) arousal emotions; the other matrix merges the results of positive (\textit{happiness}, \textit{content}, \textit{astonishment}, and \textit{tiredness}) and negative (\textit{anger}, \textit{frustration}, \textit{boredom}, and \itemsadness) emotions.
+Additionally, two confusion matrices were created: one merging the results from all high (\textit{Anger}, \textit{Happiness}, \textit{Frustration} and \textit{Astonishment}) and low (\textit{Sadness}, \textit{Content}, \textit{Boredom}, and \textit{Tiredness}) arousal emotions; the other matrix merges the results of positive (\textit{Happiness}, \textit{Content}, \textit{Astonishment}, and \textit{Tiredness}) and negative (\textit{Anger}, \textit{Frustration}, \textit{Boredom}, and \textit{Sadness}) emotions.
 For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated.
 The results are shown in table~\ref{table:Precision}.
-They show that there is significant evidence to conclude that \textit{anger}, \textit{\textit{happiness}}, and \textit{sadness} could be perceived, while the implementation of \textit{content} was not significantly recognized.
+They show that there is significant evidence to conclude that \textit{Anger}, \textit{\textit{Happiness}}, and \textit{Sadness} could be perceived, while the implementation of \textit{Content} was not significantly recognized.
 Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence.
@@
 
-To analyse whether any emotion expression was misinterpreted with any other, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.
-The results suggest that the implementations of \textit{anger} and \textit{happiness} ($p-value=0.9$), and, respectively, \textit{sadness} and \textit{content} ($p-value=0.9$) are interpreted as similar, while all the other emotion expressions are distinguished from each other.
+To analyse whether any emotion expression was misinterpreted among them, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.
+The results suggest that the implementations of \textit{Anger} and \textit{Happiness} ($p-value=0.9$), and, respectively, \textit{Sadness} and \textit{Content} ($p-value=0.9$) are interpreted as similar, while all the other emotion expressions are distinguished from each other.
 
-From the results of both questionnaires, we can say that \textit{anger} and \textit{happiness} were confused, as well \textit{sadness} and \textit{content}.
-\textit{Fear} was selected when the two emotions with low arousal (\textit{sadness} and \textit{content}) were shown.
+From the results of both questionnaires, we can say that \textit{Anger} and \textit{Happiness} were confused, as well \textit{Sadness} and \textit{Content}.
+\textit{Fear} was selected when the two emotions with low arousal (\textit{Sadness} and \textit{Content}) were shown.
 These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions, respectively.
@@
 As in the previous case studies, a questionnaire was used.
-This time, the emotions listed in the questionnaire were the same used during the experiment: \textit{anger}, \textit{fear}, \textit{sadness}, and \textit{happiness}.
-Moreover, two mental states were added: \textit{excited} and \textit{tender}, which correspond to high and low arousal, respectively.
+This time, the emotions listed in the questionnaire were the same used during the experiment: \textit{Anger}, \textit{Fear}, \textit{Sadness}, and \textit{Happiness}.
+Moreover, two mental states were added: \textit{Excited} and \textit{Tender}, which correspond to high and low arousal, respectively.
 As it was done in the previous cases, the questionnaire included the option ''unknown''.
@@
 
-It could be observed that both implementations of \textit{happiness} are confused with \textit{anger} and \textit{excitement}, as it could have been expected.
-The first implementation of \textit{anger} was recognized as \textit{anger} just 10\% of the times, but it was confused as \textit{excitement} 42\%.
+It could be observed that both implementations of \textit{Happiness} are confused with \textit{Anger} and \textit{Excitement}, as it could have been expected.
+The first implementation of \textit{Anger} was recognized as \textit{Anger} just 10\% of the times, but it was confused as \textit{Excitement} 42\%.
 On the other hand, the second implementation showed an improvement from 10\% to 38\% on recognition.
-This implementation was perceived also as \textit{happiness}, \textit{fear} and \textit{excitement} by 18\%, 17\%, and 17\%, respectively.
-Both implementations of \textit{fear} have a high level of recognition 54\% and 50\% and are mostly confused with \textit{excitement}, 17\% for the first implementation and 27\% for the second implementation.
-Lastly, the first implementation of \textit{sadness} was confused with \textit{fear} and \textit{tenderness} by 26\% and 24\%, respectively.
-The second implementation was confused again with \textit{fear} and \textit{tenderness} by 19\% and 19\%, respectively.
+This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement} by 18\%, 17\%, and 17\%, respectively.
+Both implementations of \textit{Fear} have a high level of recognition 54\% and 50\% and are mostly confused with \textit{Excitement}, 17\% for the first implementation and 27\% for the second implementation.
+Lastly, the first implementation of \textit{Sadness} was confused with \textit{Fear} and \textit{Tenderness} by 26\% and 24\%, respectively.
+The second implementation was confused again with \textit{Fear} and \textit{Tenderness} by 19\% and 19\%, respectively.
 
-To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied for 10 different combinations.
+To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied to 10 different combinations.
 The results are shown in Table~\ref{table:result_compare_fourth}.
-As the results suggest, the two implementations of \textit{anger} are the only ones that were considered as different from all others.
+As results suggest, two implementations of \textit{Anger} are the only ones that were considered as different from all others.
 
@@
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that one implementation of \textit{anger}, and both those of \textit{fear} and \textit{sadness} could be perceived correctly, while both implementations of \textit{happiness} and the other one of \textit{anger} were not.
+They show that there is significant evidence to conclude that one implementation of \textit{Anger}, and both those of \textit{Fear} and \textit{Sadness} could be perceived correctly, while both implementations of \textit{Happiness} and the other one of \textit{Anger} were not.
 

### 2016-11-30 JournalInteractionStudies/Parts/conclusions.tex
Minor changes based on the last comments

@@
 
-	\item The change in the body shape increases the emotion identification rate of the observers.
+	\item Change in the body shape increases the emotion identification rate of the observers.
 However, the characteristics that should be changed to increment the emotions perception are still to be investigated.
@@
 Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions.
-For example, the emotional expression of \textit{fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.
+For example, the emotional expression of \textit{Fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.
 

### 2016-11-30 JournalInteractionStudies/Parts/system.tex
Add files via upload
Minor changes based on the last comments

@@
-The system used in the case studies here reported has been developed to support the identification of features that could be used to project emotions with a non-bio-inspired platform.
+The system used in the case studies here reported has been developed to support identification of features that could be used to project emotions with a non-bio-inspired platform.
 This system is composed of two complementary parts: robotic platform and emotional enrichment system.
@@
 \subsection{Robotic Platform}
-The platform is a holonomic base, as shown in Figure~\ref{fig:holonomic-platform}.
+The platform is a holonomic base, shown in Figure~\ref{fig:holonomic-platform}.
 The first prototype included three metal gear motors with encoders, an Arduino Mega micro-controller, one servo motor and X-Bee system to enable the communication between Arduino and a remote computer.
 The mechanical design of the prototype is shown in Figure~\ref{fig:triskar-prototype}.
-A PID controller for each wheel was implemented and tuned to guarantee linear and angular velocity.
+A PID controller for each wheel was implemented and tuned to guarantee the desired linear and angular velocity.
 
-This prototype was modified after the first experiments to improve the expressiveness of the upper part.
-Two additional servo motors and a mechanical structure to support all these motors were added.
+This prototype was modified after the first case study to improve the expressiveness of the upper part.
+Two additional servo motors and mechanical structure to support all these motors were added.
 The two motors attached to beams could be controlled to obtain an asymmetric or opening-closing movement.
@@
 To hide the structure, foam and a light blue cloth covering the foam were used, as it could be seen in Figure~\ref{fig:triskar-cover}.
-The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Naz2012}.
+The light blue color was selected to not generate any particular arousal in people~\cite{Naz2012}.
 
@@
 Two reasons motivated these changes.
-First the deformation system was not changing the shape enough to be clearly perceived by subjects; second, the beams were damaging the foam.
+First the upper deformation was not clearly perceived by subjects; second, the beams were damaging the foam.
 Therefore, a lever was added to the deformation motor, and a piece of rubber was adopted to safely connect the beams with the foam.
@@
 	\centering
-	\includegraphics[width=\textwidth]{./Images/upperFirstB.png}
-	\caption{Platform prototype.}
-	\label{fig:triskar-prototype}
+	\includegraphics[width=\textwidth]{./Images/upperSecondC.png}
+	\caption{First version blueprint.}
+	\label{fig:triskar-first-design}
 	\end{subfigure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{./Images/upperSecondC.png}
-	\caption{First version design.}
-	\label{fig:triskar-first-design}
+	\includegraphics[width=\textwidth]{./Images/upperThirdD.png}
+	\caption{Second version blueprint.}
+	\label{fig:triskar-second-design}
 	\end{subfigure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{./Images/upperThirdD.png}
-	\caption{Second version design.}
-	\label{fig:triskar-second-design}
+	\includegraphics[width=\textwidth]{./Images/upperFourthD.png}
+	\caption{Third version blueprint.}
+	\label{fig:triskar-third-design}
 	\end{subfigure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{./Images/upperFourthD.png}
-	\caption{Third version design.}
-	\label{fig:triskar-third-design}
+	\includegraphics[width=\textwidth]{./Images/upperFirstB.png}
+	\caption{Final version blueprint.}
+	\label{fig:triskar-prototype}
 	\end{subfigure}

### 2016-12-06 HRI-LBR/HRI-LBR2017.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

\documentclass{sig-alternate-05-2015}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{url}
\usepackage{caption}
\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%
% --- Author Metadata here ---
\conferenceinfo{HRI}{'17 Vienna, Austria}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Towards an Enriching Robot's Actions with Affective Movements}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
Author name\\
       \affaddr{Author institution}\\
       \affaddr{Institution's address}\\
       \affaddr{City}\\
       \email{mail@mail.com}
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
%\alignauthor
%Julian M. Angel-Fernandez\\
%       \affaddr{Automation and Control Institute, Vienna University of Technology}\\
%       \affaddr{Karlspltz 13, 1040}\\
%       \affaddr{Vienna, Austria}\\
%       \email{jangelfe@tuwien.ac.at}
%% 2nd. author
%\alignauthor
%Andrea Bonarini\\
%       \affaddr{Dipartimento di Elettronica, Informazione e Bioingegneria, Politecnico di Milano}\\
%       \affaddr{Piazza Leonardo da Vinci 31, 20133}\\
%       \affaddr{Milan, Italy}\\
%       \email{andrea.bonarini@polimi.it}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues. Although there have been works that have studied emotion expression in robotics, the mechanism created to project emotion are highly integrated to their solutions. This unable the possibility to create a general approach. 
This paper presents a system that has been initially created for a theatrical robot to enrich with emotions its actions, but it has been designed to be adaptable to other fields. The emotional enrichment system has been envisioned to be used with any action decision system. 
\end{abstract}

\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Human-Robot Interaction; Emotions Enrichment System; Emotion Projection}

\section{Introduction}
The development of fast, cheap and reliable electronics has enabled the creation of new devices and versatile robotic platforms. These new platforms' capabilities have expanded the frontiers of robots applications  to new environments, where robots are expected to interact with humans, such as health care, house cleaning, among others. However, bringing robots in these context raise the challenge to increase their acceptance. Although improving robots' appearances and capabilities could be though as a possible solution, it is probable that people would treat robots as humans has they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill their expectations.

Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}. As consequence researchers~\cite{Breazeal2002} have added specific emotional poses and expression to their robots. Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}. Nevertheless, these works have developed modules to show emotions that are strongly integrated to their solutions, which eliminate the possibility to re-use or adapt their solutions into other projects.

This paper presents an Emotional Enrichment System, which modify actions' parameters and add additional actions to create the illusion of emotion expression in a robot. Although the system was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extendable to other platforms and adaptable to new tasks. To achieve this goal, the system relies on an Emotional Execution Tree, which is based on simple actions or primitive, sequential and parallel nodes. Additionally, it is used the concept of compound actions to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions  generated by specific combinations of simple actions and other nodes.

\section{Emotional Enrichment System}

The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional action". To obtain a differentiation between previous approaches, the system has been envisioned to also allow: (i) interoperability among different platform, (ii) introduction of new parameters and emotions and (iii) interface with diverse action decision systems.

Therefore, the system could be thought as a black-box that receives a desired action and emotion to blend them together through addition of other actions and modification of actions' parameters. This modification is done following the description given in two configuration files. One defines how actions' parameters should be modified and what actions should be added to project the specific emotion. The second file describes "personal" traits to specific emotions. For example, one person could intensify his happiness but conceal his sadness.

\subsection{Basic Concepts}

The system is founded on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}.  \textit{Simple actions} are actions that are considered as primitives and they are used as building blocks. Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place. Their description specifies mandatory and optional parameters that are required to execute the action. \textit{Compound actions} are actions that are created from simple actions. As it could be expected, these actions are not implemented in the system but if it is required they can be described in it (e.g. compound actions that are used often). \textit{Action message} establishes the structure of the message to describe any kind of action (i.e. simple and compound). This message also specifies how the actions are executed (i.e. parallel or sequential) and which action is the predominant (i.e. primary and secondary). \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action. This description could also include addition of other simple actions. \textit{Character description} enables the possibility to establish how to modify emotions expression to generate diverse treats. Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed. This tree is first created from the action message description and then modified using the emotional parameters and character description.

\subsection{Emotional Execution Tree}

Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertices and $|E|$ edges. The root and non-leaf nodes could be \textit{parallel} or \textit{sequence} type. The parallel node could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous. Sequential nodes could just be one of two sub-types: (i) emotion synchronous or (ii) asynchronous. Action synchronous means that each time that a parallel node receives a finish notification (i.e. success or failure), it will send a finish message to all the nodes that derived from it. On the other hand, emotion synchronous means that each time that a node (i.e. sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches.

This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action and also lets synchronization among parallel actions. Finally, leaf nodes could only be simple action nodes. All nodes can assume two levels: principal or  secondary. If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary cannot propagate any message to its predecessor.

\subsection{Process}

Every time the system is launched, it starts reading emotion and character descriptors, and it creates an internal representation. Every time that the system receives a new action message, which includes action's name with its parameters values, the verification process starts. If the action is compound, it is first decomposed in simple actions, which will be labeled as primary actions, and checked if all actions exists in the system and the parameters correspond to the specification. If both conditions are fulfilled, the system generates an Emotion Execution Tree that represents the specified action. A similar procedure is done for simple action but instead of decomposing the action, the system directly verify the parameters and then generates the execution tree. Once the emotional execution tree has been created, the system proceeds to add actions that are required to express the desired emotion. Then it proceeds to modify the parameters to convey the emotion, considering emotion and character descriptors. When the process is completed, the system informed the correct "drivers", which have been implemented to execute the desired action on a specific platform. Every time that a driver detects the end of the action, it informs the Emotional enrichment system, which will take the proper actions.

\subsection{Implementation}

The system has been implemented in C++ and interfaced with ROS. To fulfill all the requirements, the system was implemented in two different nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms. The system has been tested in two physical platforms, with different degrees of freedom: Triskarino and Keepon.

\section{Conclusions and Further Work}

An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential. Simple actions are primitive actions that are used as building blocks for more complex actions. Sequential executes in order the sequence of actions associated to this type of node, while parallel executes them all at the same time. To enable synchronization among simple actions, parallel nodes could be one of four different sub-types, and sequential just one of two different sub-types. This implementation allowed the use of generic approach to enrich actions with emotion without considering the physical constrains of the platform. This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different "drivers".

As a further work is envision to add additional parameters and new actions into the system. These new actions will correspond to other modalities, such as facial expression and voice.
\bibliographystyle{splncs}
\bibliography{Bibliography,BibloNew,Biblography}
\end{document}

### 2016-12-06 HRI-LBR/Parts/System-HRI.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

--- 2016-09-26 HRI/Parts/System.tex
@@
 
-The non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance.
+A non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance.
 The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
@@
 The Arduino Due is in charge to be the interface between the hardware (e.g.
-motors) and Odroid, which host all the emotion enrichment system.
+motors) and Odroid, which host all the Emotion Enrichment System.
 
@@
 
-The main idea of Emotional Enrichment System (EES) is to blend an emotion and a action to produce an "emotional action".
+The main idea of Emotional Enrichment System is to blend an emotion and a action to generate the effect of "emotional action".
 However this is not far as previous works have done so far.
-Therefore, the system has been envisioned to also allow:
+Therefore, the system has been envisioned to also enable:
 
@@
 
-In other words, the system could be thought as a box that receives a desire action, action's parameters and emotion to blend them together without paying particular attention on who or how the decision to execute a the particular action was made.
+In other words, the system could be thought as a black box that receives a desire action, action's parameters and emotion to blend them together without paying particular attention on who or how the decision to execute a particular action was made.
 This is achieved through the use of messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.
@@
 
-Every time the system receives a new action, it verifies if the action exists and the parameters corresponds to the action.
+Every time the system receives a new action, it verifies if the action exists and parameters corresponds to the desire action.
 If these two conditions are met, then the system checks if the action is compound or simple.
-If it is a simple, the system proceeds to add all the required actions (emotive actions) and change their parameters to convey the desired emotion.
+If it is a simple, the system proceeds to add all the required actions (emotional actions) and change their parameters to convey the desired emotion.
 On the other hand if the action is compound, the action is first decomposed in simple actions (mandatory actions).
-Each one of these actions is then process to add their emotive actions.
+Each one of these actions is then process to add their emotional actions.
 However, this addition is done taking in consideration to not add any action that was previously added.
@@
 On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints.
-Since each action is characterized by different parameters, the parameters' modifications to obtain an emotional action will be different for each of them.
+Since each action is characterized by different parameters, parameters' modifications to obtain an emotional action will be different for each of them.
 On the other hand, compound action is an action created from other compound or simple actions.
-For example, suppose that it is required that the robot has to \textit{recite} some dialogue and \textit{walk} to a different position, as doing a trajectory.
+For example, suppose that it is required that the robot has to \textit{recite} some dialogue and \textit{walk} to a different positions, as doing a trajectory.
 A possible implementation could consist on speak simple action in parallel to two consecutive action walk, which is also a compound action that is composed by three parallel actions: balance left arm, balance right arm, and move body.
@@
 This parameters' verification is done on the implemented description for each simple action, which describes the parameters that are mandatory and those that are optional.
-When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created.
+When the verification is done, and all the action exists and  the parameters correspond, an $EXT$ is created.
 
-	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase.
-In this phase new simple actions are added to the $ext$ and the simple action's parameters are modified following the emotion description, which is loaded from files.
+	\item \textit{Emotion addition:} uses the $EXT$ created in the previous phase.
+In this phase new simple actions are added to the $EXT$ and the simple action's parameters are modified following emotions' descriptors, which are loaded from files.
 This process is broken down in two steps.
@@
 
-	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
+	\item \textit{Execution:} this is the last phase and it is done after the $EXT$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.

### 2016-12-06 JournalIJSR/IJSR.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
               Tel.: +43-158801\\
-              \email{jangelfe@tuwien.ac.at}           %  \\
+              \email{julian.angel.fernandez@tuwien.ac.at}           %  \\
 %             \emph{Present address:} of F. Author  %  if needed
@@
 \begin{abstract}
-Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that cannot have a humanoid shape, and still have to interact with humans.
-As a consequence,  features not related with shape should be exploited to support robot acceptance.
-This paper presents an experiment made to understand the contribution to humans' perception of emotion of angular and linear velocity, body orientation, and movement direction of a non-anthropomorphic robot.
-A top 10 table of feature values combination was created for each enlisted emotion using alpha agreement for the whole treatment and for the desired emotion.
+Social environments are intricate spaces where people behave in ways that are socially accepted.
+In a similar way, robots that interact with humans on daily bases are expected to develop certain behaviours to be socially accepted by people.
+This creates the necessity to make robots with high social presence that let humans to feel comfortable with their presence.
+The straightest way to fulfill is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics.
+As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions.
+Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that not required anthropomorphic shape due to the nature of the tasks that they have to perform.
+As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance.
+This paper presents an experiment made to understand humans' perception of emotion for angular and linear velocity, body orientation, and movement direction.
+Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features.
+Moreover a Likert questionnaire was used to measure participants' perception for different treatments.
+The Krippendorff's alpha agreement was used to create a top 10 table for each of the emotions listed in the questionnaire.
 The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
-\keywords{Robot-Human Interaction \and Emotion Projection}
+\keywords{Human-Robot Interaction \and Emotion Expression \and Experiment \and Non-anthropomorphic Platform \and Emotions Expression with Non-anthropomorphic Platform}
 % \PACS{PACS code1 \and PACS code2 \and more}

### 2016-12-06 JournalIJSR/Parts/Conclusion.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
 This paper presented an experiment made to understand the contribution of angular and linear velocity, body's orientation, and movement direction on humans' perception of emotion expression by a non-anthropomorphic platform.
-The emotions covered in this experiment correspond to four of the ones enlisted by Ekman~\cite{Ekman2001} as basic emotions: anger, happiness, fear and sadness.
+The emotions covered in this experiment correspond to four of the ones enlisted by Ekman~\cite{Ekman2001} as basic emotions: \textit{Anger}, \textit{Happiness}, \textit{Fear} and \textit{Sadness}.
 To study the contribution of the desired features, a non-anthropomorphic, holonomic platform was used.

### 2016-12-06 JournalIJSR/Parts/Emotion_Projection.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
 It addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
-His results reaffirm that movement and body postures are indicative of intensity for some emotions, while, for other emotions, these two characteristics seem to be enough to identify them.
-%TODO I cannot understand: do you mean that in the later case movement and body postures could only be used for identification, but not for detecting the intensity?
-The sentence is not clear.
+His results reaffirm that movement and body postures are indicative of intensity for some emotions.
+But at the same time, these two characteristics seem to be enough to identify other emotions.
 
@@
 
-The direct consequence of the abundance of works in face elicitation in humans is the amount of works done in Human-Robot Interaction (HRI) focused also on faces.
+As a direct consequence of the abundance of works in face elicitation in humans, most of the works done in Human-Robot Interaction (HRI) have focused also on faces.
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
-The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{happiness}, \textit{surprise}, \textit{anger}, \textit{disgust}, \textit{fear}, and \textit{sadness}), plus \textit{interest}.
-%TODO Let's have a common code: if emotions are in italic, they have o be so in all the paper.
-If they are not, italic should disappear here and wherever it has been used.
-The face's physical design was done so to invite humans to treat it as if it was a social creature.
-The interaction studies done with this platform were conceived to consider a person as a caregiver and the robot as the receiver; it seems that the system was capable to engage people in a long term interaction.
-To achieve this goal, the system had six sub-systems: vision, hearing, motivational, behavioral, speaking, and emotion selection system.
+The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (happiness, surprise, anger, disgust, fear, and sadness), plus interest.
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
-In this experiment, each participant was asked to look at seven videos, one for each implemented emotion.
-After a video was projected, each participant selected the emotion from a list containing  the seven implemented emotions, only.
-The results showed a percentage of recognition of about 57\%.
+Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions.
+In same direction Destephe and collaborators~\cite{Destephe2013b,Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
+More recently Knight and Simmons~\cite{knight2016} used Keepon and NAO platforms to study the possibility to project inner states with just head movements.
+Although use of videos has the advantage to cover a major number of participants, the lack of interaction with the real platform make these works lose the impact that a robot could generate on the participants.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-Saerbeck and Christoph~\cite{Saerbeck2010} analyzed the relationship between robots' motion characteristics and perceived affect.
-They first did a literature review to select characteristics that could be used to show affection.
-From their literature review, they decided to use acceleration and curvature on robot's trajectory.
-Using these two characteristics, they did an experiment with eighteen participants.
-For the experiment they used two different platforms (iCat and Roomba) to verify if the embodiment had any impact on affection determination.
-For the Roomba researchers decided to use a circular trajectory in the room.
-While for the iCat two objects were place in front of it.
-It starts in a central position to then move to the left, right, and back to center.
-To reduce variables' possibilities, they picked three definite values for each variable.
-Each participant was exposed to both embodiments and all possible variable combinations.
-To assess participants' perception, they used PANAS~\cite{WatsonClarkTellegen88} and Self-Assessment Manikin (SAM)~\cite{Lang2008}.
-Their results show that there was no significant difference between the two embodiments used and that participants were able to assign different emotions to the movement patterns shown to them.
-More importantly, they found out that acceleration was correlated with the perceived arousal, but not with valence.
+The use of real platforms to study emotion projection could be dived in two lines: using anthropomorphic and non-anthropomorphic platforms.
+In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}.
+In some cases, special attention has been taken to determine head's angle and arms position contribution in specific emotions~\cite{Brown2014}.
+Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements.
+To overcome this limitation, some researchers have reduce the human appearance (e.g.
+eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
+Pushing forward the reduction on anthropomorphic features, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
+Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the  work done by Camurri et al.~\cite{pop00002}.
+Continuing with her research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
+The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love).
+Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
 
-%%%%%%%%%%%%%%%%
-As part of their work on detecting emotions in humans, with a case of use in robot games, Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from movement.
-The behavior parameters were selected based on the work done by Camurri et al.~\cite{pop00002}.
-To focus participants' attention on movement, they used the e-puck platform~\cite{Mondada09thee-puck}.
-Their experiment is not fully described, but authors highlighted that the subjects were not given any list with possible emotions, rather they asked participants how they think that the robot was feeling.
-The results showed a very high recognition rate for the implementations of sadness, nervousness, and fear.
-The implementations for anger and happiness were confused.
+Other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement.
+For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}.
+Their results suggest that arousal increases as speed increases and that there is not any clear tendency for smoothness.
+On the other hand, granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal.
+Alike, Tan and collaborators~\cite{Tan2016} have studied the contribution of velocity, fluidity, direction and orientation of a small box.
+Their results suggest that direction is directly correlated with dominance, but that fluidity does not influence the perception.
+While flat orientation is related to positive valence, leaning position are related with negative valance.
+Finally the velocity is correlated with valence, arousal and dominance.
 
-%%%%%%%%%%%%%%%%
-Barakova and collaborators used a closet robot~\cite{Barakova2013}, which does not show any anthropomorphic resemblance, to study new possibilities in social interaction.
-This closet robot can perceive human presence and react to show behaviours that could be perceived as emotions or mental states.
-The closet robot had several sensors to detect human state and several lights to convey its behaviours.
-The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love).
-A pilot to test the five implemented behaviours was made.
-The five behaviours correspond to two implementations of dominance, two of submission, and a neutral behaviour.
-These behaviours differ from each other in the way that the light is turned on and its intensity.
-From pilot's results, they selected two most convincing behaviours, one dominant and one submissive.
-Using these two behaviours, they did an experiment with three different scenarios, in which all the participants were exposed.
-To measure participants' appreciations, they used the Social Dominance Orientation (SDO)~\cite{ pratto1994social} questionnaire and SAM.
-Their results suggest that people prefer systems that display submissive behaviors.
-More importantly, their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
-
-%%%%%%%%%%%%%%%%
-Using a humanoid platform NAO~\cite{NAO2013}, Ca\~namero and collaborators~\cite{Canamero2010,Beck2010} studied the perception of key body poses designed to show emotions.
-They suggested that the techniques used to convey emotions in virtual characters could not be used in robots, due to the fact that virtual characters have no physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007, Canamero2010}.
-They proposed a set of poses that could be used to express emotions with NAO, paying a particular attention to the contribution of the head.
-They did two experiments in which they show the participants different poses and each participant had to pick one emotion from the list given to them.
-The list presented to the subjects included six emotions: pride, happiness, excitement, fear, sadness and anger.
-Their results showed a recognition rate of 88\%, 85\%, 92\%, 88\%, 73\%, and 73\% for anger, sadness, fear, pride, happiness and excitement, respectively.
-The major finding from their experiments is that moving the head up improved the identification of pride, happiness, and excitement.
-While moving the head down improved the identification of anger and sadness.
-However, these key poses are taken statically, without any displacement of the robot in the environment.
-
-%%%%%%%%%%%%%%%%%%%%%%
-Li and Chignell~\cite{Li2011} used a teddy bear robot capable to move its arms and head to study the contribution of these movements to emotion projection.
-To achieve this, they did a total of four studies.
-In the first one, four participants were asked to create a gesture that the robot would do in one of the twelve scenarios presented to them.
-These gestures were recorded and used in the second study.
-The experiment consisted of two parts: one just showing the gestures, and the second one describing a scenario were the gestures were generated.
-The participants had to select from a list the emotion that they thought the robot was conveying.
-The list included basic emotions and mental states, which were selected from the comments obtained during the first study.
-The results showed that giving a context increased the recognition rate.
-In the third experiment, they asked five novices and five puppeteers to create gestures for each of the six Ekman's basic emotions.
-The generated gestures were recorded and used as input in their last test, where the subjects had to select an emotion from a list including the names of the six basic Ekman's emotions.
-Their results showed that it is possible to convey emotions just using movements of head and arms.
-Also they found out that the gestures made by the puppeteers had a better recognition for disgust and fear.
-Although they presented numerical information about their findings, this information is shown in a way that is not possible to discern the recognition rate of each emotion for each experiment.
-
-%%%%%%%%%%%%%%%%%%%%%%
-Daryl~\cite{Arras2012} is an anthropomorphic robot, without facial expression, nor limbs, but with mobility capabilities.
-This platform was used to test whether it is possible to project emotions without using cues used in a human-like platform (e.g., tail, ears, and head).
-This robot has head, ears, ability to generate colors in a RGB-LED set positioned in its chest, and a speaker system.
-The head had no capabilities to show facial expressions, but its movements and robot translations were used to show emotions.
-The emotions implemented were: happiness, sadness, fear, curiosity, disappointment, and embarrassment.
-During the experiments done by the researchers, special attention was put to the final distance between the robot and the subject, but the approaching velocity and the followed trajectory were not taken into consideration.
-The subjects were exposed to a sequence of movements.
-For each sequence the subject was asked to rate the intensity of each emotion enlisted in a five-point Likert scale questionnaire.
-The enlisted emotions were the six implemented plus anger, disgust and surprise.
-Their results showed that participants gave a higher intensity to the desired emotion, but also to similar ones, such as in the case of sadness and disappointment.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-Using the platform WABIAN-2R, Destephe and collaborators~\cite{Destephe2013b} studied the attribution of emotion to a robot's gait.
-To obtain the robot's movements, the researchers asked two professional actors to walk in a room conveying anger, happiness, sadness, and fear with different intensities (low, regular, normal, high, and exaggerated).
-All the actors' walking were recorded using a Cortex motion capture system.
-These data were then reported to robot's embodiment.
-To verify their data, the researchers first did a pilot study with just two emotions (happiness and sadness) and thirteen subjects~\cite{Destephe2013}.
-Each subject was exposed to a series of videos.
-After each video, the subject was asked to select one emotion from a list (happiness, neutral, or sadness) and to state the intensity of the selected emotion.
-The showed videos were not made with the real robot, but with a virtual model of the robot.
-From the results obtained, they decided not to use the low intensity because it had a very low recognition rate.
-During the experiment they adopted the same procedure, emotion and its intensity, but this time showing all the emotions and intensities, excluding low, to the participants.
-Their results showed that sadness was recognized 73.81\% (average) of the times with an intensity of 21.43\%, happiness was recognized 66.67\% (average) of the times with an intensity of 30.95\%, anger was recognized 61.9\% of the times with an intensity of 26.19\%, and fear was recognized 83.33\% (average) of the times with an intensity of 28.58\%.
-%TODO What does it mean "with an intensity of x%?
-These results show that people could reasonably well recognize emotions from the robot's gait.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-Lakatos and Collaborators~\cite{Lakatos2014} take inspiration from human-animal interaction
-to create behaviours that could enrich human-robot interaction.
-They conducted an experiment to analyse the recognition rate of emotion expression, using as inspiration the movements done by dogs to convey emotions.
-The experiment was done using a Wizard-of-Oz setting and its goal was to determine if people could distinguish two emotions (happiness and fear).
-They use a game approach to determine participant's appraisal of the robot emotion.
-This was done in order to avoid asking the participants the emotion they believe the robot is eliciting.
-Therefore, in the experiment, each participant had two balls (yellow and black) and they could play with the robot using one of this balls at a time.
-However, one of the balls triggers robot's happiness and the other fear.
-The dog's favourite ball was changed from participant to participant to avoid any bias for the balls' color.
-The results of this experiment showed that the participants decided to use more dog's favourite ball to play with the dog, which is consistent with the idea that the participants could discern which ball produced ''happiness'' in the robot.
-
-%%%%%%%%%%%%%%%%% %
-Brown and Howard focused their interest on head and arm movements using the DARwIn-OP platform~\cite{Brown2014}.
-Their hypothesis was that using some principles, that they evaluated as important, it is possible to express happiness and sadness in a way that people could recognize.
-These principles establish that to show happiness is necessary to quickly move robot's head up and arms up.
-While to express sadness the head goes down, arms down, both slowly.
-To test their hypothesis they conducted an experiment with thirteen participants.
-Each participant was exposed to fifteen sequences of poses and he/she had to answer for each sequence a five-point Likert scale (very-sad to very happy, with neutral in the middle).
-They obtained a 95\%, 59\%, and 94\% of accuracy for happiness, neutral and sadness respectively.
-Their results show that the selected features are determinant to convey happiness and sadness.
-
-%%%%%%%%%%%%%%%%%%%
-Sharma and collaborators~\cite{Sharma2013} used a quadrotor to study how different Laban's effort~\cite{Laban1968} parameters could impact on the perception of affection.
+Due to the popularity that quadrocoptors have received in the last years, Sharma and collaborators~\cite{Sharma2013} used a quadrotor to study how different Laban's effort~\cite{Laban1968} parameters could impact on the perception of affection.
 A professional Laban certified actor was asked to generate 16 different paths, for each one changing one of the four Laban's parameters (space, weight, time, and flow).
 Each generated path was recorded using the Vicon motion-tracking system.
-Then, they did an experiment were people were asked to assess each path using the Self-Assessment Manikin (SAM)~\cite{Lang2008}.
-In order to analyse the results, they mapped them on the circumplex model of emotion, and evaluated the contribution of each Laban's parameter in the 2-D circumplex model (arousal and valence).
-The results show that it is possible to increase both valence and arousal by using a more indirect space, or by performing the motion more quickly, and to decrease valence or arousal by a more direct use of space, or a more sustained motion.
-Although they suggest the use of Laban's model as a tool to specify affection movements in Human-Robot Interaction, how to use these parameters in the actual implementation remains an open question, since Laban defined them qualitatively, with reference to human people, and they leave very open questions about the most appropriate numerical values to be used with robots.
-
-%%%%%%%%%%%%%%%%%%%
-Suk and collaborators studied the human emotional interpretation for speed, smoothness, granularity and volume of a non-bioinspired object~\cite{NAM2014}. %TODO What is granularity for this robot?
-Two experiments were designed to determine the relationship among these features and the emotional interpretation.
-To assess participants' emotional response they used SAM.
-The first experiment was focused on speed and smoothness movement features, selecting five different values for each one of these two features.
-Each participant was exposed to twenty five movements.
-After a participant observed a movement, the participant marked the two SAM graphic figures (pleasure and arousal).
-The results from this first experiment show that the arousal increases as speed increases, but that there is not any clear tendency for smoothness.
-In the second experiment they evaluated the other two features (granularity and volume) using the same procedure followed in the first experiment.
-Their results show that granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal.
-As overall result, they found a major contribution of speed on arousal and minor contribution of granularity and volume.
-
-%%%%%%%%%%%%%%%%%%%
-To improve the coordination between humans and robots Novikova and Watss~\cite{Novika2015} proposed the use of emotion.
-They did studies using a own built platform called E4 to verify whether people could detect emotions from a non-human like platform.
-The E4 platform was constructed using a Lego Mindstorms NTX and it was based on a Phobot robot's design.
-In all their experiments they used six emotional expressions (scared, surprised, excited, angry, happy, sad) and neutral.
-The emotion list used in their experiments was balanced using the 2-D circumplex model (arousal and valence), selecting three from each quadrant for a total of twelve emotions, plus the options of ``other'' and ``don't know''.
-They obtained a recognition rate of 52\%, 42\%, 41\%, 36\% and 15\% for surprise, fear, sadness, happiness, and anger respectively.
-
-The works presented in this section provide guidance about features that could be exploited to project certain emotions.
-However, range of values to convey specific emotions will guide other researchers in what values could be used to convey the desired emotion or what values not to use because they could be misinterpreted as negative emotions.
-%TODO I cannot catch the meaning of the last sentence.
-Starting with "However" raises the expectation of something negative, e.g., nobody provides values for the features that could be used.
-The sentence seems instead positive.
-So, either remove "However" or make evident what is negative in the statement.
-
-%TODO Maybe the table could summarize what presented.
-It would also be nice if you could say some words either at the end of each presentation or at the begining, so to justify why you have selected them and not others, and what they bring as important for your work.
-
-%%%%%%%%%%%%%%%%%%
-%Table~\ref{table:comparison_work_emotion_projection} summarizes all the robotics studies to convey emotion that we considered, highlighting the following characteristics:
-%\begin{itemize}
-%	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;
-%	\item \textit{Platform used} gives the name of the platform used in the study;
-%	\item The\textit{Locomotion} criterion was added to put in evidence whether the platform uses displacement movement to express emotion;
-%	\item \textit{Emotion Evaluation Method} refers to the methodology used to collect the data in the studies.
-%	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;
-%	\item \textit{Emotions Implemented} gives the list of emotions showed to the subjects;
-%	\item \textit{Type of test} tells if it was done an experiment or a case study.
-%	\item \textit{How is the emotion conveyed?} This tells what medium was used to convey the emotion. The media considered were: movement, body posture and face poses.
-%\end{itemize}
-%\begin{table}[h]
-%\caption{Comparison among works on emotion projection in robotics. NA = Not Available}
-%\label{table:comparison_work_emotion_projection}
-%\begin{center}
-%\tiny %\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-%\begin{tabular}{|p{1.0 cm}|p{0.5 cm}|p{0.9 cm}|p{0.8 cm}|p{0.8 cm}|p{1.1 cm}|p{0.9 cm}|p{1.1 cm}|p{0.8 cm}|p{0.8 cm}|}
-%%\begin{tabular}{|p{1.5 cm}|p{1.0 cm}|p{1.5 cm}|p{1.5 cm}|p{1.5 cm}|p{2.0 cm}|p{1.5}|p{2.0 cm}|p{1.0 cm}|p{1.5 cm}|}
-%\hline 
-%\textbf{Work} & \textbf{Year} & \textbf{Embodiment} & \textbf{Platform Used} & \textbf{Locomotion} & \textbf{Emotion Evaluation Method} & \textbf{Emotion Presentation} & \textbf{Emotions Implemented} &  \textbf{Type of test} & \textbf{How is the emotion conveyed?}\\
-%\hline 
-%Breazeal~\cite{Breazeal2002} & 2002 & Face & Kismet & NA & Questionnaire & Video & Happiness, surprise, anger, disgust, fear, sadness and interest & Experiment & Face poses\\ 
-%\hline
-%Saerbeck and Christoph~\cite{Saerbeck2010} &2010& Animal/ Non-Human like& iCat / Roomba & NA / Differential &PANAS and SAM & Real Robot & NA & Experiment & Movement\\
-%\hline 
-%Ca\~namero and collaborators~\cite{Canamero2010,Beck2010}& 2010 &Human-Like & NAO & Bipedal & Questionnaire & Real robot & Anger, sadness, fear, pride, happiness, and excitement & Experiment & Body poses\\
-%\hline
-%Li and Chignell~\cite{Li2011}&2011&Animal-Like& Teddy Bear Robot& NA & Questionnaire & Video (Real robot) & Random + Anger, disgust, fear, happiness, sadness, and surprise & Experiment & Body poses\\
-%\hline
-%Barakova and collaborators~\cite{Barakova2013} & 2013 & NA & Closet robot& NA & SDO and SAM & Real robot & NA & Experiment & Changing lights on and intensity\\ 
-%\hline
-%Sharma and collaborators~\cite{Sharma2013}& 2013 & Non-Human/Animal & Quadrotor & Aerial & SAM + Questionnaire + Interview &  Real Robot & Laban's poles & Experiment & Movement\\
-%\hline
-%Destephe and collaborators~\cite{Destephe2013b}&2013&Human-like & WABIAN-2R & Bipedal & Questionnaire & Video (Virtual Robot) & Fear, anger, happiness, and sadness & Experiment & Movement (Gait)+Body Poses\\
-%\hline 
-%Embgen and collaborators~\cite{Arras2012} & 2014 & Human-like & Daryl &  Differential& Questionnaire & Real Robot & Happiness, sadness, fear, curiosity, embarrassment, and disappointment & Experiment & Movement + Body poses \\
-%\hline
-%Lakatos and Collaborators~\cite{Lakatos2014}& 2014 & Animal-Like & Dog & Holonomic & Indirect (Interaction with the robot) & Real Robot & Happiness and Fear & Experiment & Move + Body poses \\
-%\hline
-%Brown and Howard~\cite{Brown2014} & 2014& Human-Like & DARwIn-OP & Bipedal & Questionnaire & Real Robot & Happiness and sadness & Experiment & Body poses\\
-%\hline
-%Suk and collaborators ~\cite{NAM2014}& 2014 &  Non-Human/Animal & Self-made & NA & SAM & Real Robot & NA & Experiment & Speed, smoothness, granularity and volume\\
-%\hline
-%Novikova and Watss~\cite{Novika2015}& 2015&Non-Human/Animal & Lego & Differential& Questionnaire& Real Robot & Scared, surprise, excited, angry, neutral, happiness and sadness & Experiment& Movement + Poses\\
-%\hline 
-%\end{tabular} 
-%\end{center}
-%\end{table}
+Continuing with the use of quadrocoptors, Cauchard and collaborators~\cite{Cauchard2016} studied how flight paths could project personal traits and emotional attributes.
+All these works present a very nice starting to point to identify features and values that could be used to project emotions in robotics, which could help in coordinating humans and robots~\cite{Novika2015}.
+However, all of these works not give a price guideline to elicit precise emotions, which from our previous case studies could lead to the misinterpretation of movements emotions~\cite{Angel2016}.
+For example people could confuse an implementation of \textit{Happiness} with \textit{Anger}.

### 2016-12-06 JournalIJSR/Parts/ExperimentDesign.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
-The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation can give to the expression of happiness, anger, sadness, and fear, which are four out of the six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
+The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation can give to the expression of \textit{Happiness}, \textit{Anger}, \textit{Sadness}, and \textit{Fear}, which are four out of the six emotions considered by Ekman~\cite{Ekman2004} as basic emotions, which are characterized to have short duration, cultural universal~\cite{Ekman94}, derive from evolution~\cite{Buck99}, and could influence cognition and action~\cite{Campos2004}.
+Moreover, these four emotions here selected are overlap with emotion schemas~\cite{Izard2007}.
 %%%%%%%%%%%%%%%%%%%
@@
 
-The three first variables are shown in Figure~\ref{fig:angular_movement}. The robot's frame of reference is drawn to show that it could move straight while it is rotating.
+The three first variables are depicted in Figure~\ref{fig:angular_movement}.
+The robot's frame of reference is drawn to show that it could move straight while it is rotating.
+It is important to highlight that linear velocity is respected when the robot is also oscillating.
 
@@
 Based on this test, specific values for oscillation angle, and angular and linear velocities were selected.
-The values for the remaining two variables were selected according to what was needed by the experiment.
-%TODO I've tried to make this sentence clearer, but it is still obscure.
-What does it mean?
-
+The values for the remaining two variables were selected to verify the impact of direction and orientation.
+This goes in accordance to our observations in previous case studies~\cite{angel2014}, in which people had a better recognition of fear when the robot was moving far.
 The chosen values are shown in Table~\ref{table:variables_values}.
@@
 
-To get a better idea about the Direction and Orientation values, in Figure~\ref{fig:possibilities_orientation_direction} are reported all the possibilities for these two variables.
+To get a better idea about the Direction and Orientation values, in Figure~\ref{fig:possibilities_orientation_direction} are reported all  possibilities for these two variables.
 
@@
 
-The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, %TODO What does "desired procedures to compare" mean?
+Treatments, meant as desired combination of independent variables to compare~\cite{oehlert2000first},
 were generated from the combination of independent variables' values for a total of 384 combinations.
-All the experiences that would not add any significant information to the experiment were removed, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of experiences to 195.
+Treatments that would not add any significant information to the experiment were removed, such as treatment with $\theta=0$ and $\omega \neq 0$, which reduced total amount of treatments to 195.
 
@@
 
+Two dependent variables were determined, and they are described below.
+
 \begin{itemize}
-	\item \textbf{Emotion} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
+	\item \textbf{Emotion} is the feeling perceived by the participants from the robot's movement. From previous experiences~\cite{angel2014}
 	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed, two mental states that could be misinterpreted from these emotions, and the option of ``other''.
@@
 	\item \textbf{Emotion's intensity} indicates the emotion intensity as perceived by the subject.
-This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.
+This variable is measured on a Likert scale, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.
 
@@
 
-It was decided that each subject had to be exposed to twenty over one hundred and ninety five possible experiences, trial that lasted  from 10 to 15 minutes.
+It was decided that each subject had to be exposed to twenty over 195 possible treatments.
+Each presentation lasted  from 10 to 15 minutes.
 This was decided because each subject was a volunteer, so the time dedicated to the experiment had to be kept limited.
 The twenty treatments were selected picking a number without replacement from 1 to 195.
-A total of 980 answers were collected, guaranteeing a minimum of 5 trials for each motion type.
+A total of 980 answers were collected, guaranteeing a minimum of 5 trials for each treatment.
 
@@
 \end{table}
- %TODO I would say how many times each experience was tested. This is a needed parameter for this experimental setup.
 %%%%%%%%%%%%%%%%%%%
@@
 
-The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
+The order of the options listed in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
 

### 2016-12-06 JournalIJSR/Parts/Introduction.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
-%TODO Here, even before what follows, the need for emotion expression should be justified, ad possibily supported by literature
-
-Emotions and mental states are not just presented through facial expression, but also by body postures and other features~\cite{Gelder2008}.
-However,  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
-This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been widely used to convey emotions.
+Social environments are intricate spaces where people behave in ways that lead to their acceptance in social groups.
+Similarly, studies in social robotics have shown that robots acceptance increases when robots project a high social presence~\cite{Heerink08}.
+The straightest way to fulfill is through imitation of humans' characteristics, such us body form, behaviors and social characteristics.
+This has inspired most researchers to focus on how express emotions and mental states exploiting anthropomorphic features, in many occasions relying just on faces.
+However emotions and mental states are not just presented through facial expression, but also by body postures and other features~\cite{Gelder2008}.
+Nonetheless in psychology has been a clear tendency to study the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
+This trend has been followed by robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been widely used to convey emotions.
 Nevertheless, in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
-Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
+Most of the current and future robotics platforms on the market will not require anthropomorphic faces or limbs.
 In some cases, like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
@@
 The amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those that exploit anthropomorphic features.
-Moreover, these works do not prescribe any specific range of values for the characteristics to be used to express the  implemented emotionsb.
+Moreover, these works do not prescribe any specific range of values for the characteristics to be used to express the  implemented emotions.
 For example, Suk and collaborators~\cite{NAM2014}, in their study, give specific values for acceleration, curvature, but their connection to specific emotions is not given.
-Rather, they give a relationship between their features and values in terms of valence and arousal.
-This could lead to select features to convey certain emotions, but it would be better to know the specific range of values for those features to convey the single emotions, or to know the values that could lead to misinterpret the emotional expression.
+Rather, they gave a relationship between their features and values in terms of valence and arousal.
+Another possibility is the use of professional human actors to study how they convey certain emotions.
+However, a direct mapping between humans and robots is not possible~\cite{Saerbeck2007,Canamero2010} due to robots' physical capabilities.
+In addition, the significance of the agreement obtained from the studies that used human actors is on discussion~\cite{Russell2003}.
+As a consequence determine precise values to project emotions in non-anthropomorphic platforms is required.
 
@@
 The experiment's design is explained in section~\ref{sec:experiment}.
-Finally sections~\ref{sec:study} and~\ref{sec:result} present the study done and the obtained results.
+Finally sections~\ref{sec:experiment} and~\ref{sec:result} present the study done and the obtained results.

### 2016-12-06 JournalIJSR/Parts/Platform.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
 Robot's frame of reference, in which all the velocities are going to be calculated, is depicted by the two black arrows.
-So, as it could be observed, to make the robot move forward a velocity along the $y$ axis is selected by the control system.
+Therefore, as it could be observed, to make the robot move forward a velocity along the $y$ axis is selected by the control system.
 
@@
 The second command is a set point ($<x, Y, \theta>$) to be reached, given in the world reference frame.
-This frame of reference is set every time the system is reset or boot.
+This world frame of reference is set every time the system is reset or boot.
 For example, if the robot finishes a trajectory and then it is reset, the new frame is going to be in the robot's current position.
-%TODO From this description it seems that this second reference frame is again associated to the robot, in particular that it is a reference frame that is activated when the robot starts, and does not move with the robot.
-So it is a world reference frame reset each time the robot starts a new movement.
-It should have a name, to be found.
-If it was always associated with the robot it would have been called "deictic".
-
-%TODO I'm sorry, but the following is an implementation detail that does not add anything to the scientific relevance of this paper, and this is not a paper about the interface.
-%In addition to this low level control, a graphical interface, depicted in Figure~\ref{fig:experimental_interface}, was created to reduce the possibility of introducing wrong values for a desired sequence.
-This interface loads the sequences from a .txt file and displays sequences' numbers on it.
-Every time that a new sequence should be presented to a participant, the sequence's number is selected in the interface, which will display sequence's values.
-Once the robot has been positioned to the correct position, the execution could be started by clicking on send button.
-Here two commands are send, one resetting the controller and the second the desire position.
-In case that the sequence's execution should be aborted, it should be clicked the button stop.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.45\textwidth]{./Images/ExperimentInterface.png} 
-%	\caption{Interface used in the experiment.
-Once a sequence is selected, the interface shows sequence's values.
-Also, the interface give information about the current position of the robot and its velocity.}
-%	\label{fig:experimental_interface}
-%\end{figure}

### 2016-12-06 JournalIJSR/Parts/Results.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

@@
-A table with subjects' answers was generated for each experience. Table~\ref{table:example_table} is an example of the generated tables.
+A table with subjects' answers was generated for each treatment. Table~\ref{table:example_table} is an example of the generated tables.
 
@@
 This was checked using the Shapiro-Wilk Test.
-Additionally, a contingency table for each emotion was generated in each experience as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean, including the option ``other''.
-For all tables, including the contingency,  the Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated: it is a reliability coefficient to measure the agreement among different participants.
+Additionally, a contingency table for each emotion was generated in each treatment, as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean of their intensity, including the option ``other''.
+Therefore a total of seven tables for each treatment were created.
+For all these tables, Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated, which is a reliability coefficient to measure the agreement among different participants.
 Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.
@@
 This calculation was done using the R's package \textit{irr}.
-To improve the table interpretation, it was decided to just register the emotions' alpha values that had a mean greater than zero.
-The $\alpha$ for each experience is shown in Figure~\ref{fig:alpha_experience}.
-Additionally, for each emotion was generated a table with a top ten ranking experiences that considers the following items:(i) the mean intensity of the respective emotions, (ii) the alpha agreement for the respective emotion, and (iii) the alpha agreement for the specific experience.
-Experiences in these tables were first organized by mean, then by the emotion's agreement and finally by general agreement.
-%TODO This is critical, it is not clear (make an example) and should be fully justified, since on this is based all the reasoning about results
-
-The decision to give more importance to emotion's alpha was taken based on the situation that the participants could be agreed about the precise emotion but not for the rest of the words enlisted.
-%TODO You just said that the first is the mean, not alpha...
-This sentence is not clear, anyway
+To improve contingency tables' interpretation, it was decided to just register emotions' alpha and intensity values greater than zero.
+The $\alpha$ for each treatment is shown in Figure~\ref{fig:alpha_experience}.
+As it could be observed, this table does not provide any information about the interpretation for each emotion.
+Therefore, it was decided to create top ten raking of treatments from the contingency tables of each emotion.
+This ranking is generated considering the following items in the respective order:(i) the mean intensity of the respective emotion, (ii) the alpha agreement of contingency table for the respective emotion, and (iii) the alpha agreement for the specific treatment.
 From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:
@@
 
-	\item Fear was the only emotion that had six over ten movements obtaining both general and specific alpha agreement over 0.41, which is the lower bound for moderate agreement~\cite{Viera2005}.
+	\item \textit{Fear} was the only emotion that had six over ten movements obtaining both general and specific alpha agreement over 0.41, which is the lower bound for moderate agreement~\cite{Viera2005}.
 Also, it was mostly selected (eight over ten) when $direction = \pi$ and $orientation = \pi$.
@@
 
-	\item Sadness was mostly attributed to linear velocities of $0 mm/s$ (two over ten) and $200 mm/s$ (eight over ten), and angular velocities of $0 rad/s$ and $1 rad/s$, with higher predilection of the second (eight over ten).
+	\item \textit{Sadness} was mostly attributed to linear velocities of $0 mm/s$ (two over ten) and $200 mm/s$ (eight over ten), and angular velocities of $0 rad/s$ and $1 rad/s$, with higher predilection of the second (eight over ten).
 It seems that people attribute sadness to slow velocities with slow angular velocity and small oscillation angle.
@@
 
-	\item Happiness is attributed to different values of the independent variables.
+	\item \textit{Happiness} is attributed to different values of the independent variables.
 But it is the only emotion that is highly perceived when the linear velocity is $0$ with four over ten.
@@
 
-	\item Anger is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$.
+	\item \textit{Anger} is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$.
 It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the persons while approaching them.

### 2016-12-06 HRI-LBR/HRI-LBR2017.tex
Add files via upload

@@
 
-\title{Towards an Enriching Robot's Actions with Affective Movements}
+\title{Towards Enriching Robot's Actions with Affective Movements}
 %\subtitle{[Extended Abstract]
@@
 \begin{abstract}
-Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues.
-Although there have been works that have studied emotion expression in robotics, the mechanism created to project emotion are highly integrated to their solutions.
-This unable the possibility to create a general approach.
-This paper presents a system that has been initially created for a theatrical robot to enrich with emotions its actions, but it has been designed to be adaptable to other fields.
+Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues that people expects in interaction.
+Although there have been works that have studied emotion expression in robotics, the mechanisms created to project emotion are usually highly integrated in each solution.
+This limits the possibility to develop a general approach.
+This paper presents a system that has been initially created for a theatrical robot to enrich its actions with emotions, but it has been designed to be adaptable to other fields.
 The emotional enrichment system has been envisioned to be used with any action decision system.
@@
 The development of fast, cheap and reliable electronics has enabled the creation of new devices and versatile robotic platforms.
-These new platforms' capabilities have expanded the frontiers of robots applications  to new environments, where robots are expected to interact with humans, such as health care, house cleaning, among others.
+These new platforms' capabilities have expanded the frontiers of robots applications to new environments, where robots are expected to interact with humans, such as health care, and house cleaning, among others.
 However, bringing robots in these context raise the challenge to increase their acceptance.
-Although improving robots' appearances and capabilities could be though as a possible solution, it is probable that people would treat robots as humans has they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill their expectations.
+Improving robots' appearances and capabilities may be thought as a possible solution, and it is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill people's expectations.
 
 Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
-As consequence researchers~\cite{Breazeal2002} have added specific emotional poses and expression to their robots.
+As a consequence, some researchers (e.g.,~\cite{Breazeal2002}) have added specific emotional poses and expression to their robots.
 Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}.
-Nevertheless, these works have developed modules to show emotions that are strongly integrated to their solutions, which eliminate the possibility to re-use or adapt their solutions into other projects.
+Nevertheless, these research activities have developed modules to show emotions that are strongly integrated with their solutions, which eliminate the possibility to re-use or adapt their solutions for other projects.
 
-This paper presents an Emotional Enrichment System, which modify actions' parameters and add additional actions to create the illusion of emotion expression in a robot.
-Although the system was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extendable to other platforms and adaptable to new tasks.
-To achieve this goal, the system relies on an Emotional Execution Tree, which is based on simple actions or primitive, sequential and parallel nodes.
-Additionally, it is used the concept of compound actions to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions  generated by specific combinations of simple actions and other nodes.
+This paper presents an Emotional Enrichment System, which modifies actions' parameters and add additional actions to create the illusion of emotion expression in a robot.
+Although the system was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extensible to other platforms and adaptable to new tasks.
+To achieve this goal, the system relies on an Emotional Execution Tree, which is based on simple actions or primitive, sequential, and parallel nodes.
+Additionally, the concept of compound actions is adopted to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions generated by specific combinations of simple actions and other nodes.
 
@@
 The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional action".
-To obtain a differentiation between previous approaches, the system has been envisioned to also allow: (i) interoperability among different platform, (ii) introduction of new parameters and emotions and (iii) interface with diverse action decision systems.
+To obtain a differentiation between previous approaches, the system has been envisioned to also allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
 
-Therefore, the system could be thought as a black-box that receives a desired action and emotion to blend them together through addition of other actions and modification of actions' parameters.
+Therefore, the system could be thought as a black-box that receives a desired action and emotion, and obtains an emotional enriched action through addition of other actions to the original one, and modification of actions' parameters.
 This modification is done following the description given in two configuration files.
@@
 The second file describes "personal" traits to specific emotions.
-For example, one person could intensify his happiness but conceal his sadness.
+For example, one person could intensify his happiness, but conceal his sadness.
 
@@
 
-The system is founded on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}.
-\textit{Simple actions} are actions that are considered as primitives and they are used as building blocks.
+The system is based on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}.
+\textit{Simple actions} are actions that are considered as primitives: they are used as building blocks.
 Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place.
@@
 \textit{Compound actions} are actions that are created from simple actions.
-As it could be expected, these actions are not implemented in the system but if it is required they can be described in it (e.g.
+As it could be expected, these actions are not implemented in the system, but, if it is needed, they can be described in it (e.g.
 compound actions that are used often).
-\textit{Action message} establishes the structure of the message to describe any kind of action (i.e.
-simple and compound).
-This message also specifies how the actions are executed (i.e.
-parallel or sequential) and which action is the predominant (i.e.
-primary and secondary).
+\textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
+This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is the predominant (i.e., primary or secondary).
 \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
 This description could also include addition of other simple actions.
-\textit{Character description} enables the possibility to establish how to modify emotions expression to generate diverse treats.
+\textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse treats.
 Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed.
@@
 
-Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertices and $|E|$ edges.
-The root and non-leaf nodes could be \textit{parallel} or \textit{sequence} type.
+Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges.
+The root and non-leaf nodes could be either of \textit{parallel} or \textit{sequence} type.
 The parallel node could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
 Sequential nodes could just be one of two sub-types: (i) emotion synchronous or (ii) asynchronous.
-Action synchronous means that each time that a parallel node receives a finish notification (i.e.
-success or failure), it will send a finish message to all the nodes that derived from it.
-On the other hand, emotion synchronous means that each time that a node (i.e.
-sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches.
+Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will send a finish message to all the nodes that derived from it.
+On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches.
+%TODO the sentence before is a little bit confusing and the full set of possibility is not completely described.
 
-This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action and also lets synchronization among parallel actions.
+This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action and also enables synchronization among parallel actions.
 Finally, leaf nodes could only be simple action nodes.
-All nodes can assume two levels: principal or  secondary.
-If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary cannot propagate any message to its predecessor.
+Any node can belong to one of two levels: principal or  secondary.
+If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
 
@@
 
-Every time the system is launched, it starts reading emotion and character descriptors, and it creates an internal representation.
-Every time that the system receives a new action message, which includes action's name with its parameters values, the verification process starts.
+Every time the system is launched, it starts reading emotion and character descriptors, and it creates an internal representation. %TODO Characters have not been introduced here
+Every time the system receives a new action message, which includes action's name with its parameters' values, the verification process starts.
 If the action is compound, it is first decomposed in simple actions, which will be labeled as primary actions, and checked if all actions exists in the system and the parameters correspond to the specification.
@@
 Once the emotional execution tree has been created, the system proceeds to add actions that are required to express the desired emotion.
-Then it proceeds to modify the parameters to convey the emotion, considering emotion and character descriptors.
-When the process is completed, the system informed the correct "drivers", which have been implemented to execute the desired action on a specific platform.
+Then, it proceeds to modify the parameters to convey the emotion, considering emotion and character descriptors.
+When the process is completed, the system feeds information to the correct ``drivers'', which have been implemented to execute the desired action on a specific platform.
 Every time that a driver detects the end of the action, it informs the Emotional enrichment system, which will take the proper actions.
@@
 
-The system has been implemented in C++ and interfaced with ROS.
+The system has been implemented in C++ and interfaced with ROS %TODO Cite
+.
 To fulfill all the requirements, the system was implemented in two different nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
-The system has been tested in two physical platforms, with different degrees of freedom: Triskarino and Keepon.
+The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite
+ and Keepon%TODO Cite
+ .
 
@@
 Simple actions are primitive actions that are used as building blocks for more complex actions.
-Sequential executes in order the sequence of actions associated to this type of node, while parallel executes them all at the same time.
+Sequential nodes execute in order the sequence of actions associated to them, while parallel nodes execute them all at the same time.
 To enable synchronization among simple actions, parallel nodes could be one of four different sub-types, and sequential just one of two different sub-types.
@@
 
-As a further work is envision to add additional parameters and new actions into the system. These new actions will correspond to other modalities, such as facial expression and voice.
+Further work is envisioned to add additional parameters and new actions into the system. These new actions will correspond to other modalities, such as facial expression and voice/sound.
 \bibliographystyle{splncs}

### 2017-01-05 HRI-LBR/HRI-LBR2017.tex
The HRI-LBR has been accepted and improved base on reviewers' comments

@@
 
-\numberofauthors{1} %  in this sample file, there are a *total*
+\numberofauthors{2} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \author{
-Author name\\
-       \affaddr{Author institution}\\
-       \affaddr{Institution's address}\\
-       \affaddr{City}\\
-       \email{mail@mail.com}
+%Author name\\
+%       \affaddr{Author institution}\\
+%       \affaddr{Institution's address}\\
+%       \affaddr{City}\\
+%       \email{mail@mail.com}
 % You can go ahead and credit any number of authors here,
@@
 % 1st. author
-%\alignauthor
-%Julian M. Angel-Fernandez\\
-%       \affaddr{Automation and Control Institute, Vienna University of Technology}\\
-%       \affaddr{Karlspltz 13, 1040}\\
-%       \affaddr{Vienna, Austria}\\
-%       \email{jangelfe@tuwien.ac.at}
+\alignauthor
+Julian M. Angel-Fernandez\\
+       \affaddr{Automation and Control Institute, Vienna University of Technology}\\
+       \affaddr{Karlspltz 13, 1040}\\
+       \affaddr{Vienna, Austria}\\
+       \email{julian.angel.fernandez@tuwien.ac.at}
 %% 2nd. author
-%\alignauthor
-%Andrea Bonarini\\
-%       \affaddr{Dipartimento di Elettronica, Informazione e Bioingegneria, Politecnico di Milano}\\
-%       \affaddr{Piazza Leonardo da Vinci 31, 20133}\\
-%       \affaddr{Milan, Italy}\\
-%       \email{andrea.bonarini@polimi.it}
+\alignauthor
+Andrea Bonarini\\
+       \affaddr{Dipartimento di Elettronica, Informazione e Bioingegneria, Politecnico di Milano}\\
+       \affaddr{Piazza Leonardo da Vinci 31, 20133}\\
+       \affaddr{Milan, Italy}\\
+       \email{andrea.bonarini@polimi.it}
 }
@@
 \begin{abstract}
-Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues that people expects in interaction.
+Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues.
 Although there have been works that have studied emotion expression in robotics, the mechanisms created to project emotion are usually highly integrated in each solution.
@@
 \section{Introduction}
-The development of fast, cheap and reliable electronics has enabled the creation of new devices and versatile robotic platforms.
+%The development of fast, cheap and reliable electronics has enabled the creation of new devices and versatile robotic platforms.
 These new platforms' capabilities have expanded the frontiers of robots applications to new environments, where robots are expected to interact with humans, such as health care, and house cleaning, among others.
@@
 
+Bringing robots in social context raise the challenge to increase their acceptance.
+Improving robots' appearances and capabilities may be thought as a possible solution, and it is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill people's expectations.
 Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
-As a consequence, some researchers (e.g.,~\cite{Breazeal2002}) have added specific emotional poses and expression to their robots.
+As a consequence, specific emotional poses and expression have been added to their robots.
 Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}.
@@
 The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional action".
-To obtain a differentiation between previous approaches, the system has been envisioned to also allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
+To obtain a differentiation between previous approaches, the system has been envisioned to allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
 
@@
 Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place.
-Their description specifies mandatory and optional parameters that are required to execute the action.
+Their description specifies mandatory and optional parameters that are required to execute an action.
 \textit{Compound actions} are actions that are created from simple actions.
-As it could be expected, these actions are not implemented in the system, but, if it is needed, they can be described in it (e.g.
+These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g.
 compound actions that are used often).
@@
 Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges.
-The root and non-leaf nodes could be either of \textit{parallel} or \textit{sequence} type.
+The root and non-leaf nodes could be either \textit{parallel} or \textit{sequential} type.
 The parallel node could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
-Sequential nodes could just be one of two sub-types: (i) emotion synchronous or (ii) asynchronous.
-Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will send a finish message to all the nodes that derived from it.
-On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches.
-%TODO the sentence before is a little bit confusing and the full set of possibility is not completely described.
+Sequential nodes could just be one of two sub-types: emotion synchronous or asynchronous.
+Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor.
+If a sequence node receives a finish message, it will execute the next branch.
+In case that all branches have been executed, it communicates the end of the action.
+On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message; it will propagate the message to all branches to move to the consecutive emotional parameter.
+If a node is principal and it has finished of executing all actions, it will inform to its predecessor.
 
-This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action and also enables synchronization among parallel actions.
-Finally, leaf nodes could only be simple action nodes.
+This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions.
+Finally, leaf nodes could only be simple action nodes that have been implemented in the system.
 Any node can belong to one of two levels: principal or  secondary.
 If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
+Compound actions are implemented combining all type of nodes.
 
@@
 
-Every time the system is launched, it starts reading emotion and character descriptors, and it creates an internal representation. %TODO Characters have not been introduced here
-Every time the system receives a new action message, which includes action's name with its parameters' values, the verification process starts.
+When the system is launched, it starts reading emotion descriptors, and it creates an internal representation.
+Every time the system receives a new action message the verification process starts.
+This message includes a description of actions that should be executed, with their respective values.
 If the action is compound, it is first decomposed in simple actions, which will be labeled as primary actions, and checked if all actions exists in the system and the parameters correspond to the specification.
@@
 
-The system has been implemented in C++ and interfaced with ROS %TODO Cite
+The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight
 .
@@
 The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite
- and Keepon%TODO Cite
- .
+ and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
+The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$.
 
@@
 To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential.
-Simple actions are primitive actions that are used as building blocks for more complex actions.
-Sequential nodes execute in order the sequence of actions associated to them, while parallel nodes execute them all at the same time.
-To enable synchronization among simple actions, parallel nodes could be one of four different sub-types, and sequential just one of two different sub-types.
-This implementation allowed the use of generic approach to enrich actions with emotion without considering the physical constrains of the platform.
 This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different "drivers".

### 2017-01-05 HRI-LBR/HRI-LBR2017.tex
Update HRI-LBR2017.tex
Few noted and TODO's marked with Andy

@@
 \begin{abstract}
-Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues.
+Emotions are considered by many researchers as beneficial in social robotics, since they can enrich human-robot interaction with non-verbal clues.
 Although there have been works that have studied emotion expression in robotics, the mechanisms created to project emotion are usually highly integrated in each solution.
@@
 
-Bringing robots in social context raise the challenge to increase their acceptance.
-Improving robots' appearances and capabilities may be thought as a possible solution, and it is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill people's expectations.
+Bringing robots in a social context raise the challenge to increase their acceptance. %Improving robots' appearances and capabilities may be thought as a possible solution, and i
+It is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary to devise robots that match people's expectations.
 Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
-As a consequence, specific emotional poses and expression have been added to their robots.
+As a consequence, they added specific emotional poses and expressions to their robots.
 Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}.
-Nevertheless, these research activities have developed modules to show emotions that are strongly integrated with their solutions, which eliminate the possibility to re-use or adapt their solutions for other projects.
+Nevertheless, these research activities have developed modules to show emotions that are strongly integrated with their specific setting, which eliminate the possibility to re-use or adapt their solutions for other projects.
 
-This paper presents an Emotional Enrichment System, which modifies actions' parameters and add additional actions to create the illusion of emotion expression in a robot.
-Although the system was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extensible to other platforms and adaptable to new tasks.
+This paper presents an Emotional Enrichment System, which modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
+Although the system was originally conceived to be used in an autonomous performance robot to enrich actions with emotions~\cite{angel2013}, its design was devised to make it extensible to other platforms and adaptable to new tasks.
 To achieve this goal, the system relies on an Emotional Execution Tree, which is based on simple actions or primitive, sequential, and parallel nodes.
@@
 
-The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional action".
-To obtain a differentiation between previous approaches, the system has been envisioned to allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
+The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional actions".
+Differently from previous approaches, the system has been envisioned to allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
 
-Therefore, the system could be thought as a black-box that receives a desired action and emotion, and obtains an emotional enriched action through addition of other actions to the original one, and modification of actions' parameters.
+Therefore, the system could be thought as a black-box that receives a desired action and emotion, and produces an emotionally enriched action through modification of actions' parameters and addition of other actions to the original one.
 This modification is done following the description given in two configuration files.
 One defines how actions' parameters should be modified and what actions should be added to project the specific emotion.
-The second file describes "personal" traits to specific emotions.
+The second file describes ``personal'' traits to specific emotions.
 For example, one person could intensify his happiness, but conceal his sadness.
@@
 \textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
-This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is the predominant (i.e., primary or secondary).
+This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is predominant (i.e., primary or secondary).
 \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
@@
 Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges.
-The root and non-leaf nodes could be either \textit{parallel} or \textit{sequential} type.
+The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type.
 The parallel node could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
@@
 If a sequence node receives a finish message, it will execute the next branch.
-In case that all branches have been executed, it communicates the end of the action.
-On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message; it will propagate the message to all branches to move to the consecutive emotional parameter.
-If a node is principal and it has finished of executing all actions, it will inform to its predecessor.
+When all branches have been executed, it communicates the end of the action.
+On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression.
+If a node is principal and it has finished to execute all actions, it will notify its predecessor.
 
@@
 Any node can belong to one of two levels: principal or  secondary.
-If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
+If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.%Why is this needed?
 Compound actions are implemented combining all type of nodes.
@@
 If both conditions are fulfilled, the system generates an Emotion Execution Tree that represents the specified action.
-A similar procedure is done for simple action but instead of decomposing the action, the system directly verify the parameters and then generates the execution tree.
-Once the emotional execution tree has been created, the system proceeds to add actions that are required to express the desired emotion.
+A similar procedure is done for simple action, but, instead of decomposing the action, the system directly verifies the parameters and then generates the execution tree.
+Once the Emotion Execution Tree has been created, the system proceeds to add actions that are required to express the desired emotion.
 Then, it proceeds to modify the parameters to convey the emotion, considering emotion and character descriptors.
 When the process is completed, the system feeds information to the correct ``drivers'', which have been implemented to execute the desired action on a specific platform.
-Every time that a driver detects the end of the action, it informs the Emotional enrichment system, which will take the proper actions.
+Every time that a driver detects the end of the action, it informs the Emotional Enrichment System, which will take the proper actions.
 
@@
 
-The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight
-.
-To fulfill all the requirements, the system was implemented in two different nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
-The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite
+The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
+. To fulfill all the requirements, the system was implemented in two different nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
+: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
+The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite Andy-You may also just cite our paper already in the list.
+There are no papers specific to this platform.
  and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
 The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$.
+%TODO Andy-a sentence about how the drivers could apply the description to these two so different platforms (e.g., Keepon is not moving) would be needed.
 
@@
 An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions.
-To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential.
-This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different "drivers".
+%To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential.
+Andy-This can be left away since it has been already described
+This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different drivers.
 

### 2017-01-05 HRI-LBR/HRI-LBR2017.tex
addition and correction of some sentences

@@
 The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
-. To fulfill all the requirements, the system was implemented in two different nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
+. To fulfill all the requirements, the system was implemented in two different ROS nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
 : one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
-The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite Andy-You may also just cite our paper already in the list.
-There are no papers specific to this platform.
+The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013}
  and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
+
 The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$.
-%TODO Andy-a sentence about how the drivers could apply the description to these two so different platforms (e.g., Keepon is not moving) would be needed.
+The drivers for these actions were implemented for each platform.
+But, they were grouped by an interface, which hides the existence of them to the rest of the system.
 

### 2017-01-08 HRI-LBR/HRI-LBR2017.tex
Update HRI-LBR2017.tex

@@
 
-The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
-. To fulfill all the requirements, the system was implemented in two different ROS nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
-: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
-The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013}
- and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
+The system has been implemented in C++ and interfaced with ROS.
+To fulfill all the requirements, the system was implemented in two different ROS nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
+The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013} and Keepon\footnote{The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
 
@@
 An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. 
-%To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential.
-Andy-This can be left away since it has been already described
 This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different drivers.

### 2017-01-09 RO-MAN-2017-1/Parts/Antecedents.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-09-26 HRI/Parts/Antecedents.tex
@@
-An experiment was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness, which correspond to four basic emotions suggested by Ekman~\cite{Ekman2001}.
+An experiment was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness, which correspond to four of six basic emotions suggested by Ekman~\cite{Ekman2001}.
 These features were selected after study emotion projection in robotics, humans (i.e.
@@
 A Google form was used to collect participants' answers.
-The form included the four emotions plus two mental states (i.e.
+The form included four emotions plus two mental states (i.e.
 excitement and tenderness) and option ''other''.
-These mental state were added to see if people could confuse the desired emotion with them.
+These mental states were added to see if people could confuse the desired emotion with them.
 Each participant was exposed to twenty over one hundred and ninety five possible treatments.
@@
 After collecting all the data, it was created a table for each treatment.
-Each table contain the following information mean, standard deviation, and median.
+Each table contained the following information mean, standard deviation, and median.
 ANOVA test was not possible to be used over the data because the assumption of normality is not achieved in the collected data.
@@
 This calculation was done using the R package \textit{irr}.
-To improve the table interpretation, it was decided to just record the emotions' alpha values that had a mean greater than zero.
+To improve table interpretation, it was decided to just record the emotions' alpha values that had a mean greater than zero.
 Therefore, tables with a top ten ranking have been set up.

### 2017-01-09 RO-MAN-2017-1/Parts/CaseStudy.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-10-04 HRI/Parts/CaseStudy.tex
@@
-The case study was done at Researcher's Night 2015 with two main objectives (i) cross-validate the findings obtained from the experiment, and (ii) use the Emotional Enrichment System to verify whether the participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
-The Emotional Enrichment System was used in both cases.
+The case study was done at Researcher's Night 2015 with two main objectives:
+\begin{enumerate}
+	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}.
+This experiment was done to study the attribution of different linear and angular velocities, oscillation angel, direction and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
+A total of 196 were designed, but just 20 treatments were presented to each participant.
+The questionnaire provided included the four emotions and two mental states (i.e.
+Excitement and tenderness).
+	\item Verify if participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression. 
+\end{enumerate}
 To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage.
-The detection of the AR tags was done through the use of the ROS package ar\_track\_alvar~\cite{artag2015}.
+AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}.
 The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.
@@
 	\includegraphics[width=0.45\textwidth]{./Images/FourthCase.png} 
-	\caption{Environment setup for the case study.}
+	\caption{Environment setup for the case study. The crosses represent the starting points.}
 	\label{fig:setup_fourth}
@@
 
-The parameters selected for each of four emotions (\textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) are shown in Table~\ref{table:selected_fourth}.
-The main considerations to select the two implementations for each emotion were: (i) the linear velocity should be greater than $0$.
+The parameters selected from the experiment to express \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
+As it could be observed, two implementations of each emotions were selected.
+These implementations were selected considering: (i) the linear velocity should be greater than $0$.
 In other words the robot should show some linear displacement.
@@
 
-\begin{table}[h]
+\begin{table}
 \centering
@@
 			\hline
-			Happiness 1&$0$&$0$&$500$&$3$&$0.349$\\
+			Happiness-1&$0$&$0$&$500$&$3$&$0.349$\\
 			\hline
-			Happiness 2&$0$&$0$&$900$&$3$&$0.174$\\
+			\co Happiness-2&\co $0$&\co $0$&\co $900$&\co $3$&\co $0.174$\\
 			\hline
-			Anger 1&$\pi$&$0$&$500$&$3$&$0.087$\\
+			Anger-1&$\pi$&$0$&$500$&$3$&$0.087$\\
 			\hline
-			Anger 2&$0$&$0$&$900$&$1$&$0.087$\\
+			\co Anger-2&\co $0$&\co $0$&\co $900$&\co $1$&\co $0.087$\\
 			\hline
-			Fear 1&$\pi$&$\pi$&$900$&$2$&$0.174$\\
+			Fear-1&$\pi$&$\pi$&$900$&$2$&$0.174$\\
 			\hline
-			Fear 2&$\pi$&$\pi$&$500$&$2$&$0.087$\\
+			\co Fear-2&\co $\pi$&\co $\pi$&\co $500$&\co $2$&\co $0.087$\\
 			\hline
-			Sadness 1&$\pi$&$0$&$200$&$1$&$0.349$\\
+			Sadness-1&$\pi$&$0$&$200$&$1$&$0.349$\\
 			\hline
-			Sadness 1&$0$&$\pi$&$200$&$1$&$0.349$\\
+			\co Sadness-2&\co $0$&\co $\pi$&\co $200$&\co $1$&\co $0.349$\\
 			\hline
@@
 This idea was brought from human theatrical actors, who prepared their movements based on zones on the stage~\cite{wilson2009theatre}.
-This allows them to adapt their position based on other actors.
+This allows them to adapt their position based on other actors and stage dimensions.
 Therefore, the stage was discretized in 9x9 matrix as is shown in Figure~\ref{fig:stage_division}.
 Robot's movements are given in terms of the matrix positions to the Emotional Enrichment System.
-This allows the adaptation to different stage dimensions because robot's final position is calculated by the Emotional Enrichment System during execution, which takes under consideration the stage dimensions given.
-For instance, during the scene's preparation in the laboratory the stage was 3 meters per 3 meters, but in the final presentation the stage was 2.5 meters per 2.5 meters.
+Robot's final position is calculated by the Emotional Enrichment System during execution.
+For instance, during the scene's preparation stage was 3 meters per 3 meters, but in the final presentation it was 2.5 meters per 2.5 meters.
 
@@
 
-The scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
-Then, the robot moves to upstage right center and rotates by $\pi/2$ left (See~\cite{Artopia}).
-Next the robot moves to the right center to then go to the center.
+Scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
+Then, the robot moves to upstage right center and rotates to $\pi/2$ left (See~\cite{Artopia}).
+Next the robot moves to the right center.
+Then it goes to the center.
 When it arrives there, it turns full back and move backwards to downstage center with a full front orientation.
@@
 	\includegraphics[width=0.95\textwidth]{./Images/fourthCaseSceneD.png} 
-	\caption{Sequence of movements done by the robot.
-The red arrows show the trajectory done by the robot, while the numbers show the order among the movements.
-a) The first ten movements b) The last five movements }
+	\caption{Sequence of movements provided to the robot. The red arrows show the trajectory, while the numbers show the order among the movements. a) The first ten movements b) The last five movements }
 	\label{fig:movement}
@@
 
-The relation between emotion and movement is as follow: movements one, two, three, four and five are expressed without any emotion.
-Movements six, seven, eight, nine and ten show fear.
+The relation between emotion and movement is as follow: movements one to five do not express any emotion.
+Movements six to ten show fear.
 Movement eleven depicts happiness, and the remaining movements depict sadness.
-The two scenes are executed by the Emotional Enrichment System using the same ''script'' and the emotion selection is done manually via graphical interface (Figure~\ref{fig:graphical_interface}).
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.48\textwidth]{./Images/InterfaceExperiment.png} 
-	\caption{Graphical interface used to communicate with the Emotional Enrichment System.
-a) It is the interface used to send the actions sequence.
-b) It is the interface used to send a emotion and its intensity.}
-	\label{fig:graphical_interface}
-\end{figure}
+The actions describing this scene are executed by the Emotional Enrichment System and the emotion selection is done manually via a graphical interface.
 
@@
 This case study was done during Researchers' Night, 2015.
-During a period of two days, people were asked to participate to this study.
-Each subject was exposed to two rounds, in each one the robot was performing a different emotion.
-And  they were also exposed twice to a small scene, one with emotion and other without emotions.
-The emotions showed in each trial and the order of the scenes (with or without emotion) were generated randomly beforehand.
+During a period of two days, people were asked to participate to this study, which was divided in to parts.
+In the first one, each subject was exposed to two rounds of emotions.
+The emotion presented and the order were generated randomly before hand.
+In the second part, they were explained that a small scene was going to be presented twice.
+Thus, they should to selected the one they like it more.
+The order of the scenes (e.g.
+with or without emotion) were generated beforehand.
 The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender.

### 2017-01-09 RO-MAN-2017-1/Parts/Conclusions.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-10-04 HRI/Parts/Conclusions.tex
@@
 For each one of four emotions (i.e.
-Anger, Happiness, Sadness and Fear) studied in the experiment were selected a two set of parameters.
-These parameters were described in files and used as input to the Enrichment Emotional System, which was in charge to combine actions with emotions.
-The results show that both implementations of happiness were confused with anger and excitement, while one implementation of anger was just confused with excitement.
+Anger, Happiness, Sadness and Fear) studied in the experiment were selected a two set of parameters.The results show that both implementations of happiness were confused with anger and excitement, while one implementation of anger was just confused with excitement.
 Both implementations of sadness were confused with tenderness and fear.
 Both implementations of fear had a recognition rate over 50\%.
-Scene's results show that people prefer scenes with emotional movements and there is not any difference in gender.
+Scenes results show that people prefer scenes with emotional movements and there is not any difference in gender.
 

### 2017-01-09 RO-MAN-2017-1/Parts/Introduction.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-10-04 HRI/Parts/Introduction.tex
@@
 Many psychological studies have been focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
-This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been used to convey emotions.
+This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
+%~\cite{haering2011},
+~\cite{Destephe2013}
+) have been used to convey emotions.
 However in many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
@@
 
-It has been noticed that the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those exploiting anthropomorphic features.
+It has been noticed that the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
+%,Lakatos2014,Sharma2013,Novika2015}
+) remains still small in comparison to those exploiting anthropomorphic features.
 Moreover, these works do not give specific range of values for the characteristics used to expressed  emotions implemented.
@@
 Section~\ref{sec:related_work} introduce some previous works done in conveying emotion.
-Then the experiment is briefly described in section~\ref{sec:experiment}.
 Section~\ref{sec:system} presents the platform used in the case study and the Emotional Enrichment System.

### 2017-01-09 RO-MAN-2017-1/Parts/RelatedWork.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-12-06 JournalIJSR/Parts/Emotion_Projection.tex
@@
-Although it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010}, human studies provide guidelines about possible features and values that could be used to generate emotional motion.
-
-\subsection{Human Studies}
-
-Emotion plays an important role in human-human interaction, and can be expressed through diverse channels such as body gestures and poses, body movements, face expressions.
-Given the complex structure of human face, where more than 43 muscles act, face configurations are considered as a primary channel to express emotion.
-As a consequence, many works have focused on facial expression, mainly, but not only, influenced by the work done by Ekman~\cite{Ekman2004}.
-However, the role that body plays in emotion projection was recognized, too, and started to be studied~\cite{Gelder2008,Wallboot1998}.
-Nevertheless, the amount of works related to body expression of emotions is still small compared to studies about facial expression.
-
-Analysing some of the few works that have studied human body expressiveness, it is possible to recognize two different methodologies to create the data base of movements to be assessed during the experiments.
-Applying a first methodology, human actors (either professionals, or amateurs) are asked to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}.
-Each trial is recorded and later shown to each subjects that have to classify all the sequences.
-The second methodology uses virtual agents~\cite{Roether2009,Venture2014} to generate the very same set up for the experiments; the agent's movements are generated from the data recorded from human actors.
-
-The work done by Wallboot~\cite{Wallboot1998} has been used as a reference by others.
-It addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
-His results reaffirm that movement and body postures are indicative of intensity for some emotions.
-But at the same time, these two characteristics seem to be enough to identify other emotions.
-
-Complementary studies using virtual agents have been performed by  Kluwer and collaborators~\cite{Kluwer2004}, who studied the contribution of postures and angle view in the interpretation of emotions.
-They generated 176 static positions for happiness, anger, disgust, fear, sadness and surprise.
-Each image was later rendered from three different angles (front, left, and above and behind left shoulder) producing a total of 528 images.
-All the participants were exposed to all 528 images and were asked to label the image with the emotions that best represent it.
-Their results show that five out of six emotions were quite well recognized independently from the angle of view., while disgust was for some postures confused with fear.
-
-The main drawback of all these projects is the use of video recorded sequences, which misses the impact related to a complete physical experience.
-For instance, it is clearly different facing an angry robot really rushing against us, or looking at a video where this happens.
-
-\subsection{Robotic Studies}
-%%%%%%%%%%%%%%%%%%%%%%
-
-As a direct consequence of the abundance of works in face elicitation in humans, most of the works done in Human-Robot Interaction (HRI) have focused also on faces.
+Most of the works done in Human-Robot Interaction (HRI) have focused on faces, due to the abundance of works in face elicitation in humans.
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
-The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (happiness, surprise, anger, disgust, fear, and sadness), plus interest.
+The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest.
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
 Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions.
-In same direction Destephe and collaborators~\cite{Destephe2013b,Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
-More recently Knight and Simmons~\cite{knight2016} used Keepon and NAO platforms to study the possibility to project inner states with just head movements.
-Although use of videos has the advantage to cover a major number of participants, the lack of interaction with the real platform make these works lose the impact that a robot could generate on the participants.
+In same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
+Knight and Simmons~\cite{knight2016} used two platforms (i.e.
+Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements.
+Although the use of videos has the advantage to cover a major number of participants, they loss the impact that is created from the interaction between the participant and the platform.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-The use of real platforms to study emotion projection could be dived in two lines: using anthropomorphic and non-anthropomorphic platforms.
+The use of real platforms to study emotion projection could be dissect by the type of platform used.
+Therefore two tendencies could been observed: use of anthropomorphic and non-anthropomorphic platforms.
 In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}.
@@
 eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
-Pushing forward the reduction on anthropomorphic features, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
+Trying to reduce the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
 Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the  work done by Camurri et al.~\cite{pop00002}.
@@
 All these works present a very nice starting to point to identify features and values that could be used to project emotions in robotics, which could help in coordinating humans and robots~\cite{Novika2015}.
-However, all of these works not give a price guideline to elicit precise emotions, which from our previous case studies could lead to the misinterpretation of movements emotions~\cite{Angel2016}.
+However, these works not give a price guideline to elicit precise emotions.
+This could lead to implementations that express a not desired emotion~\cite{Angel2016}.
 For example people could confuse an implementation of \textit{Happiness} with \textit{Anger}.

### 2017-01-09 RO-MAN-2017-1/Parts/Results.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

This section reports the results obtained during two days for the two parts of the case study.

\subsection{Part I: Emotion Recognition}

The results obtained from the presentation of emotional movements are summarized in 
Table~\ref{table:result_fourth}. 
\begin{table}
\centering
\small
\caption{Summary of the answers obtained in the presentation of emotional movements.}
		\label{table:result_fourth}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
			\hline
\rotatebox{90}{\textbf{Presented/Reported } }&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{ \textbf{Anger}} &
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Excitement}}&
\rotatebox{90}{\textbf{Tenderness}}&
\rotatebox{90}{\textbf{Other}}&
\rotatebox{90}{\textbf{Total}}\\	
			\hline
			Happiness-1&8&16&7&4&16&4&7&62\\
			\hline
			\co Happiness-2&\co 11&\co 11&\co 6&\co 2&\co 19&\co 3&\co 1&\co 53\\
			\hline
			Anger-1&7&5&6&2&21&7&1&49\\
			\hline
			\co Anger-2&\co 14&\co 29&\co 13&\co 2&\co 13&\co 3&\co 2&\co 76\\
			\hline
			Fear-1&6&2&28&1&9&6&0&52\\
			\hline
			\co Fear-2&\co 7&\co 3&\co 37&\co 2&\co 20&\co 4&\co 1&\co 74\\
			\hline
			Sadness-1&3&5&17&14&5&16&5&65\\
			\hline
			\co Sadness-2&\co 5&\co 5&\co 15&\co 28&\co 6&\co 15&\co 7&\co 81\\
			\hline
			\end{tabular}
\end{table}

It could be observed that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}. In a similar way, Anger-1 was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
Anger-2 shows an improvement of perception from 10\% to 38\%, respect Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
Both implementations of \textit{Fear} had a high level of recognition 54 \% and 50 \% and mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation. Finally, the two implementation of \textit{Sadness} were confused with \textit{Fear} and \textit{Tenderness}.

To have a clear idea about these misinterpretations among implemented emotions, a Fisher's exact test was applied for ten different combinations. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation. The results are reported in Table~\ref{table:result_compare_fourth}. The following are the hypothesis used for this test:

\begin{itemize}
	\item $H_0 = $ there is a difference in the recognition of the two compared implementations.
	\item $H_1 = $ there is not a difference in the recognition of the two compared implementations.
\end{itemize}

As this analysis suggest, both implementation of \textit{Anger} were perceived as two different emotions. Also shows that both implementation of \textit{Happiness} were perceived as similar to Anger-2.

\begin{table}
\centering
\small
\caption{Pair comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
		\label{table:result_compare_fourth}
		\begin{tabular}{|c|c|c|}
			\hline	
\textbf{Pair Compared} & \textbf{p-value} & \textbf{p-value*}\\	
			\hline
			Happiness-1 vs Happiness-2 &$0.38$&$1.0$\\
			\hline
			Anger-1 vs Anger-2 & $<0.001$ 
			%7.3e-4
			& $<0.001$
			%4.4e-3
			\\
			\hline
			Anger-2 vs Happiness-1 & $0.137$&$0.69$\\
			\hline
			Anger-2 vs Happiness-2 & $0.157$&$0.69$\\
			\hline
			Fear-1 vs Fear-2 & $0.74$&$1.0$\\
			\hline
			Sadness-1 vs Sadness-2 & $0.665$&$1.0$\\
			\hline
			Fear-1 vs Sadness-1& $<0.001$ 
			%8.35e-5
			& $<0.001$
			%5.8e-4
			\\
			\hline
			Fear-1 vs Sadness-2 & $<0.001$
			%5e-7
			& $<0.001$
			%4e-6
			\\
			\hline
			Fear-2 vs Sadness-1 & $<0.001$
			%2e-7
			& $<0.001$
			%1.8e-6
			\\
			\hline
			Fear-2 vs Sadness-2 & $<0.001$
			%1e-7
			& $<0.001$
			%1e-6
			\\
			\hline
			\end{tabular}
\end{table} 
Moreover, an analysis was done per groups, for each presented emotion. For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This lead to a table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

For each table the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed. The results are shown in table~\ref{table:Precision2}. The following are the hypothesis used for this test:

\begin{itemize}
	\item $H_0 = $ there is a difference in recognition between the implementation respect the others.
	\item $H_1 = $ there is not a difference in recognition between one implementation respect the others.
\end{itemize}

They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with the others. While both implementation of \textit{Happiness} and Anger-1 are considered as similar to the other implementations. %TODO make clear this part

\begin{table}
\centering
\small
\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the case study.} 
\label{table:Precision2}
		\begin{tabular}{|p{1.6 cm}|p{1.5 cm}|c|c|c|}
		\hline
		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
		\hline
		Happiness-1 & $0.13$ & $0.79$ & $0.11$ & $0.74$\\
		\hline
		\co Happiness-2 &\co $0.21$ &\co $0.81$ &\co $3.7$ &\co$0.054$\\
		\hline
		Anger-1 & $0.1$ & $0.8$ & $3.8e^{-29}$ & $1$\\
		\hline
		\co Anger-2 &\co $0.38$ &\co $0.81$ &\co $34.4$ &\co $<0.001$ 
		%4.47e-9
		\\
		\hline
		Fear-1 & $0.54$ & $0.8$ & $36.2$ & $<0.001$ 
		%1.8-e9
		\\
		\hline 
		\co Fear-2 &\co $0.5$ &\co $0.78$ &\co $35.8$ &\co $<0.001$ 
		%5.3e-10
		\\
		\hline
		Sadness-1 & $0.22$ & $0.85$ & $27.4$ & $<0.001$
		%$1.63e-7$
		\\
		\hline
		\co Sadness-2 &\co 0.35 &\co 0.85 &\co 72.9 &\co $<0.001$
		%2.2e-16
		\\		 
		\hline
			\end{tabular}
\end{table}

 For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}. The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$). 
Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape. Another important factor to highlight is the impact words listed in the questionnaire have on the perception rate. As it was expected, mental states Excitement and Tenderness were confused with emotions with similar arousal level. In this precise case the emotions Anger, Happiness and Fear were confused with Excitement, and Sadness was confused with Tenderness. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

\begin{table}
\centering
\small
		\caption{Classification accuracy of the presented emotions by the single panels, computed as mentioned in the text, with corresponding 95\% confidence interval, no-information rate, and p-value that accuracy is greater than the NIR.}		
		\label{table:nir_fourth}
			\begin{tabular}{|p{1.8 cm}|c|c|c|c|}
				\hline		
\rotatebox{90}{\textbf{Presented Emotion}}&
\rotatebox{90}{\textbf{Classification Accuracy}}&
\rotatebox{90}{\textbf{95\% CI}}&
\rotatebox{90}{\textbf{No-Information Rate}}&
\rotatebox{90}{\textbf{P-Value [Acc $>$ NIR]}}\\
				\hline
			Happiness-1&0.79&(0.75,0.82)&0.89&1.0\\
			\hline
			\co Happiness-2&\co 0.81&\co (0.77,0.84)&\co 0.88&\co 1.0\\
			\hline
			Anger-1&0.8&(0.76,0.83)&0.88&1.0\\
			\hline
			\co Anger-2&\co 0.89&\co (0.76,0.84)&\co 0.83&\co 0.95\\
			\hline
			Fear-1&0.79&(0.75,0.83)&0.88&1\\
			\hline
			\co Fear-2&\co 0.78&\co (0.73,0.81)&\co 0.83&\co 0.99\\
			\hline
			Sadness-1&0.85&(0.81,0.88)&0.84&0.47\\
			\hline
			\co Sadness-2&\co 0.85&\co (0.81,0.88)&\co 0.81&\co 0.035\\
			\hline
			\end{tabular}
\end{table}

\subsection{Part II: Scene Preference}

The results obtained form the small scene are presented in Table~\ref{table:preference_selection}. From this data, two questions wanted to be answer:
\begin{enumerate}
	\item Do people prefer scenes with or without emotions?
	\item Has gender an impact in the preference?
\end{enumerate}
To answer these questions the following hypothesis were created:
\begin{enumerate}
	\item $H_0 =$ there is a preference towards scenes with emotions. $H_1$ there is a preference towards scenes without emotions. 
	\item $H_0 =$ there is an association between gender and the preference. $H_1 =$ there is not an association between gender and the preference. 
\end{enumerate}
A $\chi^2$ test with one degree of freedom and $\alpha = 0.05$ was done to verify them. The results of the tests show that there is enough statistical evidence to accept that people prefer scenes with emotions ($p<0.001$). On the other hand, the test shows that there is not association between gender and preference $(p=0.85)$.

\begin{table}
\centering
		\caption{Answers obtained for the small scene.}		
		\label{table:preference_selection}
			\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Gender}&\textbf{With Emotion}&\textbf{Without Emotion}&\textbf{Total}\\
			\hline
			Male & 84 & 43 & 127\\
			\hline
			Female & 81 & 45 & 126\\
			\hline
			\textbf{Total} & 165 & 88 & 253\\
			\hline
			\end{tabular}
\end{table}

### 2017-01-09 RO-MAN-2017-1/Parts/System.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

--- 2016-09-25 HRI/Parts/System.tex
@@
-The system used is divided in the platform and emotional enrichment system.
-
-\subsection{Robotic Platform}
-
-A non-anthropomorphic robotic platform without any bio-inspired appearance was developed and used in this case study.
+A non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance.
 The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
-The platform could be observed in Figure~\ref{fig:Robot}
+The platform could be observed in Figure~\ref{fig:Robot}.
+The Arduino Due is in charge to be the interface between the hardware (e.g.
+motors) and Odroid, which host all the Emotion Enrichment System.
 
@@
 \end{figure}
-
-\subsection{Emotion Enrichment System}
-
-The main idea of Emotional Enrichment System (EES) is to blend an emotion and a action to produce an "emotional action".
-However this is not far as previous works have done so far.
-The system has been envisioned to also allow:
-
-\begin{itemize}
-	\item Interoperability among different platform.
-	\item Introduction of new parameters and emotions.
-	\item Interface with diverse action decision system.
-\end{itemize}
-
-In other words, the system could be thought as a box that receives a desire action, action's parameters and emotions to blend them together without paying particular attention who or how the decision to execute a particular action with specific parameters were made.
-This is achieved through the use of text messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.
-To change the emotion without affecting the action that is being executed, these information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity.
-
-Every time the system receives a new action, it verifies if the action exists and the parameters corresponds to the action.
-If these two conditions are met, then the system checks if the action is compound or simple.
-If it is a simple, the system proceeds to add all the required actions (emotive actions) and change their parameters to convey the desired emotion.
-On the other hand if the action is compound, the action is first decomposed in simple actions (mandatory actions).
-Each one of these actions is then process to add their emotive actions.
-However, this addition is done taking in consideration to not add any action that was previously added.
-Once all the set of simple actions and their parameters are determined, the system proceeds to verify the drivers' existence to execute these actions in the desired platform.
-If the system finds out that one or more mandatory actions could not be executed, it triggers a message to inform that the desire action could not be executed.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Simple and Compound Actions}
-To achieve actions' enrichment with emotions, two different types of actions are used: simple and compound actions.
-Simple actions are actions that could be considered as ''atomic''; these actions can be enriched with emotion changing their specific parameters.
-For example, consider two simple actions: speak and move body.
-The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement.
-Therefore, for the speaking action the following parameters are expected: text, pitch and tone.
-On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints.
-Since each action is characterized by different parameters, the parameters' modifications to obtain an emotional action will be different for each of them.
-
-\subsubsection{Emotional Execution Tree}
-The \textit{Emotional Enrichment System}  is grounded on the use of \textit{Emotional Execution Tree} ($EXT$), which is a computational representation of actions desired actions that should be executed.
-$EXT$ is a connected acyclic graph with vertices and  edges.
-The root and non-leaf nodes could be \textit{parallel} or \textit{sequence} type.
-The parallel node could be one out of four different sub-types: action and emotion synchronous, action synchronous and emotion asynchronous, action asynchronous and emotion synchronous, or action and emotion asynchronous.
-Sequential nodes could just be one of two sub-types: emotion synchronous or asynchronous.
-Action synchronous means that each time that a parallel node receives a finish notification (success or failure), it will send a finish message to all the nodes that derived from it.
-On the other hand, emotion synchronous means that each time that a node (sequence or parallel) receives an emotion synchronization message, it will propagate the message to all the actions in the branches.
-This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of the desired action.
-Finally, the leaf nodes could only be simple action nodes.
-All the nodes can assume two levels: principal or secondary.
-If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary cannot propagate any message to its predecessor.
-
-\subsubsection{Implementation}
-Figure~\ref{fig:system_architecture} presents the design used to achieve the desire goals.
-As it could be observed, the system is divided in two parts.
-The first part in charge to enrich a given action with a desired emotion, and the second in charge to hide the real execution of the action.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{Images/SystemArchitecture.png} 	
-	\caption{General system design.
-Each simple action corresponds to one ROS node, and there is just one node for the emotion enrichment system.
-The ovals represent the ROS topic parameters, rectangles represent \textit{black boxes}, and texts outside containers represent input files that contain the system parametrization.}
-	\label{fig:system_architecture}
-\end{figure*}
-
-The process to enrich an action is threefold as follows:
-\begin{enumerate}
-
-	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received.
-The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described on the message.
-This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
-When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created.
-
-	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase.
-In this phase new $sa$ are added to the $ext$ and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
-This process is broken down in two steps.
-First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
-Second, the emotional parameters are modulated based on the emotion's intensity and character traits.
-
-	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
-The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
-In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.
-
-\end{enumerate}
+An Emotional Enrichment System was designed and implemented to automatize the process of emotion expression~\cite{Angel2017}.
+It modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
+To achieve this, the system receives two messages.
+One message describes actions and the order in which they should be executed.
+These actions could be executed in parallel, sequentially or a combination of both.
+This kind of description enables the possibility to communicate several actions in one message.
+The other message informs the system with the desire emotion and its intensity.
+These two messages could arrive asynchronously and without any particular order.
+Every time a message is received, the system updates the robot movements to convey the desire emotion in the specific action.

### 2017-01-09 RO-MAN-2017-1/RO-MAN2017.tex
First version of RO-Man article base on the last case study. this article has been improved from the one submitted to HRI, but it is still necessary to review the general idea and how to make everything more clear

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
                                   % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{url}
\usepackage{slashbox}
\newcommand{\co}{\cellcolor{gray!40}}
\usepackage[table]{xcolor}
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins

\title{\LARGE \bf
Cross Validation of Emotional Features with a non-Anthropomorphic Platform
}

\author{Julian M. Angel-Fernandez$^{1}$ and Andrea Bonarini$^{2}$% <-this % stops a space
\thanks{$^{1}$Julian M. Angel-Fernandez is a Research at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
        {\tt\small julian.angel.fernandez@tuwien.ac.at}}%
\thanks{$^{2}$Andrea Bonarini is a Professor at the Department of Electronics, Information, and Bioengineering, Politecnico di Milano, Milan, Italy,
        {\tt\small andrea.bonarini@polimi.it}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Robots should be able to express emotional states to interact with people as social agents. Emotions are a peculiar characterization of humans and usually conveyed through face expression or body language. However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure. This is the case of home cleaners, package carriers, and many others platforms. Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes. The work presented in this paper studies emotion expression in non-anthropomorphic platform and how it is perceived by humans. The work uses results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness. Results show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions. Additionally, it was done a small scene to verify if people prefer emotions with or without emotion. 
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\label{sec:related_work}
\section{Related Work}
\input{./Parts/RelatedWork}
\section{System}
\label{sec:system}
\input{./Parts/System}
\section{Case Study}
\label{sec:case}
\input{./Parts/CaseStudy}
\section{Results}
\label{sec:results}
\input{./Parts/Results}
\section{Conclusions and Further work}
\input{./Parts/Conclusions}
\bibliographystyle{IEEEtran}
\bibliography{Bibliography,BibloNew,Biblography}

\addtolength{\textheight}{-12cm}
\end{document}

### 2017-01-25 RO-MAN-2017-1/Parts/CaseStudy.tex
New version of the last case study

@@
-The case study was done at Researcher's Night 2015 with two main objectives:
+The case study presented in this paper was done at Researcher's Night 2015 with two main objectives:
 \begin{enumerate}
@@
 This experiment was done to study the attribution of different linear and angular velocities, oscillation angel, direction and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
-A total of 196 were designed, but just 20 treatments were presented to each participant.
+A total of 196 treatments were designed, but just 20 were presented to each participant.
 The questionnaire provided included the four emotions and two mental states (i.e.
@@
 	\item Verify if participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
-\end{enumerate}
 To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage.
@@
 
+\end{enumerate}
+
 \subsection{Emotion Description}
 
-The parameters selected from the experiment to express \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
-As it could be observed, two implementations of each emotions were selected.
-These implementations were selected considering: (i) the linear velocity should be greater than $0$.
+The parameters selected from the experiment to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
+As it could be observed, two treatments for each emotions were selected to be implemented.
+These treatments were selected considering: (i) the linear velocity should be greater than $0$.
 In other words the robot should show some linear displacement.
@@
 This case study was done during Researchers' Night, 2015.
-During a period of two days, people were asked to participate to this study, which was divided in to parts.
-In the first one, each subject was exposed to two rounds of emotions.
-The emotion presented and the order were generated randomly before hand.
-In the second part, they were explained that a small scene was going to be presented twice.
-Thus, they should to selected the one they like it more.
+During a period of two days, people were asked to participate in this study, which was divided in to parts.
+The first one, each subject was exposed to two rounds of emotions.
+The two emotions and their other were generated randomly before hand.
+The second part, participants were explained that a small scene was going to be presented twice.
+Thus, they should to selected the one they like more.
 The order of the scenes (e.g.

### 2017-01-25 RO-MAN-2017-1/Parts/Introduction.tex
New version of the last case study

@@
-Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}.
-Many psychological studies have been focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states.
-This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
+Emotions and mental states are not just expressed through facial expression and voice but also by body postures and other features~\cite{Gelder2008}.
+Many psychological studies have focused their attention on how emotions are conveyed through they face~\cite{Ekman2004},~\cite{kleinsmith2012affective}.
+Similarly, the robotics community uses anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
 %~\cite{haering2011},
 ~\cite{Destephe2013}
-) have been used to convey emotions.
-However in many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
-Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}, for instance in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
-This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.
+) to convey emotions.
+In many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
+Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
+For instance, floor cleaning robots are robots that do not have any anthropomorphic characteristics and still they accomplish their task.
+This generates the necessity to study other mechanisms that could help to convey emotions, which could give people an idea about the robots' state, and engage the user in long term relations.
 
-It has been noticed that the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
+However,the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
 %,Lakatos2014,Sharma2013,Novika2015}
 ) remains still small in comparison to those exploiting anthropomorphic features.
-Moreover, these works do not give specific range of values for the characteristics used to expressed  emotions implemented.
-For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature,  but their connection to specific emotions is not explicited.
-Rather, they establish a relationship between their values and pleasure/arousal dimensions.
+Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented.
+For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature,  but their connection to specific emotions is not described.
+Rather, they established a relationship between their values and pleasure/arousal dimensions.
 This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristics to avoid  misinterpretation with wrong emotions.

### 2017-01-25 RO-MAN-2017-1/Parts/RelatedWork.tex
New version of the last case study

@@
-Most of the works done in Human-Robot Interaction (HRI) have focused on faces, due to the abundance of works in face elicitation in humans.
-One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
-The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest.
+%Most works in Human-Robot Interaction (HRI) focus their attention on faces and human-like bodies, due to the abundance of works in face elicitation in humans. Moreover, 
+Some works in Human-Robot Interaction (HRI) uses videos to evaluate their implementations of emotions.
+One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and show emotions.
+The face had enough degrees of freedom to portray the emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest.
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-The use of real platforms to study emotion projection could be dissect by the type of platform used.
-Therefore two tendencies could been observed: use of anthropomorphic and non-anthropomorphic platforms.
+The use of real platforms to study emotion projection could be dissect in two tendencies: use of anthropomorphic and non-anthropomorphic platforms.
 In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}.
@@
 Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements.
-To overcome this limitation, some researchers have reduce the human appearance (e.g.
+To overcome this limitation, some researchers have reduce the human resemblance (e.g.
 eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
-Trying to reduce the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
+Reducing even more the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
 Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the  work done by Camurri et al.~\cite{pop00002}.
@@
 Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
+Despite the type of platform used, these works offers an overview of features that could be used to express certain emotions but they not give precise values to implement the emotions.
 
-Other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement.
+Therefore, other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement.
 For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}.

### 2017-01-25 RO-MAN-2017-1/Parts/Results.tex
New version of the last case study

@@
 
-To have a clear idea about these misinterpretations among implemented emotions, a Fisher's exact test was applied for ten different combinations.
-Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation.
-The results are reported in Table~\ref{table:result_compare_fourth}.
-The following are the hypothesis used for this test:
+An analysis was done per groups, for each presented emotion.
+For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
+This lead to a table, which is known as contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
+\begin{table}[!htbp]
+\begin{center}
+\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
+\label{table:singleEmotion}
+\begin{tabular}{|c|c|c|}
+\hline 
+Presented/Reported&Happiness&Other\\
+\hline 
+Happiness-1&8&54\\
+\hline 
+Other&42&355\\
+\hline
+\end{tabular}
+\end{center}
+%\vspace{-0.5cm}
+\end{table}
+
+For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e.
+the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}.
+The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$).
+
+\begin{table}
+\centering
+\small
+		\caption{Classification accuracy of the presented emotions by the single panels, computed as mentioned in the text, with corresponding 95\% confidence interval, no-information rate, and p-value that accuracy is greater than the NIR.}
+		\label{table:nir_fourth}
+			\begin{tabular}{|p{1.8 cm}|c|c|c|c|}
+				\hline		
+\rotatebox{90}{\textbf{Presented Emotion}}&
+\rotatebox{90}{\textbf{Classification Accuracy}}&
+\rotatebox{90}{\textbf{95\% CI}}&
+\rotatebox{90}{\textbf{No-Information Rate}}&
+\rotatebox{90}{\textbf{P-Value [Acc $>$ NIR]}}\\
+				\hline
+			Happiness-1&0.79&(0.75,0.82)&0.89&1.0\\
+			\hline
+			\co Happiness-2&\co 0.81&\co (0.77,0.84)&\co 0.88&\co 1.0\\
+			\hline
+			Anger-1&0.8&(0.76,0.83)&0.88&1.0\\
+			\hline
+			\co Anger-2&\co 0.89&\co (0.76,0.84)&\co 0.83&\co 0.95\\
+			\hline
+			Fear-1&0.79&(0.75,0.83)&0.88&1\\
+			\hline
+			\co Fear-2&\co 0.78&\co (0.73,0.81)&\co 0.83&\co 0.99\\
+			\hline
+			Sadness-1&0.85&(0.81,0.88)&0.84&0.47\\
+			\hline
+			\co Sadness-2&\co 0.85&\co (0.81,0.88)&\co 0.81&\co 0.035\\
+			\hline
+			\end{tabular}
+\end{table}
+
+Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypothesis used in the test were:
 
 \begin{itemize}
-	\item $H_0 = $ there is a difference in the recognition of the two compared implementations.
-	\item $H_1 = $ there is not a difference in the recognition of the two compared implementations.
+	\item $H_0 = $ there is a difference in recognition between the implementation respect the others.
+	\item $H_1 = $ there is not a difference in recognition between one implementation respect the others.
 \end{itemize}
 
-As this analysis suggest, both implementation of \textit{Anger} were perceived as two different emotions.
-Also shows that both implementation of \textit{Happiness} were perceived as similar to Anger-2.
+The results are shown in table~\ref{table:Precision2}.
+They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with other implementations.
+While both implementations of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.
+
+\begin{table}
+\centering
+\small
+\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the case study.} 
+\label{table:Precision2}
+		\begin{tabular}{|p{1.6 cm}|p{1.5 cm}|c|c|c|}
+		\hline
+		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
+		\hline
+		Happiness-1 & $0.13$ & $0.79$ & $0.11$ & $0.74$\\
+		\hline
+		\co Happiness-2 &\co $0.21$ &\co $0.81$ &\co $3.7$ &\co$0.054$\\
+		\hline
+		Anger-1 & $0.1$ & $0.8$ & $3.8e^{-29}$ & $1$\\
+		\hline
+		\co Anger-2 &\co $0.38$ &\co $0.81$ &\co $34.4$ &\co $<0.001$ 
+		%4.47e-9
+		\\
+		\hline
+		Fear-1 & $0.54$ & $0.8$ & $36.2$ & $<0.001$ 
+		%1.8-e9
+		\\
+		\hline 
+		\co Fear-2 &\co $0.5$ &\co $0.78$ &\co $35.8$ &\co $<0.001$ 
+		%5.3e-10
+		\\
+		\hline
+		Sadness-1 & $0.22$ & $0.85$ & $27.4$ & $<0.001$
+		%$1.63e-7$
+		\\
+		\hline
+		\co Sadness-2 &\co 0.35 &\co 0.85 &\co 72.9 &\co $<0.001$
+		%2.2e-16
+		\\		 
+		\hline
+			\end{tabular}
+\end{table}
+
+To determine if which implementations were perceived as different or similar, a Fisher's exact test was applied for ten different combinations of the implementations.
+Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation.
+The following are the hypothesis used in this test:
+
+\begin{itemize}
+	\item $H_0 = $ there is a difference in the recognition of the two compared emotions.
+	\item $H_1 = $ there is not a difference in the recognition of the two compared emotions.
+\end{itemize}
+
+The results are reported in Table~\ref{table:result_compare_fourth}.
+As it could be observed, both implementation of \textit{Anger} were perceived as two different emotions ($p<0.001$).
+Also shows that both implementation of \textit{Happiness} were perceived as to Anger-2 ($p=0.69$ in both cases).
 
@@
 \end{table}
-Moreover, an analysis was done per groups, for each presented emotion.
-For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
-This lead to a table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
-\begin{table}[!htbp]
-\begin{center}
-\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
-\label{table:singleEmotion}
-\begin{tabular}{|c|c|c|}
-\hline 
-Presented/Reported&Happiness&Other\\
-\hline 
-Happiness-1&8&54\\
-\hline 
-Other&42&355\\
-\hline
-\end{tabular}
-\end{center}
-%\vspace{-0.5cm}
-\end{table}
 
-For each table the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed.
-The results are shown in table~\ref{table:Precision2}.
-The following are the hypothesis used for this test:
-
-\begin{itemize}
-	\item $H_0 = $ there is a difference in recognition between the implementation respect the others.
-	\item $H_1 = $ there is not a difference in recognition between one implementation respect the others.
-\end{itemize}
-
-They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with the others.
-While both implementation of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.
-%TODO make clear this part
-
-\begin{table}
-\centering
-\small
-\caption{Accuracy, precision and results of Pearson's $\chi^2$ for each contingency matrix with $\alpha = 0.05$ for the case study.} 
-\label{table:Precision2}
-		\begin{tabular}{|p{1.6 cm}|p{1.5 cm}|c|c|c|}
-		\hline
-		\textbf{Presented Emotion} & \textbf{Positive Predicted Value} & \textbf{Accuracy} & \textbf{$\chi^2(1)$} & \textbf{p-value}\\
-		\hline
-		Happiness-1 & $0.13$ & $0.79$ & $0.11$ & $0.74$\\
-		\hline
-		\co Happiness-2 &\co $0.21$ &\co $0.81$ &\co $3.7$ &\co$0.054$\\
-		\hline
-		Anger-1 & $0.1$ & $0.8$ & $3.8e^{-29}$ & $1$\\
-		\hline
-		\co Anger-2 &\co $0.38$ &\co $0.81$ &\co $34.4$ &\co $<0.001$ 
-		%4.47e-9
-		\\
-		\hline
-		Fear-1 & $0.54$ & $0.8$ & $36.2$ & $<0.001$ 
-		%1.8-e9
-		\\
-		\hline 
-		\co Fear-2 &\co $0.5$ &\co $0.78$ &\co $35.8$ &\co $<0.001$ 
-		%5.3e-10
-		\\
-		\hline
-		Sadness-1 & $0.22$ & $0.85$ & $27.4$ & $<0.001$
-		%$1.63e-7$
-		\\
-		\hline
-		\co Sadness-2 &\co 0.35 &\co 0.85 &\co 72.9 &\co $<0.001$
-		%2.2e-16
-		\\		 
-		\hline
-			\end{tabular}
-\end{table}
-
- For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e.
-the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}.
-The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$).
 Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape.
@@
 Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
-
-\begin{table}
-\centering
-\small
-		\caption{Classification accuracy of the presented emotions by the single panels, computed as mentioned in the text, with corresponding 95\% confidence interval, no-information rate, and p-value that accuracy is greater than the NIR.}
-		\label{table:nir_fourth}
-			\begin{tabular}{|p{1.8 cm}|c|c|c|c|}
-				\hline		
-\rotatebox{90}{\textbf{Presented Emotion}}&
-\rotatebox{90}{\textbf{Classification Accuracy}}&
-\rotatebox{90}{\textbf{95\% CI}}&
-\rotatebox{90}{\textbf{No-Information Rate}}&
-\rotatebox{90}{\textbf{P-Value [Acc $>$ NIR]}}\\
-				\hline
-			Happiness-1&0.79&(0.75,0.82)&0.89&1.0\\
-			\hline
-			\co Happiness-2&\co 0.81&\co (0.77,0.84)&\co 0.88&\co 1.0\\
-			\hline
-			Anger-1&0.8&(0.76,0.83)&0.88&1.0\\
-			\hline
-			\co Anger-2&\co 0.89&\co (0.76,0.84)&\co 0.83&\co 0.95\\
-			\hline
-			Fear-1&0.79&(0.75,0.83)&0.88&1\\
-			\hline
-			\co Fear-2&\co 0.78&\co (0.73,0.81)&\co 0.83&\co 0.99\\
-			\hline
-			Sadness-1&0.85&(0.81,0.88)&0.84&0.47\\
-			\hline
-			\co Sadness-2&\co 0.85&\co (0.81,0.88)&\co 0.81&\co 0.035\\
-			\hline
-			\end{tabular}
-\end{table}
 

### 2017-01-25 RO-MAN-2017-1/Parts/System.tex
New version of the last case study

@@
-A non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance.
-The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
+A non-anthropomorphic robotic platform was created to no influence participants' perception.
+The robotic platform is holonomic and it was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
 The platform could be observed in Figure~\ref{fig:Robot}.
@@
 \end{figure}
+
 An Emotional Enrichment System was designed and implemented to automatize the process of emotion expression~\cite{Angel2017}.

### 2017-01-25 RO-MAN-2017-1/RO-MAN2017.tex
New version of the last case study

@@
 Robots should be able to express emotional states to interact with people as social agents.
-Emotions are a peculiar characterization of humans and usually conveyed through face expression or body language.
+Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice.
 However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure.
@@
 Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes.
-The work presented in this paper studies emotion expression in non-anthropomorphic platform and how it is perceived by humans.
-The work uses results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness.
-Results show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions.
+This paper presents a case study, which studies emotion expression in non-anthropomorphic platform and how it is perceived by humans.
+This case study was design base on results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness.
+Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions.
 Additionally, it was done a small scene to verify if people prefer emotions with or without emotion.
@@
 \input{./Parts/Introduction}
+\section{Related Work}
 \label{sec:related_work}
-\section{Related Work}
 \input{./Parts/RelatedWork}

### 2017-01-26 RO-MAN-2017-1/RO-MAN2017.tex
Update RO-MAN2017.tex

@@
 Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice.
-However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure.
+However, there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks that require a specific structure.
 This is the case of home cleaners, package carriers, and many others platforms.
-Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes.
-This paper presents a case study, which studies emotion expression in non-anthropomorphic platform and how it is perceived by humans.
-This case study was design base on results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness.
+Therefore, emotional states need to be represented by exploiting non-anthropomorphic features, such as movements and shape changes.
+This paper presents a case study concerning emotion expression in non-anthropomorphic platform and how it is perceived by humans.
+This case study was designed basing on results obtained from a previous experiment, done to assess precise values for linear velocity, angular velocity, oscillation angle, direction, and orientation that could be used to express happiness, anger, fear, and sadness.
 Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions.
-Additionally, it was done a small scene to verify if people prefer emotions with or without emotion.
+Additionally, a small scene was played to verify whether people prefer actions with or without emotion expression.
 \end{abstract}

### 2017-01-26 RO-MAN-2017-1/Parts/Introduction.tex
Update Introduction.tex

@@
 Emotions and mental states are not just expressed through facial expression and voice but also by body postures and other features~\cite{Gelder2008}.
-Many psychological studies have focused their attention on how emotions are conveyed through they face~\cite{Ekman2004},~\cite{kleinsmith2012affective}.
+Many psychological studies have focused their attention on how emotions are conveyed through the face~\cite{Ekman2004},~\cite{kleinsmith2012affective}.
 Similarly, the robotics community uses anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
@@
 For instance, floor cleaning robots are robots that do not have any anthropomorphic characteristics and still they accomplish their task.
-This generates the necessity to study other mechanisms that could help to convey emotions, which could give people an idea about the robots' state, and engage the user in long term relations.
+This generates the necessity to study other mechanisms that could help to convey emotions, which could give people an idea about the robot's state, and engage the user in long term relations.
 
@@
 ) remains still small in comparison to those exploiting anthropomorphic features.
-Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented.
+Moreover, these works do not provide specific range of values for the characteristics used to express the implemented emotions.
 For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature, but their connection to specific emotions is not described.
 Rather, they established a relationship between their values and pleasure/arousal dimensions.
-This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristics to avoid  misinterpretation with wrong emotions.
-These values could be used in social robotics to show emotions and as consequence increase their acceptance.
+This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristic to avoid misinterpretation with wrong emotions.
+These values could be used in social robotics to show emotions and, as consequence, increase their acceptance.
 
 This paper is organized as follows.
-Section~\ref{sec:related_work} introduce some previous works done in conveying emotion.
+Section~\ref{sec:related_work} introduces some previous works done in conveying emotion.
 Section~\ref{sec:system} presents the platform used in the case study and the Emotional Enrichment System.
-Finally, sections~\ref{sec:case} and~\ref{sec:results} presented case study's design and results.
+Finally, sections~\ref{sec:case} and~\ref{sec:results} present case study's design and results.

### 2017-01-26 RO-MAN-2017-1/Parts/RelatedWork.tex
Update RelatedWork.tex

@@
 %Most works in Human-Robot Interaction (HRI) focus their attention on faces and human-like bodies, due to the abundance of works in face elicitation in humans. Moreover, 
-Some works in Human-Robot Interaction (HRI) uses videos to evaluate their implementations of emotions.
+Some researchers in Human-Robot Interaction (HRI) use videos to evaluate their implementations of emotions.
 One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and show emotions.
-The face had enough degrees of freedom to portray the emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest.
+The face had enough degrees of freedom to portray the emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus \textit{Interest}.
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
 Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions.
-In same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
-Knight and Simmons~\cite{knight2016} used two platforms (i.e.
-Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements.
-Although the use of videos has the advantage to cover a major number of participants, they loss the impact that is created from the interaction between the participant and the platform.
+In the same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
+Knight and Simmons~\cite{knight2016} used two platforms (i.e., Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements.
+Although the use of videos has the advantage to cover a major number of participants, they miss the impact created from the physical interaction between the participant and the platform.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-The use of real platforms to study emotion projection could be dissect in two tendencies: use of anthropomorphic and non-anthropomorphic platforms.
-In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}.
-In some cases, special attention has been taken to determine head's angle and arms position contribution in specific emotions~\cite{Brown2014}.
+The use of real platforms to study emotion projection follows two paths: use of anthropomorphic and non-anthropomorphic platforms.
+The first path is characterized by the use of cue positions to project emotions~\cite{NAO2013}.
+In some cases, special attention has been taken to determine head's angle and arms' position contribution to specific emotion expressions~\cite{Brown2014}.
 Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements.
-To overcome this limitation, some researchers have reduce the human resemblance (e.g.
-eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
+To overcome this limitation, some researchers have reduced the human resemblance (e.g., eliminating limbs and facial expressions) to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
 Reducing even more the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
@@
 
-Therefore, other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement.
+Other approaches have been adopted to get a better understanding of the contribution of diverse features to express emotions through movement.
 For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}.
@@
 Their results suggest that direction is directly correlated with dominance, but that fluidity does not influence the perception.
-While flat orientation is related to positive valence, leaning position are related with negative valance.
-Finally the velocity is correlated with valence, arousal and dominance.
+While flat orientation is related to positive valence, leaning positions are related with negative valence.
+Finally, the velocity is correlated with valence, arousal and dominance.
 
-Due to the popularity that quadrocoptors have received in the last years, Sharma and collaborators~\cite{Sharma2013} used a quadrotor to study how different Laban's effort~\cite{Laban1968} parameters could impact on the perception of affection.
+Due to the popularity that quadrocopters have received in the last years, Sharma and collaborators~\cite{Sharma2013} used a quadrotor to study how different Laban's effort~\cite{Laban1968} parameters could impact on the perception of affection.
 A professional Laban certified actor was asked to generate 16 different paths, for each one changing one of the four Laban's parameters (space, weight, time, and flow).
-Each generated path was recorded using the Vicon motion-tracking system.
-Continuing with the use of quadrocoptors, Cauchard and collaborators~\cite{Cauchard2016} studied how flight paths could project personal traits and emotional attributes.
-All these works present a very nice starting to point to identify features and values that could be used to project emotions in robotics, which could help in coordinating humans and robots~\cite{Novika2015}.
-However, these works not give a price guideline to elicit precise emotions.
-This could lead to implementations that express a not desired emotion~\cite{Angel2016}.
+Each generated path was recorded using the Vicon motion-tracking system ad then replicated on the quadrocopter.
+Cauchard and collaborators~\cite{Cauchard2016} studied how flight paths could project personal traits and emotional attributes.
+All these works present a very nice starting point to identify features and values that could be used to project emotions in robotics, which could help in coordinating humans and robots~\cite{Novika2015}.
+However, these works do not give a clear guideline to elicit precise emotions.
+This could lead to implementations that express an undesired emotion~\cite{Angel2016}.
 For example people could confuse an implementation of \textit{Happiness} with \textit{Anger}.

### 2017-01-26 RO-MAN-2017-1/Parts/CaseStudy.tex
Update CaseStudy.tex

@@
-The case study presented in this paper was done at Researcher's Night 2015 with two main objectives:
+ The case study presented in this paper was held at an exhibition with two main objectives:
 \begin{enumerate}
 	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}.
-This experiment was done to study the attribution of different linear and angular velocities, oscillation angel, direction and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
-A total of 196 treatments were designed, but just 20 were presented to each participant.
-The questionnaire provided included the four emotions and two mental states (i.e.
-Excitement and tenderness).
-	\item Verify if participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression.
-To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage.
+This experiment was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
+A total of 196 value combinations were designed, 20 of which were presented to each participant.
+Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}).
+	\item Verify whether participants would prefer scenes when the robot moves expressing emotions or rather moves on the same trajectory without any emotion expression.
+To control scene variability two cameras and eight AR tags were used together with a Kalman filter to improve robot localization on the stage.
 AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}.
-The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.
+The distribution of thecameras and the tags is reported in Figure~\ref{fig:setup_fourth}.
 
@@
 
-The parameters selected from the experiment to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
-As it could be observed, two treatments for each emotions were selected to be implemented.
-These treatments were selected considering: (i) the linear velocity should be greater than $0$.
-In other words the robot should show some linear displacement.
-And (ii) it should be in the top 10 list of the emotion obtained in the experiment.
+The parameters selected to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
+As it could be observed, two configurations for each emotion were selected among the ones evaluated in the previous experiment to be cross-checked.
+These configurations had to satisfy two conditions: (i) the linear velocity should be greater than $0$, so the robot should show some displacement, and (ii) it should be in the top 10 list of the configurations tested in the previous experiment.
 
@@
 \small
-\caption{Parameters' values selected from the experiment.}
+\caption{Parameter values selected from the previous experiment.}
 		\label{table:selected_fourth}
@@
 Stage discretization was used to give zones of movements instead of absolute positions.
-This idea was brought from human theatrical actors, who prepared their movements based on zones on the stage~\cite{wilson2009theatre}.
+This idea was brought from human theatrical actors, who arrange their movements based on zones on the stage~\cite{wilson2009theatre}.
 This allows them to adapt their position based on other actors and stage dimensions.
-Therefore, the stage was discretized in 9x9 matrix as is shown in Figure~\ref{fig:stage_division}.
-Robot's movements are given in terms of the matrix positions to the Emotional Enrichment System.
-Robot's final position is calculated by the Emotional Enrichment System during execution.
-For instance, during the scene's preparation stage was 3 meters per 3 meters, but in the final presentation it was 2.5 meters per 2.5 meters.
+The stage was discretized in 9x9 matrix as shown in Figure~\ref{fig:stage_division}.
+Robot's movements are given in terms of matrix positions to the Emotional Enrichment System.
+The robot's final position is calculated by the Emotional Enrichment System during execution.
+For instance, the scene was designedon a 3 x 3 meters stage, but in the presentation at teh exhibition the stage was 2.5 x 2.5 meters.
 
@@
 	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseScene.png} 
-	\caption{Stage discretization  used for the small scene. The blue squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
+	\caption{Stage discretization  used for the scene. The blue squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
 	\label{fig:stage_division}
@@
 
-Scene's description is the following: the robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
+The scene can be described as follows.
+The robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
 Then, the robot moves to upstage right center and rotates to $\pi/2$ left (See~\cite{Artopia}).

### 2017-01-26 RO-MAN-2017-1/Parts/CaseStudy.tex
Update CaseStudy.tex

@@
 The robot's final position is calculated by the Emotional Enrichment System during execution.
-For instance, the scene was designedon a 3 x 3 meters stage, but in the presentation at teh exhibition the stage was 2.5 x 2.5 meters.
+For instance, the scene was designed on a 3 x 3 meters stage, but in the presentation at the exhibition the stage was 2.5 x 2.5 meters.
 
@@
 The scene can be described as follows.
-The robot starts in the middle of the stage to move to the upstage right (See~\cite{Musical}), close to the right wing.
-Then, the robot moves to upstage right center and rotates to $\pi/2$ left (See~\cite{Artopia}).
+The robot starts in the middle of the stage to move to the upstage right (see~\cite{Musical}), close to the right wing.
+Then, the robot moves to upstage right center and rotates to $\pi/2$ left (see~\cite{Artopia}).
 Next the robot moves to the right center.
@@
 Finally the robot turns to profile right and it does a step back; then it goes to the upstage center and then upstage right.
-The sequence of movements programmed to the robot are depicted in Figure~\ref{fig:movement}.
+The sequence of movements of the robot are depicted in Figure~\ref{fig:movement}.
 \begin{figure*}
@@
 	\includegraphics[width=0.95\textwidth]{./Images/fourthCaseSceneD.png} 
-	\caption{Sequence of movements provided to the robot. The red arrows show the trajectory, while the numbers show the order among the movements. a) The first ten movements b) The last five movements }
+	\caption{Sequence of robot's movements. The red arrows show the trajectory, while the numbers show the order among the movements. a) The first ten movements b) The last five movements }
 	\label{fig:movement}
@@
 
-The relation between emotion and movement is as follow: movements one to five do not express any emotion.
-Movements six to ten show fear.
+Movements have been enriched by emotional expression as follows: movements one to five do not express any emotion, movements six to ten show fear.
 Movement eleven depicts happiness, and the remaining movements depict sadness.
-The actions describing this scene are executed by the Emotional Enrichment System and the emotion selection is done manually via a graphical interface.
+The actions describing this scene are executed by the Emotional Enrichment System and the emotion selection is designed via a graphical interface.
 
@@
 
-This case study was done during Researchers' Night, 2015.
-During a period of two days, people were asked to participate in this study, which was divided in to parts.
-The first one, each subject was exposed to two rounds of emotions.
-The two emotions and their other were generated randomly before hand.
-The second part, participants were explained that a small scene was going to be presented twice.
-Thus, they should to selected the one they like more.
-The order of the scenes (e.g.
-with or without emotion) were generated beforehand.
+This case study was done at an exhibition during a period of two days.
+People coming to the stand were asked to participate in this study, which was divided in to parts.
+In the first one, each subject was exposed to two emotion expressions.
+%TODO Was it so?
+I have turned the sentence...
+The two emotions were generated to guarantee a random uniform presentation.
+In the second part, participants were explained that a small scene was going to be presented twice, and they had to select the one they like more.
+The order of the scenes (e.g., with or without emotion) was generated beforehand.
 The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender.
 The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76.
+We accepted this variability as representative of a general population.

### 2017-01-26 RO-MAN-2017-1/Parts/System.tex
Update System.tex

@@
-A non-anthropomorphic robotic platform was created to no influence participants' perception.
-The robotic platform is holonomic and it was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels.
-The platform could be observed in Figure~\ref{fig:Robot}.
-The Arduino Due is in charge to be the interface between the hardware (e.g.
-motors) and Odroid, which host all the Emotion Enrichment System.
+A non-anthropomorphic robotic platform was created to limit the influence of shape on the participants' perception.
+The robotic platform is holonomic and it included Odroid U3 and Arduino Due, 3 metal gear motors with 64 CPR encoders, and omniwheels.
+Arduino Due is in charge to interface motors and Odroid U3, which hosts the Emotion Enrichment System described here below.
+The platform is shown in Figure~\ref{fig:Robot}.
 
@@
 One message describes actions and the order in which they should be executed.
-These actions could be executed in parallel, sequentially or a combination of both.
-This kind of description enables the possibility to communicate several actions in one message.
-The other message informs the system with the desire emotion and its intensity.
+These actions could be executed in parallel, sequentially or as a combination of both.
+This kind of representation enables the possibility to communicate several actions in one message.
+The other message tells the system the emotion to be expressed and its intensity.
 These two messages could arrive asynchronously and without any particular order.
-Every time a message is received, the system updates the robot movements to convey the desire emotion in the specific action.
+Every time a message is received, the system updates the robot movements to convey the desired emotion in the specific action.

### 2017-01-26 RO-MAN-2017-1/Parts/Results.tex
Update Results.tex

@@
 It could be observed that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}.
-In a similar way, Anger-1 was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
-Anger-2 shows an improvement of perception from 10\% to 38\%, respect Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
-Both implementations of \textit{Fear} had a high level of recognition 54 \% and 50 \% and mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation.
+In a similar way, \textit{Anger-1} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
+\textit{Anger-2} shows an improvement of perception from 10\% to 38\% with respect to Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
+Both implementations of \textit{Fear} had a high level of recognition, respectively 54\% and 50\%, although they have been mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation.
 Finally, the two implementation of \textit{Sadness} were confused with \textit{Fear} and \textit{Tenderness}.
@@
 An analysis was done per groups, for each presented emotion.
-For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
-This lead to a table, which is known as contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
+For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many of those identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
+This lead to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
 \begin{table}[!htbp]
@@
 
-For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e.
+For each of the contingency tables the classification accuracy and the no-information rate (NIR), i.e.
 the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}.
-The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$).
+The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations with some statistical significance ($p<0.05$).
 
@@
 \begin{itemize}
-	\item $H_0 = $ there is a difference in recognition between the implementation respect the others.
-	\item $H_1 = $ there is not a difference in recognition between one implementation respect the others.
+	\item $H_0 = $ there is a difference in recognition between the implementation with respect to the others.
+	\item $H_1 = $ there is not a difference in recognition between one implementation with respect to the others.
 \end{itemize}
@@
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with other implementations.
+They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compared with other implementations.
 While both implementations of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.
@@
 
-To determine if which implementations were perceived as different or similar, a Fisher's exact test was applied for ten different combinations of the implementations.
+To determine which implementations were perceived as different or similar, a Fisher's exact test was applied for ten different combinations of the implementations.
 Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation.
@@
 The results are reported in Table~\ref{table:result_compare_fourth}.
-As it could be observed, both implementation of \textit{Anger} were perceived as two different emotions ($p<0.001$).
-Also shows that both implementation of \textit{Happiness} were perceived as to Anger-2 ($p=0.69$ in both cases).
+As it could be observed, both implementations of \textit{Anger} were perceived as two different emotions ($p<0.001$) and both implementations of \textit{Happiness} were perceived as Anger-2 ($p=0.69$ in both cases).
 
@@
 \small
-\caption{Pair comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study.
+\caption{Pairwise comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study.
 The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
@@
 
-Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape.
-Another important factor to highlight is the impact words listed in the questionnaire have on the perception rate.
-As it was expected, mental states Excitement and Tenderness were confused with emotions with similar arousal level.
-In this precise case the emotions Anger, Happiness and Fear were confused with Excitement, and Sadness was confused with Tenderness.
-Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
+Nevertheless, it is important to notice that the results were obtained using the lower part of the robot without any change in its shape.
+Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate.
+As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level.
+In this precise case the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}.
+Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
 
@@
 
-The results obtained form the small scene are presented in Table~\ref{table:preference_selection}. From this data, two questions wanted to be answer:
+The results obtained from the scene trials are presented in Table~\ref{table:preference_selection}. From this data, two questions had to be answered:
 \begin{enumerate}
@@
 \end{enumerate}
-To answer these questions the following hypothesis were created:
+To answer these questions the following hypotheses were created:
 \begin{enumerate}
@@
 The results of the tests show that there is enough statistical evidence to accept that people prefer scenes with emotions ($p<0.001$).
-On the other hand, the test shows that there is not association between gender and preference $(p=0.85)$.
+On the other hand, the test shows that there is no association between gender and preference $(p=0.85)$.
 
@@
 \centering
-		\caption{Answers obtained for the small scene.}		
+		\caption{Answers obtained for the scene trials.}		
 		\label{table:preference_selection}

### 2017-01-26 RO-MAN-2017-1/Parts/Conclusions.tex
Update Conclusions.tex

--- 2016-09-21 HRI/Parts/Conclusions.tex
@@
-The case study presented in this chapter was done to cross validate the findings in the experiment.
-For each one of the four emotions studied in the experiment were selected two set of parameters.
-The results show that both implementations of happiness were confused with anger and excitement, while one implementation of anger was just confused with excitement.
-Both implementations of sadness were confused with tenderness and fear.
-Both implementations of fear had a recognition rate over 50\%.
-Additionally to the cross validation, it was done a small scene to check if people have preference to scenes where emotional movements are presented or not.
-The results show that people prefer scenes with emotional movements.
+The case study presented in this paper was done to cross validate the findings in a previous experiment~\cite{}, and to verify whether the subjects would prefer scenes when the robot expresses emotions rather than the same trajectories without any emotion expression.
+For each one of four emotions (i.e., \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) studied in the experiment two set of parameters were selected to express them.
+The results show that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}, while one implementation of \textit{Anger} was confused with \textit{Excitement}.
+Both implementations of \textit{Sadness} were confused with \textit{Tenderness} and \textit{Fear}.
+This supports the hypothesis that the selected parameter values are related to arousal, since confusion appears among emotions with high arousal, and among those with low arousal.
+Both implementations of \textit{Fear} had a recognition rate over 50\%.
+This, together with the last statement may suggest that people have different models of \textit{Fear} and that thsi single label is not enough to distinguish among them.
+
+In the scene trials, people showed, without any difference in gender, to prefer scenes with emotional movements.
+
+Additionally to the already mentioned results, it resulted that there are words that could bias participants' perception.
+For instance, \textit{Happiness} and \textit{Anger} were considered as \textit{Excitement}.
+This misinterpretation is not a surprise, given the fact that there is not a unique definition of emotion~\cite{Plutchik2001,cacioppo2000handbook}, and each person would interpret a situation differently, so they will give a different label to the presented movement.
+Moreover, a misinterpretation of \textit{Happiness} and \textit{Anger} could suggest that additional features (e.g., trajectory or shape) should be added to increase differentiation between them.
+For example, Venture and collaborators~\cite{Venture2014} had found out that in human bodies the recognition rate of \textit{Anger} and \textit{Fear} are increased when torso and head are downwards.
+On the other hand, they found that \textit{Happiness} perception is increased when the torso and head are moved upwards.
+This example could bring some insight to possible body changes that could occur in non-human like bodies, but this should still to be tested in this kind of platforms.

### 2017-02-22 RO-MAN-2017-2/Parts/EmotionalTree.tex
first version

--- 2017-01-08 HRI-LBR/HRI-LBR2017.tex
@@
-\documentclass{sig-alternate-05-2015}
-
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{float}
-\usepackage{url}
-\usepackage{caption}
-\begin{document}
-
-% Copyright
-\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-%
-% --- Author Metadata here ---
-\conferenceinfo{HRI}{'17 Vienna, Austria}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
-\title{Towards Enriching Robot's Actions with Affective Movements}
-%\subtitle{[Extended Abstract]
-%\titlenote{A full version of this paper is available as
-%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-%\LaTeX$2_\epsilon$\ and BibTeX} at
-%\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{2} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-%Author name\\
-%       \affaddr{Author institution}\\
-%       \affaddr{Institution's address}\\
-%       \affaddr{City}\\
-%       \email{mail@mail.com}
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Julian M. Angel-Fernandez\\
-       \affaddr{Automation and Control Institute, Vienna University of Technology}\\
-       \affaddr{Karlspltz 13, 1040}\\
-       \affaddr{Vienna, Austria}\\
-       \email{julian.angel.fernandez@tuwien.ac.at}
-%% 2nd. author
-\alignauthor
-Andrea Bonarini\\
-       \affaddr{Dipartimento di Elettronica, Informazione e Bioingegneria, Politecnico di Milano}\\
-       \affaddr{Piazza Leonardo da Vinci 31, 20133}\\
-       \affaddr{Milan, Italy}\\
-       \email{andrea.bonarini@polimi.it}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-%\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-
-\maketitle
-\begin{abstract}
-Emotions are considered by many researchers as beneficial in social robotics, since they can enrich human-robot interaction with non-verbal clues.
-Although there have been works that have studied emotion expression in robotics, the mechanisms created to project emotion are usually highly integrated in each solution.
-This limits the possibility to develop a general approach.
-This paper presents a system that has been initially created for a theatrical robot to enrich its actions with emotions, but it has been designed to be adaptable to other fields.
-The emotional enrichment system has been envisioned to be used with any action decision system.
-\end{abstract}
-
-\printccsdesc
-
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{Human-Robot Interaction; Emotions Enrichment System; Emotion Projection}
-
-\section{Introduction}
-%The development of fast, cheap and reliable electronics has enabled the creation of new devices and versatile robotic platforms.
-These new platforms' capabilities have expanded the frontiers of robots applications to new environments, where robots are expected to interact with humans, such as health care, and house cleaning, among others.
-However, bringing robots in these context raise the challenge to increase their acceptance.
-Improving robots' appearances and capabilities may be thought as a possible solution, and it is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfill people's expectations.
-
-Bringing robots in a social context raise the challenge to increase their acceptance. %Improving robots' appearances and capabilities may be thought as a possible solution, and i
-It is expected that people would treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary to devise robots that match people's expectations.
-Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
-As a consequence, they added specific emotional poses and expressions to their robots.
-Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}.
-Nevertheless, these research activities have developed modules to show emotions that are strongly integrated with their specific setting, which eliminate the possibility to re-use or adapt their solutions for other projects.
-
-This paper presents an Emotional Enrichment System, which modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
-Although the system was originally conceived to be used in an autonomous performance robot to enrich actions with emotions~\cite{angel2013}, its design was devised to make it extensible to other platforms and adaptable to new tasks.
-To achieve this goal, the system relies on an Emotional Execution Tree, which is based on simple actions or primitive, sequential, and parallel nodes.
-Additionally, the concept of compound actions is adopted to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions generated by specific combinations of simple actions and other nodes.
-
-\section{Emotional Enrichment System}
-
-The main idea of Emotional Enrichment System is to blend a specific emotion with a desired action to generate "emotional actions".
-Differently from previous approaches, the system has been envisioned to allow: (i) interoperability among different platforms, (ii) introduction of new parameters and emotions, and (iii) interface with diverse action decision systems.
-
-Therefore, the system could be thought as a black-box that receives a desired action and emotion, and produces an emotionally enriched action through modification of actions' parameters and addition of other actions to the original one.
-This modification is done following the description given in two configuration files.
-One defines how actions' parameters should be modified and what actions should be added to project the specific emotion.
-The second file describes ``personal'' traits to specific emotions.
-For example, one person could intensify his happiness, but conceal his sadness.
-
-\subsection{Basic Concepts}
-
-The system is based on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}.
-\textit{Simple actions} are actions that are considered as primitives: they are used as building blocks.
-Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place.
-Their description specifies mandatory and optional parameters that are required to execute an action.
-\textit{Compound actions} are actions that are created from simple actions.
-These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g.
-compound actions that are used often).
-\textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
-This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is predominant (i.e., primary or secondary).
-\textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
-This description could also include addition of other simple actions.
-\textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse treats.
-Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed.
-This tree is first created from the action message description and then modified using the emotional parameters and character description.
-
-\subsection{Emotional Execution Tree}
-
 Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges.
@@
 Compound actions are implemented combining all type of nodes.
-
-\subsection{Process}
-
-When the system is launched, it starts reading emotion descriptors, and it creates an internal representation.
-Every time the system receives a new action message the verification process starts.
-This message includes a description of actions that should be executed, with their respective values.
-If the action is compound, it is first decomposed in simple actions, which will be labeled as primary actions, and checked if all actions exists in the system and the parameters correspond to the specification.
-If both conditions are fulfilled, the system generates an Emotion Execution Tree that represents the specified action.
-A similar procedure is done for simple action, but, instead of decomposing the action, the system directly verifies the parameters and then generates the execution tree.
-Once the Emotion Execution Tree has been created, the system proceeds to add actions that are required to express the desired emotion.
-Then, it proceeds to modify the parameters to convey the emotion, considering emotion and character descriptors.
-When the process is completed, the system feeds information to the correct ``drivers'', which have been implemented to execute the desired action on a specific platform.
-Every time that a driver detects the end of the action, it informs the Emotional Enrichment System, which will take the proper actions.
-
-\subsection{Implementation}
-
-The system has been implemented in C++ and interfaced with ROS.
-To fulfill all the requirements, the system was implemented in two different ROS nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms.
-The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013} and Keepon\footnote{The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.
-
-The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$.
-The drivers for these actions were implemented for each platform.
-But, they were grouped by an interface, which hides the existence of them to the rest of the system.
-
-\section{Conclusions and Further Work}
-
-An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. 
-This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different drivers.
-
-Further work is envisioned to add additional parameters and new actions into the system. These new actions will correspond to other modalities, such as facial expression and voice/sound.
-\bibliographystyle{splncs}
-\bibliography{Bibliography,BibloNew,Biblography}
-\end{document}

### 2017-02-22 RO-MAN-2017-2/Parts/Implementation.tex
first version

The system was implemented in \textit{C++} with interface with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description done in previous sections. 
\begin{figure*}
	\centering
	\includegraphics[width=1.0\textwidth]{Images/SystemArchitecture.png} 	
	\caption{General system design. Each simple action corresponds to one ROS node, and there is just one node for the emotion enrichment system. The ovals represent the ROS topic parameters, rectangles represent \textit{black boxes}, and texts outside containers represent input files that contain the system parametrization.}
	\label{fig:system_architecture}
\end{figure*}
The emotion enrichment core is divided in three different modules. 
Each module is responsible for one of the following phases:
\begin{enumerate}
	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received. The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described on the message. This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional. When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created such as the one presented in the Figure~\ref{fig:reference} that corresponds to the example of walk and speak.
	\begin{figure}
		\centering
		%Representation
	\includegraphics[width=0.45\textwidth]{./Images/Representation.png}
	\caption{Emotional Execution Tree for the example shown in the Figure~\ref{fig:compound_example}. The context node colored in purple represents a sequential context, while the other represents a parallel.}
	\label{fig:reference}
	\end{figure}
	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase. In this phase new $sa$ are added to the $ext$ and the $sa$'s parameters are modified following the emotion description, which is loaded from files. This process is broken down in two steps. First, all the actions that are required to convey the desired emotion, and that are not yet present are added. Second, the emotional parameters are modulated based on the emotion's intensity and character traits.
	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters). The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution. In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.
\end{enumerate}
%The first one is in charge to receive any action and built a $EXT$. Once this tree is created, the second part is in charge to decorate this tree with the additional actions and modify the parameters of all the actions. The last part is the one that executes the final tree and communicate to all the simple actions ROS nodes the parameters that should be executed by them. It is important to notice that the action's parameters and the emotional parameters are communicated via two different channels. This is done to not affect actions' execution when the emotion or its intensity is changed.
All the text message broadcast among the nodes are written using JSON format, which is human understandable, is light and there are diverse available parser.\\ 
To test the system was used to different platforms: Keepon Pro and an own made platform called Triskarino.
Keepon was used to test the interoperability of the system to different platforms, while Triskarino has been used as a part of the robot actor project~\cite{angel2013}. The whole TheatreBot architecture has not finished just, thus the change of emotion and selection of action to execute were done manually.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Keepon Test}
To test the system with Keepon (Fig.~\ref{fig:keepon}) was just necessary to implement the platform's controllers in each one of the simple action ROS nodes. Given that this platform does not have the capability to displace its body, the action move body was not implemented. Once added these controllers to the system, we proceeded to modify the configuration files to use this platform instead of Triskarino. With this small modification, we were able to change from one platform to other. In the video\footnote{YouTube video name Emotional Enrichment System, url: https://youtu.be/bRSXQ0rzkO8}
 is shown the test where Keepon has to move its torso forward and backward with a ``happy'' emotion. 
\begin{figure}
	\centering
	\includegraphics[width=0.2\textwidth]{./Images/Keepon.jpg}
	\caption{Keepon platform.}
	\label{fig:keepon}
\end{figure} 
 The action is given by a console telling the robot to bend the torso to a desire angle in x. The torso oscillation in y is added automatically by the system following the description given to happiness. 
 %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Triskarino Test}
 The system has been widely used with Triskarino (Fig.~\ref{fig:robot}) during our studies on projecting emotions with a non human like platform. 
\begin{figure}
	\centering
	\begin{subfigure}[c]{0.2\textwidth}
	\includegraphics[width=\textwidth]{./Images/upperFourthD.png}
	\caption{Triskarino design.}
	\label{fig:design}
	\end{subfigure}
	\begin{subfigure}[c]{0.2\textwidth}
	\includegraphics[width=\textwidth]{./Images/platform_fome.jpg}
	\caption{Triskarino with its cover.}
	\label{fig:triskar}
	\end{subfigure}
	\caption{Triskarino platform.}
	\label{fig:robot}
\end{figure}  
 During these studies the system was just used to move the robot in straight line with different emotions, each one selected from our command console. But to show the whole capabilities of the emotional enrichment system and the approach used by us, it was described a little scene that we are preparing. The scene is a modification of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}. The simplified sketch of our version could be seen in the Fig.~\ref{fig:triskar_test}. As it can be seen the stage was divided in 81 squares and the positions were given to the system in term on the desire square, which allow the robot to adjust to the stage's dimension. The whole sequence of actions were specified as unique action, having several sequential context and just move body action. The other actions, such oscillate body or blend upper body were added online accordingly the desired emotion.  
\begin{figure}
	\centering
	%\begin{subfigure}[c]{0.2\textwidth}
	%\includegraphics[width=\textwidth]{./Images/FourthCaseScene.png}
	%\caption{Division of the stage.}  
	%\label{fig:design}
	%\end{subfigure}
	%\begin{subfigure}[c]{0.2\textwidth}
	\includegraphics[width=0.4\textwidth]{./Images/FourthCaseSceneB.png}
	%\caption{Movements.}
	%\label{fig:triskar}
	%\end{subfigure}
	\caption{Sketch of Romeo's movements for the balcony scene in Romeo and Juliet play. The arrows show the direction of the movements, and the numbers their sequence.}
	\label{fig:triskar_test}
\end{figure} 
%The sequence of movements done by the robot could be seen in Fig.~\ref{fig:triskar_movements} and in the video. As it could be seen the robot  and they were selected and executed autonomously by the system.
%\begin{figure*}
%	\centering
%	\includegraphics[width=1.0\textwidth]{Images/Sequence_Triskar.png} 
%	\caption{The actual movements of Triskarino in the Balcony scene.}
%	\label{fig:triskar_movements}
%\end{figure*}

### 2017-02-22 RO-MAN-2017-2/Parts/Introduction.tex
first version

The development of fast, cheap, and reliable electronics has enabled the creation of new devices and versatile robotic platforms. These new platforms' capabilities have expanded the frontiers of the robots applications  to new environments where robot are expected to interact with humans, such as health care, and house cleaning, among others. However, bringing robots in these environment raises the challenge to increase robots' acceptance. Although this could be seen as an easy task that just would need improvements in robots' appearances and capabilities, it is possible that people would expect to treat robots as humans has  as they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfil this expectations.

Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}. As consequence researchers~\cite{Breazeal2002,Arras2012} have added specific emotional poses and expression to their robots. Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}. Nevertheless, these works have created modules to show emotions that are strongly integrated to their solutions, which eliminate the possibility to re-use or adapt their systems into other projects.

In theory, the projection of emotion with humanoid embodiments could be simplified to mimic the same movements that humans. However, this idea is not possible due robots physical limitations. Therefore, an exact matching of humans’ movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}. Therefore diverse researchers are studying diverse features and values to express emotions with different platforms. As a consequence, these results could not be widely used due to the differences of the platforms.

This paper presents an Emotional Enrichment System (EES), which modify actions' parameters and add additional actions to create the illusion of emotion expression in a robot. Although the EES was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extendable to other platforms and adaptable to new tasks. To achieve this goal, the system relies on an Emotional Execution Tree (EXT), which is based on simple actions, sequential and parallel nodes. Additionally, it is used the concept of compound actions to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions  generated by specific combinations of simple actions and other nodes. This EXT has been formalized to give a guideline to further implementations and extensions.

The rest of the paper is organized as follows. Section~\ref{sec:related_work} provides a brief overview of particularly relevant work related to our system. Section~\ref{ref:theatre} gives a brief explanation on TheatreBot architecture. Section~\ref{ref:general_system} gives a general introduction to the system ideas. Section~\ref{sec:emotional_execution_tree} gives the basic formalization of our system and principal components terms used on it. Section~\ref{sec:implementation} describes the implementation of the system and shows two demonstrations done with the system using platforms with different capabilities.

### 2017-02-22 RO-MAN-2017-2/Parts/RelatedWork.tex
first version

The use of emotion enrichment to improve human robot interaction is not new trend. There have been several works that have enhance their social robots with emotions or study how to convey them in robotic platforms~\cite{Li2011,Brown2014}. One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and show emotions. This platform uses a specific set of movements based on the Ekman's studies on human emotion expression~\cite{Ekman2004}. Other approaches have tried to use anthropomorphic~\cite{Arras2012} and human-like platforms to convey emotions to study the response of people towards the robot. However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization was not available.\\
On the other hand, studies focused on entertainment robotics have tried to introduce emotional actions to improve the audience's experience. Breazeal and collaborators~\cite{Breazeal2003} used one robot on the stage. This anemone-like robot had few behaviours, which included getting scared when a person comes too close; the robot was able to show some basic emotions (i.e., fear and interest). Knight~\cite{Knight2011b,Knight2010} used the platform NAO to produce a sort of stand-up comedy. The robot performs basic actions to add some expressiveness to the joke, but it is not intended to project any emotion. Trying to add some theatrical realism, Breazeal and collaborators~\cite{Breazeal2008} designed and implemented a system to control a lamp. The main characteristic of this lamp is that it could be controlled by just one person, which selected pre-coded emotions.\\
Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012,Lemaignan2012}, Fan and collaborators~\cite{Fan2009,Fan2013}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} uses robots in performances with real actors but without any emotion expression.\\
Although these works use emotions, their main focus was the interpretation of postures or just the use of emotions to increase their robot appealing, but none of them considered the importance of emotional system that could be used by others. As a consequence, most of these works have created emotional systems that could just work in their specific system.

### 2017-02-22 RO-MAN-2017-2/Parts/SimpleActions.tex
first version

In order to generate a system that could be used in diverse platforms require an abstraction level in which all of them could fall. Therefore simple and compound actions are used to achieve this goal. Simple actions are actions that are considered as primitives: they are used as building blocks. Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place. Their description specifies mandatory and optional parameters that are required to execute an action. Compound actions are actions that are created from simple actions. These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g. compound actions that are used often).

The simple actions to be implemented to test the system were selected by considering platforms' capabilities and the requirements. The eight actions selected are: move body, oscillate body, move shoulder, oscillate shoulder, move torso, oscillate torso, and do nothing. Description for each action, its mandatory parameters and optional parameters are shown in Table~\ref{table:actions_implemented}.

\begin{table}
\centering
\caption{Description of the seven simple actions implemented, and their respective parameters. Where  P is 2D position, V is 2D velocity vector and angular velocity, and T is time}
\label{table:actions_implemented}
\begin{tabular}{|c|p{3.9cm}|p{1.4cm}|}
\hline
\textbf{Action Name}& \textbf{Description} &\textbf{Parameter(s)} \\
\hline
Do nothing & It waits for a time $t$ before it is terminated. It could be seen as a delay.  & $T$\\
\hline
Move body & It moves the platform from its current position $a$ to a desired position $b$. & $P$, and $V$\\
\hline
Oscillate body & It generates an oscillation in the whole platform by an angle $\theta$. &  $\theta$ and $V$ \\
\hline
Move shoulder & It moves the shoulders to a desired angle $\theta$. It is considered as angular movement. & $\theta$ and $V$ \\
\hline
Oscillate shoulder & It oscillates the shoulders by a given angle $\theta$ & $\theta$ and $V$\\
\hline
Move torso & It moves the torso to a desired angle in $yaw$, $pitch$ and $roll$& $yaw$, $pithc$, $roll$ and $V$\\
\hline
Oscillate torso & It oscillates the shoulders by a given angle $\theta$ & $\theta$ and $V$\\  
\hline
\end{tabular}
\end{table}

%TODO add an example for this, very simple and presenting how to do it

### 2017-02-22 RO-MAN-2017-2/Parts/description.tex
first version

The description files allow the parametrization of the system and its adaptation to different circumstances.  The system has the following parametric data:

\begin{itemize}

	\item \textit{Emotion description} gives information of the parameters that should be changed in all the simple actions to express the desired emotion. Therefore, for each combination emotion-action should be given a description of how the parameters are defined. If there is any action that does not have any specification, the system will not change its parameters. The following is the EBFN generated to modify movement parameters: 
\begin{grammar}
[(colon){$\models$}]
[(semicolon)$|$]
[(comma){}]
[(period){\\}]
[(quote){\begin{bf}}{\end{bf}}]
[(nonterminal){$\langle$}{$\rangle$}]
<emotion description>: "'\{'","'emotion:'",<string> "','","'observation:'",<string> "','",<action>"'(,'",<action>)* "'\}'".
<action>:<string>"':\{'",<description> "','",<actions affected> "'\}'".
<description>:"'description:\{'",<action name>"','",<emotion>"','"\\
<parameter's type>"'\}'".
<action name>:"'emotionProfileAction:'",<string>.
<emotion>:"'emotionProfileEmotion:'",<string>.
<parameter's type>: "'movement\_parameter'".
<actions affected>:"'actions:\{'",<action parameter>,\\("','"<action parameter>)*"'\}'".
<action parameter>: <string>"':\{'",<reference>"','"\\<repetition>"','",<parameters>"'\}'".
<reference>: "'reference:'",<number>.
<repetition>: "'repetition:'","'yes'";"'no'".
<parameters>: "'parameters:['" <parameter description>\\("','",<parameter description>)* "']'".
<parameter description>: <movement parameter description>;<new parameters>.
<movement parameter description>:"'\{time:'",<number>"',space:'"\\<number>"'\}'".
\end{grammar}

	\item \textit{Character's emotions} parameters give the system information about character's ''rhythm'' for each pair action-emotion. In other words, it is going to say how the emotional parameters for the desired action should be modulated. If there is not any information, the system will use the default emotional values for the action. The following is the corresponding EBFN:
\begin{grammar}
[(colon){$\models$}]
[(semicolon)$|$]
[(comma){}]
[(period){\\}]
[(quote){\begin{bf}}{\end{bf}}]
[(nonterminal){$\langle$}{$\rangle$}]
<character emotion profile>:"'\{'" <emotion>"','",<actions>"'\}'".
<emotion>: "'emotion:'",<string>.
<actions>: "'actions:['", <action>("','",<actions descriptor>)* "']'".
<action>: "'\{ action: '", <string> "','","'bias:'", <number> "','"\\" 'amplitude:'", <number> ", 'long:'",<number> "\}". 
\end{grammar}

	\item \textit{Action message} contains all the necessary information for to execute an action. The following is a script's EBNF:
\begin{grammar}
[(colon){$\models$}]
[(semicolon)$|$]
[(comma){}]
[(period){\\}]
[(quote){\begin{bf}}{\end{bf}}]
[(nonterminal){$\langle$}{$\rangle$}]
<action>: <simple action>;<compound action>;<context>.
<simple action>: "'\{'" <action header> "','","'parameters:['" <simple action parameters> "']\}'".
<compound action>: "'\{'" <action header> "','","'parameters:['" <compound action parameters> "']\}'".
<action header>: "'type:'", <action type> "','","'name: '" <string>  "','", <is primary>.
<simple action parameters>: "'\{'"<parameter header> "','" ,<parameter description> "'\}'". 
<compound action parameters>:  <simple action parameters> ("','", <simple action parameters>)* .
<context>:"'\{'" <action type> "','", <emotion sync> "','", <action sync> "','", <is primary> "','"\\" 'information:'", <string> "','"," 'actions: '", <action> "'\}'".
<parameter header>: "'type:'", <parameter type> "','"," 'name:'",<string>.
<parameter description>: <parameter amplitude>;<parameter circle>;<parameter landmark>;\\<parameter point>;<parameter speech>;\\<parameter square>;<parameter time>.
<parameter type>: "'mandatory\_parameter'";"'optional\_parameter'". 
<is primary>: "'yes'";"'no'".
<emotion sync>: "'yes'";"'no'".
<action type>: "'parallel\_context'";"'serial\_context'";"'simple\_action'";\\"'composite\_action'".
\end{grammar}
\end{itemize}

### 2017-02-22 RO-MAN-2017-2/RO-MAN2017-2.tex
first version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
                                   % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{multirow} 
\usepackage{subcaption}
\usepackage{caption}
\usepackage{url}
\usepackage{bnf}
\usepackage{slashbox}
\newcommand{\co}{\cellcolor{gray!40}}
\usepackage[table]{xcolor}
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins

\title{\LARGE \bf
Enriching Robot's Actions with Affective Movements
}

\author{Julian M. Angel-Fernandez$^{1}$ and Andrea Bonarini$^{2}$% <-this % stops a space
\thanks{$^{1}$Julian M. Angel-Fernandez is a Research at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
        {\tt\small julian.angel.fernandez@tuwien.ac.at}}%
\thanks{$^{2}$Andrea Bonarini is a Professor at the Department of Electronics, Information, and Bioengineering, Politecnico di Milano, Milan, Italy,
        {\tt\small andrea.bonarini@polimi.it}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues. Although there have been works that have studied emotion expression in robots, mechanism to generate emotion are highly integrated with the rest of the system. This unable the possibility to use their approaches in different applications. This paper present a system that has been initially created for a theatrical robot to enrich with emotions its actions, but it has been designed to enable the possibility to be adapted to be used in other fields. The emotional enrichment system has been envisioned to be used with a action decision system. A formal description of the system is provided to be used as a formal reference for further extensions and possible modifications. The system has been adapted to two different platforms with different grades of freedom: Keepon and Triskarino. 
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Related Work}
\input{./Parts/RelatedWork}
\section{Basic Concepts}
\label{sec:concepts}
The system is based on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}. \textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound). This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is predominant (i.e., primary or secondary). \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action. This description could also include addition of other simple actions. \textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse treats. Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed. This tree is first created from the action message description and then modified using the emotional parameters and character description.  
\subsection{Simple and Compound Actions}
\input{./Parts/SimpleActions} 
\section{Describing Components}
\input{./Parts/description}
\section{Emotional Tree}
\input{./Parts/EmotionalTree}
\section{Implementation}
\input{./Parts/Implementation}
\section{Conclusions and Further work}
An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential. Simple actions are functions that map a set of parameters to specific movements. Sequential executes in order the sequence of actions associated to this type of node, while parallel executes them all at the same time. To enable synchronization among simple actions, parallel nodes could be one of four different subtypes, and sequential just one of two different subtypes. A formalization of the Emotional Execution Tree and the principal consideration during the implementation of the system have also been provided. To show the system's versatility, it was used with quite different platforms such as a Keepon Pro and Triskarino. Keepon was used to perform simple actions, while Triskarino was used to test complex actions with different parametrizations of emotions.\\
The results obtained show that the system could enrich the robotic actions with emotions, which could be parametrized from configuration files. Additionally, the design of the system makes it possible to  adopt it for different platforms using the same action description.
%\input{./Parts/Conclusions}
\bibliographystyle{IEEEtran}
\bibliography{Bibliography,BibloNew,Biblography}

\addtolength{\textheight}{-12cm}
\end{document}

### 2017-03-08 RO-MAN-2017-2/Parts/EmotionalTree.tex
new changes

@@
 The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type.
-The parallel node could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
-Sequential nodes could just be one of two sub-types: emotion synchronous or asynchronous.
-Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor.
+Sequential nodes execute one branch after the other.
+Once all the branches have been executed, it notifies to its predecessor to continue with the execution of other nodes.
+The parallel node offers two type of synchronization.
+one is at action and the other at emotion.
+This distinction between action and emotion synchronization enables the possibility to change emotion parameter without affecting the action.
+done could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
+ Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor, which will stop their execution.
+
  If a sequence node receives a finish message, it will execute the next branch.
@@
 Any node can belong to one of two levels: principal or  secondary.
-If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.%Why is this needed?
+If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
+This enables the possibility to have actions that are the ones to command over the others.
 Compound actions are implemented combining all type of nodes.

### 2017-03-08 RO-MAN-2017-2/Parts/Introduction.tex
new changes

@@
 However, this idea is not possible due robots physical limitations.
-Therefore, an exact matching of humans’ movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}.
+Therefore, an exact matching of humans' movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}.
 Therefore diverse researchers are studying diverse features and values to express emotions with different platforms.
@@
 This paper presents an Emotional Enrichment System (EES), which modify actions' parameters and add additional actions to create the illusion of emotion expression in a robot.
-Although the EES was originally conceived to be used in an autonomous performance robot~\cite{angel2013} to enrich actions with emotions, its design was devised to make it extendable to other platforms and adaptable to new tasks.
+Although the EES was originally conceived to be used to facilitate the study of emotion projection, its design was devised to make it extendable to other platforms and adaptable to new tasks.
 To achieve this goal, the system relies on an Emotional Execution Tree (EXT), which is based on simple actions, sequential and parallel nodes.

### 2017-03-08 RO-MAN-2017-2/Parts/RelatedWork.tex
new changes

@@
 Other approaches have tried to use anthropomorphic~\cite{Arras2012} and human-like platforms to convey emotions to study the response of people towards the robot.
-However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization was not available.\\
+However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization was not available.
+
 On the other hand, studies focused on entertainment robotics have tried to introduce emotional actions to improve the audience's experience.
@@
 Trying to add some theatrical realism, Breazeal and collaborators~\cite{Breazeal2008} designed and implemented a system to control a lamp.
-The main characteristic of this lamp is that it could be controlled by just one person, which selected pre-coded emotions.\\
+The main characteristic of this lamp is that it could be controlled by just one person, which selected pre-coded emotions.
+
 Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012,Lemaignan2012}, Fan and collaborators~\cite{Fan2009,Fan2013}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} uses robots in performances with real actors but without any emotion expression.\\

### 2017-03-08 RO-MAN-2017-2/Parts/description.tex
new changes

@@
 	\item \textit{Emotion description} gives information of the parameters that should be changed in all the simple actions to express the desired emotion.
-Therefore, for each combination emotion-action should be given a description of how the parameters are defined.
-If there is any action that does not have any specification, the system will not change its parameters.
-The following is the EBFN generated to modify movement parameters:
+Therefore, for each combination emotion-action should be given a description of how the parameters are defined and how they change in time.
+%If there is any action that does not have any specification, the system will not change its parameters. 
+The first version of this parameters is done for movement.
+Therefore, it was considered four descriptors for this type of parameter.
+The first is the reference, which inform the system the velocity used to calculate the parameter.
+This reference is used to let the modulation of the parameters depending on the character.
+The second descriptor is the tuple space and time.
+with this tuple is possible to calculate the velocity in which the movement must be done in order to convey the desire emotion.
+in order to enable the possibility to have different velocities during the execution, it could be described a sequence of this tuple.
+in this case, the space descriptor plays an important role, which is to inform the length in which the desired velocity must be used.
+This bring the last description which is the repetition that is used if there is more than one tuple and it should be repeat during the duration of the movement.
+The EBFN to described these descriptors in the system is the following:
 \begin{grammar}
@@
 	\item \textit{Character's emotions} parameters give the system information about character's ''rhythm'' for each pair action-emotion.
-In other words, it is going to say how the emotional parameters for the desired action should be modulated.
-If there is not any information, the system will use the default emotional values for the action.
-The following is the corresponding EBFN:
-\begin{grammar}
-[(colon){$\models$}]
-[(semicolon)$|$]
-[(comma){}]
-[(period){\\}]
-[(quote){\begin{bf}}{\end{bf}}]
-[(nonterminal){$\langle$}{$\rangle$}]
-<character emotion profile>:"'\{'" <emotion>"','",<actions>"'\}'".
-<emotion>: "'emotion:'",<string>.
-<actions>: "'actions:['", <action>("','",<actions descriptor>)* "']'".
-<action>: "'\{ action: '", <string> "','","'bias:'", <number> "','"\\" 'amplitude:'", <number> ", 'long:'",<number> "\}". 
-\end{grammar}
+To describe this changes, it was decided to used bias, amplitude and long as descriptors.
+Bias refers to a constant value that is added to all the sequence of emotional parameters.
+Amplitude amplify the velocity respect the bias if the number is bigger than one, or attenuate if it is between zero and one.
+%TODO if there is enough space add an imagine explaining these concepts
 
-	\item \textit{Action message} contains all the necessary information for to execute an action. The following is a script's EBNF:
+	\item \textit{Action message} contains all the necessary information for to execute an action. The following is the EBNF of an action:
 \begin{grammar}

### 2017-03-08 RO-MAN-2017-2/RO-MAN2017-2.tex
new changes

@@
 Although there have been works that have studied emotion expression in robots, mechanism to generate emotion are highly integrated with the rest of the system.
-This unable the possibility to use their approaches in different applications.
-This paper present a system that has been initially created for a theatrical robot to enrich with emotions its actions, but it has been designed to enable the possibility to be adapted to be used in other fields.
-The emotional enrichment system has been envisioned to be used with a action decision system.
-A formal description of the system is provided to be used as a formal reference for further extensions and possible modifications.
+This unable the possibility to use their approaches in other applications.
+This paper present a system that has been initially created to facilitate the study of emotion projection, but it was designed to enable its adaptations in other fields.
+The emotional enrichment system has been envisioned to be used with any action decision system.
+A description of the system components and its characteristics are provided.
 The system has been adapted to two different platforms with different grades of freedom: Keepon and Triskarino.
@@
 \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
-This description could also include addition of other simple actions.
+This description could also include addition of other simple actions and vary over time.
 \textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse treats.

### 2017-03-19 RO-MAN-2017-2/RO-MAN2017-2.tex
Update RO-MAN2017-2.tex
Revised English

@@
 \author{Julian M. Angel-Fernandez$^{1}$ and Andrea Bonarini$^{2}$% <-this % stops a space
-\thanks{$^{1}$Julian M. Angel-Fernandez is a Research at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
+\thanks{$^{1}$Julian M. Angel-Fernandez is Researcher at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
         {\tt\small julian.angel.fernandez@tuwien.ac.at}}%
-\thanks{$^{2}$Andrea Bonarini is a Professor at the Department of Electronics, Information, and Bioengineering, Politecnico di Milano, Milan, Italy,
+\thanks{$^{2}$Andrea Bonarini is Full Professor at the Department of Electronics, Information, and Bioengineering, Politecnico di Milano, Milan, Italy,
         {\tt\small andrea.bonarini@polimi.it}}%
@@
 \begin{abstract}
-Emotions are considered by many researches as a characteristic that could be beneficial in social robotics, since they enrich human-robot interaction with non-verbal clues.
+Emotions are considered by many researchers as beneficial elements in social robotics, since they can enrich human-robot interaction with non-verbal clues.
 Although there have been works that have studied emotion expression in robots, mechanism to generate emotion are highly integrated with the rest of the system.
-This unable the possibility to use their approaches in other applications.
-This paper present a system that has been initially created to facilitate the study of emotion projection, but it was designed to enable its adaptations in other fields.
+This limits the possibility to use these approaches in other applications.
+This paper presents a system that has been initially created to facilitate the study of emotion projection, but it has been designed to enable its adaptation in other fields.
 The emotional enrichment system has been envisioned to be used with any action decision system.
-A description of the system components and its characteristics are provided.
-The system has been adapted to two different platforms with different grades of freedom: Keepon and Triskarino.
+A description of the system components and their characteristics are provided.
+The system has been adapted to two different platforms with different degrees of freedom: Keepon and Triskarino.
 \end{abstract}
@@
 Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed.
-This tree is first created from the action message description and then modified using the emotional parameters and character description.
+This tree is created from the action message description and then modified using the emotional parameters and character description.
 \subsection{Simple and Compound Actions}
@@
 Simple actions are functions that map a set of parameters to specific movements.
-Sequential executes in order the sequence of actions associated to this type of node, while parallel executes them all at the same time.
+Sequential nodes execute the sequence of actions associated to this type of node in a sequential order, while parallel executes them all at the same time.
 To enable synchronization among simple actions, parallel nodes could be one of four different subtypes, and sequential just one of two different subtypes.
-A formalization of the Emotional Execution Tree and the principal consideration during the implementation of the system have also been provided.
+A formalization of the Emotional Execution Tree and the principal considerations during the implementation of the system have also been provided.
 To show the system's versatility, it was used with quite different platforms such as a Keepon Pro and Triskarino.
 Keepon was used to perform simple actions, while Triskarino was used to test complex actions with different parametrizations of emotions.\\
-The results obtained show that the system could enrich the robotic actions with emotions, which could be parametrized from configuration files.
+The obtained results show that the system could enrich the robotic actions with emotions, which could be parametrized from configuration files.
 Additionally, the design of the system makes it possible to  adopt it for different platforms using the same action description.

### 2017-03-19 RO-MAN-2017-2/Parts/Introduction.tex
Update Introduction.tex
Fixed English mispellings

@@
 However, bringing robots in these environment raises the challenge to increase robots' acceptance.
-Although this could be seen as an easy task that just would need improvements in robots' appearances and capabilities, it is possible that people would expect to treat robots as humans has  as they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots that fulfil this expectations.
+Although this could be seen as an easy task that just would need improvements in robots' appearances and capabilities, it is possible that people would expect to treat robots as humans as they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil this expectations.
 
 Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
-As consequence researchers~\cite{Breazeal2002,Arras2012} have added specific emotional poses and expression to their robots.
-Others have studied how to convey emotions with specific platforms~\cite{Li2011,Brown2014}.
+To this purpose, some researchers~\cite{Breazeal2002, Arras2012} have added specific emotional poses and expression to their robots.
+Others have studied how to convey emotions with specific platforms~\cite{Li2011, Brown2014}.
 Nevertheless, these works have created modules to show emotions that are strongly integrated to their solutions, which eliminate the possibility to re-use or adapt their systems into other projects.
 
-In theory, the projection of emotion with humanoid embodiments could be simplified to mimic the same movements that humans.
-However, this idea is not possible due robots physical limitations.
-Therefore, an exact matching of humans' movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}.
-Therefore diverse researchers are studying diverse features and values to express emotions with different platforms.
-As a consequence, these results could not be widely used due to the differences of the platforms.
+In theory, the projection of emotion with humanoid embodiments could be simplified by mimicing the human movements.
+However, this idea cannot be fully implemented, due physical limitations in robots.
+Since an exact matching of human movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}, some researchers are studying diverse features and values to express emotions with different platforms.
+As a consequence, these results could not be widely used due to the difference among the platforms.
 
-This paper presents an Emotional Enrichment System (EES), which modify actions' parameters and add additional actions to create the illusion of emotion expression in a robot.
+This paper presents an Emotional Enrichment System (EES) that modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
 Although the EES was originally conceived to be used to facilitate the study of emotion projection, its design was devised to make it extendable to other platforms and adaptable to new tasks.
 To achieve this goal, the system relies on an Emotional Execution Tree (EXT), which is based on simple actions, sequential and parallel nodes.
-Additionally, it is used the concept of compound actions to group a bunch of nodes, which reduces the tree dimension and allows the reuse of recurrent actions  generated by specific combinations of simple actions and other nodes.
+Additionally, the concept of compound actions is used to group a bunch of nodes, thus reducing the tree dimension and allowing the reuse of recurrent actions generated by specific combinations of simple actions and other nodes.
 This EXT has been formalized to give a guideline to further implementations and extensions.

### 2017-03-19 RO-MAN-2017-2/Parts/RelatedWork.tex
Update RelatedWork.tex
Fixed English

@@
-The use of emotion enrichment to improve human robot interaction is not new trend.
-There have been several works that have enhance their social robots with emotions or study how to convey them in robotic platforms~\cite{Li2011,Brown2014}.
-One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and show emotions.
+The use of emotion enrichment to improve human robot interaction is not new.
+There have been several researchers that have enhanced their social robots with emotions or studied how to convey emotions in robotic platforms~\cite{Li2011,Brown2014}.
+One of the first, well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions.
 This platform uses a specific set of movements based on the Ekman's studies on human emotion expression~\cite{Ekman2004}.
 Other approaches have tried to use anthropomorphic~\cite{Arras2012} and human-like platforms to convey emotions to study the response of people towards the robot.
-However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization was not available.
+However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization is not available.
 
@@
 Trying to add some theatrical realism, Breazeal and collaborators~\cite{Breazeal2008} designed and implemented a system to control a lamp.
-The main characteristic of this lamp is that it could be controlled by just one person, which selected pre-coded emotions.
+The main characteristic of this lamp is that it could be controlled by just one person, by selecting pre-coded emotions.
 
-Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012,Lemaignan2012}, Fan and collaborators~\cite{Fan2009,Fan2013}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} uses robots in performances with real actors but without any emotion expression.\\
-Although these works use emotions, their main focus was the interpretation of postures or just the use of emotions to increase their robot appealing, but none of them considered the importance of emotional system that could be used by others.
-As a consequence, most of these works have created emotional systems that could just work in their specific system.
+Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012,Lemaignan2012}, Fan and collaborators~\cite{Fan2009,Fan2013}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression.\\
+Although these works use emotions, their main focus was the interpretation of postures or just the use of emotions to increase their robot appealing, but none of them considered the importance of an emotional system that could be used by others.
+As a consequence, most of these works have created emotional systems that could just work in their specific framework.

### 2017-03-19 RO-MAN-2017-2/Parts/SimpleActions.tex
Update SimpleActions.tex

@@
-In order to generate a system that could be used in diverse platforms require an abstraction level in which all of them could fall.
+In order to generate a system that could be used in diverse platforms, an abstraction level in which all of them could fall is required.
 Therefore simple and compound actions are used to achieve this goal.
@@
 Compound actions are actions that are created from simple actions.
-These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g.
-compound actions that are used often).
+These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g., compound actions that are used often).
 
@@
 
-%TODO add an example for this, very simple and presenting how to do it
+%TODO add an example for this, very simple and presenting how to do it. IT WOULD BE VERY NICE

### 2017-03-20 RO-MAN-2017-2/Parts/description.tex
Fixed some English. Many descr. still unclear

--- 2017-02-22 RO-MAN-2017-2/Parts/description.tex
@@
 \begin{itemize}
-
-	\item \textit{Emotion description} gives information of the parameters that should be changed in all the simple actions to express the desired emotion.
-Therefore, for each combination emotion-action should be given a description of how the parameters are defined.
-If there is any action that does not have any specification, the system will not change its parameters.
-The following is the EBFN generated to modify movement parameters:
+%TODO In the following the term "parameter" is misleading. A parameter should be a number, which doees not seem to be for all teh features you are describing. all teh descriptions are really unclear.
+	\item \textit{Emotion description} gives the values of the parameters that should be changed in all the simple actions to express the desired emotion.
+Therefore, for each emotion-action combination, a description of how the parameters are defined and how they change in time should be provided.
+%If there is any action that does not have any specification, the system will not change its parameters. 
+Four descriptors to describe any emotional movement are provided. %TODO I cannot understand this first descriptor
+The first is the reference, which informs the system about the velocity used to calculate the parameter.
+This reference is used to let the modulation of the parameters depending on the character.
+The second descriptor is the tuple space and time.
+used to compute the velocity of the movement required to convey the desired emotion.
+%TODO I canot understand the following sentences.
+All this paragraph is confused and grammatically incorrect
+in order to enable the possibility to have different velocities during the execution, it could be described a sequence of this tuple.
+In this case, the space descriptor plays the important role of stating the amount of space for which the desired velocity must be used.
+This brings the last description which is the repetition that is used if there is more than one tuple and it should be repeat during the duration of the movement.
+The EBFN to describethese descriptors in the system is the following:
 \begin{grammar}
@@
 	\item \textit{Character's emotions} parameters give the system information about character's ''rhythm'' for each pair action-emotion.
-In other words, it is going to say how the emotional parameters for the desired action should be modulated.
-If there is not any information, the system will use the default emotional values for the action.
-The following is the corresponding EBFN:
-\begin{grammar}
-[(colon){$\models$}]
-[(semicolon)$|$]
-[(comma){}]
-[(period){\\}]
-[(quote){\begin{bf}}{\end{bf}}]
-[(nonterminal){$\langle$}{$\rangle$}]
-<character emotion profile>:"'\{'" <emotion>"','",<actions>"'\}'".
-<emotion>: "'emotion:'",<string>.
-<actions>: "'actions:['", <action>("','",<actions descriptor>)* "']'".
-<action>: "'\{ action: '", <string> "','","'bias:'", <number> "','"\\" 'amplitude:'", <number> ", 'long:'",<number> "\}". 
-\end{grammar}
+To describe these changes, it was decided to use bias, amplitude and length as descriptors.
+Bias refers to a constant value that is added to the sequence of emotional parameters.
+Amplitude amplifies the velocity with respect to the bias if the number is bigger than one, or attenuate if it is between zero and one.
+%TODO if there is enough space add an image explaining these concepts
 
-	\item \textit{Action message} contains all the necessary information for to execute an action. The following is a script's EBNF:
+	\item \textit{Action message} contains all the necessary information for to execute an action. The following is the EBNF of an action:
 \begin{grammar}

### 2017-03-20 RO-MAN-2017-2/Parts/Implementation.tex
Fixed some English. Still many probems

@@
-The system was implemented in \textit{C++} with interface with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description done in previous sections. 
+The system was implemented in \textit{C++} and interfaced with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description presented in previous sections. 
 \begin{figure*}
@@
 	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received.
-The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described on the message.
+The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action included in the message.
 This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
-When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created such as the one presented in the Figure~\ref{fig:reference} that corresponds to the example of walk and speak.
+%TODO????
+When the verification is done, and all the actions exist and the parameters correspond, an $ext$ %TODO WHat is this?
+is created such as the one presented in Figure~\ref{fig:reference}, which corresponds to the example of walk and speak.
 	\begin{figure}
@@
 	\caption{Emotional Execution Tree for the example shown in the Figure~\ref{fig:compound_example}.
-The context node colored in purple represents a sequential context, while the other represents a parallel.}
+The context node colored in purple represents a sequential context, while the other one represents a parallel.} %TODO Up to now no context node was mentioned.
+What is it?
 	\label{fig:reference}
 	\end{figure}
-	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase.
-In this phase new $sa$ are added to the $ext$ and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
+	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase. In this phase new $sa$ %TODO What is an sa??
+are added to the $ext$, and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
 This process is broken down in two steps.
 First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
-Second, the emotional parameters are modulated based on the emotion's intensity and character traits.
+Second, the emotional parameters are modulated basing on the emotion's intensity and character traits.
 	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
-In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.
+In this phase a reference to the mandatory %TODO What is a mandatory action?
+and emotional action is maintained, thus, when a new emotion is to be expressed, the system stops the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
 \end{enumerate}
@@
 This is done to not affect actions' execution when the emotion or its intensity is changed.
-All the text message broadcast among the nodes are written using JSON format, which is human understandable, is light and there are diverse available parser.\\ 
-To test the system was used to different platforms: Keepon Pro and an own made platform called Triskarino.
-Keepon was used to test the interoperability of the system to different platforms, while Triskarino has been used as a part of the robot actor project~\cite{angel2013}.
+All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and there are many available parsers.\\ 
+To test the system two different platforms were used: Keepon Pro %TODO da citare la prima volta il paper descrittivo
+and an own made platform called Triskarino.
+Keepon has been used to test the interoperability of the system to different platforms, while Triskarino has been used as a part of the robot actor project~\cite{angel2013}.
+%TODO ????
 The whole TheatreBot architecture has not finished just, thus the change of emotion and selection of action to execute were done manually.
@@
 In the video\footnote{YouTube video name Emotional Enrichment System, url: https://youtu.be/bRSXQ0rzkO8}
- is shown the test where Keepon has to move its torso forward and backward with a ``happy'' emotion. 
+is shown the test where Keepon had to move its torso forward and backward to express a ``happy'' emotion. 
 \begin{figure}
@@
 \end{figure} 
- The action is given by a console telling the robot to bend the torso to a desire angle in x.
+The action is given by console telling the robot to bend the torso to a desired angle in x.
 The torso oscillation in y is added automatically by the system following the description given to happiness.
@@
 \end{figure}  
- During these studies the system was just used to move the robot in straight line with different emotions, each one selected from our command console.
-But to show the whole capabilities of the emotional enrichment system and the approach used by us, it was described a little scene that we are preparing.
+ During these studies the system was used in different experiments to move the robot on a straight line showing different emotions, each one selected from our command console.
+Moreover, to show the whole capabilities of the emotional enrichment system, a little scene was set up.
 The scene is a modification of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
 The simplified sketch of our version could be seen in the Fig.~\ref{fig:triskar_test}.
-As it can be seen the stage was divided in 81 squares and the positions were given to the system in term on the desire square, which allow the robot to adjust to the stage's dimension.
+As it can be seen the stage was divided in 81 squares and the positions were given to the system in terms of the desire square to be reached, which allows the robot to adjust to the stage's dimension.
+%TODO I cannot understand what follows.
+What is a context?
 The whole sequence of actions were specified as unique action, having several sequential context and just move body action.
-The other actions, such oscillate body or blend upper body were added online accordingly the desired emotion.
+The other actions, such as oscillate body or blend upper body were added online accordingly the desired emotion.
 \begin{figure}

### 2017-03-20 RO-MAN-2017-2/Parts/EmotionalTree.tex
Fixed some Eng. Many pb to solve

@@
 Once all the branches have been executed, it notifies to its predecessor to continue with the execution of other nodes.
-The parallel node offers two type of synchronization.
-one is at action and the other at emotion.
+The parallel node offers two types of synchronization: one is at action and the other at emotion.
 This distinction between action and emotion synchronization enables the possibility to change emotion parameter without affecting the action.
+%TODO ????
 done could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
- Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor, which will stop their execution.
+Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor %TODO ????
+, which will stop their execution.
 
- If a sequence node receives a finish message, it will execute the next branch.
-When all branches have been executed, it communicates the end of the action.
-On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression.
+If a sequence node receives a finish message, it will execute the next branch. When all branches have been executed, it communicates the end of the action.
+
+Emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression.
 If a node is principal and it has finished to execute all actions, it will notify its predecessor.
+%TODO Not clear at all
+ This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions.
 
-This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions.
 Finally, leaf nodes could only be simple action nodes that have been implemented in the system.
@@
 If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
-This enables the possibility to have actions that are the ones to command over the others.
+This enables the possibility to have actions that have priority on others.
 Compound actions are implemented combining all type of nodes.

### 2017-03-23 RO-MAN-2017-1/RO-MAN2017.tex
Updated Absract

@@
 Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice.
-However, there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks that require a specific structure.
+However, there are cases where robots cannot have any anthropomorphic shape, for example when they have to perform tasks that require a specific structure.
 This is the case of home cleaners, package carriers, and many others platforms.
@@
 This case study was designed basing on results obtained from a previous experiment, done to assess precise values for linear velocity, angular velocity, oscillation angle, direction, and orientation that could be used to express happiness, anger, fear, and sadness.
-Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions.
-Additionally, a small scene was played to verify whether people prefer actions with or without emotion expression.
+Results of this case study show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions.
+Additionally, a simple scene was played to verify whether people prefer actions including emotional expression.
 \end{abstract}

### 2017-03-23 RO-MAN-2017-1/Parts/Introduction.tex
Update Introduction.tex

@@
-Emotions and mental states are not just expressed through facial expression and voice but also by body postures and other features~\cite{Gelder2008}.
+Emotions and mental states are not just expressed through facial expression and voice, but also by body postures and other features~\cite{Gelder2008}.
 Many psychological studies have focused their attention on how emotions are conveyed through the face~\cite{Ekman2004},~\cite{kleinsmith2012affective}.
@@
 ) to convey emotions.
-In many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
+In many situations, the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
 Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
@@
 Rather, they established a relationship between their values and pleasure/arousal dimensions.
-This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristic to avoid misinterpretation with wrong emotions.
+This could help to select specific features to convey certain emotions, but it would be better to know the precise range of values to be assigned to each characteristic to avoid misinterpretation with wrong emotions.
 These values could be used in social robotics to show emotions and, as consequence, increase their acceptance.

### 2017-03-23 RO-MAN-2017-1/Parts/RelatedWork.tex
Update RelatedWork.tex

@@
 Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants.
-Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions.
+A similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions.
 In the same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-The use of real platforms to study emotion projection follows two paths: use of anthropomorphic and non-anthropomorphic platforms.
+The use of real platforms to study emotion projection follows two paths, using both anthropomorphic and non-anthropomorphic platforms.
+
 The first path is characterized by the use of cue positions to project emotions~\cite{NAO2013}.
 In some cases, special attention has been taken to determine head's angle and arms' position contribution to specific emotion expressions~\cite{Brown2014}.
-Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements.
+Nevertheless, current humanoid platforms cannot generate smooth gaits, and this limits the quality of body movements.
 To overcome this limitation, some researchers have reduced the human resemblance (e.g., eliminating limbs and facial expressions) to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
@@
 Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the work done by Camurri et al.~\cite{pop00002}.
-Continuing with her research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
+Continuing with their research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
 The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love).
 Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
-Despite the type of platform used, these works offers an overview of features that could be used to express certain emotions but they not give precise values to implement the emotions.
+Despite the type of platform used, these works offers an overview of features that could be used to express certain emotions, but they not give precise feature values to implement the emotions.
 
@@
 While flat orientation is related to positive valence, leaning positions are related with negative valence.
-Finally, the velocity is correlated with valence, arousal and dominance.
+Finally, velocity is correlated with valence, arousal and dominance.
 
@@
 This could lead to implementations that express an undesired emotion~\cite{Angel2016}.
-For example people could confuse an implementation of \textit{Happiness} with \textit{Anger}.
+For example, people could confuse an implementation of \textit{Happiness} with \textit{Anger}.

### 2017-03-23 RO-MAN-2017-1/Parts/System.tex
Update System.tex

@@
 A non-anthropomorphic robotic platform was created to limit the influence of shape on the participants' perception.
-The robotic platform is holonomic and it included Odroid U3 and Arduino Due, 3 metal gear motors with 64 CPR encoders, and omniwheels.
-Arduino Due is in charge to interface motors and Odroid U3, which hosts the Emotion Enrichment System described here below.
+The robotic platform is holonomic and it included Odroid U3 and Arduino Due as processors, 3 metal gear motors with 64 CPR encoders, and omniwheels.
+Arduino Due is in charge to interface motors, and Odroid U3 hosts the Emotion Enrichment System described here below.
 The platform is shown in Figure~\ref{fig:Robot}.
@@
 An Emotional Enrichment System was designed and implemented to automatize the process of emotion expression~\cite{Angel2017}.
-It modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
+It is intended to provide an emotional expression to an action decided a priori, e.g., by the planner.
+It modifies actions' parameters and adds actions to create the illusion of emotion expression in a robot.
 To achieve this, the system receives two messages.

### 2017-03-23 RO-MAN-2017-1/Parts/CaseStudy.tex
Update CaseStudy.tex

@@
 \begin{enumerate}
-	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}.
-This experiment was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
-A total of 196 value combinations were designed, 20 of which were presented to each participant.
-Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}).
-	\item Verify whether participants would prefer scenes when the robot moves expressing emotions or rather moves on the same trajectory without any emotion expression.
+	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}, which was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to express: \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
+A total of 196 value combinations were designed, 20 of which, randomly selected, were presented to each participant.
+Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}), added as confounding terms.
+	\item Verify whether participants would prefer scenes where the robot moves expressing emotions, or rather moves on the same trajectory without any emotion expression.
 To control scene variability two cameras and eight AR tags were used together with a Kalman filter to improve robot localization on the stage.
 AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}.
-The distribution of thecameras and the tags is reported in Figure~\ref{fig:setup_fourth}.
+The distribution of the cameras and the tags is reported in Figure~\ref{fig:setup_fourth}.
 
@@
 
-Stage discretization was used to give zones of movements instead of absolute positions.
+Stage discretization was used to give zones of movement instead of absolute positions.
 This idea was brought from human theatrical actors, who arrange their movements based on zones on the stage~\cite{wilson2009theatre}.
@@
 The robot's final position is calculated by the Emotional Enrichment System during execution.
-For instance, the scene was designed on a 3 x 3 meters stage, but in the presentation at the exhibition the stage was 2.5 x 2.5 meters.
+In this setting, the scene was designed on a 3 x 3 meters stage, but in the presentation at the exhibition the stage was 2.5 x 2.5 meters.
 
@@
 	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseScene.png} 
-	\caption{Stage discretization  used for the scene. The blue squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
+	\caption{Stage discretization  used for the scene. The dark squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
 	\label{fig:stage_division}
@@
 This case study was done at an exhibition during a period of two days.
-People coming to the stand were asked to participate in this study, which was divided in to parts.
+People coming to the stand were asked to volunteerto participate in this study, which was divided in to parts.
 In the first one, each subject was exposed to two emotion expressions.

### 2017-03-23 RO-MAN-2017-1/Parts/Results.tex
Update Results.tex

@@
 It could be observed that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}.
-In a similar way, \textit{Anger-1} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
+In a similar way, \textit{Anger-1} was mostly confused with \textit{Excitement}, which was voted twenty one times by forty nine subjects exposed to it.
 \textit{Anger-2} shows an improvement of perception from 10\% to 38\% with respect to Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
@@
 An analysis was done per groups, for each presented emotion.
-For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many of those identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
-This lead to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
+For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
+This leads to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
 \begin{table}[!htbp]
@@
 
-Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypothesis used in the test were:
+Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypotheses used in the test were:
 
@@
 As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level.
-In this precise case the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}.
+In this precise case, the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}.
 Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
@@
 	\item Do people prefer scenes with or without emotions?
-	\item Has gender an impact in the preference?
+	\item Has gender an impact on the preference?
 \end{enumerate}
-To answer these questions the following hypotheses were created:
+To answer these questions the following hypotheses were considered:
 \begin{enumerate}

### 2017-03-23 RO-MAN-2017-1/Parts/Conclusions.tex
Update Conclusions.tex

@@
-The case study presented in this paper was done to cross validate the findings in a previous experiment~\cite{}, and to verify whether the subjects would prefer scenes when the robot expresses emotions rather than the same trajectories without any emotion expression.
-For each one of four emotions (i.e., \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) studied in the experiment two set of parameters were selected to express them.
+The case study presented in this paper was done to cross validate the findings in a previous experiment~\cite{Angel2017-2}, and to verify whether the subjects would prefer scenes when the robot expresses emotions rather than the same trajectories without any emotion expression.
+For each one of four emotions (i.e., \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) studied in the experiment two sets of parameters were selected to express them.
 The results show that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}, while one implementation of \textit{Anger} was confused with \textit{Excitement}.
@@
 Both implementations of \textit{Fear} had a recognition rate over 50\%.
-This, together with the last statement may suggest that people have different models of \textit{Fear} and that thsi single label is not enough to distinguish among them.
+This, together with the last statement may suggest that people have different models of \textit{Fear} and that this single label is not enough to distinguish among them.
 
@@
 For instance, \textit{Happiness} and \textit{Anger} were considered as \textit{Excitement}.
-This misinterpretation is not a surprise, given the fact that there is not a unique definition of emotion~\cite{Plutchik2001,cacioppo2000handbook}, and each person would interpret a situation differently, so they will give a different label to the presented movement.
+This misinterpretation is not surprising, given the fact that there is not a unique definition of emotion~\cite{Plutchik2001,cacioppo2000handbook}, and each person would interpret a situation differently, so they will give a different label to the presented movement.
 Moreover, a misinterpretation of \textit{Happiness} and \textit{Anger} could suggest that additional features (e.g., trajectory or shape) should be added to increase differentiation between them.
-For example, Venture and collaborators~\cite{Venture2014} had found out that in human bodies the recognition rate of \textit{Anger} and \textit{Fear} are increased when torso and head are downwards.
+For example, Venture and collaborators~\cite{Venture2014} had reported that in human bodies the recognition rate of \textit{Anger} and \textit{Fear} are increased when torso and head are downwards.
 On the other hand, they found that \textit{Happiness} perception is increased when the torso and head are moved upwards.
-This example could bring some insight to possible body changes that could occur in non-human like bodies, but this should still to be tested in this kind of platforms.
+These results could bring some insight to possible body changes that could occur in non-human like bodies, but it should still be tested in this kind of platforms.

### 2017-03-24 RO-MAN-2017-2/Parts/EmotionalTree.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

--- 2017-03-08 RO-MAN-2017-2/Parts/EmotionalTree.tex
@@
 Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges.
-The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type.
+The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type, which represent the type of actions that would be executed by the system.
 Sequential nodes execute one branch after the other.
-Once all the branches have been executed, it notifies to its predecessor to continue with the execution of other nodes.
-The parallel node offers two type of synchronization.
-one is at action and the other at emotion.
-This distinction between action and emotion synchronization enables the possibility to change emotion parameter without affecting the action.
-done could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
- Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor, which will stop their execution.
+Once all the branches have been executed, it notifies its predecessor to continue with the execution of other branches.
+The parallel node executes all the branches at the same time.
+This type of node offers two levels of synchronization: action and emotion.
+The action level synchronization enables the possibility to stop all the branches once the main branch has completed its execution.
+This main branch is established in the action message.
+On the other hand, the emotion level synchronization update to a new emotional parameter of all the branches once the main branch updates to a  new emotional parameter.
+In both cases, any update or finish message will be ignored if the branch is not principal.
+These two levels of synchronization creates four sub-types of parallel nodes: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
 
- If a sequence node receives a finish message, it will execute the next branch.
-When all branches have been executed, it communicates the end of the action.
-On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression.
-If a node is principal and it has finished to execute all actions, it will notify its predecessor.
-
-This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions.
-Finally, leaf nodes could only be simple action nodes that have been implemented in the system.
+Finally, leaf nodes are only simple action nodes that have been implemented in the system.
 Any node can belong to one of two levels: principal or secondary.
 If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor.
-This enables the possibility to have actions that are the ones to command over the others.
-Compound actions are implemented combining all type of nodes.
+This enables the possibility to have actions that have priority over others.
+To exemplify this, lets continue with the sequence of actions depicted in Figure~\ref{fig:sequence_actions}.
+The Emotional Execution Tree for that sequence of actions would be like the one presented in Figure~\ref{fig:emotional_enrichment}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{./Images/Representation.png}
+	\caption{Emotional Execution Tree for the sequence of actions depicted in Figure~\ref{fig:sequence_actions}. The $*$ symbolize that node is principal. S. represents sequential.}
+	\label{fig:emotional_enrichment}
+\end{figure}
+
+\subsection{Formalization of Simple and Compound Actions}
+Formalizing simple and compound actions generates a common system to design them and verify if they are described correctly.
+Simple actions ($SA$) could be seen as functions that map a set of parameters $p^{pl}_{i} \in P$ to specific platform ($pl$) movements ($m^{pl}_{j}\in M^{pl}$) in the set of movements for that platform ($m^{pl}_{j} =sa^{pl}(\lbrace p^{pl}_{i} \rbrace)$).
+Each $sa^{pl}$ could have different implementations due to different reasons such as: platform's type, action's goal, how the mapping from inputs to outputs are done, among others.
+In our case, we consider that two actions are different if $(\forall sa_{i}, sa_{j} \in SA, \forall q, t \in PL | Param( sa_{i}^q ) \neq Param( sa_{j}^t )\Rightarrow sa_{i}^q \neq sa_{j}^t)$, 
+where $PL$ is the set of all the possible platforms, $Param(\cdot)$ returns the set of parameters that are input of the $sa$ (e.g., $vel$,$pitch$,$text$). 
+On the other hand, we will consider two actions as equivalents if $(\forall sa_{i}, sa_{j} \in SA , \forall q, t \in PL | Param( sa_{i}^q ) = Param(sa_{j}^t ) \wedge Obj(sa_{i}^q) = Obj(sa_{j}^t) \Rightarrow sa_{i}^q \equiv sa_{j}^t)$,
+where $Obj(\cdot)$ returns the set of objectives that are intended to be achieved by a given action.
+This $SA$ equivalence allows us to avoid the specification of all the platforms for all the actions that share the same objective and hide leaf nodes that do not give relevant information to understand the emotional tree.
+
+With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$ but with the parameters modified in order to convey the desire emotion $e$, or even a set of $sa$ with their parameters modified.
+This definition goes along with the idea that new $sa$ could be added to convey a specific emotion.
+In addition, the $Enrichment(\cdot)$ function has the following properties:
+\begin{itemize}
+	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $sa_{i} \equiv sa_{j} \Rightarrow Enrichment(sa_{i},e,...) \equiv Enrichment(sa_{j},e,...))$
+	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $(sa_{i} \not\equiv sa_{j}) \Rightarrow Enrichment(sa_{i},e,...) \not \equiv Enrichment(sa_{j},e,...))$
+\end{itemize}
+
+The concept of compound action ($CA$) is defined as $g = ca(\{p_{i}\})$, where $(p_{i} \in Param(sa))$, $(sa \subseteq SA)$, $(g \in EXT)$.

### 2017-03-24 RO-MAN-2017-2/Parts/Implementation.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

@@
+%TODO in this section is missing a review on the terms and explain some concepts that are depicted in the figures.
+
 The system was implemented in \textit{C++} and interfaced with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description presented in previous sections. 
@@
 %TODO????
-When the verification is done, and all the actions exist and the parameters correspond, an $ext$ %TODO WHat is this?
-is created such as the one presented in Figure~\ref{fig:reference}, which corresponds to the example of walk and speak.
+When the verification is done, and all the actions exist and the parameters correspond, an Emotional Execution Tree (EXT)
+is created such as the one presented in Figure~\ref{fig:emotional_enrichment}
+	\item \textit{Emotion addition:} uses the EXT created in the previous phase. In this phase new simple actions ($sa$)
+are added to the EXT, and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
+This process is broken down in two steps.
+First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
+Second, the emotional parameters are modulated basing on the emotion's intensity and character traits.
+The final EXT is presented in Figure~\ref{fig:reference}.
 	\begin{figure}
@@
 		%Representation
-	\includegraphics[width=0.45\textwidth]{./Images/Representation.png}
-	\caption{Emotional Execution Tree for the example shown in the Figure~\ref{fig:compound_example}.
-The context node colored in purple represents a sequential context, while the other one represents a parallel.} %TODO Up to now no context node was mentioned.
-What is it?
+	\includegraphics[width=0.45\textwidth]{./Images/exampleTreeE.png}
+	\caption{Enrich Emotional Execution Tree.} 
 	\label{fig:reference}
 	\end{figure}
-	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase. In this phase new $sa$ %TODO What is an sa??
-are added to the $ext$, and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
-This process is broken down in two steps.
-First, all the actions that are required to convey the desired emotion, and that are not yet present are added.
-Second, the emotional parameters are modulated basing on the emotion's intensity and character traits.
 	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
-In this phase a reference to the mandatory %TODO What is a mandatory action?
-and emotional action is maintained, thus, when a new emotion is to be expressed, the system stops the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
+In this phase a reference to the principal and emotional action is maintained, thus, when a new emotion is to be expressed, the system stops the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
 \end{enumerate}
-%The first one is in charge to receive any action and built a $EXT$.
-Once this tree is created, the second part is in charge to decorate this tree with the additional actions and modify the parameters of all the actions.
-The last part is the one that executes the final tree and communicate to all the simple actions ROS nodes the parameters that should be executed by them.
-It is important to notice that the action's parameters and the emotional parameters are communicated via two different channels.
-This is done to not affect actions' execution when the emotion or its intensity is changed.
+
 All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and there are many available parsers.\\ 
@@
 and an own made platform called Triskarino.
-Keepon has been used to test the interoperability of the system to different platforms, while Triskarino has been used as a part of the robot actor project~\cite{angel2013}.
-%TODO ????
-The whole TheatreBot architecture has not finished just, thus the change of emotion and selection of action to execute were done manually.
+Keepon has been used to test the interoperability of the system to different platforms, while Triskarino has been used in diverse case studies to explore emotion projection with a non anthropomorphic platform.
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The other actions, such as oscillate body or blend upper body were added online accordingly the desired emotion.
-\begin{figure}
-	\centering
-	%\begin{subfigure}[c]{0.2\textwidth}
-	%\includegraphics[width=\textwidth]{./Images/FourthCaseScene.png}
-	%\caption{Division of the stage.}  
-	%\label{fig:design}
-	%\end{subfigure}
-	%\begin{subfigure}[c]{0.2\textwidth}
-	\includegraphics[width=0.4\textwidth]{./Images/FourthCaseSceneB.png}
-	%\caption{Movements.}
-	%\label{fig:triskar}
-	%\end{subfigure}
-	\caption{Sketch of Romeo's movements for the balcony scene in Romeo and Juliet play. The arrows show the direction of the movements, and the numbers their sequence.}
-	\label{fig:triskar_test}
-\end{figure} 
-%The sequence of movements done by the robot could be seen in Fig.~\ref{fig:triskar_movements} and in the video.
-As it could be seen the robot  and they were selected and executed autonomously by the system.
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1.0\textwidth]{Images/Sequence_Triskar.png} 
-%	\caption{The actual movements of Triskarino in the Balcony scene.}
-%	\label{fig:triskar_movements}
-%\end{figure*}

### 2017-03-24 RO-MAN-2017-2/Parts/Introduction.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

@@
 The rest of the paper is organized as follows.
-Section~\ref{sec:related_work} provides a brief overview of particularly relevant work related to our system.
-Section~\ref{ref:theatre} gives a brief explanation on TheatreBot architecture.
-Section~\ref{ref:general_system} gives a general introduction to the system ideas.
+Section~\ref{sec:related_work} provides a brief overview of relevant work.
+Section~\ref{sec:concepts} introduces all the concepts that are used in the system.
 Section~\ref{sec:emotional_execution_tree} gives the basic formalization of our system and principal components terms used on it.
+Section~\ref{sec:description} presents the EBFN created to specify the files used by the system.
 Section~\ref{sec:implementation} describes the implementation of the system and shows two demonstrations done with the system using platforms with different capabilities.

### 2017-03-24 RO-MAN-2017-2/Parts/RelatedWork.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

@@
 This anemone-like robot had few behaviours, which included getting scared when a person comes too close; the robot was able to show some basic emotions (i.e., fear and interest).
-Knight~\cite{Knight2011b,Knight2010} used the platform NAO to produce a sort of stand-up comedy.
+Knight~\cite{Knight2011b} used the platform NAO to produce a sort of stand-up comedy.
 The robot performs basic actions to add some expressiveness to the joke, but it is not intended to project any emotion.
@@
 
-Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012,Lemaignan2012}, Fan and collaborators~\cite{Fan2009,Fan2013}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression.\\
-Although these works use emotions, their main focus was the interpretation of postures or just the use of emotions to increase their robot appealing, but none of them considered the importance of an emotional system that could be used by others.
-As a consequence, most of these works have created emotional systems that could just work in their specific framework.
+Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012}, Fan and collaborators~\cite{Fan2009}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression.
+Although these works have expressed emotions in their studies, they were not focus on create a framework that could be used by others researchers in HRI.
+Therefore, the use of affective architectures for virtual agents (e.g.
+SAIBA/BML framework~\cite{Kopp2006}) could be though as a feasible solution.
+However these framework describe high level actions without given relevant details to its implementation in physical platform.
+This gap cannot be closed by making a direct map the abstract actions and the physical platforms.
+This is due the fact that virtual agents do not have physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007,Canamero2010}.

### 2017-03-24 RO-MAN-2017-2/Parts/SimpleActions.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

@@
 Simple actions are actions that are considered as primitives: they are used as building blocks.
-Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place.
+As a consequence, these actions are described in the system and are the ones in which the parameters are changed to embed the emotions.
 Their description specifies mandatory and optional parameters that are required to execute an action.
-Compound actions are actions that are created from simple actions.
+These parameters are modified accordingly to the information provided in the emotional parameters.
+Compound actions are actions that are created from simple actions and other compound actions.
 These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g., compound actions that are used often).
 
-The simple actions to be implemented to test the system were selected by considering platforms' capabilities and the requirements.
-The eight actions selected are: move body, oscillate body, move shoulder, oscillate shoulder, move torso, oscillate torso, and do nothing.
-Description for each action, its mandatory parameters and optional parameters are shown in Table~\ref{table:actions_implemented}.
+A set of simple actions to be implemented were selected to test the system.
+These actions were selected considering the capabilities of Keepon and Triskarino.
+The eight actions selected were: move body, oscillate body, move shoulder, oscillate shoulder, move torso, oscillate torso, and do nothing.
+Description for each action, its mandatory parameters and optional parameters are presented in Table~\ref{table:actions_implemented}.
 
@@
 
-%TODO add an example for this, very simple and presenting how to do it. IT WOULD BE VERY NICE
+To exemplify the use of these actions, lets consider a sequence of movements illustrated in Figure~\ref{fig:triskar_test}.
+This sequence of movements correspond to an adaptation of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
+The fist part of this scene is characterized by strong changes in Romeo's emotional state, which is the perfect test for the system.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseSceneB.png}
+	\caption{Sketch of Romeo's movements for the balcony scene in Romeo and Juliet play. The arrows show the direction of the movements, and the numbers their sequence.}
+	\label{fig:triskar_test}
+\end{figure} 
+However, just body movements would not exploit the other movements of the platform neither test the whole system.
+Thus, additional movements are added to illustrate and test the system.
+A partial view of the whole sequence of actions is illustrated in Figure~\ref{fig:sequence_actions}.
+The first node correspond to the first action in Figure~\ref{fig:triskar_test}.
+The second actions corresponds to a compound action created by the parallel execution of the simple action move body and other compound action.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{./Images/sequenceActions.png}
+	\caption{Sequence of simple actions for the movements depicted in Figure~\ref{fig:triskar_test}.}
+	\label{fig:sequence_actions}
+\end{figure}

### 2017-03-24 RO-MAN-2017-2/Parts/description.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

--- 2017-02-22 RO-MAN-2017-2/Parts/description.tex
@@
-The description files allow the parametrization of the system and its adaptation to different circumstances.  The system has the following parametric data:
+The description files allow the parametrization and extent the system to fit other applications is required.
+To standarized the mechanisms to describe these files, it was decided to create a language to describe them.
+This allows other researchers to create their own files and extended the language to fit their needs.
+It was decided to use EBNF to describe language.
+\subsection{Emotion Description} 
+The language created to describe emotion descriptors is the following:
+\begin{small}
 
-\begin{itemize}
+\begingrammar
+%		
+<emotion description>: "'\{'" "'emotion:'" <string>"','" "'observation:'" <string>"','" <action> ("','"<action>)* "'\}'".
 
-	\item \textit{Emotion description} gives information of the parameters that should be changed in all the simple actions to express the desired emotion.
-Therefore, for each combination emotion-action should be given a description of how the parameters are defined.
-If there is any action that does not have any specification, the system will not change its parameters.
-The following is the EBFN generated to modify movement parameters:
-\begin{grammar}
-[(colon){$\models$}]
-[(semicolon)$|$]
-[(comma){}]
-[(period){\\}]
-[(quote){\begin{bf}}{\end{bf}}]
-[(nonterminal){$\langle$}{$\rangle$}]
-<emotion description>: "'\{'","'emotion:'",<string> "','","'observation:'",<string> "','",<action>"'(,'",<action>)* "'\}'".
-<action>:<string>"':\{'",<description> "','",<actions affected> "'\}'".
-<description>:"'description:\{'",<action name>"','",<emotion>"','"\\
-<parameter's type>"'\}'".
-<action name>:"'emotionProfileAction:'",<string>.
-<emotion>:"'emotionProfileEmotion:'",<string>.
+<action>:<string>"': \{'" <description>"','" <actions affected> "'\}'".
+
+<description>: "'description: \{'" <action name>"','";<emotion>"','" <parameter's type> "'\}'".
+
+<action name>: "'emotionProfileAction:'" <string>.
+
+<emotion>: "'emotionProfileEmotion:'" <string>.
+
 <parameter's type>: "'movement\_parameter'".
-<actions affected>:"'actions:\{'",<action parameter>,\\("','"<action parameter>)*"'\}'".
-<action parameter>: <string>"':\{'",<reference>"','"\\<repetition>"','",<parameters>"'\}'".
-<reference>: "'reference:'",<number>.
-<repetition>: "'repetition:'","'yes'";"'no'".
-<parameters>: "'parameters:['" <parameter description>\\("','",<parameter description>)* "']'".
-<parameter description>: <movement parameter description>;<new parameters>.
-<movement parameter description>:"'\{time:'",<number>"',space:'"\\<number>"'\}'".
-\end{grammar}
 
-	\item \textit{Character's emotions} parameters give the system information about character's ''rhythm'' for each pair action-emotion.
-In other words, it is going to say how the emotional parameters for the desired action should be modulated.
-If there is not any information, the system will use the default emotional values for the action.
-The following is the corresponding EBFN:
-\begin{grammar}
-[(colon){$\models$}]
-[(semicolon)$|$]
-[(comma){}]
-[(period){\\}]
-[(quote){\begin{bf}}{\end{bf}}]
-[(nonterminal){$\langle$}{$\rangle$}]
-<character emotion profile>:"'\{'" <emotion>"','",<actions>"'\}'".
-<emotion>: "'emotion:'",<string>.
-<actions>: "'actions:['", <action>("','",<actions descriptor>)* "']'".
-<action>: "'\{ action: '", <string> "','","'bias:'", <number> "','"\\" 'amplitude:'", <number> ", 'long:'",<number> "\}". 
-\end{grammar}
+<actions affected>: "'actions: \{'" <action parameter> ; ("','" <action parameter>)* "'\}'".
 
-	\item \textit{Action message} contains all the necessary information for to execute an action. The following is a script's EBNF:
-\begin{grammar}
-[(colon){$\models$}]
-[(semicolon)$|$]
-[(comma){}]
-[(period){\\}]
-[(quote){\begin{bf}}{\end{bf}}]
-[(nonterminal){$\langle$}{$\rangle$}]
-<action>: <simple action>;<compound action>;<context>.
-<simple action>: "'\{'" <action header> "','","'parameters:['" <simple action parameters> "']\}'".
-<compound action>: "'\{'" <action header> "','","'parameters:['" <compound action parameters> "']\}'".
-<action header>: "'type:'", <action type> "','","'name: '" <string>  "','", <is primary>.
-<simple action parameters>: "'\{'"<parameter header> "','" ,<parameter description> "'\}'". 
-<compound action parameters>:  <simple action parameters> ("','", <simple action parameters>)* .
-<context>:"'\{'" <action type> "','", <emotion sync> "','", <action sync> "','", <is primary> "','"\\" 'information:'", <string> "','"," 'actions: '", <action> "'\}'".
-<parameter header>: "'type:'", <parameter type> "','"," 'name:'",<string>.
-<parameter description>: <parameter amplitude>;<parameter circle>;<parameter landmark>;\\<parameter point>;<parameter speech>;\\<parameter square>;<parameter time>.
-<parameter type>: "'mandatory\_parameter'";"'optional\_parameter'". 
-<is primary>: "'yes'";"'no'".
-<emotion sync>: "'yes'";"'no'".
-<action type>: "'parallel\_context'";"'serial\_context'";"'simple\_action'";\\"'composite\_action'".
-\end{grammar}
-\end{itemize}
+<action parameter>: <string>"':\{'" <reference>"','" <repetition>"','" <parameters> "'\}'".
+
+<reference>: "'reference:'" <number>.
+
+<repetition>: "'repetition:'" "'yes'" | "'no'".
+
+<parameters>: "'parameters: ['" <parameter description> ("','" <parameter description>)* "']'".
+
+<parameter description>: <movement parameter description>.
+
+<movement parameter description>: "'\{time:'" <number> "', space:'" <number> "'\}'".
+
+\endgrammar
+\end{small}
+%TODO give information regardin 1) why repetition 2) why a set of parameters 3) why use of time and space
+
+\subsection{Action Message}
+The language created to describe action Messages is the following:
+\begin{small}
+\begingrammar
+%		
+<action>: <simple action> <compound action> <context>.
+
+<simple action>: "'\{'" <action header>"','" "'parameters: ['" <simple action parameters> "'] \}'".
+
+<compound action>: "'\{'" <action header>"','" "'parameters:['" <compound action parameters> "']\}'".
+
+<action header>: "'type:'" <action type>"','" "'name: '" <string>"','" <is primary>.
+
+<simple action parameters>: "'\{'" <parameter header>"','" <parameter description> "'\}'".
+
+<compound action parameters>:  <simple action parameters> ("','" <simple action parameters>)* .
+
+<context>: "'\{'" <action type>"','" <emotion sync>"','" <action sync>"','" <is primary>"','" " 'information:'" <string>"','" " 'actions: '" <action> "'\}'".
+
+<parameter header>: "'type:'" <parameter type>"','" " 'name:'" <string>.
+
+<parameter description>: <parameter amplitude> |; <parameter circle> | <parameter landmark> | <parameter point> | <parameter speech> | <parameter square> | <parameter time>.
+
+<parameter type>: "'mandatory\_parameter'" | ;"'optional\_parameter'".
+
+<is primary>: "'yes'" | "'no'".
+
+<emotion sync>: "'yes'" | "'no'".
+
+<action type>: "'parallel\_node'" | "'sequential\_node'" | ;"'simple\_action'" | "'composite\_action'".
+
+\endgrammar
+\end{small}
+
+%TODO give information regarding: primary and emotion synch

### 2017-03-24 RO-MAN-2017-2/RO-MAN2017-2.tex
Changes in some of the files. Improvements in explanations that were missing before. Improvement of the EBFN description. Shift of the section description after the introduction of the emotional execution three to improve the readability of the description section. I still need to correct and extend some explanations in the article.

@@
 \newcommand{\co}{\cellcolor{gray!40}}
+\input bnf.tex
 \usepackage[table]{xcolor}
+
+ \usepackage{amsmath}
+ \usepackage{amssymb}
 %\usepackage{mathptmx} % assumes new font selection scheme installed
@@
 \section{Related Work}
+\label{sec:related_work}
 \input{./Parts/RelatedWork}
@@
 \label{sec:concepts}
-The system is based on six main concepts: \textit{simple actions}, \textit{compound actions}, \textit{action message}, \textit{emotional descriptors}, \textit{character description} and \textit{emotional execution tree}.
-\textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
+The system is based on six main concepts that structures and enables the enrichment of actions with emotions.
+(i) \textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
 This message also specifies how the actions are executed (i.e., in parallel or in sequence) and which action is predominant (i.e., primary or secondary).
-\textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
+(ii) \textit{Emotional parameters} describe how the emotional enrichment should be done to convey a specific emotion in a specific simple action.
 This description could also include addition of other simple actions and vary over time.
-\textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse treats.
-Finally, \textit{Emotional Execution Tree} is a computational representation of desired actions that should be executed.
+(iii) \textit{Character description} enables the possibility to establish how to modify emotional expressions to generate diverse "rhythms".
+(iv) \textit{Emotional Execution Tree} (EXT) is a computational representation of desired actions that should be executed.
 This tree is created from the action message description and then modified using the emotional parameters and character description.
+The remaining two concepts are explained below.
+
+\subsection{Emotion Parameters}
+The emotion parameters specify how actions parameters should be modified in order to express an emotion.
+However, there is going to be a diverse set of parameters depending on the nature of the action.
+For example, consider the action move body and speak.
+The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement.
+The speaking action would have the following parameters: text, pitch and tone.
+On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints.
+Since each action is characterized by different parameters, their modification must be done accordingly to the parameters.
+Therefore, a variety of emotional parameters would be necessary to describe the modification of all type of actions.So, it was decided to focus on the parameters that could be used to express emotions with the Triskarino and Keepon.
+It was determined that these parameters could just use movement actions, which are described by position, velocity and acceleration.
 \subsection{Simple and Compound Actions}
 \input{./Parts/SimpleActions} 
+\section{Emotional Tree}
+\label{sec:emotional_execution_tree}
+\input{./Parts/EmotionalTree}
 \section{Describing Components}
+\label{sec:description}
 \input{./Parts/description}
-\section{Emotional Tree}
-\input{./Parts/EmotionalTree}
 \section{Implementation}
+\label{sec:implementation}
 \input{./Parts/Implementation}
@@
 To show the system's versatility, it was used with quite different platforms such as a Keepon Pro and Triskarino.
-Keepon was used to perform simple actions, while Triskarino was used to test complex actions with different parametrizations of emotions.\\
+Keepon was used to perform simple actions, while Triskarino was used to test complex actions with different parametrizations of emotions.
+
 The obtained results show that the system could enrich the robotic actions with emotions, which could be parametrized from configuration files.

### 2017-03-25 RO-MAN-2017-2/RO-MAN2017-2.tex
Fixed few grammar issues

@@
 Emotions are considered by many researchers as beneficial elements in social robotics, since they can enrich human-robot interaction with non-verbal clues.
-Although there have been works that have studied emotion expression in robots, mechanism to generate emotion are highly integrated with the rest of the system.
+Although there have been works that have studied emotion expression in robots, mechanisms to express emotion are usually highly integrated with the rest of the system.
 This limits the possibility to use these approaches in other applications.
@@
 \label{sec:concepts}
-The system is based on six main concepts that structures and enables the enrichment of actions with emotions.
+The system is based on six main concepts that structure and enable the enrichment of actions with emotions.
 (i) \textit{Action message} establishes the structure of the message to describe any kind of action (i.e., simple and compound).
@@
 However, there is going to be a diverse set of parameters depending on the nature of the action.
-For example, consider the action move body and speak.
-The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement.
+For example, consider the actions \textit{move body} and \textit{speak}.
+The human action of speaking is related to changes in the vocal cords to produce different sounds, while \textit{move body} is directly related to the body movement.
 The speaking action would have the following parameters: text, pitch and tone.
-On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints.
+On the other hand, the action \textit{move body} would have as parameters the desired destination, velocity, and trajectory constraints.
 Since each action is characterized by different parameters, their modification must be done accordingly to the parameters.
-Therefore, a variety of emotional parameters would be necessary to describe the modification of all type of actions.So, it was decided to focus on the parameters that could be used to express emotions with the Triskarino and Keepon.
+Therefore, a variety of emotional parameters would be necessary to describe the modification of all type of actions.
+So, it was decided to focus on the parameters that could be used to express emotions with the robots we have considered: Triskarino and Keepon.
 It was determined that these parameters could just use movement actions, which are described by position, velocity and acceleration.
@@
 An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions.
-To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential.
+To achieve this,  an Emotional Execution Tree created from three different types of nodes was used: simple actions, parallel, and sequential.
 Simple actions are functions that map a set of parameters to specific movements.

### 2017-03-25 RO-MAN-2017-2/Parts/Introduction.tex
Fixed few grammatical errors

@@
 However, bringing robots in these environment raises the challenge to increase robots' acceptance.
-Although this could be seen as an easy task that just would need improvements in robots' appearances and capabilities, it is possible that people would expect to treat robots as humans as they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil this expectations.
+Although this could be seen as an easy task that just would need improvements in robots' appearance and capabilities, it is possible that people would expect to treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil this expectations.
 
-Some researchers have suggested that embedding emotion expression capabilities to robots could improve their acceptance in social environments~\cite{Pavia2014}.
+Some researchers have suggested that embedding emotion expression capabilities in robots could improve their acceptance in social environments~\cite{Pavia2014}.
 To this purpose, some researchers~\cite{Breazeal2002, Arras2012} have added specific emotional poses and expression to their robots.
 Others have studied how to convey emotions with specific platforms~\cite{Li2011, Brown2014}.
-Nevertheless, these works have created modules to show emotions that are strongly integrated to their solutions, which eliminate the possibility to re-use or adapt their systems into other projects.
+Nevertheless, these works have created modules to show emotions that are strongly integrated to their systems, which eliminate the possibility to re-use or adapt them for other projects.
 
-In theory, the projection of emotion with humanoid embodiments could be simplified by mimicing the human movements.
-However, this idea cannot be fully implemented, due physical limitations in robots.
+In theory, the projection of emotion with humanoid embodiments could be simplified by mimicking human movements.
+However, this cannot be fully implemented, due physical limitations in robots.
 Since an exact matching of human movements to convey emotions could not be used in robots \cite{Saerbeck2007,Canamero2010}, some researchers are studying diverse features and values to express emotions with different platforms.
@@
 
-This paper presents an Emotional Enrichment System (EES) that modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot.
+This paper presents an Emotional Enrichment System (EES) that modifies actions' parameters and adds actions to create the illusion of emotion expression in a robot.
 Although the EES was originally conceived to be used to facilitate the study of emotion projection, its design was devised to make it extendable to other platforms and adaptable to new tasks.
@@
 Additionally, the concept of compound actions is used to group a bunch of nodes, thus reducing the tree dimension and allowing the reuse of recurrent actions generated by specific combinations of simple actions and other nodes.
-This EXT has been formalized to give a guideline to further implementations and extensions.
+This EXT has been formalized to provide a guideline to further implementations and extensions.
 

### 2017-03-25 RO-MAN-2017-2/Parts/RelatedWork.tex
Update RelatedWork.tex

@@
 Breazeal and collaborators~\cite{Breazeal2003} used one robot on the stage.
-This anemone-like robot had few behaviours, which included getting scared when a person comes too close; the robot was able to show some basic emotions (i.e., fear and interest).
+Their anemone-like robot had few behaviours, which included getting scared when a person comes too close; the robot was able to show some basic emotions (i.e., fear and interest).
 Knight~\cite{Knight2011b} used the platform NAO to produce a sort of stand-up comedy.
@@
 Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012}, Fan and collaborators~\cite{Fan2009}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression.
-Although these works have expressed emotions in their studies, they were not focus on create a framework that could be used by others researchers in HRI.
+Although these works have expressed emotions in their studies, they did not focus on creating a framework that could be used by other researchers in HRI.
 Therefore, the use of affective architectures for virtual agents (e.g.
 SAIBA/BML framework~\cite{Kopp2006}) could be though as a feasible solution.
-However these framework describe high level actions without given relevant details to its implementation in physical platform.
-This gap cannot be closed by making a direct map the abstract actions and the physical platforms.
-This is due the fact that virtual agents do not have physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007,Canamero2010}.
+However, these frameworks describe high level actions without giving relevant details to its implementation in physical platforms.
+This gap cannot be filled by making a direct mapping between the abstract actions and the physical platforms.
+This is due to the fact that virtual agents do not have physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007,Canamero2010}.

### 2017-03-25 RO-MAN-2017-2/Parts/description.tex
Fixed some grammar errors

@@
 The description files allow the parametrization and extent the system to fit other applications is required.
-To standarized the mechanisms to describe these files, it was decided to create a language to describe them.
-This allows other researchers to create their own files and extended the language to fit their needs.
-It was decided to use EBNF to describe language.
+To standarize the mechanisms to describe these files, it was decided to create a language to describe them.
+This allows other researchers to create their own files and to extend the language to fit their needs.
+It was decided to use the Extended Backus-NAur Form (EBN)F to describe this language.
 \subsection{Emotion Description} 

### 2017-03-25 RO-MAN-2017-2/Parts/SimpleActions.tex
Update SimpleActions.tex

@@
 Simple actions are actions that are considered as primitives: they are used as building blocks.
-As a consequence, these actions are described in the system and are the ones in which the parameters are changed to embed the emotions.
+As a consequence, these actions are described in the system and are the ones whose parameters are changed to embed the emotions.
 Their description specifies mandatory and optional parameters that are required to execute an action.
-These parameters are modified accordingly to the information provided in the emotional parameters.
+These parameters are modified accordingly to the information provided by the emotional parameters.
 Compound actions are actions that are created from simple actions and other compound actions.
 These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g., compound actions that are used often).
+%TODO it is not clear what does it mean that they are not implemented.
 
-A set of simple actions to be implemented were selected to test the system.
-These actions were selected considering the capabilities of Keepon and Triskarino.
-The eight actions selected were: move body, oscillate body, move shoulder, oscillate shoulder, move torso, oscillate torso, and do nothing.
+A set of simple actions to be implemented were selected to test the system, considering the capabilities of Keepon and Triskarino.
+The eight actions selected were: \textit{move body}, \textit{oscillate body}, \textit{move shoulder}, \textit{oscillate shoulder}, \textit{move torso}, \textit{oscillate torso}, and \textit{do nothing}.
 Description for each action, its mandatory parameters and optional parameters are presented in Table~\ref{table:actions_implemented}.
@@
 \centering
-\caption{Description of the seven simple actions implemented, and their respective parameters. Where  P is 2D position, V is 2D velocity vector and angular velocity, and T is time}
+\caption{Description of the seven simple actions implemented, and their respective parameters, where P is 2D position, V is 2D velocity vector and angular velocity, and T is time}
 \label{table:actions_implemented}
@@
 
-To exemplify the use of these actions, lets consider a sequence of movements illustrated in Figure~\ref{fig:triskar_test}.
-This sequence of movements correspond to an adaptation of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
-The fist part of this scene is characterized by strong changes in Romeo's emotional state, which is the perfect test for the system.
+To exemplify the use of these actions, let us consider a sequence of movements illustrated in Figure~\ref{fig:triskar_test}.
+This sequence of movements corresponds to an adaptation of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
+The fist part of this scene is characterized by strong changes in Romeo's emotional state, thus it was selected as significant test for the system.
 \begin{figure}
@@
 A partial view of the whole sequence of actions is illustrated in Figure~\ref{fig:sequence_actions}.
-The first node correspond to the first action in Figure~\ref{fig:triskar_test}.
-The second actions corresponds to a compound action created by the parallel execution of the simple action move body and other compound action.
+The first node corresponds to the first action in Figure~\ref{fig:triskar_test}.
+The second actions corresponds to a compound action created by the parallel execution of the simple action \textit{move body} and other compound actions.
 

### 2017-03-25 RO-MAN-2017-2/Parts/EmotionalTree.tex
Fixed some grammar issues

@@
 Sequential nodes execute one branch after the other.
-Once all the branches have been executed, it notifies its predecessor to continue with the execution of other branches.
+Once all the branches have been executed, asequential node notifies its predecessor to continue with the execution of other branches.
 The parallel node executes all the branches at the same time.
@@
 This main branch is established in the action message.
-On the other hand, the emotion level synchronization update to a new emotional parameter of all the branches once the main branch updates to a  new emotional parameter.
+On the other hand, the emotion level synchronization updates to a new emotional parameter of all the branches once the main branch updates to a new emotional parameter.
+%TODO The previous sentence is not clear.
+I cannot understando so I cannot fix it.
+What does it mean that updates to a parameter?
 In both cases, any update or finish message will be ignored if the branch is not principal.
-These two levels of synchronization creates four sub-types of parallel nodes: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
+These two levels of synchronization create four sub-types of parallel nodes: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous.
 
@@
 This enables the possibility to have actions that have priority over others.
-To exemplify this, lets continue with the sequence of actions depicted in Figure~\ref{fig:sequence_actions}.
-The Emotional Execution Tree for that sequence of actions would be like the one presented in Figure~\ref{fig:emotional_enrichment}.
+To exemplify this, let us consider the sequence of actions depicted in Figure~\ref{fig:sequence_actions}.
+The Emotional Execution Tree for this sequence would be like the one presented in Figure~\ref{fig:emotional_enrichment}.
 
@@
 	\includegraphics[width=0.45\textwidth]{./Images/Representation.png}
-	\caption{Emotional Execution Tree for the sequence of actions depicted in Figure~\ref{fig:sequence_actions}. The $*$ symbolize that node is principal. S. represents sequential.}
+	\caption{Emotional Execution Tree for the sequence of actions depicted in Figure~\ref{fig:sequence_actions}. The $*$ symbol denotes principal nodes. $S$ represents sequential.}
 	\label{fig:emotional_enrichment}
@@
 \subsection{Formalization of Simple and Compound Actions}
-Formalizing simple and compound actions generates a common system to design them and verify if they are described correctly.
+Formalizing simple and compound actions enables the generation of a system to design them and verify if they are described correctly.
 Simple actions ($SA$) could be seen as functions that map a set of parameters $p^{pl}_{i} \in P$ to specific platform ($pl$) movements ($m^{pl}_{j}\in M^{pl}$) in the set of movements for that platform ($m^{pl}_{j} =sa^{pl}(\lbrace p^{pl}_{i} \rbrace)$).
-Each $sa^{pl}$ could have different implementations due to different reasons such as: platform's type, action's goal, how the mapping from inputs to outputs are done, among others.
+Each $sa^{pl}$ could have different implementations due to different reasons such as: platform's configuration, action's goal, how the mapping from inputs to outputs are done, among others.
 In our case, we consider that two actions are different if $(\forall sa_{i}, sa_{j} \in SA, \forall q, t \in PL | Param( sa_{i}^q ) \neq Param( sa_{j}^t )\Rightarrow sa_{i}^q \neq sa_{j}^t)$, 
@@
 
-With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$ but with the parameters modified in order to convey the desire emotion $e$, or even a set of $sa$ with their parameters modified.
+With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$, but with the parameters modified in order to convey the desired emotion $e$, or even a set of $sa$ with modified parameters.
 This definition goes along with the idea that new $sa$ could be added to convey a specific emotion.

### 2017-03-25 RO-MAN-2017-2/Parts/Implementation.tex
Fixed some grammar issues

@@
 
-The system was implemented in \textit{C++} and interfaced with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description presented in previous sections. 
+The system was implemented in \textit{C++} and interfaced with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description presented in the previous sections. 
 \begin{figure*}
@@
 This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
-%TODO????
-When the verification is done, and all the actions exist and the parameters correspond, an Emotional Execution Tree (EXT)
-is created such as the one presented in Figure~\ref{fig:emotional_enrichment}
+%TODO Why some are mandatory and some not?
+What does this mean?
+When the verification is done, and all the actions exist and the parameters correspond, an Emotional Execution Tree (EXT) such as the one presented in Figure~\ref{fig:emotional_enrichment} is created
 	\item \textit{Emotion addition:} uses the EXT created in the previous phase. In this phase new simple actions ($sa$)
-are added to the EXT, and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
+can be added to the EXT, and the $sa$'s parameters are modified following the emotion description, which is loaded from files.
 This process is broken down in two steps.
@@
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
-In this phase a reference to the principal and emotional action is maintained, thus, when a new emotion is to be expressed, the system stops the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
+In this phase a reference to the principal and emotional action is maintained, thus, when a new emotion is to be expressed, the system terminates the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
+%TODO NOt clear.
+t seems that actually some action execution changes.
+What would you like to say?
 \end{enumerate}
 
-All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and there are many available parsers.\\ 
-To test the system two different platforms were used: Keepon Pro %TODO da citare la prima volta il paper descrittivo
+All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and can be parsed by many systems.\\ 
+To test the system, two different platforms were used: Keepon Pro %TODO da citare la prima volta il paper descrittivo
 and an own made platform called Triskarino.

### 2017-03-26 RO-MAN-2017-1/Parts/CaseStudy.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
  The case study presented in this paper was held at an exhibition with two main objectives:
-\begin{enumerate}
-	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}, which was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to express: \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
+ (i) Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}, which was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to express: \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}.
 A total of 196 value combinations were designed, 20 of which, randomly selected, were presented to each participant.
 Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}), added as confounding terms.
-	\item Verify whether participants would prefer scenes where the robot moves expressing emotions, or rather moves on the same trajectory without any emotion expression.
+(ii) Verify whether participants would prefer scenes where the robot moves expressing emotions, or rather moves on the same trajectory without any emotion expression.
 To control scene variability two cameras and eight AR tags were used together with a Kalman filter to improve robot localization on the stage.
@@
 \end{figure}
-
-\end{enumerate}
 
@@
 This case study was done at an exhibition during a period of two days.
-People coming to the stand were asked to volunteerto participate in this study, which was divided in to parts.
+People coming to the stand were asked to volunteer to participate in this study, which was divided in to parts.
 In the first one, each subject was exposed to two emotion expressions.

### 2017-03-26 RO-MAN-2017-1/Parts/Introduction.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 Emotions and mental states are not just expressed through facial expression and voice, but also by body postures and other features~\cite{Gelder2008}.
-Many psychological studies have focused their attention on how emotions are conveyed through the face~\cite{Ekman2004},~\cite{kleinsmith2012affective}.
-Similarly, the robotics community uses anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
-%~\cite{haering2011},
-~\cite{Destephe2013}
-) to convey emotions.
+Many psychological studies have focused their attention on how emotions are conveyed through the face~\cite{kleinsmith2012affective}.
+Similarly, the robotics community uses anthropomorphic faces (e.g.~\cite{Breazeal2002}) and bodies (e.g.~\cite{Canamero2010}) to convey emotions.
 In many situations, the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
@@
 
-However,the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
-%,Lakatos2014,Sharma2013,Novika2015}
-) remains still small in comparison to those exploiting anthropomorphic features.
+However,the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}) remains still small in comparison to those exploiting anthropomorphic features.
 Moreover, these works do not provide specific range of values for the characteristics used to express the implemented emotions.

### 2017-03-26 RO-MAN-2017-1/Parts/RelatedWork.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the work done by Camurri et al.~\cite{pop00002}.
-Continuing with their research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
-The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love).
+Similarly, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
+The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB).
 Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.

### 2017-03-26 RO-MAN-2017-1/RO-MAN2017.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 \usepackage{slashbox}
+
+\usepackage[table]{xcolor}
 \newcommand{\co}{\cellcolor{gray!40}}
-\usepackage[table]{xcolor}
 %\usepackage{mathptmx} % assumes new font selection scheme installed
@@
 \author{Julian M. Angel-Fernandez$^{1}$ and Andrea Bonarini$^{2}$% <-this % stops a space
-\thanks{$^{1}$Julian M. Angel-Fernandez is a Research at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
+\thanks{$^{1}$Julian M. Angel-Fernandez is a Researcher at Automation and Control Institute, Vienna University of Technology, Vienna, Austria
         {\tt\small julian.angel.fernandez@tuwien.ac.at}}%

### 2017-03-26 RO-MAN-2017-2/Parts/EmotionalTree.tex
fiixed some grammar issues
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 Sequential nodes execute one branch after the other.
-Once all the branches have been executed, asequential node notifies its predecessor to continue with the execution of other branches.
+Once all the branches have been executed, a sequential node notifies its predecessor to continue with the execution of other branches.
 The parallel node executes all the branches at the same time.
@@
 This main branch is established in the action message.
-On the other hand, the emotion level synchronization updates to a new emotional parameter of all the branches once the main branch updates to a new emotional parameter.
-%TODO The previous sentence is not clear.
-I cannot understando so I cannot fix it.
-What does it mean that updates to a parameter?
+On the other hand, the emotion level synchronization makes all branches to shift to the next descriptor of the emotion.
 In both cases, any update or finish message will be ignored if the branch is not principal.

### 2017-03-26 RO-MAN-2017-2/Parts/Implementation.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
-%TODO in this section is missing a review on the terms and explain some concepts that are depicted in the figures.
-
 The system was implemented in \textit{C++} and interfaced with ROS. The design (Fig.~\ref{fig:system_architecture}) was created following the description presented in the previous sections. 
@@
 The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action included in the message.
-This parameters' verification is done on the implemented description for each action, which describes the parameters that are mandatory and those that are optional.
-%TODO Why some are mandatory and some not?
-What does this mean?
-When the verification is done, and all the actions exist and the parameters correspond, an Emotional Execution Tree (EXT) such as the one presented in Figure~\ref{fig:emotional_enrichment} is created
+When the verification is done, and all the actions exist and the parameters correspond, an EXT such as the one presented in Figure~\ref{fig:emotional_enrichment} is created.
 	\item \textit{Emotion addition:} uses the EXT created in the previous phase. In this phase new simple actions ($sa$)
@@
 	\includegraphics[width=0.45\textwidth]{./Images/exampleTreeE.png}
-	\caption{Enrich Emotional Execution Tree.} 
+	\caption{EXT enriched with emotion for the EXT presented in Figure~\ref{fig:emotional_enrichment}.} 
 	\label{fig:reference}
 	\end{figure}
-	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
+	\item \textit{Execution:} this is the last phase and it is done after the EXT is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
-In this phase a reference to the principal and emotional action is maintained, thus, when a new emotion is to be expressed, the system terminates the previous emotional action and starts executing the new ones without affecting the general execution of the actions.
-%TODO NOt clear.
-t seems that actually some action execution changes.
-What would you like to say?
 \end{enumerate}
@@
 As it can be seen the stage was divided in 81 squares and the positions were given to the system in terms of the desire square to be reached, which allows the robot to adjust to the stage's dimension.
-%TODO I cannot understand what follows.
-What is a context?
-The whole sequence of actions were specified as unique action, having several sequential context and just move body action.
+The whole sequence of actions were specified as unique action, having several sequential nodes and just move body action.
 The other actions, such as oscillate body or blend upper body were added online accordingly the desired emotion.

### 2017-03-26 RO-MAN-2017-2/Parts/SimpleActions.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 Compound actions are actions that are created from simple actions and other compound actions.
-These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g., compound actions that are used often).
-%TODO it is not clear what does it mean that they are not implemented.
+For example, two actions that are executed in parallel are considered as compound actions.
+These actions are not always implemented in the system.
+They can be described in the action messages without being implemented.
+In case that a compound action is used often, it could be implemented in the system.
+The implementation describes action's parameters, other compound actions, simple actions and mapping between actions and parameters.
 

### 2017-03-26 RO-MAN-2017-2/Parts/description.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 This allows other researchers to create their own files and to extend the language to fit their needs.
-It was decided to use the Extended Backus-NAur Form (EBN)F to describe this language.
+It was decided to use the Extended Backus-Naur Form (EBNF) to describe this language.
 \subsection{Emotion Description} 
@@
 \end{small}
-%TODO give information regardin 1) why repetition 2) why a set of parameters 3) why use of time and space
+The attribute repetition is used to specify if the descriptors of an emotion parameters must be executed in an infinite loop.
+As it was already mentioned, the emotional parameters implemented for this version correspond to the move actions.
 
@@
 \end{small}
-
-%TODO give information regarding: primary and emotion synch

### 2017-03-26 RO-MAN-2017-2/RO-MAN2017-2.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles

@@
 The emotion parameters specify how actions parameters should be modified in order to express an emotion.
-However, there is going to be a diverse set of parameters depending on the nature of the action.
+These parameters could include a sequence of descriptors.
+For example, these descriptors could be used to generate changes of velocity over time or position to express an emotion.
+However, there is going to be a diverse set of parameters and descriptors depending on the nature of the action.
 For example, consider the actions \textit{move body} and \textit{speak}.
@@
 On the other hand, the action \textit{move body} would have as parameters the desired destination, velocity, and trajectory constraints.
-Since each action is characterized by different parameters, their modification must be done accordingly to the parameters.
-Therefore, a variety of emotional parameters would be necessary to describe the modification of all type of actions.
+However, in order to express emotion in speak action, it is required to modify pitch variables (i.e.
+fundamental frequency level, contour and jitter), intensity and speech rate~\cite{Gunes2011}.
+On the other hand, changing linear velocity and adding oscillation could be used to convey emotion in the move body action~\cite{Angel2016c}.
+Since each action requires modification on diverse parameters, a variety of emotional parameters would be necessary to describe the modification of all type of actions.
 So, it was decided to focus on the parameters that could be used to express emotions with the robots we have considered: Triskarino and Keepon.

### 2017-04-23 JournalIJSR/IJSR.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
 Social environments are intricate spaces where people behave in ways that are socially accepted.
-In a similar way, robots that interact with humans on daily bases are expected to develop certain behaviours to be socially accepted by people.
-This creates the necessity to make robots with high social presence that let humans to feel comfortable with their presence.
-The straightest way to fulfill is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics.
+In a similar way, robots that interact with humans on a daily bases are expected to develop certain behaviours to be socially accepted by people.
+This creates the necessity to point out our attention on social presence of robots, to let humans feel comfortable with them.
+The straightest way to fulfill this is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics.
 As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions.
@@
 As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance.
-This paper presents an experiment made to understand humans' perception of emotion for angular and linear velocity, body orientation, and movement direction.
+This paper presents an experiment made to understand humans' perception of emotion given angular and linear velocity, body orientation, and movement direction.
 Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features.
@@
 \input{./Parts/Introduction}
+\section{Emotional Models}
+\input{./Parts/EmotionModels}
 \section{Related Work}
@@
 \input{./Parts/Results}
+\section{Discussion}
+\label{sec:discussion}
+\input{./Parts/Discussion}
 \section{Conclusions and Further Work}

### 2017-04-23 JournalIJSR/Parts/Conclusion.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
 
-The values obtained in this experiment could be used to express emotions in non-anthropomorphic platforms.
+The values obtained in this experiment could be used as a guide to express emotions in non-anthropomorphic platforms with similar features as the one used in the experiment.
 It is still needed to cross validate the values and to determine what values from the top ten could more accurately express the desired emotion.
 It is important to mention that is not expected to have a 100\% of correct emotion recognition by the participants.
-As it has been observed in previous work in humans and robots, it is not possible to get a 100\% of correct recognition.
+As it has been observed in previous work in humans and robots, it is not possible to obtain a 100\% of correct recognition due to diverse factors such as current emotional state of the observer.
 This cross validation would help to reduce the number of feature combinations to the ones with higher possibility of identification.
 Moreover, additional experiments should be done to obtain analogous values for changes in shape and in different platform's size.
+Moreover, it is still necessary to study the influence that plays the embodiment on the perception of emotions.
+This is going to be beneficial to validate this study but it would also generalize other works done on the same direction.
+
+Even thought the number of works studying how to project emotions with robotic platforms is increasing, it is still required a framework that standardize the processes for the design of this endevours.
+This could is due the following four reasongs.
+First, there are a variety of emotion theories that could be used as a based to design the experiments or case studies.
+Hence, researchers must know who to use them correctly and how they are connected among them.
+For example, the model suggested by Izard~\cite{Izard2007} redefines the idea of basic emotions and make a connection with dimensional theories.
+Second, researcher are using different platforms to do their experiments, at time of writing, there is not a formal evidence that clarify the impact of the embodiment on the perception of emotions.
+This generates situations in which two works could not be comparable.
+Third, the use of actors to generate the movements are not reliable.
+Actors use diverse techniques to create believable representations of specific emotions.
+However, this does not ensure that all actor convey emotions in same way.
+Therefore, several records are done and the ones with the highest agreement are selected.
+This brings the technical question on how to interpret the significance of agreement obtained~\cite{Russell2003}.
+Fourth, there is not a generic format to present the finding and movements used.
+Each researcher is using diverse methodologies to present their findings, for example some uses Laban's theory~\cite{Sharma2013} while others present the postures~\cite{NAO2013}.

### 2017-04-23 JournalIJSR/Parts/Discussion.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

--- 2016-12-06 JournalIJSR/Parts/Results.tex
@@
-A table with subjects' answers was generated for each treatment. Table~\ref{table:example_table} is an example of the generated tables.
-
-\begin{table*}
-\centering
-\caption{Example of the table generated for each experience. This table corresponds to the experience with $ID=1$.}
-\label{table:example_table}
-\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |  }
-\hline
-	\rotatebox{90}{ \textbf{Sex}} & 
-	\rotatebox{90}{ \textbf{Background}} & 
-	\rotatebox{90}{ \textbf{Age}} & 
-	\rotatebox{90}{ \textbf{Country of Origin}} & 
-	\rotatebox{90}{ \textbf{Happy}} &
-	\rotatebox{90}{ \textbf{Excited}} & 
-	\rotatebox{90}{ \textbf{Tender}} & 
-	\rotatebox{90}{ \textbf{Scared}} & 
-	\rotatebox{90}{ \textbf{Angry}} & 
-	\rotatebox{90}{ \textbf{Sad}} & 
-	\rotatebox{90}{ \textbf{Other}} & 
-	\rotatebox{90}{ \textbf{Explain}} \\ \hline
-	Masculine & electronic engineering & 29 & Iran &  0 & 2 & 8 & 0 & 0 & 0 & 0 & \  \\ \hline
-	Feminine & Computer science & 25 & Italy &  0 & 0 & 6 & 0 & 0 & 8 & 0 & \  \\ \hline
-	Masculine & Computer science & 24 & Italy &  0 & 0 & 0 & 8 & 0 & 7 & 0 & \  \\ \hline
-	Feminine & Pedagogical Science & 26 & Italy &  0 & 0 & 0 & 0 & 0 & 0 & 7 & Dubbioso \\ \hline
-	Masculine & Computer science & 24 & Italy &  4 & 8 & 0 & 0 & 0 & 0 & 0 & \  \\ \hline
-\multicolumn{12}{c}{}
-\end{tabular}
-\end{table*}
-
-For each table, mean, standard deviation, and median were calculated.
-It was not possible to use ANOVA test over the data because the assumption of normality is not satisfied in the collected data.
-This was checked using the Shapiro-Wilk Test.
-Additionally, a contingency table for each emotion was generated in each treatment, as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean of their intensity, including the option ``other''.
-Therefore a total of seven tables for each treatment were created.
-For all these tables, Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated, which is a reliability coefficient to measure the agreement among different participants.
-Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.
-
-This calculation was done using the R's package \textit{irr}.
-To improve contingency tables' interpretation, it was decided to just register emotions' alpha and intensity values greater than zero.
-The $\alpha$ for each treatment is shown in Figure~\ref{fig:alpha_experience}.
-As it could be observed, this table does not provide any information about the interpretation for each emotion.
-Therefore, it was decided to create top ten raking of treatments from the contingency tables of each emotion.
-This ranking is generated considering the following items in the respective order:(i) the mean intensity of the respective emotion, (ii) the alpha agreement of contingency table for the respective emotion, and (iii) the alpha agreement for the specific treatment.
 From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:
@@
 %alpha general
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{./Images/Alpha.png} 
-	\caption{Alpha values for each movement.}
-	\label{fig:alpha_experience}
-\end{figure*}
-
-\begin{table}
-\centering
-\small
-\caption{Top 10 attributions for Happiness.  This tops table was generated by ordering the results from highest to lowest first by Happy mean, then by Happy alpha, and finally by Movement alpha.}
-\label{table:happy_top_ten}
-\rotatebox{-90}{
-\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
-\hline
-\multicolumn{5}{|c|}{Features} & 
-\multicolumn{8}{|c|}{Alpha} & 
-\multicolumn{7}{c|}{Mean} \\ \hline
-	\rotatebox{90}{\textbf{Direction (rad)}} &
-	\rotatebox{90}{\textbf{Orientation (rad)}} & 
-	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
-	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
-	\rotatebox{90}{\textbf{Angle (rad)}} &   
-	\rotatebox{90}{\textbf{General}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} \\ \hline
-	0 & 0 & 500 & 3 & 0.349 &  0.38 & 0.71 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 6.8 & 3 & 2.6 & 0 & 1.4 & 0 & 1.4 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.174 &  0.53 & 0.71 & 0 & 0 & 0 & 0 & 0 & 0 & 6.8 & 3.8 & 2 & 0 & 0 & 0 & 0 \\ \hline
-	0 & 0 & 900 & 3 & 0.174 &  0.33 & 0.22 & 0 & 0.13 & 0 & 0 & 0 & 0 & 6.6 & 2.6 & 0.6 & 0 & 1.6 & 0 & 0 \\ \hline
-	$\pi$ & $\pi$ & 0 & 3 & 0.349 &   0.21 & 0.21 & 0 & 0.13 & 0 & 0.23 & 0.34 & 0 & 6.6 & 3.6 & 1.4 & 2 & 0.8 & 0.4 & 0 \\ \hline
-	$\pi$ & 0 & 900 & 3 & 0.349 &   0.48 & 0.11 & 0.72 & 0.12 & 0 & 0.76 & 0 & 0 & 6.4 & 6.8 & 1.2 & 4 & 0.2 & 0 & 0 \\ \hline
-	0 & $\pi$ & 0 & 2 & 0.349 &  0.34 & 0.71 & 0 & 0 & 0.13 & 0.47 & 0.23 & 0 & 6 & 1.4 & 3.2 & 1.6 & 0.4 & 0.6 & 0 \\ \hline
-	$\pi$ & $\pi$ & 0 & 2 & 0.174 &   0.31 & 0.12 & 0 & 0 & 0.61 & 0 & 0 & 0.13 & 6 & 4.8 & 4.8 & 0.4 & 0 & 0 & 2 \\ \hline
-	$\pi$ & 0 & 500 & 2 & 0.349 &  0.43 & 0.11 & 0 & 0 & 0 & 0.13 & 0 & 0 & 6 & 0 & 3.4 & 0 & 0.6 & 0 & 2 \\ \hline
-	0 & 0 & 500 & 1 & 0.174 &  0.24 & 0.11 & 0 & 0 & 0 & 0 & 0 & 0.13 & 6 & 4 & 4.2 & 0 & 2.2 & 0 & 1.2 \\ \hline
-	$\pi$ & 0 & 200 & 3 & 0.349 &  0.28 & 0.22 & 0 & 0 & 0 & 0 & 0 & 0 & 5.8 & 0.8 & 3 & 0 & 0 & 0 & 1.4 \\ \hline
-\multicolumn{16}{c}{}
-\end{tabular}
-}
-\end{table}
-
-\begin{table}
-\centering
-\small
-\caption{Top 10 attributions for Anger. This tops table was generated by ordering from highest to lowest first by Angry mean, then by Angry alpha, and finally by Movement alpha.}
-\label{table:Angry_top_ten}
-\rotatebox{-90}{
-\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
-\hline
-\multicolumn{5}{|c|}{Features} & 
-\multicolumn{8}{|c|}{Alpha} & 
-\multicolumn{7}{c|}{Mean} \\ \hline
-	\rotatebox{90}{\textbf{Direction (rad)}} &
-	\rotatebox{90}{\textbf{Orientation (rad)}} & 
-	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
-	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
-	\rotatebox{90}{\textbf{Angle (rad)}} &  
-	\rotatebox{90}{\textbf{General}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} \\ \hline
-	0 & 0 & 0 & 2 & 0.087 & 0.19 & 0 & 0.13 & 0.13 & 0.13 & 0.22 & 0 & 0 & 3.2 & 1.4 & 1.2 & 1.8 & 6.4 & 0 & 0 \\ \hline
-	0 & 0 & 900 & 2 & 0.087 & 0.29 & 0.13 & 0 & 0.76 & 0.13 & 0.21 & 0 & 0 & 1.6 & 3.8 & 0.2 & 1 & 6.4 & 0 & 0 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 900 & 0 & 0 & 0.60 & 0 & 0 & 0 & 0.13 & 0.73 & 0 & 0 & 0 & 1.6 & 0 & 1.4 & 6.2 & 0 & 0 \\ \hline
-	0 & 0 & 900 & 3 & 0.349 & 0.44 & 0 & 0 & 0 & 0 & 0.12 & 0 & 0 & 3 & 5 & 0 & 2.8 & 6.2 & 0 & 0 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 200 & 3 & 0.087 & 0.41 & 0 & 0 & 0 & 0 & 0.11 & 0.47 & 0 & 0 & 4.8 & 2.6 & 0 & 5.8 & 0.4 & 0 \\ \hline
-	$\pi$ & 0 & 500 & 3 & 0.087 & 0.44 & 0.13 & 0 & 0 & 0 & 0.43 & 0 & 0 & 0.8 & 2.6 & 0 & 1.4 & 5.2 & 0 & 0 \\ \hline
-	0 & 0 & 200 & 3 & 0.087 & 0.13 & 0.13 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 2.4 & 5.2 & 0 & 1.8 \\ \hline
-	0 & 0 & 900 & 1 & 0.087 & 0.54 & 0 & 0.16 & 0 & 0 & 0.16 & 0 & 0 & 2.4 & 6.4 & 0 & 0 & 5 & 0 & 0 \\ \hline
-	0 & 0 & 900 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 0.13 & 0 & 0 & 0.13 & 1.6 & 3 & 1 & 1.6 & 5 & 0 & 1.8 \\ \hline
-	$\pi$ & 0 & 500 & 2 & 0.087 & 0.30 & 0.13 & 0 & 0 & 0 & 0.21 & 0 & 0 & 1 & 1.8 & 0 & 3.4 & 4.8 & 0 & 0 \\ \hline
-\multicolumn{16}{c}{}
-\end{tabular}
-}
-\end{table}
-
-\begin{table}
-\centering
-\small
-\caption{Top 10 attributions for Fear.  This tops table was generated by ordering from highest to lowest first by Fear mean, then by Fear alpha, and finally by Movement alpha.}
-\label{table:Scared_top_ten}
-\rotatebox{-90}{
-\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
-\hline
-\multicolumn{5}{|c|}{Features} & 
-\multicolumn{8}{|c|}{Alpha} & 
-\multicolumn{7}{c|}{Mean} \\ \hline
-	\rotatebox{90}{\textbf{Direction (rad)}} &
-	\rotatebox{90}{\textbf{Orientation (rad)}} & 
-	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
-	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
-	\rotatebox{90}{\textbf{Angle (rad)}} &
-	\rotatebox{90}{\textbf{General}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} \\ \hline
-	$\pi$ & $\pi$ & 900 & 2 & 0.174 & 0.85 & 0 & 0 & 0.15 & 0.83 & 0 & 0 & 0 & 0 & 0 & 1.2 & 9.6 & 0 & 0 & 0 \\ \hline
-	$\pi$ & $\pi$ & 900 & 1 & 0.087  & 0.73 & 0 & 0 & 0.15 & 0.79 & 0 & 0.79 & 0 & 0 & 0 & 0.6 & 9.6 & 0 & 0.2 & 0 \\ \hline
-	$\pi$ & $\pi$ & 500 & 3 & 0.087 & 0.41 & 0.13 & 0 & 0 & 0.75 & 0 & 0 & 0 & 2 & 3.4 & 0 & 9 & 3.6 & 0 & 0 \\ \hline
-	$\pi$ & $\pi$ & 500 & 2 & 0.174 & 0.33 & 0.24 & 0.24 & 0 & 0.34 & 0.24 & 0 & 0.25 & 1.33 & 1.5 & 0 & 7.83 & 0.66 & 0 & 1.66 \\ \hline
-	$\pi$ & $\pi$ & 500 & 2 & 0.087 & 0.68 & 0 & 0 & 0 & 0.72 & 0.13 & 0 & 0 & 0 & 0 & 0 & 7.8 & 0.6 & 2.20 & 0 \\ \hline
-	$\pi$ & $\pi$ & 200 & 2 & 0.087 & 0.44 & 0.13 & 0.13 & 0 & 0.66 & 0 & 0 & 0 & 1 & 1 & 1.2 & 7.6 & 1.6 & 0 & 0 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.087 & 0.35 & 0.35 & 0.13 & 0 & 0.22 & 0 & 0 & 0 & 0.4 & 1.2 & 0 & 7.4 & 3 & 0 & 0 \\ \hline
-	0 & $\pi$ & 900 & 3 & 0.087 & 0.53 & 0 & 0 & 0 & 0.30 & 0 & 0 & 0 & 0 & 0 & 0 & 7 & 2.20 & 0 & 0 \\ \hline
-	$\pi$ & $\pi$ & 500 & 3 & 0.349 & 0.20 & 0.13 & 0.13 & 0 & 0.16 & 0.34 & 0 & 0 & 1.8 & 1.6 & 0 & 6.8 & 0.4 & 2.4 & 0 \\ \hline
-	$\pi$ & $\pi$ & 200 & 2 & 0.174 & 0.53 & 0 & 0 & 0.13 & 0.71 & 0.13 & 0.13 & 0 & 0 & 0 & 1 & 6.6 & 0.8 & 1.2 & 0 \\ \hline
-\multicolumn{16}{c}{}
-\end{tabular}
-}
-\end{table}
-
-\begin{table}
-\centering
-\small
-\caption{Top 10 attributions for Sadness.  This tops table was generated by ordering from highest to lowest first by Sadness mean, then by Sadness alpha, and finally by Movement alpha.}
-\label{table:Sad_top_ten}
-\rotatebox{-90}{
-\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
-\hline
-\multicolumn{5}{|c|}{Features} & 
-\multicolumn{8}{|c|}{Alpha} & 
-\multicolumn{7}{c|}{Mean} \\ \hline
-	\rotatebox{90}{\textbf{Direction (rad)}} &
-	\rotatebox{90}{\textbf{Orientation (rad)}} & 
-	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
-	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
-	\rotatebox{90}{\textbf{Angle (rad)}} &
-	\rotatebox{90}{\textbf{General}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} & 
-	\rotatebox{90}{\textbf{Happiness}} & 
-	\rotatebox{90}{\textbf{Excitement}} & 
-	\rotatebox{90}{\textbf{Tenderness}} & 
-	\rotatebox{90}{\textbf{Fear}} & 
-	\rotatebox{90}{\textbf{Anger}} & 
-	\rotatebox{90}{\textbf{Sadness}} & 
-	\rotatebox{90}{\textbf{Other}} \\ \hline
-	$\pi$ & 0 & 200 & 1 & 0.349 & 0.64 & 0 & 0 & 0 & 0 & 0.13 & 0.73 & 0.13 & 0 & 0 & 0 & 0 & 1.2 & 7.4 & 1.6 \\ \hline
-	0 & $\pi$ & 0 & 1 & 0.349 & 0.39 & 0 & 0 & 0.13 & 0 & 0 & 0.22 & 0 & 0 & 0 & 1.8 & 0 & 0 & 7.2 & 3.2 \\ \hline
-	0 & 0 & 200 & 1 & 0.349 & 0.18 & 0.13 & 0 & 0 & 0 & 0.13 & 0.11 & 0 & 1.6 & 2 & 5.4 & 2.6 & 1.6 & 6 & 0 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 200 & 0 & 0 & 0.10 & 0.13 & 0.29 & 0 & 0 & 0 & 0 & 0 & 0.8 & 0.4 & 1.8 & 0 & 0 & 6 & 3.2 \\ \hline
-	$\pi$ & $\pi$ & 200 & 1 & 0.349 & 0 & 0 & 0 & 0.13 & 0.13 & 0.14 & 0 & 0 & 0 & 0 & 0.6 & 1.4 & 1.2 & 6 & 2.4 \\ \hline
-	0 & $\pi$ & 200 & 0 & 0 & 0.27 & 0.13 & 0 & 0 & 0 & 0 & 0.21 & 0 & 1.2 & 0 & 3.4 & 1.8 & 0 & 5.8 & 0 \\ \hline
-	$-\frac{\pi}{2}$ & 0 & 0 & 1 & 0.087 & 0.14 & 0 & 0.13 & 0.13 & 0.13 & 0 & 0.21 & 0.13 & 0 & 2 & 2 & 1.2 & 0 & 5.8 & 1.6 \\ \hline
-	0 & $\pi$ & 200 & 1 & 0.349 & 0.40 & 0 & 0.13 & 0 & 0 & 0 & 0.57 & 0.13 & 0 & 0.8 & 3 & 3 & 0 & 5.6 & 0.6 \\ \hline
-	$\pi$ & $\pi$ & 200 & 0 & 0 & 0.32 & 0.69 & 0.69 & 0 & 0 & 0 & 0.16 & 0 & 0.2 & 0.2 & 1.2 & 3.2 & 0 & 5.4 & 0 \\ \hline
-	0 & $\pi$ & 200 & 1 & 0.087 & 0.36 & 0 & 0 & 0 & 0 & 0 & 0.16 & 0 & 0 & 0 & 3.6 & 3.6 & 0 & 5.4 & 0 \\ \hline
-\multicolumn{16}{c}{}
-\end{tabular}
-}
-\end{table}
-
-\begin{table}
-\caption{Contingency table formula used for each emotion and experience.
-Where $k$ is the kth experience, $j$ is jth emotion for the kth experience, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
-\label{table:table_contingency}
-\small
-\begin{tabular}{|l|l|l|}
-\hline
-Participant & Desire Emotion & Other Emotions \\
-\hline
-$1$ & $Value_{k,j}^{1}$  & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{1})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
-\hline
-$2$ & $Value_{k,j}^{2}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
-\hline
-... & ... & ...\\
-\hline
-$n$ & $Value_{k,j}^{n}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
-\hline
-\multicolumn{3}{c}{}
-\end{tabular}
-\end{table}
+Although this information gives suggest some parameters that could be used to express the emotions studied, this suggestions are limited to the platform used on it.
+Hence, it is still necessary to study the influence that plays the embodiment on the perception of emotions.
+This is going to be beneficial to validate this study but it would also generalize other works done on the same direction.

### 2017-04-23 JournalIJSR/Parts/EmotionModels.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

There are many theories of emotion, differing in assumptions and components involved in the process. They can be classified in different ways. For example~\cite{Scherer2010,marsella_computational_2010} use the following categories:
\begin{itemize}
	\item \textit{Adaptational:} based on the idea that emotions are an evolving system used to detect stimuli that are of vital importance.
	\item \textit{Dimensional:} organize emotions according to different characteristics, usually valence (pleasantness-unpleasantness) and arousal. One of the most widely used is the Russel's circumplex model of affect~\cite{Russell1980}, which assumes that emotions can be mapped in a two dimensional plane. Two axis are used on this plane, one is the arousal (i.e. High and Low) and the other valance (i.e. pleasant and unpleasant). Other authors, such as Russel and Mehrabian~\cite{mehrabian1974approach} have suggested three axis to mapped emotions. These axis are pleasure, arousal and dominance, which is used to give the name to this model PAD. 
	\item \textit{Appraisal:} argues that emotions arise from the individual's judgment, based on its believes, desires, and intentions with respect to the current situation. This is a predominant theory among the others primarily because it gives explicit the link between emotion elicitation and response. 
	\item \textit{Motivational:} studies how motivational drives could generate emotions. Some theories then argued that emotions is a result of an evolutionary needs that should be cover.
	\item \textit{Circuit:} supports the fact that emotions correspond to a specific neuron path in the brain. Model that falls in this theory use the assumption that emotions' differentiation and the number of emotions are genetically coded as neural circuits.
	\item \textit{Discrete:} are theories based on Darwin's work, \textit{the expression of emotion in man and animals}. These theories use as a pillar the idea of the existence of a basic emotions that are international recognized. One of its most world known theorist is Paul Ekman, who has postulate the existence of six basic emotions (anger, fear, joy, sadness, and disgust) that are ''cross-cultural''~\cite{Ekman2004}. Other authors diverge in the amount of basic emotions and the ones that are included. Nevertheless, authors have started to integrated this theory with other theories. For example Izard~\cite{Izard2007} suggests two terms natural kinds and emotion schemas. Natural kinds are the basic emotions, which are emotions that are detected by specific parts of the brain and do not involve any kind of cognition. The emotion schemas involve cognition and may involve complex appraisal process and they would be what people call emotions.
	\item \textit{Other approaches} are lexical, social constructivist, anatomic, rational, and communicative.
\end{itemize}
In practice, these theoretical categories overlap. The difference among these theories is mainly in how the process, inputs and elicitation phases are considered in each one. This overlap goes along with the suggestion done by Izard~\cite{Izard1993}, among others, that emotion elicitation can be performed at different levels, and at some of these levels people are not aware of the process.

### 2017-04-23 JournalIJSR/Parts/Emotion_Projection.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
-Although it is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010}, human studies provide guidelines about possible features and values that could be used to generate emotional motion.
+It is not possible to apply a direct mapping from human studies to robots~\cite{Saerbeck2007,Canamero2010}.
+Nevertheless works done in human studies provide guidelines about possible features and values that could be used to generate emotional motion.
 
@@
 
-Emotion plays an important role in human-human interaction, and can be expressed through diverse channels such as body gestures and poses, body movements, face expressions.
-Given the complex structure of human face, where more than 43 muscles act, face configurations are considered as a primary channel to express emotion.
-As a consequence, many works have focused on facial expression, mainly, but not only, influenced by the work done by Ekman~\cite{Ekman2004}.
-However, the role that body plays in emotion projection was recognized, too, and started to be studied~\cite{Gelder2008,Wallboot1998}.
+Emotion plays an important role in human-human interaction and can be expressed through diverse channels such as body gestures and poses, body movements, face expressions.
+The human face is a complex structure that embraces more than 43 muscles act.
+Hence, the face has been considered as a primary channel to express emotion.
+As a consequence, many works have focused on facial expression, mainly but not only, influenced by the work done by Ekman~\cite{Ekman2004}.
+However, the role that body plays in emotion projection has been recognized and it has been started to be studied~\cite{Gelder2008,Wallboot1998}.
 Nevertheless, the amount of works related to body expression of emotions is still small compared to studies about facial expression.
@@
 Analysing some of the few works that have studied human body expressiveness, it is possible to recognize two different methodologies to create the data base of movements to be assessed during the experiments.
-Applying a first methodology, human actors (either professionals, or amateurs) are asked to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}.
+The first methodology uses human actors (either professionals or amateurs) to walk straight from point A to point B conveying specific emotions~\cite{Dael2012,Meijer1989,Wallboot1998}.
 Each trial is recorded and later shown to each subjects that have to classify all the sequences.
@@
 
-The work done by Wallboot~\cite{Wallboot1998} has been used as a reference by others.
+The work done by Wallboot~\cite{Wallboot1998} has been used as a reference by other researches.
 It addressed the question: \textit{Are specific body postures indicative of emotion or are they only used to indicate the intensity of the emotion?} To answer this question, he recorded 224 videos for joy, happiness, sadness, despair, fear, terror, coldness anger, hot anger, disgust, contempt, shame, guilt, pride, and boredom, and showed them to the subjects.
@@
 
-The main drawback of all these projects is the use of video recorded sequences, which misses the impact related to a complete physical experience.
+There are two main drawbacks of all these projects that use video recorded sequences.
+First, they miss the impact related to a complete physical experience.
 For instance, it is clearly different facing an angry robot really rushing against us, or looking at a video where this happens.
+Second, each actor has his/her own way to represent a given emotion~\cite{Russell2003,Gunes2011}.
+Actors use diverse techniques to create believable representations of specific emotions.
+However, this does not ensure that all actor convey emotions in same way.
+Therefore, several records are done and the ones with the highest agreement are selected.
+This brings the technical question on how to interpret the significance of agreement obtained~\cite{Russell2003}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-
 As a direct consequence of the abundance of works in face elicitation in humans, most of the works done in Human-Robot Interaction (HRI) have focused also on faces.
@@
 Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements.
-To overcome this limitation, some researchers have reduce the human appearance (e.g.
+For example Karg et al.~\cite{Karg2010} tried to map actors gaits on an hexadop robot to understand the contribution of step length, height and velocity.
+Their results suggest that using this approach is not suitable because the difference between different gaits are not recognizable.
+So they suggest that movements must be exagereted.
+Some researchers have reduced the human appearance (e.g.
 eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}.
@@
 For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}.
+They used the self-assessment (SAM)~\cite{Lang2008} method to evaluate participants.
 Their results suggest that arousal increases as speed increases and that there is not any clear tendency for smoothness.
@@
 Alike, Tan and collaborators~\cite{Tan2016} have studied the contribution of velocity, fluidity, direction and orientation of a small box.
+They evaluated participants' perception using SAM.
 Their results suggest that direction is directly correlated with dominance, but that fluidity does not influence the perception.
@@
 Finally the velocity is correlated with valence, arousal and dominance.
+Using an hexapod robot, Karg et al.
+studied
 

### 2017-04-23 JournalIJSR/Parts/ExperimentDesign.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
-The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation can give to the expression of \textit{Happiness}, \textit{Anger}, \textit{Sadness}, and \textit{Fear}, which are four out of the six emotions considered by Ekman~\cite{Ekman2004} as basic emotions, which are characterized to have short duration, cultural universal~\cite{Ekman94}, derive from evolution~\cite{Buck99}, and could influence cognition and action~\cite{Campos2004}.
-Moreover, these four emotions here selected are overlap with emotion schemas~\cite{Izard2007}.
+The experiment was designed to get a better understanding about the contribution given by linear and angular velocity, oscillation angle, direction, and orientation to the expression of \textit{Happiness}, \textit{Anger}, \textit{Sadness}, and \textit{Fear}.
+These four emotions were selected because they are considered as natural kinds and emotion schemas~\cite{Izard2007}.
+Moreover they are derive from evolution~\cite{Buck99} and could influence cognition and action~\cite{Campos2004}, which could be considered in congintive architecures.
+In addition, \textit{Anger} and \textit{Happiness} have been confused in previous studies~\cite{Angel2016}.
+Hence, given a better understanding on how to express these emotions could give researchers a better idea how to avoid misinterpretations that could be critical in a real context.
+
 %%%%%%%%%%%%%%%%%%%
@@
 \hline
-\backslashbox{Variable}{Possibilities} & First & Second & Third & Fourth\\
+\backslashbox{Variable}{Possibilities} & \rotatebox{-90}{First} & \rotatebox{-90}{Second} & \rotatebox{-90}{Third} & \rotatebox{-90}{Fourth}\\
 \hline   
@@
 	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.
+This was decided because from previous works done in robotics, it was reported that body movement is related to arousal.
+As it was already mentioned, some psychologist suggest that diverse theoretical emotions could overlap, so combining discrete and dimensional theories is possible.
 
@@
 
-	\item The robot was shown to the participant and the experiment procedure explained.
+	\item The robot was shown to the participant and it was explained its characteristics and layout. Then the experiment procedure explained. If the participants had any questions, they were answered.
 
-	\item An example of the questionnaire was presented and a sample movement of the robot shown.
+	\item An example of the questionnaire was presented and a sample movement of the robot shown. The participant is remember where the front of the robot is.
 
@@
 
-The order of the options listed in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
+The order of the options listed in the questionnaire changed for each question to prevent any kind of bias.
+Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.
+As it could be observed, the questionnaire allows the participant to introduce more than one emotion.
 

### 2017-04-23 JournalIJSR/Parts/Introduction.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
-Social environments are intricate spaces where people behave in ways that lead to their acceptance in social groups.
+Social environments are intricate spaces where people behave in ways that aim to their acceptance in social groups.
 Similarly, studies in social robotics have shown that robots acceptance increases when robots project a high social presence~\cite{Heerink08}.
@@
 However, a direct mapping between humans and robots is not possible~\cite{Saerbeck2007,Canamero2010} due to robots' physical capabilities.
-In addition, the significance of the agreement obtained from the studies that used human actors is on discussion~\cite{Russell2003}.
-As a consequence determine precise values to project emotions in non-anthropomorphic platforms is required.
+In addition, the significance of the agreement obtained from the studies that used human actors is still on discussion~\cite{Russell2003}.
+As a consequence is required the necessity to determine to project emotions in non-anthropomorphic platforms.
 
@@
 The perceived emotions and their intensities were considered as dependent variables.
-It is to be observed that it was given the possibility to the subjects to provide their evaluation of emotional intensity for more than one emotion for each experience.
+It is to be observed that it was given the possibility to the subjects to provide their evaluation of emotional intensity for more than one emotion for each movement of the robot or treatment.
 The experiment took place in Politecnico di Milano during June and July of 2015, where students from diverse departments were asked to participate without any economical retribution.

### 2017-04-23 JournalIJSR/Parts/Platform.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
 To guarantee that the correct robot's velocity for each motor could be achieved, a PID controller was implemented.
-PID's set point is established by a higher level controller that could receive two different types of commands.
-The first commands are robot's velocities ($<V_x,V_y,\omega>$), given in robot's reference frame.
+PID's sets the velocity  that each motor must maintain when the platform receives a high level command.
+To maintain the velocity, the PID uses the velocity calculated using the odometry.
+Figure~\ref{fig:distribution} the general distribution of all the components, which include kinematics calculation, motors' velocity and platform velocity.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{Images/version-2-program.png} 
+	\caption{General distribution and communication scheme among the diverse software components running on the Arduino.}
+	\label{fig:distribution}
+\end{figure}
+
+Two commands could be received,  the first command specifies robot's velocities ($<V_x,V_y,\omega>$), given in robot's reference frame.
 The second command is a set point ($<x, Y, \theta>$) to be reached, given in the world reference frame.

### 2017-04-23 JournalIJSR/Parts/Results.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

@@
 
-For each table, mean, standard deviation, and median were calculated.
+For each table were calculated mean, standard deviation, and median.
 It was not possible to use ANOVA test over the data because the assumption of normality is not satisfied in the collected data.
@@
 This ranking is generated considering the following items in the respective order:(i) the mean intensity of the respective emotion, (ii) the alpha agreement of contingency table for the respective emotion, and (iii) the alpha agreement for the specific treatment.
-From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:
-
-\begin{itemize}
-
-	\item \textit{Fear} was the only emotion that had six over ten movements obtaining both general and specific alpha agreement over 0.41, which is the lower bound for moderate agreement~\cite{Viera2005}.
-Also, it was mostly selected (eight over ten) when $direction = \pi$ and $orientation = \pi$.
-The angle and the angular velocity attributed six over ten times were $0.087$ and $2$, respectively.
-So it seems that people perceive the movement as a fear expression when the robot is looking at them and moving far from them fast.
-
-	\item \textit{Sadness} was mostly attributed to linear velocities of $0 mm/s$ (two over ten) and $200 mm/s$ (eight over ten), and angular velocities of $0 rad/s$ and $1 rad/s$, with higher predilection of the second (eight over ten).
-It seems that people attribute sadness to slow velocities with slow angular velocity and small oscillation angle.
-Regarding the other two features, there is not any defined pattern that could lead to make a generalization.
-
-	\item \textit{Happiness} is attributed to different values of the independent variables.
-But it is the only emotion that is highly perceived when the linear velocity is $0$ with four over ten.
-However the oscillation angle for these four cases is equally divided between the values $0.174$ and $3.49$.
-%TODO BTW, is this angle in radians?
-It is a quite big difference...
-So it seems that happiness is mainly attributed to fast angular velocities and big oscillations angles. Specific agreement among the other features is not present.
-
-	\item \textit{Anger} is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$.
-It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the persons while approaching them.
-\end{itemize} 
-%alpha general
+Table~\ref{table:happy_top_ten} for Happiness, Table~\ref{table:Angry_top_ten} for Anger, Table~\ref{table:Sad_top_ten} for Sadness, and Table~\ref{table:Scared_top_ten} for Fear.
 

### 2017-06-08 RO-MAN-2017-2/Parts/Implementation.tex
it was added some references that were missing, such as keepon and case studies. Two sentences highlighting the use of the system in real settings were added.

@@
 
-All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and can be parsed by many systems.\\ 
-To test the system, two different platforms were used: Keepon Pro %TODO da citare la prima volta il paper descrittivo
+All the text message broadcast among the nodes are written using JSON format, which is human understandable, light, and can be parsed by many systems.
+
+To test the system, two different platforms were used: Keepon Pro~\cite{Kozima–2009}
 and an own made platform called Triskarino.
@@
 \subsection{Triskarino Test}
-The system has been widely used with Triskarino (Fig.~\ref{fig:robot}) during our studies on projecting emotions with a non human like platform. 
+The system has been widely used with Triskarino (Fig.~\ref{fig:robot}) during our studies on projecting emotions with a non human like platform~\cite{angel2017robots}. 
 \begin{figure}
@@
  During these studies the system was used in different experiments to move the robot on a straight line showing different emotions, each one selected from our command console.
-Moreover, to show the whole capabilities of the emotional enrichment system, a little scene was set up.
+These studies were done in diverse events, such as Researchers' night and Maker Fair.
+Moreover, to show the whole capabilities of the emotional enrichment system and verify if could be used in real time, a little scene was set up.
 The scene is a modification of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.

### 2017-06-10 RO-MAN-2017-1/RO-MAN2017.tex
Create RO-MAN2017.tex
Reviewed, just a small change

@@
 Robots should be able to express emotional states to interact with people as social agents.
-Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice.
+Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language, and voice.
 However, there are cases where robots cannot have any anthropomorphic shape, for example when they have to perform tasks that require a specific structure.
@@
 Therefore, emotional states need to be represented by exploiting non-anthropomorphic features, such as movements and shape changes.
-This paper presents a case study concerning emotion expression in non-anthropomorphic platform and how it is perceived by humans.
+This paper presents a case study concerning emotion expression in a non-anthropomorphic platform and how it is perceived by humans.
 This case study was designed basing on results obtained from a previous experiment, done to assess precise values for linear velocity, angular velocity, oscillation angle, direction, and orientation that could be used to express happiness, anger, fear, and sadness.

### 2017-06-10 RO-MAN-2017-1/Parts/Introduction.tex
Create Introduction.tex
Reviewed. It is strange to have few citations here and I imagine many more later on.

@@
 In many situations, the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities.
-Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
+Most of the current and future robotics platforms on the market will not require any anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}.
 For instance, floor cleaning robots are robots that do not have any anthropomorphic characteristics and still they accomplish their task.
@@
 However,the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}) remains still small in comparison to those exploiting anthropomorphic features.
-Moreover, these works do not provide specific range of values for the characteristics used to express the implemented emotions.
-For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature, but their connection to specific emotions is not described.
+Moreover, these works do not provide any specific range of values for the features used to express the implemented emotions.
+For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and motion path, but their connection to specific emotions is not described.
 Rather, they established a relationship between their values and pleasure/arousal dimensions.
-This could help to select specific features to convey certain emotions, but it would be better to know the precise range of values to be assigned to each characteristic to avoid misinterpretation with wrong emotions.
-These values could be used in social robotics to show emotions and, as consequence, increase their acceptance.
+This could help to select specific features to convey certain emotions, but it would be better to define the precise range of values to be assigned to each feature to avoid misinterpretations.
+These values could be used in social robotics to show emotions and, as consequence, increase the robot's acceptance.
 

### 2017-06-10 RO-MAN-2017-1/Parts/RelatedWork.tex
Revised. The story is still missing, ...
... but I've seen you have included recent references.

@@
 Knight and Simmons~\cite{knight2016} used two platforms (i.e., Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements.
-Although the use of videos has the advantage to cover a major number of participants, they miss the impact created from the physical interaction between the participant and the platform.
+Although the use of videos in evaluation has the advantage to potentially involve a large number of participants, they miss the impact created from the physical interaction between the participant and the platform.
 
@@
 
-The first path is characterized by the use of cue positions to project emotions~\cite{NAO2013}.
-In some cases, special attention has been taken to determine head's angle and arms' position contribution to specific emotion expressions~\cite{Brown2014}.
+The first path is characterized by the use of cue positions to project emotions (e.g.,~\cite{NAO2013}).
+In some cases, special attention has been taken to determine the contribution of head's angle and arms' position to specific emotion expressions~\cite{Brown2014}.
 Nevertheless, current humanoid platforms cannot generate smooth gaits, and this limits the quality of body movements.
@@
 Reducing even more the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}.
-Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the work done by Camurri et al.~\cite{pop00002}.
+Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion perceived from diverse movements, selected from the work by Camurri et al.~\cite{pop00002}.
 Similarly, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours.
 The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB).
-Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.
+Their findings suggest that electronic systems can elicit a type of reaction different from the one expected by theories of interpersonal communication.
 Despite the type of platform used, these works offers an overview of features that could be used to express certain emotions, but they not give precise feature values to implement the emotions.
@@
 A professional Laban certified actor was asked to generate 16 different paths, for each one changing one of the four Laban's parameters (space, weight, time, and flow).
-Each generated path was recorded using the Vicon motion-tracking system ad then replicated on the quadrocopter.
+Each generated path was recorded using a motion-tracking system ad then replicated on the quadrocopter.
 Cauchard and collaborators~\cite{Cauchard2016} studied how flight paths could project personal traits and emotional attributes.
 All these works present a very nice starting point to identify features and values that could be used to project emotions in robotics, which could help in coordinating humans and robots~\cite{Novika2015}.
-However, these works do not give a clear guideline to elicit precise emotions.
-This could lead to implementations that express an undesired emotion~\cite{Angel2016}.
-For example, people could confuse an implementation of \textit{Happiness} with \textit{Anger}.
+However, these works do not give a clear guideline to elicit precise emotions, and do not take into account important features, e.g.
+body shape.
+This could lead to implementations that express emotions that could be misinterpreted.
+For example, people could confuse an implementation of \textit{Happiness} with \textit{Anger}~\cite{Angel2016}.

### 2017-06-10 RO-MAN-2017-1/Parts/CaseStudy.tex
Reviewed. Missing a short description of platform?

@@
 
-The parameters selected to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
-As it could be observed, two configurations for each emotion were selected among the ones evaluated in the previous experiment to be cross-checked.
-These configurations had to satisfy two conditions: (i) the linear velocity should be greater than $0$, so the robot should show some displacement, and (ii) it should be in the top 10 list of the configurations tested in the previous experiment.
+The features selected to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}.
+As it could be observed, two configurations for each emotion were selected among the ones evaluated in the previous pilot, to be cross-checked.
+These configurations had to satisfy two conditions: (i) the linear velocity had to be greater than $0$, so the robot could show some displacement, and (ii) it should be in the top 10 list of the configurations tested in the previous pilot experiment.
 
@@
 Finally the robot turns to profile right and it does a step back; then it goes to the upstage center and then upstage right.
-The sequence of movements of the robot are depicted in Figure~\ref{fig:movement}.
+The sequence of robot's movements are depicted in Figure~\ref{fig:movement}.
 \begin{figure*}
@@
 This case study was done at an exhibition during a period of two days.
-People coming to the stand were asked to volunteer to participate in this study, which was divided in to parts.
+People coming to the stand were asked to volunteer to participate in this study, which was divided in two parts.
 In the first one, each subject was exposed to two emotion expressions.
@@
 The two emotions were generated to guarantee a random uniform presentation.
-In the second part, participants were explained that a small scene was going to be presented twice, and they had to select the one they like more.
-The order of the scenes (e.g., with or without emotion) was generated beforehand.
+In the second part, participants were explained that a small scene was going to be presented twice, and they had to select the one they liked more.
+The order of the scenes (e.g., with or without emotion) was randomly generated.
 The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender.

### 2017-06-10 RO-MAN-2017-1/Parts/Results.tex
Reviewed

@@
 An analysis was done per groups, for each presented emotion.
-For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
+For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when  another one was presented, and how many subjects recognized an emotion different from the considered one when presented a different emotion.
 This leads to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1.
@@
 	\item $H_0 = $ there is a difference in recognition between the implementation with respect to the others.
-	\item $H_1 = $ there is not a difference in recognition between one implementation with respect to the others.
+	\item $H_1 = $ there is not a difference in recognition between the implementation with respect to the others.
 \end{itemize}
@@
 The results are shown in table~\ref{table:Precision2}.
-They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compared with other implementations.
-While both implementations of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.
+They show that there is significant evidence to conclude that Anger-2, and both \textit{Fear} and \textit{Sadness} are considered as different from other implementations, while both implementations of \textit{Happiness} and Anger-1 are considered as similar to other implementations.
 
@@
 
-Nevertheless, it is important to notice that the results were obtained using the lower part of the robot without any change in its shape.
+It is important to notice that the results were obtained using the lower part of the robot without any change in its shape.
 Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate.
 As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level.
-In this precise case, the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}.
-Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).
+In particular, \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}.
+Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the highest recognition rates (54\% for the first and 50\% for the second).
 

### 2017-06-10 RO-MAN-2017-1/Parts/Conclusions.tex
two ro-man articles compiled, ro-man2 still requires more work. let's see what the reviewers say about both articles
Reviewed

@@
 The case study presented in this paper was done to cross validate the findings in a previous experiment~\cite{Angel2017-2}, and to verify whether the subjects would prefer scenes when the robot expresses emotions rather than the same trajectories without any emotion expression.
-For each one of four emotions (i.e., \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}) studied in the experiment two sets of parameters were selected to express them.
+Two sets of parameters were selected from those identified in~\cite{Angel2017-2} to express each of four emotions (i.e., \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}).
 The results show that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}, while one implementation of \textit{Anger} was confused with \textit{Excitement}.
@@
 
-In the scene trials, people showed, without any difference in gender, to prefer scenes with emotional movements.
-
 Additionally to the already mentioned results, it resulted that there are words that could bias participants' perception.
@@
 Moreover, a misinterpretation of \textit{Happiness} and \textit{Anger} could suggest that additional features (e.g., trajectory or shape) should be added to increase differentiation between them.
-For example, Venture and collaborators~\cite{Venture2014} had reported that in human bodies the recognition rate of \textit{Anger} and \textit{Fear} are increased when torso and head are downwards.
+For example, Venture and collaborators~\cite{Venture2014} reported that in human bodies the recognition rate of \textit{Anger} and \textit{Fear} are increased when torso and head are downwards.
 On the other hand, they found that \textit{Happiness} perception is increased when the torso and head are moved upwards.

### 2017-06-11 RO-MAN-2017-2/RO-MAN2017-2.tex
it was added some references that were missing, such as keepon and case studies. Two sentences highlighting the use of the system in real settings were added.
Create RO-MAN2017-2.tex

@@
 \begin{abstract}
-Emotions are considered by many researchers as beneficial elements in social robotics, since they can enrich human-robot interaction with non-verbal clues.
+Emotions are considered by many researchers as beneficial elements in social robotics, since they can enrich human-robot interaction.
 Although there have been works that have studied emotion expression in robots, mechanisms to express emotion are usually highly integrated with the rest of the system.
@@
 Keepon was used to perform simple actions, while Triskarino was used to test complex actions with different parametrizations of emotions.
+The system has been used in different case studies, in which has facilitate emotions descriptions.
 

### 2017-06-11 RO-MAN-2017-2/Parts/Introduction.tex
Reviewed

@@
 The development of fast, cheap, and reliable electronics has enabled the creation of new devices and versatile robotic platforms.
-These new platforms' capabilities have expanded the frontiers of the robots applications to new environments where robot are expected to interact with humans, such as health care, and house cleaning, among others.
-However, bringing robots in these environment raises the challenge to increase robots' acceptance.
-Although this could be seen as an easy task that just would need improvements in robots' appearance and capabilities, it is possible that people would expect to treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil this expectations.
+These new platforms' capabilities have expanded the frontiers of the robotic applications to new environments, where robots are expected to interact with humans, such as health care and house cleaning, among others.
+However, bringing robots in these environments raises the challenge to increase robots' acceptance.
+Although this could be seen as an easy task that just would need improvements in robots' appearance and capabilities, it is possible that people would expect to treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil these expectations.
 
 Some researchers have suggested that embedding emotion expression capabilities in robots could improve their acceptance in social environments~\cite{Pavia2014}.
-To this purpose, some researchers~\cite{Breazeal2002, Arras2012} have added specific emotional poses and expression to their robots.
+To this purpose, some researchers (e.g.,~\cite{Breazeal2002, Arras2012}) have added specific emotional poses and expressions to their robots.
 Others have studied how to convey emotions with specific platforms~\cite{Li2011, Brown2014}.
-Nevertheless, these works have created modules to show emotions that are strongly integrated to their systems, which eliminate the possibility to re-use or adapt them for other projects.
+Nevertheless, these works have created modules to show emotions that are strongly integrated in their systems, which eliminate the possibility to re-use or adapt them for other projects.
 

### 2017-06-11 RO-MAN-2017-2/Parts/RelatedWork.tex
Reviewed

@@
 This platform uses a specific set of movements based on the Ekman's studies on human emotion expression~\cite{Ekman2004}.
-Other approaches have tried to use anthropomorphic~\cite{Arras2012} and human-like platforms to convey emotions to study the response of people towards the robot.
+Other approaches have tried to use anthropomorphic platforms~\cite{Arras2012} to convey emotions to study the response of people towards the robot.
 However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization is not available.
@@
 Although these works have expressed emotions in their studies, they did not focus on creating a framework that could be used by other researchers in HRI.
-Therefore, the use of affective architectures for virtual agents (e.g.
-SAIBA/BML framework~\cite{Kopp2006}) could be though as a feasible solution.
+The use of affective architectures for virtual agents (e.g., SAIBA/BML framework~\cite{Kopp2006}) could be thought as a feasible solution.
 However, these frameworks describe high level actions without giving relevant details to its implementation in physical platforms.

### 2017-06-11 RO-MAN-2017-2/RO-MAN2017-2.tex
Revised

@@
 This tree is created from the action message description and then modified using the emotional parameters and character description.
-The remaining two concepts are explained below.
+The remaining two concepts rquire amore detailed description, reported below.
 
@@
 These parameters could include a sequence of descriptors.
-For example, these descriptors could be used to generate changes of velocity over time or position to express an emotion.
+For example, these descriptors could be used to generate changes of velocity or position over time to express an emotion.
 However, there is going to be a diverse set of parameters and descriptors depending on the nature of the action.
@@
 The human action of speaking is related to changes in the vocal cords to produce different sounds, while \textit{move body} is directly related to the body movement.
-The speaking action would have the following parameters: text, pitch and tone.
+The speaking action would have the following parameters: text, pitch, and tone.
 On the other hand, the action \textit{move body} would have as parameters the desired destination, velocity, and trajectory constraints.
-However, in order to express emotion in speak action, it is required to modify pitch variables (i.e.
-fundamental frequency level, contour and jitter), intensity and speech rate~\cite{Gunes2011}.
+However, in order to express emotion in speak action, it is required to modify pitch variables (i.e., fundamental frequency level, contour and jitter), intensity and speech rate~\cite{Gunes2011}.
 On the other hand, changing linear velocity and adding oscillation could be used to convey emotion in the move body action~\cite{Angel2016c}.
-Since each action requires modification on diverse parameters, a variety of emotional parameters would be necessary to describe the modification of all type of actions.
+Since each action requires modification of diverse parameters, a variety of emotional parameters would be necessary to describe the modification of all types of actions.
 So, it was decided to focus on the parameters that could be used to express emotions with the robots we have considered: Triskarino and Keepon.

### 2017-06-11 RO-MAN-2017-2/Parts/SimpleActions.tex
Reviewed

@@
 In order to generate a system that could be used in diverse platforms, an abstraction level in which all of them could fall is required.
-Therefore simple and compound actions are used to achieve this goal.
+Simple and compound actions are used to achieve this goal.
 Simple actions are actions that are considered as primitives: they are used as building blocks.
@@
 They can be described in the action messages without being implemented.
-In case that a compound action is used often, it could be implemented in the system.
-The implementation describes action's parameters, other compound actions, simple actions and mapping between actions and parameters.
+If a compound action is used often, it could be implemented in the system.
+The implementation describes action's parameters, other compound actions, simple actions, and mapping between actions and parameters.
 
@@
 This sequence of movements corresponds to an adaptation of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
-The fist part of this scene is characterized by strong changes in Romeo's emotional state, thus it was selected as significant test for the system.
+The fist part of this scene is characterized by strong changes in Romeo's emotional state, thus it was selected as a significant test for the system.
 \begin{figure}
@@
 	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseSceneB.png}
-	\caption{Sketch of Romeo's movements for the balcony scene in Romeo and Juliet play. The arrows show the direction of the movements, and the numbers their sequence.}
+	\caption{Sketch of Romeo's movements for the balcony scene in Romeo and Juliet play. The arrows show the direction of the movements, and the numbers their position in the sequence.}
 	\label{fig:triskar_test}
@@
 The first node corresponds to the first action in Figure~\ref{fig:triskar_test}.
-The second actions corresponds to a compound action created by the parallel execution of the simple action \textit{move body} and other compound actions.
+The second node corresponds to a compound action created by the parallel execution of the simple action \textit{move body} and other compound actions.
 

### 2017-06-11 RO-MAN-2017-2/Parts/EmotionalTree.tex
Reviewed

@@
 In our case, we consider that two actions are different if $(\forall sa_{i}, sa_{j} \in SA, \forall q, t \in PL | Param( sa_{i}^q ) \neq Param( sa_{j}^t )\Rightarrow sa_{i}^q \neq sa_{j}^t)$, 
-where $PL$ is the set of all the possible platforms, $Param(\cdot)$ returns the set of parameters that are input of the $sa$ (e.g., $vel$,$pitch$,$text$). 
-On the other hand, we will consider two actions as equivalents if $(\forall sa_{i}, sa_{j} \in SA , \forall q, t \in PL | Param( sa_{i}^q ) = Param(sa_{j}^t ) \wedge Obj(sa_{i}^q) = Obj(sa_{j}^t) \Rightarrow sa_{i}^q \equiv sa_{j}^t)$,
+where $PL$ is the set of all the possible platforms, $Param(\cdot)$ returns the set of parameters that are input of the $sa$ (e.g., $vel$, $pitch$, $text$). 
+On the other hand, we will consider two actions as equivalent if $(\forall sa_{i}, sa_{j} \in SA , \forall q, t \in PL | Param( sa_{i}^q ) = Param(sa_{j}^t ) \wedge Obj(sa_{i}^q) = Obj(sa_{j}^t) \Rightarrow sa_{i}^q \equiv sa_{j}^t)$,
 where $Obj(\cdot)$ returns the set of objectives that are intended to be achieved by a given action.
@@
 
-With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$, but with the parameters modified in order to convey the desired emotion $e$, or even a set of $sa$ with modified parameters.
+With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$, but with modified parameters in order to express the desired emotion $e$, or even a set of $sa$ with modified parameters.
 This definition goes along with the idea that new $sa$ could be added to convey a specific emotion.

### 2017-06-11 RO-MAN-2017-2/Parts/description.tex
Reviewed

@@
-The description files allow the parametrization and extent the system to fit other applications is required.
-To standarize the mechanisms to describe these files, it was decided to create a language to describe them.
+Description files allow the parametrization and extention of the system to fit other applications.
+A language was created to define the content of these files.
 This allows other researchers to create their own files and to extend the language to fit their needs.
-It was decided to use the Extended Backus-Naur Form (EBNF) to describe this language.
+The Extended Backus-Naur Form (EBNF) that describes this language is reported below.
 \subsection{Emotion Description} 

### 2017-06-11 RO-MAN-2017-2/Parts/Implementation.tex
Reviewed

@@
 	\end{figure}
-	\item \textit{Execution:} this is the last phase and it is done after the EXT is ''coloured'' with emotional characteristics (actions additions and emotional parameters).
+	\item \textit{Execution:} this is the last phase and it is done after the EXT is ''coloured'' with emotional features (actions additions and emotional parameters).
 The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution.
@@
 \subsection{Keepon Test}
-To test the system with Keepon (Fig.~\ref{fig:keepon}) was just necessary to implement the platform's controllers in each one of the simple action ROS nodes.
-Given that this platform does not have the capability to displace its body, the action move body was not implemented.
+To test the system with Keepon (Fig.~\ref{fig:keepon}), it was just necessary to implement the platform's controllers in each one of the simple action ROS nodes.
+Given that this platform does not have the capability to displace its body, the action ``move body'' was not implemented.
 Once added these controllers to the system, we proceeded to modify the configuration files to use this platform instead of Triskarino.
@@
 The action is given by console telling the robot to bend the torso to a desired angle in x.
-The torso oscillation in y is added automatically by the system following the description given to happiness.
+The torso oscillation in y is added automatically by the system following the description defining how to express happiness.
  %%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}  
- During these studies the system was used in different experiments to move the robot on a straight line showing different emotions, each one selected from our command console.
-These studies were done in diverse events, such as Researchers' night and Maker Fair.
-Moreover, to show the whole capabilities of the emotional enrichment system and verify if could be used in real time, a little scene was set up.
+ In these studies, the system was used in different experiments to move the robot on a straight line showing different emotions, each one selected from our command console.
+Moreover, to show the whole capabilities of the emotional enrichment system and verify if it could be used in real time, a little scene was set up.
 The scene is a modification of the first part of the balcony scene of Shakespeare's Romeo and Juliet play~\cite{RAndJ}.
-The simplified sketch of our version could be seen in the Fig.~\ref{fig:triskar_test}.
-As it can be seen the stage was divided in 81 squares and the positions were given to the system in terms of the desire square to be reached, which allows the robot to adjust to the stage's dimension.
+The simplified sketch of our version could be seen in Figure~\ref{fig:triskar_test}.
+As it can be seen the stage was divided in 81 squares and the positions were given to the system in terms of the desired square to be reached, which allows the robot to adjust to the stage's dimension.
 The whole sequence of actions were specified as unique action, having several sequential nodes and just move body action.
